### 2013-04-15 PAPER/paper.tex
- First commit

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

%------------------------------------------------------------------------------

\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{cite}
\usepackage{balance}
\usepackage{float}
\usepackage{threeparttable}

\usepackage{mathptmx}
\usepackage[scaled=.90]{helvet}
\usepackage{courier}

\usepackage{listings}
\usepackage{listings}
\lstset{
   language=C,
   basicstyle=\small,
   keywordstyle=\bfseries,
   identifierstyle=\ttfamily,
   stringstyle=\ttfamily,
   numbers=left,
   numberstyle=\tiny,
   stepnumber=1,
   numbersep=-5pt,
   showstringspaces=false
%   frame=single %trbl%
}

\usepackage[normalem]{ulem}

%------------------------------------------------------------------------------

\newcommand{\etal}{\emph{et al.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etc}{\emph{etc.}}

%------------------------------------------------------------------------------

\begin{document}

%------------------------------------------------------------------------------

\title{A distribuited segment-based routing for bla bla...}

\author{\IEEEauthorblockN{Maurizio Palesi} \IEEEauthorblockA{Affiliation1\\ email1} \and
  \IEEEauthorblockN{Davide Patti} \IEEEauthorblockA{Affiliation2\\ email2} \and
  \IEEEauthorblockN{Christof Teuscher} \IEEEauthorblockA{Affiliation3\\ email3}}

\maketitle

%------------------------------------------------------------------------------

\begin{abstract}
  ...
\end{abstract}

%------------------------------------------------------------------------------

\IEEEkeywords{...}

%------------------------------------------------------------------------------

\section{Introduction}
% intro to the potential of Self-assembled nano architectures
% irregular topology -> how to route ?

%------------------------------------------------------------------------------

\section{Related Work}
% - Up/Down etc..
% - SR is ok (topology independent) but requires the knowledge of the
% topology graph -> impossible in DNA self assembly
% - Our contribution: a distribuited approach for a segment-based
%   routing. Not the "optimal" SR, just a SR "that works" in such
%   complex irregular topologies where a graph could never be
%   available.
...

%------------------------------------------------------------------------------

\section{Proposal}
% - Draft of the DiSR idea
% - how it should work
...
%------------------------------------------------------------------------------

\section{DiSR execution model}
% - what is executed at each node, which information is required
...

%------------------------------------------------------------------------------

\section{Nanoxim and simulation environment}
% - Architecture of the nanoxim simulator
% - how simulations were conducted
...

%------------------------------------------------------------------------------

\section{Experiments}
% - Graphs, tables
% - comparison against other approaches
...

%------------------------------------------------------------------------------

\section{Conclusions}
...

%------------------------------------------------------------------------------

\balance

\bibliographystyle{IEEEtran} 
\bibliography{bibliography}

%------------------------------------------------------------------------------

\end{document}

### 2013-04-15 trunk/PAPER/paper.tex
- Introduction draft

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

%------------------------------------------------------------------------------

\usepackage{cite}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{cite}
\usepackage{balance}
\usepackage{float}
\usepackage{threeparttable}

\usepackage{mathptmx}
\usepackage[scaled=.90]{helvet}
\usepackage{courier}

\usepackage{listings}
\usepackage{listings}
\lstset{
   language=C,
   basicstyle=\small,
   keywordstyle=\bfseries,
   identifierstyle=\ttfamily,
   stringstyle=\ttfamily,
   numbers=left,
   numberstyle=\tiny,
   stepnumber=1,
   numbersep=-5pt,
   showstringspaces=false
%   frame=single %trbl%
}

\usepackage[normalem]{ulem}

%------------------------------------------------------------------------------

\newcommand{\etal}{\emph{et al.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\etc}{\emph{etc.}}

%------------------------------------------------------------------------------

\begin{document}

%------------------------------------------------------------------------------

\title{A Distribuited Segment-based Approach for Topology-agnostic Nano Networks Routing}

\author{
  \IEEEauthorblockN{Vincenzo Catania} \IEEEauthorblockA{Affiliation3\\ email3}} \and
  \IEEEauthorblockN{Davide Patti} \IEEEauthorblockA{Affiliation2\\ email2}

\maketitle

%------------------------------------------------------------------------------

\begin{abstract}
In this paper we present a first effort for a distributed
segment-based approach to routing which exploits the already-proven
qualities of segment-based routing without requiring as graph
topology as input, and also without requiring a centralized setup
phase.
\end{abstract}

%------------------------------------------------------------------------------

\IEEEkeywords{...}

%------------------------------------------------------------------------------

\section{Introduction}
Exploring long term alternatives to the CMOS technology is gaining
more and more revelance as the scaling trend of such devices continue
to introduce new challenges. Power density, defect tolerance, testing
costs and many other issues are only partially mitigated by multicore
approaches~\ref{TODO}, but growing computing requirements will eventually need
even more radical architectural modifications and new paradigms in
future computer design.

DNA-self assembled nanoscale architectures~\ref{TOOD} are emerging as promising
technology due its tera/peta scale of integration, defect tolerance
tolerance and potential computing capabilities~\ref{TODO}. This
technologies is certainly still at its early stage of development,
however different laboratory demos and prof-of-concepts architectures
have been presented~\ref{TODO}.

The main idea beyond this approach is to exploit the regularity and
stabiliy of DNA sequences in orders to create grids onto which
nano-devices (e.g. nanowires and CNFET~\ref{TODO}) can be attached by
designing approapriate DNA tags. A detailed description of the
chemical properties involved is beyond the scope of this paper, since
we focus of the main challenges that this new fabrication process
introduces in Computer Design. These are:
\begin{itemize}
\item small scale control of placement and connectivity
\item large scal randomness
\item high defect rates
\end{itemize}

This aspects of a DNA-self assembled process leads some architectural implications
when approaching to the Computer Design. Architecture must consist of
a distributed network of small computing and storage nodes, randomly
connected. Data will be travelling on packets that must be routed
using a topology-agnostic strategy, since no particular regularity can
be assumed in such network.

In this paper we present a first effort for a distributed
segment-based approach to routing which exploits the already-proven
qualities of segment-based routing without requiring as graph
topology as input, and also without requiring a centralized algorithm
which perform a \"segment setup\" phase.

% irregular topology -> how to route ?

%------------------------------------------------------------------------------

\section{Related Work}
% - Up/Down etc..
% - SR is ok (topology independent) but requires the knowledge of the
% topology graph -> impossible in DNA self assembly
% - Our contribution: a distribuited approach for a segment-based
%   routing. Not the "optimal" SR, just a SR "that works" in such
%   complex irregular topologies where a graph could never be
%   available.
...
Different architectures using nano-scale devices have been presented.A
general purpose architecture for Self-Assembled Nano-Electronics has
been presented to demostrate the potential of
DNA-selfassembly~\ref{TODO}

%------------------------------------------------------------------------------

\section{Proposal}
% - Draft of the DiSR idea
% - how it should work
...
%------------------------------------------------------------------------------

\section{DiSR execution model}
% - what is executed at each node, which information is required
...

%------------------------------------------------------------------------------

\section{Nanoxim and simulation environment}
% - Architecture of the nanoxim simulator
% - how simulations were conducted
...

%------------------------------------------------------------------------------

\section{Experiments}
% - Graphs, tables
% - comparison against other approaches
...

%------------------------------------------------------------------------------

\section{Conclusions}
...

%------------------------------------------------------------------------------

\balance

\bibliographystyle{IEEEtran} 
\bibliography{bibliography}

%------------------------------------------------------------------------------

\end{document}

### 2013-04-15 PAPER/paper.tex
Trash-like transfer from DiSR gdoc

@@
 
-\title{A distribuited segment-based routing for bla bla...}
+\title{A Distribuited Segment-based Approach for Topology-agnostic Nano Networks Routing}
 
-\author{\IEEEauthorblockN{Maurizio Palesi} \IEEEauthorblockA{Affiliation1\\ email1} \and
-  \IEEEauthorblockN{Davide Patti} \IEEEauthorblockA{Affiliation2\\ email2} \and
-  \IEEEauthorblockN{Christof Teuscher} \IEEEauthorblockA{Affiliation3\\ email3}}
+\author{
+  \IEEEauthorblockN{Vincenzo Catania} \IEEEauthorblockA{Affiliation3\\ email3}} \and
+  \IEEEauthorblockN{Davide Patti} \IEEEauthorblockA{Affiliation2\\ email2}
 
@@
 \begin{abstract}
-  ...
+In this paper we present a first effort for a distributed
+segment-based approach to routing which exploits the already-proven
+qualities of segment-based routing without requiring as graph
+topology as input, and also without requiring a centralized setup
+phase.
 \end{abstract}
@@
 \section{Introduction}
-% intro to the potential of Self-assembled nano architectures
+Exploring long term alternatives to the CMOS technology is gaining
+more and more revelance as the scaling trend of such devices continue
+to introduce new challenges. Power density, defect tolerance, testing
+costs and many other issues are only partially mitigated by multicore
+approaches~\ref{TODO}, but growing computing requirements will eventually need
+even more radical architectural modifications and new paradigms in
+future computer design.
+
+DNA-self assembled nanoscale architectures~\ref{TOOD} are emerging as promising
+technology due its tera/peta scale of integration, defect tolerance
+tolerance and potential computing capabilities~\ref{TODO}. This
+technologies is certainly still at its early stage of development,
+however different laboratory demos and prof-of-concepts architectures
+have been presented~\ref{TODO}.
+
+The main idea beyond this approach is to exploit the regularity and
+stabiliy of DNA sequences in orders to create grids onto which
+nano-devices (e.g. nanowires and CNFET~\ref{TODO}) can be attached by
+designing approapriate DNA tags. A detailed description of the
+chemical properties involved is beyond the scope of this paper, since
+we focus of the main challenges that this new fabrication process
+introduces in Computer Design. These are:
+\begin{itemize}
+\item small scale control of placement and connectivity
+\item large scal randomness
+\item high defect rates
+\end{itemize}
+
+This aspects of a DNA-self assembled process leads some architectural implications
+when approaching to the Computer Design. Architecture must consist of
+a distributed network of small computing and storage nodes, randomly
+connected. Data will be travelling on packets that must be routed
+using a topology-agnostic strategy, since no particular regularity can
+be assumed in such network.
+
+In this paper we present a first effort for a distributed
+segment-based approach to routing which exploits the already-proven
+qualities of segment-based routing without requiring as graph
+topology as input, and also without requiring a centralized algorithm
+which perform a \"segment setup\" phase.
+
 % irregular topology -> how to route ?
@@
 ...
+Different architectures using nano-scale devices have been presented.A
+general purpose architecture for Self-Assembled Nano-Electronics has
+been presented to demostrate the potential of
+DNA-selfassembly~\ref{TODO}
 
@@
 
-\section{DiSR execution model}
-% - what is executed at each node, which information is required
-...
+\section{Detailed DiSR model}
+We distinct among two different kind of data stored at each node:
+local environment data (LED) and dynamic behaviour status (DBS).
 
+\subsection{Local Environment Data (LED)}
+
+The LED is like a snapshot of the DiSR algorithm on each node,
+consisting in the following variables:
+
+segID:a value used to specify a segment id for the node. Depending on
+the values of visited/tvisited variables below, the node can be
+assigned to or candidate for a specific segment id.
+
+visited : a boolean value corresponding to the visited status. If visited is true
+and segID is different from NULL, then segID specifies the segment id
+the node belongs to. Note that a value different from NULL does not
+necessarily mean the node has been assigned to some segment (e.g. when
+searching starting segment is set visited by default even if not yet
+assigned to any segment). When false, the node is not yet visited.
+
+tvisited: a boolean value corresponding to the tvisited status. If
+true, the node is being considered as candidate for a segment, and the
+segID specifies the segment id for which the node it's candidate. When
+false, the node is not currently tvisited.
+
+link_visited[]: an array
+of values representing information about attached links, that is, the
+ID of the segment owning each link. When NULL, a link has not yet been
+marked as visited. TDB: do we need to introduce some value for the
+“bridge” status ? (e.g. a node connecting the terminal node of a
+subnet with the starting one of another)
+
+link_tvisited[]: an array of
+values representing information about attached links, e.g. the ID of
+the segment for which the link is candidate. When NULL, the link is
+currently not tvisited.  starting: boolean, true if the node it's a
+starting node for the subnet terminal:boolean, true if the node it's a
+terminal node for the subnet.  subnet:the subnet the node belongs to.
+If NULL, none.
+
+\subsection{Dynamic Behaviour Status (DBS)}
+In addition to the LED variables
+described above, further information should be stored in order to
+capture the current dynamic behaviour of the node. This is represented
+by the dynamic behaviour status (DBS) variable, which strictly depends
+on the LED data and the events occurring at the node. The DBS can have
+the following values:
+
+FREE: a node that has  not been yet considered  by the DiSR algorithm.
+The node is not marked as visited/tvisited/terminal/starting.
+
+BOOTSTRAP: a node which has been explicitly set as bootstrap node from
+an upper layer via. This is required because a
+
+STARTING_SEGMENT_REQUEST packet should be injected in order to start
+the whole process.
+
+ACTIVE_SEARCHING: a node from which a find process of new segments has
+been started and not yet cancelled or confirmed. This happens when all
+the following conditions are matched: the node is marked as visited,
+that is visited = TRUE
+
+CHECK: segID is set to some value reflecting
+the segment request sent there is a link that is being investigated by
+the node, that is a tvisited_link marked with the same id of the node
+
+CANDIDATE: a node currently candidate for belonging to some segment
+with id segid, not being itself the node from which the find process
+was started. The following conditions should be matched: tvisited =
+true, with segID=X different from node's id.  Two links set as
+link_tvisited with id X. Let’s refer them as  links 'i' and 'j'. Then
+link_tvisited[i] was set = X when the find process from an adjacent
+node reached the current node, while link_tvisited[j] has been set to
+X when the node itself started to investigate its free links for the
+segment request with id X. Note that while investigating its attached
+links, if the find process fails along path 'j', the current node can
+investigate another free node 'k' if suitable.
+
+CANDIDATE_STARTING:
+same as above, but the node is currently being considered as candidate
+for starting segment. Two main differences: Can confirm
+STARTING_SEGMENT_CONFIRM with the same segID when receiving a normal
+SEGMENT_REQUEST: Overwrites its status setting it to CANDIDATE for the
+segID frees the links previously set as tvisited during flooding
+
+ASSIGNED: a node for which the segment has been determined.  The
+segment segID attribute value is set to some id X different from NULL.
+The visited value is true NOTE: an ASSIGNED state is a quick temporary
+state, since it becomes ACTIVE_SEARCHING if a not (visited/tvisited)
+link is suitable for searching new segments (see next_visited
+procedure on paper)
+
+PROCESSED: a node which should take no other
+action, since all its links have been investigated.
+
+\subsection{Packets types Required}
+TODO: a lot of description is already present elsewhere, make this
+section smaller...
+
+SEGMENT_REQUEST: used to search candidates for a segment (not the
+first of the subnet, managed separately as a starting segment).
+
+SEGMENT_CONFIRM: used to create a segment. When received, if the node
+status is tvisited with a segID corresponding to the one indicated in
+the packet, the node learns to belong to the segment associated to the
+id. Further, it should forward this packet to the link where the
+original SEGMENT_REQUEST packet came from, so that all candidate nodes
+can learn the segment id they belong to. The following LED shoud be
+updated: The state of the node changes from tvisited to visited.  the
+link_tvisited previously set with the segID should be invalidated the
+link_visited variable associated to the incoming confirm should be set
+as segID. Note that if the request was flooded across different links,
+the link_visited variable associated to the other paths shouldn’t be
+set.  the link_visited variable associated to the link from which the
+request was originated should be set segID
+
+STARTING_SEGMENT_REQUEST: the request for the first segment of a
+subnet should be differentiated since all nodes (except the starting
+one) must forward the packet using a flooding mechanism. This is
+necessary since the request packet must reach the starting node, which
+is the only node marked as visited. As stated elsewhere, it should
+remembered that the first segment of each subnet it's  a loop that
+beginning/ending on the starting node.
+
+SEGMENT_CANCEL: used when the process of searching a segment along a
+certain path fails. When a node discovers that the path that includes
+the node itself is no more suitable, a SEGMENT_CANCEL is sent back
+across the link from which the SEGMENT_REQUEST was received.  Possible
+reasons for that: The node it’s already candidate for another segment
+The node it’s free but can’t find a free link (according the
+cyclelinks timeout) The node it’s tvisited for the same request id,
+previously forwarded that request along some free direction, but now
+it’s receiving a a cancel request and has no more free links
+
+\section{DiSR Execution Phases}
+
+\subsection{Creating the starting segment}
+
+Injecting request: all nodes have status FREE, except for a
+“bootstrap node” with status BOOTSTRAP, set by some signal from an
+upper layer via. This bootstrap node sets itself as “visited” and
+changes its status to ACTIVE_SEARCHING, sending a
+STARTING_SEGMENT_REQUEST across one of its not (visited/tvisited)
+links and.
+
+Flooding: Each node receiving a STARTING_SEGMENT_REQUEST,
+if not (visited/tvisited),  forwards  to the attached links that are
+not already marked as visited/tvisited using a flooding mechanism.
+Each of these links is then marked as tvisited with the segment id
+associated to the packet. Note that a node that has already received a
+STARTING_SEGMENT_REQUEST packet can simply ignore further packets
+associated to the same request, since has already contributed to the
+flooding. Note also that each of these packets has a max_segment_hops
+field to prevent packets from travelling undefinitively.
+
+setup of the starting-segment: when this STARTING_SEGMENT_REQUEST packet reaches
+the starting node (from a different link, of course), the starting
+segment is found. Then the starting node sends back a SEGMENT_CONFIRM
+packet with the same id along the link from which it received the
+STARTING_SEGMENT_REQUEST. Each node do same by changing its own status
+from tvisited to visited. So the confirmation packet is sent back from
+node to node and the starting segment is created.
+
+Note: A node knows to be tvisited due a  STARTING_SEGMENT_REQUEST.
+Then, when receiving a SEGMENT_REQUEST for other (not the starting)
+segment, simply knows to cancel the tvisited status of the node and
+its links, since if a segment arrived it means that a starting segment
+has already been found a there’s no need to keep the tvisited status
+for those broadcast status. What happens to nodes not receiving these
+segment request? they simply remain tvisited and after a timeout reset
+their state as free. But they could also remain tvisited for the
+starting segment, since this doesn’t affect their behaviour for future
+segment requests.
+
+failure: [TODO] should we handle this case ? i.e.
+marking as terminal ?
+
+\subsection{Finding other segments}
+
+Injecting request: A node in the ASSIGNED state can initiate a search for a
+segment, by sending a SEGMENT_REQUEST with an across one of its free
+links. Note that, since this is not the starting segment, in this case
+the packet should not reach the initiator, but just another visited
+node
+
+setup of the segment: The find process is successfull when a visited
+node receives the SEGMENT_REQUEST packet. Then, a SEGMENT_CONFIRM is
+sent back along the path that originated the request.  Failing while
+searching a segment: a node received a SEGMENT_REQUEST packet but
+matched one of the following conditions: the node is free but has no
+more suitable free links (can’t forward the SEGMENT_REQUEST) the node
+is tvisited candidate for another find process the request packet
+exceeded the max_segment_hops limit.  In all these cases the node
+sends back a SEGMENT_CANCEL along the proper link modifying its state
+to free. Each of the subsequent nodes will forward this SEGMENT_CANCEL
+only if no more free links can be explored starting from them.
+
+\subsection{Intra-node vs Inter-node parallelism}
+In the processes described above, we assumed that each node in the
+READY_SEARCHING state can start a find segment process by injecting a
+SEGMENT_REQUEST. However, a more accurate decision when defining DiSR
+should be made in order to decide whether or not the node must
+actually perform this action. 
+The point above is is strictly related to the general question: which
+level of “parallelism” should we allow in DiSR ? The adopted approach
+is that, although the nature of DiSR itself is intrinsicly parallel,
+the use of parallelism makes things work in a more complex way. In
+other words, DiSR is parallel when needed, but it does not exploit
+parallelism as an “improving feature”. When not needed, things should
+be serialized. For example: when a node is “ready searching” could
+start several find segment process associated to the same segment, one
+for each free link. But serializing this by investigating the free
+links in order could be a simplest solution. We refer to this saying
+that we avoid intra-node parallelism.  Note that while intra-node
+parallelism can be avoided, trying to avoid inter-node parallelism
+could be more complex than allowing the parallelism itself. Imagine
+for example the effort of trying to coordinate nodes so that an unique
+finding node process is actually running in the whole subnet. Thus, in
+contrast to the intra-node parallelism, the inter-node parallelism is
+a structural property of the DiSR algorithm and should not be avoided.
 %------------------------------------------------------------------------------
+
+\section{Node behaviour Model}
+Assumption: when discussing of
+visited/tvisited nodes, we are assuming with an id corresponding to
+the same subnet. Nodes involved in other subnet processes can simply
+ignore these packets. (TBD: formalize more clearly in which cases
+inter-subnet packets must be ignored, probably this happens most of
+the times, but in some cases, e.g. when a terminal node is found, some
+kind of communication packets are needed in order to crearte the
+bridge between two subnets.)
+
+\subsection{Receiving a STARTING_SEGMENT_REQUEST}
+
+When a node receives a STARTING_SEGMENT_REQUEST, with id = X,  there are the following cases:
+
+The node is visited with the same segID = x, that is it was the
+initiator of the request (set visited by definition): a first segment
+was found and should be confirmed sending back a SEGMENT_CONFIRM
+packet.
+
+The node is tvisited, with the same segID of the packet: due
+the flooding mechanism, another starting segment packet reached a node
+which was previously marked as tvisited from the same starting segment
+search process. Since the node is tvisited with the same id, it means
+that it already accomplished in the task of propagating that kind
+packets, thus can simply ignore the event thrashing the packet.  If
+the node it's not visited/tvisited: it should set itself as tvisited
+and forward the packet along its free links, using flooding. TBD: how
+the status should be changed ? depend on the flooding mechanism. Note
+that these links don’t include the link from which the request was
+received.
+
+The node it's visited, with different id in the packet.
+CHECK:  it is not the initiator of the starting segment request, but
+is already assigned to some segment!? assuming again we are discussing
+of nodes belonging to the same subnet, this should NOT happen, since
+the only visited node of the subnet should be the initial node from
+which the STARTING_SEGMENT_REQUEST originated. Note again that we are
+assuming that if the the node is visited or tvisited with the id of
+another subnet can simply ignore the request.  The node it's tvisited
+but it's not the initiator of the request (different id): same as
+above, if we are assuming nodes of the same subnet, this shouldn’t
+happen. If the node is of another subnet, can simply ignore the event.
+
+\subsection{Receiving a SEGMENT_REQUEST}
+When a node receives a SEGMENT_REQUEST, the are the following cases:
+
+The node is visited (and belongs to the same subnet): a segment was
+found and it should be confirmed sending back a SEGMENT_CONFIRM
+packet.
+
+The node is tvisited: it should discard the packet sending
+back a SEGMENT_CANCEL
+
+The node it's not visited/tvisited and has free
+links: it marks itself as tvisited and forwards the SEGMENT_REQUEST
+(one request at time) to each of its free links, according to some
+ordering
+
+CHECK: the difference between confirming a STARTING_SEGMENT_REQUEST
+and confirming a SEGMENT_REQUEST is that in the first case the node
+itself it's included in the segment , while in the second case the
+receiving node DOES NOT belong to the segment found. The motivation is
+that in the second case the node was already marked as visited because
+of being assigned to some segment found before, while in the
+starting-segment case, by definition, the first segment of a subnet
+begins with the starting node, which is marked as visited by the SR
+algorithm when searching for the first (starting) segment. Remember
+that the first segment of a subnet is a loop beginning with the
+starting node.
+
+\subsection{Receiving a SEGMENT_CANCEL}
+When a node receives a SEGMENT_CANCEL packet it means that searching
+for a segment along that path was unsuccessful. But if the node still
+has other free links to try, it should forward a SEGMENT_REQUEST to
+the next link (next according to some internal ordering). So a node
+forwards back the SEGMENT_CANCEL packet along the link that originated
+the SEGMENT_REQUEST packet ONLY when there are no more free links to
+try. If this is the case, the node modifies its status from tvisited
+to free and fordwards the SEGMENT_CANCEL packet to the link from which
+the request was received. The process stops when the SEGMENT_CANCEL
+packet reach the starting node that originated the request.
 

### 2013-04-15 PAPER/paper.tex
Fixed underscores

@@
 \author{
-  \IEEEauthorblockN{Vincenzo Catania} \IEEEauthorblockA{Affiliation3\\ email3}} \and
-  \IEEEauthorblockN{Davide Patti} \IEEEauthorblockA{Affiliation2\\ email2}
+  \IEEEauthorblockN{a} \IEEEauthorblockA{Affiliation3\\ email3} \and
+  \IEEEauthorblockN{b} \IEEEauthorblockA{Affiliation2\\ email2} }
 
@@
 
-link_visited[]: an array
+link\_visited[]: an array
 of values representing information about attached links, that is, the
@@
 
-link_tvisited[]: an array of
+link\_tvisited[]: an array of
 values representing information about attached links, e.g. the ID of
@@
 
-STARTING_SEGMENT_REQUEST packet should be injected in order to start
+STARTING\_SEGMENT\_REQUEST packet should be injected in order to start
 the whole process.
 
-ACTIVE_SEARCHING: a node from which a find process of new segments has
+ACTIVE\_SEARCHING: a node from which a find process of new segments has
 been started and not yet cancelled or confirmed. This happens when all
@@
 the segment request sent there is a link that is being investigated by
-the node, that is a tvisited_link marked with the same id of the node
+the node, that is a tvisited\_link marked with the same id of the node
 
@@
 true, with segID=X different from node's id.  Two links set as
-link_tvisited with id X. Let’s refer them as  links 'i' and 'j'. Then
-link_tvisited[i] was set = X when the find process from an adjacent
-node reached the current node, while link_tvisited[j] has been set to
+link\_tvisited with id X. Let’s refer them as  links 'i' and 'j'. Then
+link\_tvisited[i] was set = X when the find process from an adjacent
+node reached the current node, while link\_tvisited[j] has been set to
 X when the node itself started to investigate its free links for the
@@
 
-CANDIDATE_STARTING:
+CANDIDATE\_STARTING:
 same as above, but the node is currently being considered as candidate
 for starting segment. Two main differences: Can confirm
-STARTING_SEGMENT_CONFIRM with the same segID when receiving a normal
-SEGMENT_REQUEST: Overwrites its status setting it to CANDIDATE for the
+STARTING\_SEGMENT\_CONFIRM with the same segID when receiving a normal
+SEGMENT\_REQUEST: Overwrites its status setting it to CANDIDATE for the
 segID frees the links previously set as tvisited during flooding
@@
 The visited value is true NOTE: an ASSIGNED state is a quick temporary
-state, since it becomes ACTIVE_SEARCHING if a not (visited/tvisited)
-link is suitable for searching new segments (see next_visited
+state, since it becomes ACTIVE\_SEARCHING if a not (visited/tvisited)
+link is suitable for searching new segments (see next\_visited
 procedure on paper)
@@
 
-SEGMENT_REQUEST: used to search candidates for a segment (not the
+SEGMENT\_REQUEST: used to search candidates for a segment (not the
 first of the subnet, managed separately as a starting segment).
 
-SEGMENT_CONFIRM: used to create a segment. When received, if the node
+SEGMENT\_CONFIRM: used to create a segment. When received, if the node
 status is tvisited with a segID corresponding to the one indicated in
@@
 id. Further, it should forward this packet to the link where the
-original SEGMENT_REQUEST packet came from, so that all candidate nodes
+original SEGMENT\_REQUEST packet came from, so that all candidate nodes
 can learn the segment id they belong to. The following LED shoud be
 updated: The state of the node changes from tvisited to visited.  the
-link_tvisited previously set with the segID should be invalidated the
-link_visited variable associated to the incoming confirm should be set
+link\_tvisited previously set with the segID should be invalidated the
+link\_visited variable associated to the incoming confirm should be set
 as segID. Note that if the request was flooded across different links,
-the link_visited variable associated to the other paths shouldn’t be
-set.  the link_visited variable associated to the link from which the
+the link\_visited variable associated to the other paths shouldn’t be
+set.  the link\_visited variable associated to the link from which the
 request was originated should be set segID
 
-STARTING_SEGMENT_REQUEST: the request for the first segment of a
+STARTING\_SEGMENT\_REQUEST: the request for the first segment of a
 subnet should be differentiated since all nodes (except the starting
@@
 
-SEGMENT_CANCEL: used when the process of searching a segment along a
+SEGMENT\_CANCEL: used when the process of searching a segment along a
 certain path fails. When a node discovers that the path that includes
-the node itself is no more suitable, a SEGMENT_CANCEL is sent back
-across the link from which the SEGMENT_REQUEST was received.  Possible
+the node itself is no more suitable, a SEGMENT\_CANCEL is sent back
+across the link from which the SEGMENT\_REQUEST was received.  Possible
 reasons for that: The node it’s already candidate for another segment
@@
 upper layer via. This bootstrap node sets itself as “visited” and
-changes its status to ACTIVE_SEARCHING, sending a
-STARTING_SEGMENT_REQUEST across one of its not (visited/tvisited)
+changes its status to ACTIVE\_SEARCHING, sending a
+STARTING\_SEGMENT\_REQUEST across one of its not (visited/tvisited)
 links and.
 
-Flooding: Each node receiving a STARTING_SEGMENT_REQUEST,
+Flooding: Each node receiving a STARTING\_SEGMENT\_REQUEST,
 if not (visited/tvisited),  forwards  to the attached links that are
@@
 associated to the packet. Note that a node that has already received a
-STARTING_SEGMENT_REQUEST packet can simply ignore further packets
+STARTING\_SEGMENT\_REQUEST packet can simply ignore further packets
 associated to the same request, since has already contributed to the
-flooding. Note also that each of these packets has a max_segment_hops
+flooding. Note also that each of these packets has a max\_segment\_hops
 field to prevent packets from travelling undefinitively.
 
-setup of the starting-segment: when this STARTING_SEGMENT_REQUEST packet reaches
+setup of the starting-segment: when this STARTING\_SEGMENT\_REQUEST packet reaches
 the starting node (from a different link, of course), the starting
-segment is found. Then the starting node sends back a SEGMENT_CONFIRM
+segment is found. Then the starting node sends back a SEGMENT\_CONFIRM
 packet with the same id along the link from which it received the
-STARTING_SEGMENT_REQUEST. Each node do same by changing its own status
+STARTING\_SEGMENT\_REQUEST. Each node do same by changing its own status
 from tvisited to visited. So the confirmation packet is sent back from
@@
 
-Note: A node knows to be tvisited due a  STARTING_SEGMENT_REQUEST.
-Then, when receiving a SEGMENT_REQUEST for other (not the starting)
+Note: A node knows to be tvisited due a  STARTING\_SEGMENT\_REQUEST.
+Then, when receiving a SEGMENT\_REQUEST for other (not the starting)
 segment, simply knows to cancel the tvisited status of the node and
@@
 Injecting request: A node in the ASSIGNED state can initiate a search for a
-segment, by sending a SEGMENT_REQUEST with an across one of its free
+segment, by sending a SEGMENT\_REQUEST with an across one of its free
 links. Note that, since this is not the starting segment, in this case
@@
 setup of the segment: The find process is successfull when a visited
-node receives the SEGMENT_REQUEST packet. Then, a SEGMENT_CONFIRM is
+node receives the SEGMENT\_REQUEST packet. Then, a SEGMENT\_CONFIRM is
 sent back along the path that originated the request.  Failing while
-searching a segment: a node received a SEGMENT_REQUEST packet but
+searching a segment: a node received a SEGMENT\_REQUEST packet but
 matched one of the following conditions: the node is free but has no
-more suitable free links (can’t forward the SEGMENT_REQUEST) the node
+more suitable free links (can’t forward the SEGMENT\_REQUEST) the node
 is tvisited candidate for another find process the request packet
-exceeded the max_segment_hops limit.  In all these cases the node
-sends back a SEGMENT_CANCEL along the proper link modifying its state
-to free. Each of the subsequent nodes will forward this SEGMENT_CANCEL
+exceeded the max\_segment\_hops limit.  In all these cases the node
+sends back a SEGMENT\_CANCEL along the proper link modifying its state
+to free. Each of the subsequent nodes will forward this SEGMENT\_CANCEL
 only if no more free links can be explored starting from them.
@@
 In the processes described above, we assumed that each node in the
-READY_SEARCHING state can start a find segment process by injecting a
-SEGMENT_REQUEST. However, a more accurate decision when defining DiSR
+READY\_SEARCHING state can start a find segment process by injecting a
+SEGMENT\_REQUEST. However, a more accurate decision when defining DiSR
 should be made in order to decide whether or not the node must
@@
 
-\subsection{Receiving a STARTING_SEGMENT_REQUEST}
+\subsection{Receiving a STARTING\_SEGMENT\_REQUEST}
 
-When a node receives a STARTING_SEGMENT_REQUEST, with id = X,  there are the following cases:
+When a node receives a STARTING\_SEGMENT\_REQUEST, with id = X,  there are the following cases:
 
@@
 initiator of the request (set visited by definition): a first segment
-was found and should be confirmed sending back a SEGMENT_CONFIRM
+was found and should be confirmed sending back a SEGMENT\_CONFIRM
 packet.
@@
 the only visited node of the subnet should be the initial node from
-which the STARTING_SEGMENT_REQUEST originated. Note again that we are
+which the STARTING\_SEGMENT\_REQUEST originated. Note again that we are
 assuming that if the the node is visited or tvisited with the id of
@@
 
-\subsection{Receiving a SEGMENT_REQUEST}
-When a node receives a SEGMENT_REQUEST, the are the following cases:
+\subsection{Receiving a SEGMENT\_REQUEST}
+When a node receives a SEGMENT\_REQUEST, the are the following cases:
 
 The node is visited (and belongs to the same subnet): a segment was
-found and it should be confirmed sending back a SEGMENT_CONFIRM
+found and it should be confirmed sending back a SEGMENT\_CONFIRM
 packet.
@@
 The node is tvisited: it should discard the packet sending
-back a SEGMENT_CANCEL
+back a SEGMENT\_CANCEL
 
 The node it's not visited/tvisited and has free
-links: it marks itself as tvisited and forwards the SEGMENT_REQUEST
+links: it marks itself as tvisited and forwards the SEGMENT\_REQUEST
 (one request at time) to each of its free links, according to some
@@
 
-CHECK: the difference between confirming a STARTING_SEGMENT_REQUEST
-and confirming a SEGMENT_REQUEST is that in the first case the node
+CHECK: the difference between confirming a STARTING\_SEGMENT\_REQUEST
+and confirming a SEGMENT\_REQUEST is that in the first case the node
 itself it's included in the segment , while in the second case the
@@
 
-\subsection{Receiving a SEGMENT_CANCEL}
-When a node receives a SEGMENT_CANCEL packet it means that searching
+\subsection{Receiving a SEGMENT\_CANCEL}
+When a node receives a SEGMENT\_CANCEL packet it means that searching
 for a segment along that path was unsuccessful. But if the node still
-has other free links to try, it should forward a SEGMENT_REQUEST to
+has other free links to try, it should forward a SEGMENT\_REQUEST to
 the next link (next according to some internal ordering). So a node
-forwards back the SEGMENT_CANCEL packet along the link that originated
-the SEGMENT_REQUEST packet ONLY when there are no more free links to
+forwards back the SEGMENT\_CANCEL packet along the link that originated
+the SEGMENT\_REQUEST packet ONLY when there are no more free links to
 try. If this is the case, the node modifies its status from tvisited
-to free and fordwards the SEGMENT_CANCEL packet to the link from which
-the request was received. The process stops when the SEGMENT_CANCEL
+to free and fordwards the SEGMENT\_CANCEL packet to the link from which
+the request was received. The process stops when the SEGMENT\_CANCEL
 packet reach the starting node that originated the request.
@@
 \section{Nanoxim and simulation environment}
-% - Architecture of the nanoxim simulator
-% - how simulations were conducted
-...
+
+The simulator Nanoxim is a SystemC tool based on a minimal version of
+the Noxim Network-on-Chip simulator. It's not a "faster noxim", but a
+drastically reduced noxim the will be able to simulate a random
+network on nodes. Current differences from noxim:
+
+removed all routing algorithms that depend on a topology (only XY left
+to test meshes) removed flit management, nodes only exchange packets
+(e.g. no wormhole)
+
+Future features:
+
+topology agnostic able to test different nano-oriented communication
+mechanism
 

### 2013-04-19 trunk/PAPER/paper.tex
Added related work (integrated in Intro)

@@
 segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized setup
-phase.
+qualities of segment-based routing without requiring as graph topology
+as input, and without the need for a centralized algorithm which
+perform a setup phase.  Our contribution is not find the
+best segment choice, but to show something that could really work in
+such complex, irregular and large sized topologies.
 \end{abstract}
@@
 
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized algorithm
-which perform a \"segment setup\" phase.
+Different works have been presented addressing the problem of topology
+agnostic routing, such as~\ref{}. Althougth they show interesting
+performances, the requirement for virtual channels resources makes
+them not suitable for the particular DNA self assembled we are
+focusing on.
 
-% irregular topology -> how to route ?
+Other topology independent algorithms not using virtual channels are
+based on turn proibition. Up-Down~\ref{} exploits the creation of a
+spanning tree of the topology, then placing bidirectional restrictions
+by avoiding a packet to traverse the same link in both up and down
+directions. The hierarchical nature of this approach can lead to
+uneven traffic distribution, with many packets traversing upper links
+(near to the root). The~\ref{} mitigates this issue, making this
+approach acceptable in small networks, however the whole restriction
+placement is still fixed, depending on the particular root selected,
+making these approaches certainly not scalable for the thousands nodes
+scenario of DNA self assembled technology.
+
+In~\ref{} authors present SR, a new approach the solves this limitation by
+allowing turn restriction to be placed locally, independently from
+other restriction. The whole network is partitioned in segments, and a
+single bidirectional turn restrictions can be chosen for each
+segment in order to guarantee deadlock freedom and connected networks.
+This locality independence makes SR scalable for large-sized networks,
+but its topology independency still requires the knowledge of the
+topology graph in order to find the segments. The small scale control,
+random placement and connectivity features discussed in the previous
+section makes having such a topology graph impossible in DNA
+self assembly, together with any other similar centralized algorithm using
+graph description as input.
+
+The contribution presented in this paper is a first effort for a
+distribuited segment-based routing in DNA based networks (DiSR).  This
+paper is not intended to show discover the "optimal" segment choice, ideally
+reachable with a whole graph topology knowledge, but to demonstrate something could
+really fit such complex, irregular and large sized topologies.
 
 %------------------------------------------------------------------------------
-
-\section{Related Work}
-% - Up/Down etc..
-% - SR is ok (topology independent) but requires the knowledge of the
-% topology graph -> impossible in DNA self assembly
-% - Our contribution: a distribuited approach for a segment-based
-%   routing. Not the "optimal" SR, just a SR "that works" in such
-%   complex irregular topologies where a graph could never be
-%   available.
-...
-Different architectures using nano-scale devices have been presented.A
-general purpose architecture for Self-Assembled Nano-Electronics has
-been presented to demostrate the potential of
-DNA-selfassembly~\ref{TODO}
-
+\section{DiSR main elements}
 %------------------------------------------------------------------------------
 
-\section{Proposal}
-% - Draft of the DiSR idea
-% - how it should work
-...
+We distinct among two different kind of data stored at each node:
+local environment data (LED) and dynamic behaviour status (DBS).
+
+\subsection{Local Environment Data (LED)}
+
+The LED is like a snapshot of the DiSR algorithm on each node,
+consisting in the following variables:
+
+segID:a value used to specify a segment id for the node. Depending on
+the values of visited/tvisited variables below, the node can be
+assigned to or candidate for a specific segment id.
+
+visited : a boolean value corresponding to the visited status. If visited is true
+and segID is different from NULL, then segID specifies the segment id
+the node belongs to. Note that a value different from NULL does not
+necessarily mean the node has been assigned to some segment (e.g. when
+searching starting segment is set visited by default even if not yet
+assigned to any segment). When false, the node is not yet visited.
+
+tvisited: a boolean value corresponding to the tvisited status. If
+true, the node is being considered as candidate for a segment, and the
+segID specifies the segment id for which the node it's candidate. When
+false, the node is not currently tvisited.
+
+link\_visited[]: an array
+of values representing information about attached links, that is, the
+ID of the segment owning each link. When NULL, a link has not yet been
+marked as visited. TDB: do we need to introduce some value for the
+“bridge” status ? (e.g. a node connecting the terminal node of a
+subnet with the starting one of another)
+
+link\_tvisited[]: an array of
+values representing information about attached links, e.g. the ID of
+the segment for which the link is candidate. When NULL, the link is
+currently not tvisited.  starting: boolean, true if the node it's a
+starting node for the subnet terminal:boolean, true if the node it's a
+terminal node for the subnet.  subnet:the subnet the node belongs to.
+If NULL, none.
+
+\subsection{Dynamic Behaviour Status (DBS)}
+In addition to the LED variables
+described above, further information should be stored in order to
+capture the current dynamic behaviour of the node. This is represented
+by the dynamic behaviour status (DBS) variable, which strictly depends
+on the LED data and the events occurring at the node. The DBS can have
+the following values:
+
+FREE: a node that has  not been yet considered  by the DiSR algorithm.
+The node is not marked as visited/tvisited/terminal/starting.
+
+BOOTSTRAP: a node which has been explicitly set as bootstrap node from
+an upper layer via. This is required because a
+
+STARTING\_SEGMENT\_REQUEST packet should be injected in order to start
+the whole process.
+
+ACTIVE\_SEARCHING: a node from which a find process of new segments has
+been started and not yet cancelled or confirmed. This happens when all
+the following conditions are matched: the node is marked as visited,
+that is visited = TRUE
+
+CHECK: segID is set to some value reflecting
+the segment request sent there is a link that is being investigated by
+the node, that is a tvisited\_link marked with the same id of the node
+
+CANDIDATE: a node currently candidate for belonging to some segment
+with id segid, not being itself the node from which the find process
+was started. The following conditions should be matched: tvisited =
+true, with segID=X different from node's id.  Two links set as
+link\_tvisited with id X. Let’s refer them as  links 'i' and 'j'. Then
+link\_tvisited[i] was set = X when the find process from an adjacent
+node reached the current node, while link\_tvisited[j] has been set to
+X when the node itself started to investigate its free links for the
+segment request with id X. Note that while investigating its attached
+links, if the find process fails along path 'j', the current node can
+investigate another free node 'k' if suitable.
+
+CANDIDATE\_STARTING:
+same as above, but the node is currently being considered as candidate
+for starting segment. Two main differences: Can confirm
+STARTING\_SEGMENT\_CONFIRM with the same segID when receiving a normal
+SEGMENT\_REQUEST: Overwrites its status setting it to CANDIDATE for the
+segID frees the links previously set as tvisited during flooding
+
+ASSIGNED: a node for which the segment has been determined.  The
+segment segID attribute value is set to some id X different from NULL.
+The visited value is true NOTE: an ASSIGNED state is a quick temporary
+state, since it becomes ACTIVE\_SEARCHING if a not (visited/tvisited)
+link is suitable for searching new segments (see next\_visited
+procedure on paper)
+
+PROCESSED: a node which should take no other
+action, since all its links have been investigated.
+
+\subsection{Packets types Required}
+TODO: a lot of description is already present elsewhere, make this
+section smaller...
+
+SEGMENT\_REQUEST: used to search candidates for a segment (not the
+first of the subnet, managed separately as a starting segment).
+
+SEGMENT\_CONFIRM: used to create a segment. When received, if the node
+status is tvisited with a segID corresponding to the one indicated in
+the packet, the node learns to belong to the segment associated to the
+id. Further, it should forward this packet to the link where the
+original SEGMENT\_REQUEST packet came from, so that all candidate nodes
+can learn the segment id they belong to. The following LED shoud be
+updated: The state of the node changes from tvisited to visited.  the
+link\_tvisited previously set with the segID should be invalidated the
+link\_visited variable associated to the incoming confirm should be set
+as segID. Note that if the request was flooded across different links,
+the link\_visited variable associated to the other paths shouldn’t be
+set.  the link\_visited variable associated to the link from which the
+request was originated should be set segID
+
+STARTING\_SEGMENT\_REQUEST: the request for the first segment of a
+subnet should be differentiated since all nodes (except the starting
+one) must forward the packet using a flooding mechanism. This is
+necessary since the request packet must reach the starting node, which
+is the only node marked as visited. As stated elsewhere, it should
+remembered that the first segment of each subnet it's  a loop that
+beginning/ending on the starting node.
+
+SEGMENT\_CANCEL: used when the process of searching a segment along a
+certain path fails. When a node discovers that the path that includes
+the node itself is no more suitable, a SEGMENT\_CANCEL is sent back
+across the link from which the SEGMENT\_REQUEST was received.  Possible
+reasons for that: The node it’s already candidate for another segment
+The node it’s free but can’t find a free link (according the
+cyclelinks timeout) The node it’s tvisited for the same request id,
+previously forwarded that request along some free direction, but now
+it’s receiving a a cancel request and has no more free links
+
+\section{DiSR Execution Model}
+
+\subsection{Creating the starting segment}
+
+Injecting request: all nodes have status FREE, except for a
+“bootstrap node” with status BOOTSTRAP, set by some signal from an
+upper layer via. This bootstrap node sets itself as “visited” and
+changes its status to ACTIVE\_SEARCHING, sending a
+STARTING\_SEGMENT\_REQUEST across one of its not (visited/tvisited)
+links and.
+
+Flooding: Each node receiving a STARTING\_SEGMENT\_REQUEST,
+if not (visited/tvisited),  forwards  to the attached links that are
+not already marked as visited/tvisited using a flooding mechanism.
+Each of these links is then marked as tvisited with the segment id
+associated to the packet. Note that a node that has already received a
+STARTING\_SEGMENT\_REQUEST packet can simply ignore further packets
+associated to the same request, since has already contributed to the
+flooding. Note also that each of these packets has a max\_segment\_hops
+field to prevent packets from travelling undefinitively.
+
+setup of the starting-segment: when this STARTING\_SEGMENT\_REQUEST packet reaches
+the starting node (from a different link, of course), the starting
+segment is found. Then the starting node sends back a SEGMENT\_CONFIRM
+packet with the same id along the link from which it received the
+STARTING\_SEGMENT\_REQUEST. Each node do same by changing its own status
+from tvisited to visited. So the confirmation packet is sent back from
+node to node and the starting segment is created.
+
+Note: A node knows to be tvisited due a  STARTING\_SEGMENT\_REQUEST.
+Then, when receiving a SEGMENT\_REQUEST for other (not the starting)
+segment, simply knows to cancel the tvisited status of the node and
+its links, since if a segment arrived it means that a starting segment
+has already been found a there’s no need to keep the tvisited status
+for those broadcast status. What happens to nodes not receiving these
+segment request? they simply remain tvisited and after a timeout reset
+their state as free. But they could also remain tvisited for the
+starting segment, since this doesn’t affect their behaviour for future
+segment requests.
+
+failure: [TODO] should we handle this case ? i.e.
+marking as terminal ?
+
+\subsection{Finding other segments}
+
+Injecting request: A node in the ASSIGNED state can initiate a search for a
+segment, by sending a SEGMENT\_REQUEST with an across one of its free
+links. Note that, since this is not the starting segment, in this case
+the packet should not reach the initiator, but just another visited
+node
+
+setup of the segment: The find process is successfull when a visited
+node receives the SEGMENT\_REQUEST packet. Then, a SEGMENT\_CONFIRM is
+sent back along the path that originated the request.  Failing while
+searching a segment: a node received a SEGMENT\_REQUEST packet but
+matched one of the following conditions: the node is free but has no
+more suitable free links (can’t forward the SEGMENT\_REQUEST) the node
+is tvisited candidate for another find process the request packet
+exceeded the max\_segment\_hops limit.  In all these cases the node
+sends back a SEGMENT\_CANCEL along the proper link modifying its state
+to free. Each of the subsequent nodes will forward this SEGMENT\_CANCEL
+only if no more free links can be explored starting from them.
+
+\subsection{Intra-node vs Inter-node parallelism}
+In the processes described above, we assumed that each node in the
+READY\_SEARCHING state can start a find segment process by injecting a
+SEGMENT\_REQUEST. However, a more accurate decision when defining DiSR
+should be made in order to decide whether or not the node must
+actually perform this action. 
+The point above is is strictly related to the general question: which
+level of “parallelism” should we allow in DiSR ? The adopted approach
+is that, although the nature of DiSR itself is intrinsicly parallel,
+the use of parallelism makes things work in a more complex way. In
+other words, DiSR is parallel when needed, but it does not exploit
+parallelism as an “improving feature”. When not needed, things should
+be serialized. For example: when a node is “ready searching” could
+start several find segment process associated to the same segment, one
+for each free link. But serializing this by investigating the free
+links in order could be a simplest solution. We refer to this saying
+that we avoid intra-node parallelism.  Note that while intra-node
+parallelism can be avoided, trying to avoid inter-node parallelism
+could be more complex than allowing the parallelism itself. Imagine
+for example the effort of trying to coordinate nodes so that an unique
+finding node process is actually running in the whole subnet. Thus, in
+contrast to the intra-node parallelism, the inter-node parallelism is
+a structural property of the DiSR algorithm and should not be avoided.
 %------------------------------------------------------------------------------
 
-\section{DiSR execution model}
-% - what is executed at each node, which information is required
-...
+\section{Detailed Node behaviour Model}
 
-%------------------------------------------------------------------------------
+%TODO: add state machines
+
+% TODO: fix, move elsewhere or delete
+Assumption: when discussing of visited/tvisited nodes, we are assuming
+with an id corresponding to the same subnet. Nodes involved in other
+subnet processes can simply ignore these packets. (TBD: formalize more
+clearly in which cases inter-subnet packets must be ignored, probably
+this happens most of the times, but in some cases, e.g. when a
+terminal node is found, some kind of communication packets are needed
+in order to crearte the bridge between two subnets.)
+
+\subsection{Receiving a STARTING\_SEGMENT\_REQUEST}
+
+When a node receives a STARTING\_SEGMENT\_REQUEST, with id = X,  there
+are the following cases:
+
+The node is visited with the same segID = x, that is it was the
+initiator of the request (set visited by definition): a first segment
+was found and should be confirmed sending back a SEGMENT\_CONFIRM
+packet.
+
+The node is tvisited, with the same segID of the packet: due
+the flooding mechanism, another starting segment packet reached a node
+which was previously marked as tvisited from the same starting segment
+search process. Since the node is tvisited with the same id, it means
+that it already accomplished in the task of propagating that kind
+packets, thus can simply ignore the event thrashing the packet.  If
+the node it's not visited/tvisited: it should set itself as tvisited
+and forward the packet along its free links, using flooding. TBD: how
+the status should be changed ? depend on the flooding mechanism. Note
+that these links don’t include the link from which the request was
+received.
+
+The node it's visited, with different id in the packet.
+CHECK:  it is not the initiator of the starting segment request, but
+is already assigned to some segment!? assuming again we are discussing
+of nodes belonging to the same subnet, this should NOT happen, since
+the only visited node of the subnet should be the initial node from
+which the STARTING\_SEGMENT\_REQUEST originated. Note again that we are
+assuming that if the the node is visited or tvisited with the id of
+another subnet can simply ignore the request.  The node it's tvisited
+but it's not the initiator of the request (different id): same as
+above, if we are assuming nodes of the same subnet, this shouldn’t
+happen. If the node is of another subnet, can simply ignore the event.
+
+\subsection{Receiving a SEGMENT\_REQUEST}
+When a node receives a SEGMENT\_REQUEST, the are the following cases:
+
+The node is visited (and belongs to the same subnet): a segment was
+found and it should be confirmed sending back a SEGMENT\_CONFIRM
+packet.
+
+The node is tvisited: it should discard the packet sending
+back a SEGMENT\_CANCEL
+
+The node it's not visited/tvisited and has free
+links: it marks itself as tvisited and forwards the SEGMENT\_REQUEST
+(one request at time) to each of its free links, according to some
+ordering
+
+CHECK: the difference between confirming a STARTING\_SEGMENT\_REQUEST
+and confirming a SEGMENT\_REQUEST is that in the first case the node
+itself it's included in the segment , while in the second case the
+receiving node DOES NOT belong to the segment found. The motivation is
+that in the second case the node was already marked as visited because
+of being assigned to some segment found before, while in the
+starting-segment case, by definition, the first segment of a subnet
+begins with the starting node, which is marked as visited by the SR
+algorithm when searching for the first (starting) segment. Remember
+that the first segment of a subnet is a loop beginning with the
+starting node.
+
+\subsection{Receiving a SEGMENT\_CANCEL}
+When a node receives a SEGMENT\_CANCEL packet it means that searching
+for a segment along that path was unsuccessful. But if the node still
+has other free links to try, it should forward a SEGMENT\_REQUEST to
+the next link (next according to some internal ordering). So a node
+forwards back the SEGMENT\_CANCEL packet along the link that originated
+the SEGMENT\_REQUEST packet ONLY when there are no more free links to
+try. If this is the case, the node modifies its status from tvisited
+to free and fordwards the SEGMENT\_CANCEL packet to the link from which
+the request was received. The process stops when the SEGMENT\_CANCEL
+packet reach the starting node that originated the request.
 
 \section{Nanoxim and simulation environment}
-% - Architecture of the nanoxim simulator
-% - how simulations were conducted
-...
+
+The simulator Nanoxim is a SystemC tool based on a minimal version of
+the Noxim Network-on-Chip simulator. It's not a "faster noxim", but a
+drastically reduced noxim the will be able to simulate a random
+network on nodes. Current differences from noxim:
+
+removed all routing algorithms that depend on a topology (only XY left
+to test meshes) removed flit management, nodes only exchange packets
+(e.g. no wormhole)
+
+Future features:
+
+topology agnostic able to test different nano-oriented communication
+mechanism
 
@@
 \section{Experiments}
-% - Graphs, tables
-% - comparison against other approaches
-...
+% Absolute results:
+% Comparison results:
 

### 2013-05-03 PAPER/paper.tex
- list items for better reading - some details about experiments

@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
+\documentclass[final,journal,letterpaper]{IEEEtran}
+%\IEEEoverridecommandlockouts
 
@@
 
-\title{A Distribuited Segment-based Approach for Topology-agnostic Nano Networks Routing}
+\title{A Distributed Segment-based Approach for Topology-agnostic Nano Networks Routing}
 
 \author{
-  \IEEEauthorblockN{a} \IEEEauthorblockA{Affiliation3\\ email3} \and
-  \IEEEauthorblockN{b} \IEEEauthorblockA{Affiliation2\\ email2} }
+%  \IEEEauthorblockN{a} \IEEEauthorblockA{Affiliation3\\ email3} \and
+%  \IEEEauthorblockN{b} \IEEEauthorblockA{Affiliation2\\ email2}
+
+  }
 
@@
 \begin{abstract}
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized setup
-phase.
+In this paper we present DiSR, a first effort for a distributed
+segment-based approach to routing in a nano-scale topology agnostic
+scenario. The aim is to exploit the already-proven
+qualities of segment-based routing without requiring a topology graph
+as input nor needing a centralized algorithm 
+performing a setup phase.  Our contribution is not find the
+best segment choice, but to show an approach that can actually work in
+such complex, irregular and large sized topologies. After describing
+all the conceptual elements required, we use the opensource Nanoxim tool to show
+some quantitive results that demonstrate how DiSR still preserve
+segment-based qualities while avoiding a centralized tree-based
+broadcasting and the usage of expensive virtual channels mechanisms.
 \end{abstract}
@@
 %------------------------------------------------------------------------------
+%\IEEEkeywords{...}
 
-\IEEEkeywords{...}
-
+\begin{IEEEkeywords}
+Nanotechnology, DNA, Self-assembly, Routing
+\end{IEEEkeywords}
 %------------------------------------------------------------------------------
 
-\section{Introduction}
+\section{Introduction and Motivation}
 Exploring long term alternatives to the CMOS technology is gaining
@@
 to introduce new challenges. Power density, defect tolerance, testing
-costs and many other issues are only partially mitigated by multicore
-approaches~\ref{TODO}, but growing computing requirements will eventually need
-even more radical architectural modifications and new paradigms in
-future computer design.
+costs and wire delays are only few of the many critical aspects~\cite{}
+and multicore approaches~\cite{TODO} are only partially mitigating the
+impact of such constraints. Thus, the growing computing demand will
+eventually need even more radical architectural modifications and new
+paradigms in order to address computer design issues of the future.
 
-DNA-self assembled nanoscale architectures~\ref{TOOD} are emerging as promising
-technology due its tera/peta scale of integration, defect tolerance
-tolerance and potential computing capabilities~\ref{TODO}. This
-technologies is certainly still at its early stage of development,
-however different laboratory demos and prof-of-concepts architectures
-have been presented~\ref{TODO}.
+In the last years, Self-assembled nanoscale architectures~\cite{TOOD}
+are emerging as promising technology due its tera/peta scale of
+integration, defect tolerance tolerance and potential computing
+capabilities~\cite{TODO}. This technologies is certainly still at its
+early stage of development, however different laboratory demos and
+prof-of-concepts architectures have been presented~\cite{TODO}.
 
@@
 stabiliy of DNA sequences in orders to create grids onto which
-nano-devices (e.g. nanowires and CNFET~\ref{TODO}) can be attached by
+nano-devices (e.g. nanowires and nanotubes~\cite{TODO}) can be attached by
 designing approapriate DNA tags. A detailed description of the
@@
 
-This aspects of a DNA-self assembled process leads some architectural implications
-when approaching to the Computer Design. Architecture must consist of
-a distributed network of small computing and storage nodes, randomly
-connected. Data will be travelling on packets that must be routed
-using a topology-agnostic strategy, since no particular regularity can
-be assumed in such network.
+This aspects of a DNA-self assembled process leads some architectural
+implications when approaching to the Computer Design. Architecture
+must consist of a distributed network of small computing and storage
+nodes, randomly placed and interconnected. Both instructions and
+data operands will be travelling on packets, routed using a
+topology-agnostic strategy that avoids deadlock, since
+no particular regularity can be assumed in such network.
+Proof-of-concept of such kind of computational model can be found
+in~\cite{}, and we will assume a similar scenario as background,
+althoght the proposed approach to defect tolerance is more general and not stricly related
+to any of these architectures.
 
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized algorithm
-which perform a \"segment setup\" phase.
+Different works have been presented addressing the problem of topology
+agnostic routing, such as~\cite{}. Althougth they show interesting
+performances, the requirement for virtual channels resources 
+to avoid deadlock makes them not suitable for the particular DNA self
+assembled networks we are focusing on.
 
-% irregular topology -> how to route ?
+Other topology independent algorithms not using virtual channels
+achieve deadlock freedom with turn proibitions, such as~\cite{}.
+Up-Down~\cite{} exploits the creation of a spanning tree of the
+topology, then placing bidirectional restrictions by avoiding a packet
+to traverse the same link in both up and down directions. The
+hierarchical nature of this approach can lead to uneven traffic
+distribution, with many packets traversing upper links (near to the
+root), however still acceptable for classical wide area networks
+topologies with a limited number of nodes.  The~\cite{} mitigates this
+issue, however the whole restriction placement is still prefixed,
+striclty depending on the particular root selected, making these
+approaches not scalable for the TODO(thousands) nodes scenario of DNA
+self assembled technology.
+
+In~\cite{} authors present SR, a new approach the solves this limitation by
+allowing turn restrictions to be placed locally, independently from
+other restrictions. The whole network is partitioned in segments, and a
+single bidirectional turn restrictions can be chosen for each
+segment in order to guarantee deadlock freedom and connected networks.
+This locality independence makes SR scalable for large-sized networks,
+but its topology independency still requires the knowledge of the
+topology graph in order to find the segments. The small scale control,
+random placement and connectivity features discussed in the previous
+section makes having such a topology graph impossible in DNA
+self assembly, together with any other similar centralized algorithm using
+graph description as input.
+
+The contribution presented in this paper is a first effort for a
+Distributed Segment-based routing in nanoscale DNA based networks
+(DiSR). The aim of this work is not intended to discover the "optimal"
+segment choice (ideally reachable with the knowledge of the whole
+topology graph) but just to demonstrate a concrete approach that can fit
+into such complex, irregular and large sized topologies.
 
 %------------------------------------------------------------------------------
-
-\section{Related Work}
-% - Up/Down etc..
-% - SR is ok (topology independent) but requires the knowledge of the
-% topology graph -> impossible in DNA self assembly
-% - Our contribution: a distribuited approach for a segment-based
-%   routing. Not the "optimal" SR, just a SR "that works" in such
-%   complex irregular topologies where a graph could never be
-%   available.
-...
-Different architectures using nano-scale devices have been presented.A
-general purpose architecture for Self-Assembled Nano-Electronics has
-been presented to demostrate the potential of
-DNA-selfassembly~\ref{TODO}
-
+\section{DiSR main concepts}
 %------------------------------------------------------------------------------
 
-\section{Proposal}
-% - Draft of the DiSR idea
-% - how it should work
-...
-%------------------------------------------------------------------------------
-
-\section{Detailed DiSR model}
 We distinct among two different kind of data stored at each node:
@@
 
-segID:a value used to specify a segment id for the node. Depending on
+\begin{itemize}
+\item{segID}:a value used to specify a segment id for the node. Depending on
 the values of visited/tvisited variables below, the node can be
 assigned to or candidate for a specific segment id.  
-
-visited : a boolean value corresponding to the visited status. If visited is true
+\item{visited}: a boolean value corresponding to the visited status. If visited is true
 and segID is different from NULL, then segID specifies the segment id
@@
 assigned to any segment). When false, the node is not yet visited.
-
-tvisited: a boolean value corresponding to the tvisited status. If
+\item{tvisited}: a boolean value corresponding to the tvisited status. If
 true, the node is being considered as candidate for a segment, and the
@@
 false, the node is not currently tvisited.  
-
-link\_visited[]: an array
+\item{link\_visited[]}: an array
 of values representing information about attached links, that is, the
@@
 subnet with the starting one of another) 
-
-link\_tvisited[]: an array of
+\item{link\_tvisited[]}: an array of
 values representing information about attached links, e.g. the ID of
@@
 If NULL, none.
+\end{itemize}
 
 \subsection{Dynamic Behaviour Status (DBS)}
-In addition to the LED variables
-described above, further information should be stored in order to
-capture the current dynamic behaviour of the node. This is represented
-by the dynamic behaviour status (DBS) variable, which strictly depends
-on the LED data and the events occurring at the node. The DBS can have
-the following values:
+In addition to the LED variables described above, further information
+should be stored in order to capture the current dynamic behaviour of
+the node. This is represented by the dynamic behaviour status (DBS)
+variable, which strictly depends on the LED data and the events
+occurring at the node. The DBS can have the following values:
 
-FREE: a node that has  not been yet considered  by the DiSR algorithm.
+\begin{itemize}
+\item{FREE}: a node that has  not been yet considered  by the DiSR algorithm.
 The node is not marked as visited/tvisited/terminal/starting.
-
-BOOTSTRAP: a node which has been explicitly set as bootstrap node from
+\item{BOOTSTRAP}: a node which has been explicitly set as bootstrap node from
 an upper layer via. This is required because a
-
-STARTING\_SEGMENT\_REQUEST packet should be injected in order to start
+\item{STARTING\_SEGMENT\_REQUEST} packet should be injected in order to start
 the whole process.
-
-ACTIVE\_SEARCHING: a node from which a find process of new segments has
+\item{ACTIVE\_SEARCHING}: a node from which a find process of new segments has
 been started and not yet cancelled or confirmed. This happens when all
@@
 that is visited = TRUE 
-
-CHECK: segID is set to some value reflecting
+TODO: segID is set to some value reflecting
 the segment request sent there is a link that is being investigated by
 the node, that is a tvisited\_link marked with the same id of the node 
-
-CANDIDATE: a node currently candidate for belonging to some segment
+\item{CANDIDATE}: a node currently candidate for belonging to some segment
 with id segid, not being itself the node from which the find process
@@
 investigate another free node 'k' if suitable.  
-
-CANDIDATE\_STARTING:
-same as above, but the node is currently being considered as candidate
+\item{CANDIDATE\_STARTING}: same as above, but the node is currently being considered as candidate
 for starting segment. Two main differences: Can confirm
@@
 segID frees the links previously set as tvisited during flooding
-
-ASSIGNED: a node for which the segment has been determined.  The
+\item{ASSIGNED}: a node for which the segment has been determined.  The
 segment segID attribute value is set to some id X different from NULL.
@@
 procedure on paper) 
-
-PROCESSED: a node which should take no other
+\item{PROCESSED}: a node which should take no other
 action, since all its links have been investigated. 
+\end{itemize}
 
@@
 
-SEGMENT\_REQUEST: used to search candidates for a segment (not the
+\begin{itemize}
+\item{SEGMENT\_REQUEST}: used to search candidates for a segment (not the
 first of the subnet, managed separately as a starting segment).
 
-SEGMENT\_CONFIRM: used to create a segment. When received, if the node
+\item{SEGMENT\_CONFIRM}: used to create a segment. When received, if the node
 status is tvisited with a segID corresponding to the one indicated in
@@
 
-STARTING\_SEGMENT\_REQUEST: the request for the first segment of a
+\item{STARTING\_SEGMENT\_REQUEST}: the request for the first segment of a
 subnet should be differentiated since all nodes (except the starting
@@
 
-SEGMENT\_CANCEL: used when the process of searching a segment along a
+\item{SEGMENT\_CANCEL}: used when the process of searching a segment along a
 certain path fails. When a node discovers that the path that includes
@@
 
-\section{DiSR Execution Phases}
+\end{itemize}
+
+\section{Draft of DiSR Execution Model}
 
@@
 
-Injecting request: all nodes have status FREE, except for a
+\begin{itemize}
+
+\item{Injecting request}: all nodes have status FREE, except for a
 “bootstrap node” with status BOOTSTRAP, set by some signal from an
@@
 
-Flooding: Each node receiving a STARTING\_SEGMENT\_REQUEST,
+\item{Flooding}: Each node receiving a STARTING\_SEGMENT\_REQUEST,
 if not (visited/tvisited),  forwards  to the attached links that are
@@
 
-setup of the starting-segment: when this STARTING\_SEGMENT\_REQUEST packet reaches
+\item{setup of the starting-segment}: when this STARTING\_SEGMENT\_REQUEST packet reaches
 the starting node (from a different link, of course), the starting
@@
 
-failure: [TODO] should we handle this case ? i.e.
+failure: TODO should we handle this case ? i.e.
 marking as terminal ?
+
+\end{itemize}
 
@@
 
-Injecting request: A node in the ASSIGNED state can initiate a search for a
+\begin{itemize}
+\item{Injecting request}: A node in the ASSIGNED state can initiate a search for a
 segment, by sending a SEGMENT\_REQUEST with an across one of its free
@@
 
-setup of the segment: The find process is successfull when a visited
+\item{setup of the segment}: The find process is successfull when a visited
 node receives the SEGMENT\_REQUEST packet. Then, a SEGMENT\_CONFIRM is
@@
 only if no more free links can be explored starting from them.
+\end{itemize}
 
@@
 
-\section{Node behaviour Model}
-Assumption: when discussing of
-visited/tvisited nodes, we are assuming with an id corresponding to
-the same subnet. Nodes involved in other subnet processes can simply
-ignore these packets. (TBD: formalize more clearly in which cases
-inter-subnet packets must be ignored, probably this happens most of
-the times, but in some cases, e.g. when a terminal node is found, some
-kind of communication packets are needed in order to crearte the
-bridge between two subnets.)
+\section{Detailed Node behaviour Model}
+
+%TODO: add state machines
+
+% TODO: fix, move elsewhere or delete
+Assumption: when discussing of visited/tvisited nodes, we are assuming
+with an id corresponding to the same subnet. Nodes involved in other
+subnet processes can simply ignore these packets. (TBD: formalize more
+clearly in which cases inter-subnet packets must be ignored, probably
+this happens most of the times, but in some cases, e.g. when a
+terminal node is found, some kind of communication packets are needed
+in order to crearte the bridge between two subnets.)
 
@@
 
-When a node receives a STARTING\_SEGMENT\_REQUEST, with id = X,  there are the following cases:
+When a node receives a STARTING\_SEGMENT\_REQUEST, with id = X,  there
+are the following cases:
 
-The node is visited with the same segID = x, that is it was the
+\begin{itemize}
+\item The node is visited with the same segID = x, that is it was the
 initiator of the request (set visited by definition): a first segment
@@
 
-The node is tvisited, with the same segID of the packet: due
+\item The node is tvisited, with the same segID of the packet: due
 the flooding mechanism, another starting segment packet reached a node
@@
 
-The node it's visited, with different id in the packet.
+\item The node it's visited, with different id in the packet.
 CHECK:  it is not the initiator of the starting segment request, but
@@
 
+\end{itemize}
+
 \subsection{Receiving a SEGMENT\_REQUEST}
@@
 
-The node is visited (and belongs to the same subnet): a segment was
+\begin{itemize}
+\item The node is visited (and belongs to the same subnet): a segment was
 found and it should be confirmed sending back a SEGMENT\_CONFIRM
@@
 
-The node is tvisited: it should discard the packet sending
+\item The node is tvisited: it should discard the packet sending
 back a SEGMENT\_CANCEL
 
-The node it's not visited/tvisited and has free
+\item The node it's not visited/tvisited and has free
 links: it marks itself as tvisited and forwards the SEGMENT\_REQUEST
@@
 
-CHECK: the difference between confirming a STARTING\_SEGMENT\_REQUEST
+\item NOTD: the difference between confirming a STARTING\_SEGMENT\_REQUEST
 and confirming a SEGMENT\_REQUEST is that in the first case the node
@@
 starting node. 
+\end{itemize}
 
@@
 
-\section{Nanoxim and simulation environment}
+\section{Simulation environment and Results}
 
-The simulator Nanoxim is a SystemC tool based on a minimal version of
-the Noxim Network-on-Chip simulator. It's not a "faster noxim", but a
-drastically reduced noxim the will be able to simulate a random
-network on nodes. Current differences from noxim:
+In this section we will test the proposed DiSR approach to demonstrate
+its effectiveness from two different perspectives:
+\begin{itemize}
+\item Against the serial segment based approach SR, to evaluate if 
+its qualities are still preserved in the new nano-scale distributed scenario
+\item Against other topology agnostic approaches based on spanning
+trees and broadcasting, to measure how DiSR performs in discovering
+the network structure 
+\end{itemize}
 
-removed all routing algorithms that depend on a topology (only XY left
-to test meshes) removed flit management, nodes only exchange packets
-(e.g. no wormhole)
+\subsection{Nanoxim tool}
 
-Future features:
-
-topology agnostic able to test different nano-oriented communication
-mechanism
+In order to quantitatively and qualitatively the proposed approach a
+specific simulation environment has been developed, resulting in
+the open source and freely available project called Nanoxim~\cite{}.
+Nanoxim is a SystemC tool based on a almost rewritten
+version of the Noxim Network-on-Chip simulator~\cite{}. While some
+complex features have been removed (e.g. wormhole, congestion/topology
+aware routing and selection strategies) new features specifically
+taylored for nanoscale scenario were introduced, like the ability to simulate a random
+network, the implementation of the DiSR to obtain the segment topology
+and the support for defective links simulation.
 
 %------------------------------------------------------------------------------
+\subsection{Experimental setup}
+The following setup parameters have been taken into account when
+performing the DiSR simulation:
+\begin{itemize}
+\item {S}: Size of the network, intended as number of nodes (from X to Y)
+\item {P}: probabily of failure, that is the probability that each
+link is disconnected or not present 
+\item {B}: bootstrap node, the node used from upper (e.g. microscale)
+layer to inject the DiSR process
 
-\section{Experiments}
-% - Graphs, tables
-% - comparison against other approaches
-...
+Other optimisation parameters which demostrated to improve the DiSR
+results have been fixed to some good values, but are not subject to
+further investigation in this initial work, where the focus is not the
+optimal set of segments, but just demostrating the working mechaninsm
+of the approach. These are:
+\begin{itemize}
+\item{cycle\_links}: 
+\item{bootstrap\_immunity}:
+\item{bootstrap\_timeout}:
+\end{itemize}
+
+\subsection{Evaluation Metrics and Results}
+\label{sec:results}
+
+The following metrics have been adopted:
+\begin{itemize}
+\item{Node coverage}: this is the fraction of non-defective node elements that
+are assigned to a segment. In the ideal case, all the non defective
+nodes should be assigned, so this metric is useful to show how some
+disconnected node regions can negativaly impact on the whole DiSR
+effectiveness.
+\item{Broadcast latency}: this measures how the time required to complete the
+segment assignment scale for increasing network sizes and defect rates
+\item{Connectivity}:
+\item{Bootstrap node effect}: this evaluates the impact of the chosen
+bootstrap node on the node coverage.
+\end{itemize}
+
+Further, to evaluate how DiSR compares against the centralized segment
+based algorithm, the following metrics have been adopted:
+\begin{itemize}
+\item {Average Path Lenght}:
+\item {Average Link Weight}:
+\item {Number of Segments}:
+\end{itemize}
+
+Node (Broadcast) Coverage(vs \%defective links) with different sizes:
+30x30, 50x50, 80x80, 100x100, ideal. Bigger networks show similar
+trends
+
+Broadcast latency (vs sqrt(N), with different \% defectived
+links. TODO: calcolare ordine di grandezza atteso O(N), rete NxN
+Effect of bootstrap node
+
+Qualcosa tipo Broadcast Tree properties (sez.  5.4)
+
+\section{Implementation Issues}
+\label{sec:implementation}
+Althought a completed and detailed floorplan of the node is not the
+focus of this work, in this section we want to give a basic idea of
+which are the main elements required to support this kind of
+architecture and the DiSR approach. There are three main classes of
+node elements:
+\begin{itemize}
+\item Node-specific: components (such ALUs, memories) that are
+strictly related to the node functionality and role inside a given
+networks: e.g. is that a computation or storage node ?
+\item Node communication:  these are elements (such as transceivers,
+buffers) required to the node to communicate with its neighbors,
+indepentently from node functionality and DiSR implementation
+\item DiSR-specific: all the hardware, such as control logic and
+configuration, required to implement the proposed DiSR approach.
+\end{itemize}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.50\textwidth]{pictures/router_schematic.eps}
+  \caption{Schematic of the router. Top-level view (top). Block
+  implementing the routing algorithm (middle). Block implementing the
+  TODO
+  }
+  \label{fig:schematic}
+\end{figure}
+
+Figure~\ref{fig:schematic} shows the schematic of a router for
+a mesh based network topology implementing DiSR . As shown, the top level scheme of the router consists of a
+set of ...
+
+The content of a routing algorithm block is more accurately shown in
+the central part of Figure~\ref{fig:schematic}. Each routing algorithm
+block consists of ...
+
+Let us now look inside the \emph{DiSR} block. A formal description of
+DiSRalgorithm has already been given in Figure~\ref{alg:disr}, thus we
+will focus on the architectural elements to be implemented.
+
+\end{itemize}
 

### 2013-05-13 trunk/PAPER/paper.tex
- completed intro draft

@@
 
-\title{A Distribuited Segment-based Approach for Topology-agnostic Nano Networks Routing}
+\title{A Distributed Segment-based Approach for Topology-agnostic
+Routing in Self-Assembled Nano Networks}
 
 \author{
-  \IEEEauthorblockN{a} \IEEEauthorblockA{Affiliation3\\ email3} \and
-  \IEEEauthorblockN{b} \IEEEauthorblockA{Affiliation2\\ email2} }
+%  \IEEEauthorblockN{a} \IEEEauthorblockA{Affiliation3\\ email3} \and
+%  \IEEEauthorblockN{b} \IEEEauthorblockA{Affiliation2\\ email2}
+
+  }
 
@@
 \begin{abstract}
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph topology
-as input, and without the need for a centralized algorithm which
-perform a setup phase.  Our contribution is not find the
-best segment choice, but to show something that could really work in
-such complex, irregular and large sized topologies.
+In this paper we present DiSR, a first effort for a distributed
+segment-based approach to routing in a nano-scale topology agnostic
+scenario based on DNA self-assembly. The main aim is exploiting the
+already-proven qualities of segment-based routing without neither requiring a
+topology graph as input, nor needing a centralized algorithm to
+discover and configure network paths. Our contribution is not to find
+the optimal segments choice, but introducing an approach that can
+actually work in such complex, irregular and large sized topologies.
+After describing the conceptual elements and the execution model of DiSR,
+we use the opensource Nanoxim tool to show some quantitive
+comparisons to demonstrate how DiSR still maintains segment-based
+qualities while avoiding a centralized tree-based broadcasting and the
+usage of expensive virtual channels mechanisms.
 \end{abstract}
@@
 %------------------------------------------------------------------------------
+%\IEEEkeywords{...}
 
-\IEEEkeywords{...}
+\begin{IEEEkeywords}
+Nanotechnology, DNA, Self-assembly, Routing
+\end{IEEEkeywords}
+%------------------------------------------------------------------------------
+
+\section{Introduction and Motivation}
+Exploring long term alternatives to the CMOS technology is gaining
+more and more revelance as the scaling trend of such devices keeps
+introducing new challenges. Power density, defect tolerance, testing
+costs and wire delays are only a few of the many critical aspects
+involved~\cite{}. While software parallelism and multicore
+approaches~\cite{TODO} are partially mitigating the impact on
+performances, it is likely that the growing computing demand will
+eventually need even more radical architectural modifications and new
+paradigms in order to address the computer design issues of the next
+decades.
+
+In the last years, Self-assembled nanoscale architectures~\cite{TOOD}
+are emerging as a promising technology due their tera/peta scale of
+integration, defect tolerance tolerance and huge potential computing
+capabilities~\cite{TODO}. These technologies are certainly still at
+their early stage of development, however different laboratory demos and
+prof-of-concepts architectures have been presented~\cite{TODO}.
+The main idea behind this approach is to exploit the physical regularity and
+stabiliy of DNA sequences in order to create a scaffold onto which
+nano-devices (e.g. nanowires and nanotubes~\cite{TODO}) can be
+attached. This can be achieved by designing approapriate complementary DNA tags for
+each terminal to be placed, so that a nano device will be attached
+only where its own DNA tag matches a complementary tag on the DNA grid
+scaffold.
+
+A detailed description of the chemical properties involved is far beyond
+the scope of this paper (see also~\cite{}), so we will focus on the
+three main challenges that this new fabrication process introduces in Computer Design. These are:
+limited node resources, large scale randomness and high defect rates.
+The first aspect is directly related to the use of complementary DNA
+tags in order to place circuit components. In a traditional CMOS
+process the complexity is introduced using a photolithography mask, so that larger
+circuits require larger masks; instead in self-assembly this
+complexity is achieved increasing the number of unique DNA tags, since
+more tags means having more control on component placement. Ideally,
+by specifying a single different tag for each nano transistor terminal,
+we could exactly choose where each component would be placed. But the
+number of DNA symbols forming the DNA sequence is limited (sequence
+of 4 nucleobases G,A,T,C) and so creating many different tags (of a
+given lenght) would mean make them more similar to
+each other, increasing the probability of incorrect/partial matching. Then,
+limiting the need of many unique tags means putting a limited
+complexity in each node. Large scale randomness and defect rates are
+the other two fundaments conditions of self-assembled technology:
+if, as seen, some complexity can be introduced by designing tag sequences in the
+DNA grid of each node, we have no control of where each of these grids
+will be placed on the whole network. Further, as a consequence, we cannot guarantee other
+typical properties of regular networks, like nodes being connected to 4
+neighbors, having a determined orientation and so on.
+
+These aspects of a DNA-self assembly process lead to some important
+architectural implications to be addressed when approaching to the
+Computer Design: computational model must be founded on a distributed
+network of small computing and storage nodes, randomly placed and
+interconnected.  Proof-of-concept of such kind of computational model
+can be found in~\cite{}, where instructions and data operands travel
+on packets and routed using a topology-agnostic strategy that avoids
+deadlock, since no particular regularity can be assumed in such
+network. Altought we will assume a similar scenario as background, it
+is important to underline that the proposed approach to defect
+tolerance is more general and not stricly dependent on any of these
+architectures.
+
+Different works have been presented addressing the problem of topology
+agnostic routing, such as~\cite{}. They show interesting
+performances, but the requirement for virtual channels resources 
+to avoid deadlock makes them not suitable for the particular DNA self
+assembled networks we are focusing on. 
+Other topology independent algorithms don't use virtual channels to
+achieve deadlock freedom but turn proibitions, like~\cite{}.
+Up-Down~\cite{} which exploits the creation of a spanning tree of the
+topology, then placing bidirectional restrictions by avoiding a packet
+to traverse the same link in both up and down directions. Should be
+noticed that the hierarchical nature of this approach can lead to uneven traffic
+distribution, with many packets traversing upper links (near to the
+root), however this is still acceptable for classical wide area networks
+topologies with a limited number of nodes.  The~\cite{} mitigates this
+issue, but the whole restriction placement is still prefixed,
+striclty depending on the particular root selected, thus making these
+approaches not scalable for the TODO(thousands) nodes scenario of DNA
+self assembled technology.
+
+In~\cite{} authors present SR, a new approach the solves this limitation by
+allowing turn restrictions to be placed locally, independently from
+other restrictions. The whole network is partitioned into segments, and a
+single bidirectional turn restrictions can be chosen for each
+segment in order to guarantee deadlock freedom and connected networks.
+This \emph{locality independence} property makes SR scalable for large-sized networks,
+but its topology independency still requires the knowledge of the
+network topology graph in order to find the segments. The small scale control,
+random placement and connectivity features discussed above
+make it impossible having such topology graph knowledge, as well as
+trying to execute a centralized algorithm that uses the graph description as input.
+
+The contribution presented in this paper is a first effort for a
+Distributed Segment-based routing in nanoscale DNA based networks
+(DiSR). The presented approach is not intended to discover the "optimal"
+segment choice (ideally reachable with the knowledge of the whole
+topology graph) but just to demonstrate a concrete model that can fit
+into such complex, irregular and large sized topologies.
 
 %------------------------------------------------------------------------------
-
-\section{Introduction}
-Exploring long term alternatives to the CMOS technology is gaining
-more and more revelance as the scaling trend of such devices continue
-to introduce new challenges. Power density, defect tolerance, testing
-costs and many other issues are only partially mitigated by multicore
-approaches~\ref{TODO}, but growing computing requirements will eventually need
-even more radical architectural modifications and new paradigms in
-future computer design.
-
-DNA-self assembled nanoscale architectures~\ref{TOOD} are emerging as promising
-technology due its tera/peta scale of integration, defect tolerance
-tolerance and potential computing capabilities~\ref{TODO}. This
-technologies is certainly still at its early stage of development,
-however different laboratory demos and prof-of-concepts architectures
-have been presented~\ref{TODO}.
-
-The main idea beyond this approach is to exploit the regularity and
-stabiliy of DNA sequences in orders to create grids onto which
-nano-devices (e.g. nanowires and CNFET~\ref{TODO}) can be attached by
-designing approapriate DNA tags. A detailed description of the
-chemical properties involved is beyond the scope of this paper, since
-we focus of the main challenges that this new fabrication process
-introduces in Computer Design. These are:
-\begin{itemize}
-\item small scale control of placement and connectivity
-\item large scal randomness
-\item high defect rates
-\end{itemize}
-
-This aspects of a DNA-self assembled process leads some architectural implications
-when approaching to the Computer Design. Architecture must consist of
-a distributed network of small computing and storage nodes, randomly
-connected. Data will be travelling on packets that must be routed
-using a topology-agnostic strategy, since no particular regularity can
-be assumed in such network.
-
-Different works have been presented addressing the problem of topology
-agnostic routing, such as~\ref{}. Althougth they show interesting
-performances, the requirement for virtual channels resources makes
-them not suitable for the particular DNA self assembled we are
-focusing on.
-
-Other topology independent algorithms not using virtual channels are
-based on turn proibition. Up-Down~\ref{} exploits the creation of a
-spanning tree of the topology, then placing bidirectional restrictions
-by avoiding a packet to traverse the same link in both up and down
-directions. The hierarchical nature of this approach can lead to
-uneven traffic distribution, with many packets traversing upper links
-(near to the root). The~\ref{} mitigates this issue, making this
-approach acceptable in small networks, however the whole restriction
-placement is still fixed, depending on the particular root selected,
-making these approaches certainly not scalable for the thousands nodes
-scenario of DNA self assembled technology.
-
-In~\ref{} authors present SR, a new approach the solves this limitation by
-allowing turn restriction to be placed locally, independently from
-other restriction. The whole network is partitioned in segments, and a
-single bidirectional turn restrictions can be chosen for each
-segment in order to guarantee deadlock freedom and connected networks.
-This locality independence makes SR scalable for large-sized networks,
-but its topology independency still requires the knowledge of the
-topology graph in order to find the segments. The small scale control,
-random placement and connectivity features discussed in the previous
-section makes having such a topology graph impossible in DNA
-self assembly, together with any other similar centralized algorithm using
-graph description as input.
-
-The contribution presented in this paper is a first effort for a
-distribuited segment-based routing in DNA based networks (DiSR).  This
-paper is not intended to show discover the "optimal" segment choice, ideally
-reachable with a whole graph topology knowledge, but to demonstrate something could
-really fit such complex, irregular and large sized topologies.
-
-%------------------------------------------------------------------------------
-\section{DiSR main elements}
+\section{DiSR main concepts}
 %------------------------------------------------------------------------------
@@
 
-\section{DiSR Execution Model}
+\end{itemize}
+
+\section{Draft of DiSR Execution Model}
 
@@
 
-The node is visited with the same segID = x, that is it was the
+\begin{itemize}
+\item The node is visited with the same segID = x, that is it was the
 initiator of the request (set visited by definition): a first segment
@@
 
-\section{Nanoxim and simulation environment}
+\section{Simulation environment and Results}
 
-The simulator Nanoxim is a SystemC tool based on a minimal version of
-the Noxim Network-on-Chip simulator. It's not a "faster noxim", but a
-drastically reduced noxim the will be able to simulate a random
-network on nodes. Current differences from noxim:
+In this section we will test the proposed DiSR approach to demonstrate
+its effectiveness from two different perspectives:
+\begin{itemize}
+\item Against the serial segment based approach SR, to evaluate if 
+its qualities are still preserved in the new nano-scale distributed scenario
+\item Against other topology agnostic approaches based on spanning
+trees and broadcasting, to measure how DiSR performs in discovering
+the network structure 
+\end{itemize}
 
-removed all routing algorithms that depend on a topology (only XY left
-to test meshes) removed flit management, nodes only exchange packets
-(e.g. no wormhole)
+\subsection{Nanoxim tool}
 
-Future features:
-
-topology agnostic able to test different nano-oriented communication
-mechanism
+In order to quantitatively and qualitatively the proposed approach a
+specific simulation environment has been developed, resulting in
+the open source and freely available project called Nanoxim~\cite{}.
+Nanoxim is a SystemC tool based on a almost rewritten
+version of the Noxim Network-on-Chip simulator~\cite{}. While some
+complex features have been removed (e.g. wormhole, congestion/topology
+aware routing and selection strategies) new features specifically
+taylored for nanoscale scenario were introduced, like the ability to simulate a random
+network, the implementation of the DiSR to obtain the segment topology
+and the support for defective links simulation.
 
 %------------------------------------------------------------------------------
+\subsection{Experimental setup}
+The following setup parameters have been taken into account when
+performing the DiSR simulation:
+\begin{itemize}
+\item {S}: Size of the network, intended as number of nodes (from X to Y)
+\item {P}: probabily of failure, that is the probability that each
+link is disconnected or not present 
+\item {B}: bootstrap node, the node used from upper (e.g. microscale)
+layer to inject the DiSR process
 
-\section{Experiments}
-% Absolute results:
-% Comparison results:
+Other optimisation parameters which demostrated to improve the DiSR
+results have been fixed to some good values, but are not subject to
+further investigation in this initial work, where the focus is not the
+optimal set of segments, but just demostrating the working mechaninsm
+of the approach. These are:
+\begin{itemize}
+\item{cycle\_links}: 
+\item{bootstrap\_immunity}:
+\item{bootstrap\_timeout}:
+\end{itemize}
+
+\subsection{Evaluation Metrics and Results}
+\label{sec:results}
+
+The following metrics have been adopted:
+\begin{itemize}
+\item{Node coverage}: this is the fraction of non-defective node elements that
+are assigned to a segment. In the ideal case, all the non defective
+nodes should be assigned, so this metric is useful to show how some
+disconnected node regions can negativaly impact on the whole DiSR
+effectiveness.
+\item{Broadcast latency}: this measures how the time required to complete the
+segment assignment scale for increasing network sizes and defect rates
+\item{Connectivity}:
+\item{Bootstrap node effect}: this evaluates the impact of the chosen
+bootstrap node on the node coverage.
+\end{itemize}
+
+Further, to evaluate how DiSR compares against the centralized segment
+based algorithm, the following metrics have been adopted:
+\begin{itemize}
+\item {Average Path Lenght}:
+\item {Average Link Weight}:
+\item {Number of Segments}:
+\end{itemize}
+
+Node (Broadcast) Coverage(vs \%defective links) with different sizes:
+30x30, 50x50, 80x80, 100x100, ideal. Bigger networks show similar
+trends
+
+Broadcast latency (vs sqrt(N), with different \% defectived
+links. TODO: calcolare ordine di grandezza atteso O(N), rete NxN
+Effect of bootstrap node
+
+Qualcosa tipo Broadcast Tree properties (sez.  5.4)
+
+\section{Implementation Issues}
+\label{sec:implementation}
+Althought a completed and detailed floorplan of the node is not the
+focus of this work, in this section we want to give a basic idea of
+which are the main elements required to support this kind of
+architecture and the DiSR approach. There are three main classes of
+node elements:
+\begin{itemize}
+\item Node-specific: components (such ALUs, memories) that are
+strictly related to the node functionality and role inside a given
+networks: e.g. is that a computation or storage node ?
+\item Node communication:  these are elements (such as transceivers,
+buffers) required to the node to communicate with its neighbors,
+indepentently from node functionality and DiSR implementation
+\item DiSR-specific: all the hardware, such as control logic and
+configuration, required to implement the proposed DiSR approach.
+\end{itemize}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.50\textwidth]{pictures/router_schematic.eps}
+  \caption{Schematic of the router. Top-level view (top). Block
+  implementing the routing algorithm (middle). Block implementing the
+  TODO
+  }
+  \label{fig:schematic}
+\end{figure}
+
+Figure~\ref{fig:schematic} shows the schematic of a router for
+a mesh based network topology implementing DiSR . As shown, the top level scheme of the router consists of a
+set of ...
+
+The content of a routing algorithm block is more accurately shown in
+the central part of Figure~\ref{fig:schematic}. Each routing algorithm
+block consists of ...
+
+Let us now look inside the \emph{DiSR} block. A formal description of
+DiSRalgorithm has already been given in Figure~\ref{alg:disr}, thus we
+will focus on the architectural elements to be implemented.
+
+\end{itemize}
 

### 2013-06-10 trunk/PAPER/paper.tex
Misc typos and fixes

--- 2013-04-15 trunk/PAPER/paper.tex
@@
 
-\title{A Distribuited Segment-based Approach for Topology-agnostic Nano Networks Routing}
+\title{A Distributed Segment-based Approach for Topology-agnostic
+Routing in Self-Assembled Nano Networks}
 
-\author{
-  \IEEEauthorblockN{Vincenzo Catania} \IEEEauthorblockA{Affiliation3\\ email3}} \and
-  \IEEEauthorblockN{Davide Patti} \IEEEauthorblockA{Affiliation2\\ email2}
+\author{Vincenzo~Catania, Salvatore Monteleone~and~Davide~Patti% 
+\thanks{The authors are with the Dipartimento di Ingegneria
+Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
+(email: \{vcatania,dpatti\}@dieei.unict.it).}}
 
@@
 \begin{abstract}
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized setup
-phase.
+In this paper we present DiSR, a first effort for a distributed
+segment-based approach to routing in a nano-scale, topology agnostic
+scenario based on DNA self-assembly. The main aim is exploiting the
+already-proven qualities of segment-based routing without neither requiring a
+topology graph as input, nor needing a centralized algorithm to
+configure network paths. 
+After introducing the conceptual elements and the execution model of
+DiSR, we developed the opensource Nanoxim tool to show how the proposed
+approach can be used to discover irregular network topology while
+estabilishing network segments. Finally, we perfomed some quantitive
+comparisons to demonstrate how DiSR compares against classic
+segment-based algorithm and other broadcasting based approaches.  The
+results shows how DiSR still preserves some important features
+(connectivity, defect tolerance, scalability)  while avoiding centralized
+tree-based broadcasting and resource hungry solutions such as virtual
+channels and hardware redundancy.
 \end{abstract}
@@
 %------------------------------------------------------------------------------
+%\IEEEkeywords{...}
 
-\IEEEkeywords{...}
-
+\begin{IEEEkeywords}
+Nanotechnology, DNA, Self-assembly, Routing
+\end{IEEEkeywords}
 %------------------------------------------------------------------------------
 
-\section{Introduction}
-Exploring long term alternatives to the CMOS technology is gaining
-more and more revelance as the scaling trend of such devices continue
-to introduce new challenges. Power density, defect tolerance, testing
-costs and many other issues are only partially mitigated by multicore
-approaches~\ref{TODO}, but growing computing requirements will eventually need
-even more radical architectural modifications and new paradigms in
-future computer design.
-
-DNA-self assembled nanoscale architectures~\ref{TOOD} are emerging as promising
-technology due its tera/peta scale of integration, defect tolerance
-tolerance and potential computing capabilities~\ref{TODO}. This
-technologies is certainly still at its early stage of development,
-however different laboratory demos and prof-of-concepts architectures
-have been presented~\ref{TODO}.
-
-The main idea beyond this approach is to exploit the regularity and
-stabiliy of DNA sequences in orders to create grids onto which
-nano-devices (e.g. nanowires and CNFET~\ref{TODO}) can be attached by
-designing approapriate DNA tags. A detailed description of the
-chemical properties involved is beyond the scope of this paper, since
-we focus of the main challenges that this new fabrication process
-introduces in Computer Design. These are:
-\begin{itemize}
-\item small scale control of placement and connectivity
-\item large scal randomness
-\item high defect rates
-\end{itemize}
-
-This aspects of a DNA-self assembled process leads some architectural implications
-when approaching to the Computer Design. Architecture must consist of
-a distributed network of small computing and storage nodes, randomly
-connected. Data will be travelling on packets that must be routed
-using a topology-agnostic strategy, since no particular regularity can
-be assumed in such network.
-
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized algorithm
-which perform a \"segment setup\" phase.
-
-% irregular topology -> how to route ?
-
-%------------------------------------------------------------------------------
-
-\section{Related Work}
-% - Up/Down etc..
-% - SR is ok (topology independent) but requires the knowledge of the
-% topology graph -> impossible in DNA self assembly
-% - Our contribution: a distribuited approach for a segment-based
-%   routing. Not the "optimal" SR, just a SR "that works" in such
-%   complex irregular topologies where a graph could never be
-%   available.
-...
-Different architectures using nano-scale devices have been presented.A
-general purpose architecture for Self-Assembled Nano-Electronics has
-been presented to demostrate the potential of
-DNA-selfassembly~\ref{TODO}
-
-%------------------------------------------------------------------------------
-
-\section{Proposal}
-% - Draft of the DiSR idea
-% - how it should work
-...
-%------------------------------------------------------------------------------
-
-\section{DiSR execution model}
-% - what is executed at each node, which information is required
-...
-
-%------------------------------------------------------------------------------
-
-\section{Nanoxim and simulation environment}
-% - Architecture of the nanoxim simulator
-% - how simulations were conducted
-...
-
-%------------------------------------------------------------------------------
-
-\section{Experiments}
-% - Graphs, tables
-% - comparison against other approaches
-...
+\input{introduction.tex}
+\input{disr.tex}
+\input{simulation.tex}
+\input{implementation.tex}
 

### 2013-07-10 trunk/PAPER/disr.tex
- splitted

%------------------------------------------------------------------------------
\section{Preliminary concepts}
%------------------------------------------------------------------------------
\label{sec:disr_concepts}

\subsection{Basic Idea}
The main concept behind of the original SR approach is the
\emph{Segment}: a Segment is basically a path of consecutive node
and links. 
The idea is to partition the network in a set of disjoint segments, and then
placing a turn restriction within each segment. It has been proved~\cite{}
that such a set of turn prohibitions guarantees dealock freedom and
while preserving connectivity of the network.

Describing the execution phases of DiSR from a top level point-of-view
is basically similar to the classic SR approach. This can be useful to
give an initial idea of the approach, however, some important
differences should be pointed out:(i) no centralized entity is
globally aware of what is going on. The status of the DiSR execution
is collectively distributed among the nodes (ii) no defect map and/or
topology graph is available as input, thus, the topology has to be
discovered \emph{while} segments are created (iii) at the end of the
execution, no segment list is created: Each node is only aware of
belonging to some segment, ignoring the presence of other nodes
in the same segment and even the presence of other segments in the
network.

Roughly speaking, the execution of can be described as the execution
of the following phases:
\begin{itemize}
\item Injection of the DiSR process from upper layer into a bootstrap
node
\item Bootstrap node broadcast to create first segment of the subnet
\item Parallel requests creating other segments
\item Turn proibition in each confirmed segment
\item Draining of remaining packet due timeouts
\end{itemize}

Once again, it should be pointed out that nowhere in the network there
is such a global vision of these exection phases. A more detailed
description of the exection model at each node is discussed in the
next section.

\subsection{Packets types Required}

The DiSR approach works with a distributed mechanism which is build
upon an exchange of small setup packets containing very simple data:
\begin{itemize}
\item{src\_id}: the id of the node that initially originated the
packet
\item{packet\_type}: this encodes that particular meaning of the
packet in the whole DiSR process.
\end{itemize}

As regards packet\_type, we can have the following control packets:
\begin{itemize}
\item{\texttt{STARTING\_SEGMENT\_REQUEST}}: Injected by the bootstrap
node to when searching for the first segment. 
\item{\texttt{STARTING\_SEGMENT\_CONFIRM}}: used when estabilishing
the starting  segment. 
\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (not the
first)
\item{\texttt{SEGMENT\_CONFIRM}}: used to estabilish a segment. 
\item{\texttt{SEGMENT\_CANCEL}}: used to cancel the process of searching a segment along a
specific link.
\end{itemize}

\subsection{DiSR Data Structures}

We distinct among two different kind of data stored at each node:
local environment data (LED) and dynamic behaviour status (DBS).

The LED is like a snapshot of the DiSR algorithm at each node,
consisting in the following variables:

\begin{itemize}
\item{segID}:a value used to specify a segment id for the node. Depending on
the values of \emph{visited}/\emph{tvisited} variables below, a node can be
assigned to or candidate for a specific segment id.  
\item{\emph{visited}}: a boolean value. If \emph{visited} is true
and segID is different from NULL, then segID specifies the segment id
to which the node has been assigne. Note that a value different from NULL does not
necessarily mean the node has been assigned to some segment (e.g. when
searching starting segment is set \emph{visited} by default even if not yet
assigned to any segment). 
\item{\emph{tvisited}}: a boolean value. If
true, the node is being considered as candidate for a segment, and the
segID value specifies the segment id for which the node it's candidate. 
\item{\emph{link\_visited[]}}: an array
of values representing information about attached links, that is, the
segID of the segment owning each link. When NULL, the corresponding link has not yet been
assigned.
%TDB: do we need to introduce some value for the
%“bridge” status ? (e.g. a node connecting the terminal node of a
%subnet with the starting one of another) 
\item{\emph{link\_tvisited[]}}: an array of
values representing information about attached links, that is, the segID of
the segment for which the link is candidate. When NULL, the link is
currently not \emph{tvisited}.  
\item{\emph{starting}}: boolean, true if the node it's a
starting node from which the whole process was initiated.
\end{itemize}

In addition to the LED variables described above, further information
should be stored in order to capture the current dynamic behaviour of
the node. This is represented by the dynamic behaviour status (DBS)
variable, which strictly depends on the LED data and the events
occurring at the node. The DBS can have the following values:

\begin{itemize}
\item{\emph{Free}}: a node that has  not been yet considered  by the DiSR algorithm.
The node is not marked as \emph{visited}/\emph{tvisited}/terminal/starting.
\item{\emph{Boostrap}}: a node which has been explicitly set as bootstrap node from
an upper layer via. This is required because a
\texttt{STARTING\_SEGMENT\_REQUEST} packet should be injected in order to start
the whole process.
\item{\emph{ActiveSearching}}: a node from which a find process of new segments has
been started and not yet cancelled or confirmed. This happens when all
the following conditions are matched: the node is marked as \emph{visited},
that is \emph{visited} = TRUE 
TODO: segID is set to some value reflecting
the segment request sent there is a link that is being investigated by
the node, that is a tvisited\_link marked with the same id of the node 
\item{\emph{Candidate}}: a node currently candidate for belonging to some segment
with id segid, not being itself the node from which the find process
was started. The following conditions should be matched: \emph{tvisited} =
true, with segID=X different from node's id.  Two links set as
\emph{link\_tvisited} with id X. Let’s refer them as  links 'i' and 'j'. Then
link\_tvisited[i] was set = X when the find process from an adjacent
node reached the current node, while link\_tvisited[j] has been set to
X when the node itself started to investigate its free links for the
segment request with id X. Note that while investigating its attached
links, if the find process fails along path 'j', the current node can
investigate another free node 'k' if suitable.  
\item{\emph{CandidateStarting}}: same as above, but the node is currently being considered as candidate
for starting segment. Two main differences: Can confirm
\texttt{STARTING\_SEGMENT\_CONFIRM} with the same segID when receiving a normal
\texttt{SEGMENT\_REQUEST}: Overwrites its status setting it to \emph{Candidate} for the
segID frees the links previously set as \emph{tvisited} during flooding
\item{\emph{Assigned}}: a node for which the segment has been determined.  The
segment segID attribute value is set to some id X different from NULL.
The \emph{visited} value is true NOTE: an \emph{Assigned} state is a quick temporary
state, since it becomes \emph{ActiveSearching} if a not (\emph{visited}/tvisited)
link is suitable for searching new segments (see next\_visited
procedure on paper) 
\end{itemize}

\subsection{Creating the starting segment}

\begin{itemize}

\item{Injecting request}: all nodes have status \emph{Free}, except for a
“bootstrap node” with status \emph{Boostrap}, set by some signal from an
upper layer via. This bootstrap node sets itself as \emph{visited} and
changes its status to \emph{ActiveSearching}, injecting a
\texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links.

\item{Flooding}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
if not (\emph{visited}/\emph{tvisited}),  forwards it to its free links using a flooding mechanism.
Each of these links is then marked as \emph{tvisited} with the segment id
associated to the request. Note that a node that has already received a
\texttt{STARTING\_SEGMENT\_REQUEST} packet can simply ignore further packets
associated to the same request, having already contributed to the
flooding. Note also that each of these packets has a max\_segment\_hops
field to prevent packets from travelling undefinitively.

\item{Confirming the Starting Segment}: when this \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
the starting node (from a different link, of course), the starting
segment is found. Then the starting node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
packet with the same id along the link from which it received the
\texttt{STARTING\_SEGMENT\_REQUEST}. Each node do same by changing its own status
from \emph{tvisited} to \emph{visited}. So the confirmation packet is sent back from
node to node and the starting segment is created.

Note: A node knows to be \emph{tvisited} due a
\texttt{STARTING\_SEGMENT\_REQUEST}.  Then, when receiving a simple
(not starting) \texttt{SEGMENT\_REQUEST} , can simply cancel its
\emph{tvisited} status and set its links as free, because the second
request means that a starting segment has already been found a
there’s no need to keep the \emph{tvisited} status for those broadcast
status. What happens to nodes not receiving these segment request?
they simply remain \emph{tvisited} and after a timeout reset their
state as free. But they could also remain \emph{tvisited} for the
starting segment, since this doesn’t affect their behaviour for future
segment requests.

%failure: TODO should we handle this case ? i.e.  marking as terminal ?
\end{itemize}

\subsection{Finding other segments}

\begin{itemize}
\item{Injecting request}: Every node in the \emph{Assigned} status can initiate a search for a
segment, by sending a \texttt{SEGMENT\_REQUEST} across one of its free
links. Note that, since this is not the starting segment, in this case
the packet should not reach the initiator, but just another visited
node

\item{setup of the segment}: The find process is successfull when a visited
node receives the \texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
sent back along the path that originated the request.  Failing while
searching a segment: a node received a \texttt{SEGMENT\_REQUEST} packet but
matched one of the following conditions: the node is free but has no
more suitable free links (can’t forward the \texttt{SEGMENT\_REQUEST}) the node
is \emph{tvisited} candidate for another find process the request packet
exceeded the max\_segment\_hops limit.  In all these cases the node
sends back a \texttt{SEGMENT\_CANCEL} along the proper link modifying its state
to free. Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
only if no more free links can be explored starting from them.
\end{itemize}

\subsection{Intra-node vs Inter-node parallelism}
In the processes described above, we assumed that each node in the
READY\_SEARCHING state can start a find segment process by injecting a
\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when defining DiSR
should be made in order to decide whether or not the node must
actually perform this action. 
The point above is is strictly related to the general question: which
level of “parallelism” should we allow in DiSR ? The adopted approach
is that, although the nature of DiSR itself is intrinsicly parallel,
the use of parallelism makes things work in a more complex way. In
other words, DiSR is parallel when needed, but it does not exploit
parallelism as an “improving feature”. When not needed, things should
be serialized. For example: when a node is “ready searching” could
start several find segment process associated to the same segment, one
for each free link. But serializing this by investigating the free
links in order could be a simplest solution. We refer to this saying
that we avoid intra-node parallelism.  Note that while intra-node
parallelism can be avoided, trying to avoid inter-node parallelism
could be more complex than allowing the parallelism itself. Imagine
for example the effort of trying to coordinate nodes so that an unique
finding node process is actually running in the whole subnet. Thus, in
contrast to the intra-node parallelism, the inter-node parallelism is
a structural property of the DiSR algorithm and should not be avoided.
%------------------------------------------------------------------------------

\section{Detailed Node behaviour Model}

The LED variables at each node are are initially set so the node and
each of its links is set as free. The only node that makes exception
is the bootstrap node, initialized in the \emph{Bootstrap} status. All
the subsequent events happening at each node are the consequence of
its current dynamic status (DBS) and the packets received, as depicted
in the Figure~\ref{fig:status_machine}.

\label{sec:disr_detailed_model}
%TODO: add state machines

% TODO: fix, move elsewhere or delete
%Assumption: when discussing of visited/\emph{tvisited} nodes, we are assuming
%with an id corresponding to the same subnet. Nodes involved in other
%subnet processes can simply ignore these packets. (TBD: formalize more
%clearly in which cases inter-subnet packets must be ignored, probably
%this happens most of the times, but in some cases, e.g. when a
%terminal node is found, some kind of communication packets are needed
%in order to crearte the bridge between two subnets.)

\subsection{Receiving a \texttt{STARTING\_SEGMENT\_REQUEST}}

The request for the first segment of a
subnet should be managed differently since all nodes (except the starting
one) must forward the packet using a flooding mechanism. This is
necessary since the request packet must reach the starting node, which
is the only node marked as \emph{visited}. As stated elsewhere, it should
remembered that the first segment of each subnet it's  a loop that
beginning/ending on the starting node.

When a node receives a \texttt{STARTING\_SEGMENT\_REQUEST}, with SegID = X,  there
are the following cases:

\begin{itemize}
\item The node is visited with the same segID = x, that is it was the
initiator of the request (set visited by definition): a first segment
was found and should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
packet.  
\item The node is \emph{tvisited}, with the same segID of the packet: due
the flooding mechanism, another starting segment packet reached a node
which was previously marked as \emph{tvisited} from the same starting segment
search process. Since the node is \emph{tvisited} with the same id, it means
that it already accomplished in the task of propagating that kind
packets, thus can simply ignore the event thrashing the packet.  If
the node it's not visited/\emph{tvisited}: it should set itself as \emph{tvisited}
and forward the packet along its free links, using flooding. TBD: how
the status should be changed ? depend on the flooding mechanism. Note
that these links don’t include the link from which the request was
received.  
\item The node it's visited, with different id in the packet.
CHECK:  it is not the initiator of the starting segment request, but
is already assigned to some segment!? assuming again we are discussing
of nodes belonging to the same subnet, this should NOT happen, since
the only visited node of the subnet should be the initial node from
which the \texttt{STARTING\_SEGMENT\_REQUEST} originated. Note again that we are
assuming that if the the node is visited or \emph{tvisited} with the id of
another subnet can simply ignore the request.  The node it's \emph{tvisited}
but it's not the initiator of the request (different id): same as
above, if we are assuming nodes of the same subnet, this shouldn’t
happen. If the node is of another subnet, can simply ignore the event.

\end{itemize}

\subsection{Receiving a \texttt{SEGMENT\_REQUEST}}
When a node receives a \texttt{SEGMENT\_REQUEST}, the are the following cases:

\begin{itemize}
\item The node is \emph{visited} (and belongs to the same subnet): a segment was
found and it should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
packet.  
\item The node is \emph{tvisited}: it should discard the packet sending
back a \texttt{SEGMENT\_CANCEL} 
\item The node it's not \emph{visited}/\emph{tvisited} and has free
links: it marks itself as \emph{tvisited} and forwards the \texttt{SEGMENT\_REQUEST}
(one request at time) to each of its free links, according to some
ordering
\item NOTD: the difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
itself it's included in the segment , while in the second case the
receiving node DOES NOT belong to the segment found. The motivation is
that in the second case the node was already marked as \emph{visited} because
of being assigned to some segment found before, while in the
starting-segment case, by definition, the first segment of a subnet
begins with the starting node, which is marked as \emph{visited} by the SR
algorithm when searching for the first (starting) segment. Remember
that the first segment of a subnet is a loop beginning with the
starting node. 
\end{itemize}

\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}
When received, if the node status is \emph{tvisited} with a segID corresponding to the one indicated in
the packet, the node learns to belong to the segment associated to the
id. Further, it should forward this packet to the link where the
original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
can learn the segment id they belong to.  LED shoud be
updated: The state of the node changes from \emph{tvisited} to \emph{visited}.  the
\emph{link\_tvisited} previously set with the segID should be invalidated the
\emph{link\_visited} variable associated to the incoming confirm should be set
as segID. Note that if the request was flooded across different links,
the \emph{link\_visited} variable associated to the other paths shouldn’t be
set.  the \emph{link\_visited} variable associated to the link from which the
request was originated should be set segID

\subsection{Receiving a \texttt{SEGMENT\_CANCEL}}
When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that searching
for a segment along that path was unsuccessful. But if the node still
has other free links to try, it should forward a \texttt{SEGMENT\_REQUEST} to
the next link (next according to some internal ordering). So a node
forwards back the \texttt{SEGMENT\_CANCEL} packet along the link that originated
the \texttt{SEGMENT\_REQUEST} packet ONLY when there are no more free links to
try. If this is the case, the node modifies its status from \emph{tvisited}
to free and fordwards the \texttt{SEGMENT\_CANCEL} packet to the link from which
the request was received. The process stops when the \texttt{SEGMENT\_CANCEL}
packet reach the starting node that originated the request.

TODO REPEAT!!

When a node discovers that the path that includes
the node itself is no more suitable, a \texttt{SEGMENT\_CANCEL} is sent back
across the link from which the \texttt{SEGMENT\_REQUEST} was received.  Possible
reasons for that: The node it’s already candidate for another segment
The node it’s free but can’t find a free link (according the
cyclelinks timeout) The node it’s \emph{tvisited} for the same request id,
previously forwarded that request along some free direction, but now
it’s receiving a a cancel request and has no more free links

### 2013-07-10 trunk/PAPER/implementation.tex
- splitted

--- 2013-04-15 PAPER/paper.tex
@@
-\documentclass[conference]{IEEEtran}
-\IEEEoverridecommandlockouts
-
-%------------------------------------------------------------------------------
-
-\usepackage{cite}
-\usepackage{amsmath}
-\usepackage{amsfonts}
-\usepackage{amssymb}
-\usepackage{graphicx}
-\usepackage{url}
-\usepackage{cite}
-\usepackage{balance}
-\usepackage{float}
-\usepackage{threeparttable}
-
-\usepackage{mathptmx}
-\usepackage[scaled=.90]{helvet}
-\usepackage{courier}
-
-\usepackage{listings}
-\usepackage{listings}
-\lstset{
-   language=C,
-   basicstyle=\small,
-   keywordstyle=\bfseries,
-   identifierstyle=\ttfamily,
-   stringstyle=\ttfamily,
-   numbers=left,
-   numberstyle=\tiny,
-   stepnumber=1,
-   numbersep=-5pt,
-   showstringspaces=false
-%   frame=single %trbl%
-}
-
-\usepackage[normalem]{ulem}
-
-%------------------------------------------------------------------------------
-
-\newcommand{\etal}{\emph{et al.}}
-\newcommand{\eg}{\emph{e.g.}}
-\newcommand{\ie}{\emph{i.e.}}
-\newcommand{\etc}{\emph{etc.}}
-
-%------------------------------------------------------------------------------
-
-\begin{document}
-
-%------------------------------------------------------------------------------
-
-\title{A Distribuited Segment-based Approach for Topology-agnostic Nano Networks Routing}
-
-\author{
-  \IEEEauthorblockN{Vincenzo Catania} \IEEEauthorblockA{Affiliation3\\ email3}} \and
-  \IEEEauthorblockN{Davide Patti} \IEEEauthorblockA{Affiliation2\\ email2}
-
-\maketitle
-
-%------------------------------------------------------------------------------
-
-\begin{abstract}
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized setup
-phase.
-\end{abstract}
-
-%------------------------------------------------------------------------------
-
-\IEEEkeywords{...}
-
-%------------------------------------------------------------------------------
-
-\section{Introduction}
-Exploring long term alternatives to the CMOS technology is gaining
-more and more revelance as the scaling trend of such devices continue
-to introduce new challenges. Power density, defect tolerance, testing
-costs and many other issues are only partially mitigated by multicore
-approaches~\ref{TODO}, but growing computing requirements will eventually need
-even more radical architectural modifications and new paradigms in
-future computer design.
-
-DNA-self assembled nanoscale architectures~\ref{TOOD} are emerging as promising
-technology due its tera/peta scale of integration, defect tolerance
-tolerance and potential computing capabilities~\ref{TODO}. This
-technologies is certainly still at its early stage of development,
-however different laboratory demos and prof-of-concepts architectures
-have been presented~\ref{TODO}.
-
-The main idea beyond this approach is to exploit the regularity and
-stabiliy of DNA sequences in orders to create grids onto which
-nano-devices (e.g. nanowires and CNFET~\ref{TODO}) can be attached by
-designing approapriate DNA tags. A detailed description of the
-chemical properties involved is beyond the scope of this paper, since
-we focus of the main challenges that this new fabrication process
-introduces in Computer Design. These are:
+\section{Implementation Issues}
+\label{sec:implementation}
+Althought a completed and detailed floorplan of the node is not the
+focus of this work, in this section we want to give a basic idea of
+which are the main elements required to support this kind of
+architecture and the DiSR approach. There are three main classes of
+node elements:
 \begin{itemize}
-\item small scale control of placement and connectivity
-\item large scal randomness
-\item high defect rates
+\item Node-specific: components (such ALUs, memories) that are
+strictly related to the node functionality and role inside a given
+networks: e.g. is that a computation or storage node ?
+\item Node communication:  these are elements (such as transceivers,
+buffers) required to the node to communicate with its neighbors,
+indepentently from node functionality and DiSR implementation
+\item DiSR-specific: all the hardware, such as control logic and
+configuration, required to implement the proposed DiSR approach.
 \end{itemize}
 
-This aspects of a DNA-self assembled process leads some architectural implications
-when approaching to the Computer Design. Architecture must consist of
-a distributed network of small computing and storage nodes, randomly
-connected. Data will be travelling on packets that must be routed
-using a topology-agnostic strategy, since no particular regularity can
-be assumed in such network.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.50\textwidth]{pictures/router_schematic.eps}
+  \caption{Schematic of the router. Top-level view (top). Block
+  implementing the routing algorithm (middle). Block implementing the
+  TODO
+  }
+  \label{fig:schematic}
+\end{figure}
 
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized algorithm
-which perform a \"segment setup\" phase.
+Figure~\ref{fig:schematic} shows the schematic of a router for
+a mesh based network topology implementing DiSR . As shown, the top level scheme of the router consists of a
+set of ...
 
-% irregular topology -> how to route ?
+The content of a routing algorithm block is more accurately shown in
+the central part of Figure~\ref{fig:schematic}. Each routing algorithm
+block consists of ...
 
-%------------------------------------------------------------------------------
-
-\section{Related Work}
-% - Up/Down etc..
-% - SR is ok (topology independent) but requires the knowledge of the
-% topology graph -> impossible in DNA self assembly
-% - Our contribution: a distribuited approach for a segment-based
-%   routing. Not the "optimal" SR, just a SR "that works" in such
-%   complex irregular topologies where a graph could never be
-%   available.
-...
-Different architectures using nano-scale devices have been presented.A
-general purpose architecture for Self-Assembled Nano-Electronics has
-been presented to demostrate the potential of
-DNA-selfassembly~\ref{TODO}
-
-%------------------------------------------------------------------------------
-
-\section{Proposal}
-% - Draft of the DiSR idea
-% - how it should work
-...
-%------------------------------------------------------------------------------
-
-\section{Detailed DiSR model}
-We distinct among two different kind of data stored at each node:
-local environment data (LED) and dynamic behaviour status (DBS).
-
-\subsection{Local Environment Data (LED)}
-
-The LED is like a snapshot of the DiSR algorithm on each node,
-consisting in the following variables:
-
-segID:a value used to specify a segment id for the node. Depending on
-the values of visited/tvisited variables below, the node can be
-assigned to or candidate for a specific segment id.
-
-visited : a boolean value corresponding to the visited status. If visited is true
-and segID is different from NULL, then segID specifies the segment id
-the node belongs to. Note that a value different from NULL does not
-necessarily mean the node has been assigned to some segment (e.g. when
-searching starting segment is set visited by default even if not yet
-assigned to any segment). When false, the node is not yet visited.
-
-tvisited: a boolean value corresponding to the tvisited status. If
-true, the node is being considered as candidate for a segment, and the
-segID specifies the segment id for which the node it's candidate. When
-false, the node is not currently tvisited.
-
-link_visited[]: an array
-of values representing information about attached links, that is, the
-ID of the segment owning each link. When NULL, a link has not yet been
-marked as visited. TDB: do we need to introduce some value for the
-“bridge” status ? (e.g. a node connecting the terminal node of a
-subnet with the starting one of another)
-
-link_tvisited[]: an array of
-values representing information about attached links, e.g. the ID of
-the segment for which the link is candidate. When NULL, the link is
-currently not tvisited.  starting: boolean, true if the node it's a
-starting node for the subnet terminal:boolean, true if the node it's a
-terminal node for the subnet.  subnet:the subnet the node belongs to.
-If NULL, none.
-
-\subsection{Dynamic Behaviour Status (DBS)}
-In addition to the LED variables
-described above, further information should be stored in order to
-capture the current dynamic behaviour of the node. This is represented
-by the dynamic behaviour status (DBS) variable, which strictly depends
-on the LED data and the events occurring at the node. The DBS can have
-the following values:
-
-FREE: a node that has  not been yet considered  by the DiSR algorithm.
-The node is not marked as visited/tvisited/terminal/starting.
-
-BOOTSTRAP: a node which has been explicitly set as bootstrap node from
-an upper layer via. This is required because a
-
-STARTING_SEGMENT_REQUEST packet should be injected in order to start
-the whole process.
-
-ACTIVE_SEARCHING: a node from which a find process of new segments has
-been started and not yet cancelled or confirmed. This happens when all
-the following conditions are matched: the node is marked as visited,
-that is visited = TRUE
-
-CHECK: segID is set to some value reflecting
-the segment request sent there is a link that is being investigated by
-the node, that is a tvisited_link marked with the same id of the node
-
-CANDIDATE: a node currently candidate for belonging to some segment
-with id segid, not being itself the node from which the find process
-was started. The following conditions should be matched: tvisited =
-true, with segID=X different from node's id.  Two links set as
-link_tvisited with id X. Let’s refer them as  links 'i' and 'j'. Then
-link_tvisited[i] was set = X when the find process from an adjacent
-node reached the current node, while link_tvisited[j] has been set to
-X when the node itself started to investigate its free links for the
-segment request with id X. Note that while investigating its attached
-links, if the find process fails along path 'j', the current node can
-investigate another free node 'k' if suitable.
-
-CANDIDATE_STARTING:
-same as above, but the node is currently being considered as candidate
-for starting segment. Two main differences: Can confirm
-STARTING_SEGMENT_CONFIRM with the same segID when receiving a normal
-SEGMENT_REQUEST: Overwrites its status setting it to CANDIDATE for the
-segID frees the links previously set as tvisited during flooding
-
-ASSIGNED: a node for which the segment has been determined.  The
-segment segID attribute value is set to some id X different from NULL.
-The visited value is true NOTE: an ASSIGNED state is a quick temporary
-state, since it becomes ACTIVE_SEARCHING if a not (visited/tvisited)
-link is suitable for searching new segments (see next_visited
-procedure on paper)
-
-PROCESSED: a node which should take no other
-action, since all its links have been investigated.
-
-\subsection{Packets types Required}
-TODO: a lot of description is already present elsewhere, make this
-section smaller...
-
-SEGMENT_REQUEST: used to search candidates for a segment (not the
-first of the subnet, managed separately as a starting segment).
-
-SEGMENT_CONFIRM: used to create a segment. When received, if the node
-status is tvisited with a segID corresponding to the one indicated in
-the packet, the node learns to belong to the segment associated to the
-id. Further, it should forward this packet to the link where the
-original SEGMENT_REQUEST packet came from, so that all candidate nodes
-can learn the segment id they belong to. The following LED shoud be
-updated: The state of the node changes from tvisited to visited.  the
-link_tvisited previously set with the segID should be invalidated the
-link_visited variable associated to the incoming confirm should be set
-as segID. Note that if the request was flooded across different links,
-the link_visited variable associated to the other paths shouldn’t be
-set.  the link_visited variable associated to the link from which the
-request was originated should be set segID
-
-STARTING_SEGMENT_REQUEST: the request for the first segment of a
-subnet should be differentiated since all nodes (except the starting
-one) must forward the packet using a flooding mechanism. This is
-necessary since the request packet must reach the starting node, which
-is the only node marked as visited. As stated elsewhere, it should
-remembered that the first segment of each subnet it's  a loop that
-beginning/ending on the starting node.
-
-SEGMENT_CANCEL: used when the process of searching a segment along a
-certain path fails. When a node discovers that the path that includes
-the node itself is no more suitable, a SEGMENT_CANCEL is sent back
-across the link from which the SEGMENT_REQUEST was received.  Possible
-reasons for that: The node it’s already candidate for another segment
-The node it’s free but can’t find a free link (according the
-cyclelinks timeout) The node it’s tvisited for the same request id,
-previously forwarded that request along some free direction, but now
-it’s receiving a a cancel request and has no more free links
-
-\section{DiSR Execution Phases}
-
-\subsection{Creating the starting segment}
-
-Injecting request: all nodes have status FREE, except for a
-“bootstrap node” with status BOOTSTRAP, set by some signal from an
-upper layer via. This bootstrap node sets itself as “visited” and
-changes its status to ACTIVE_SEARCHING, sending a
-STARTING_SEGMENT_REQUEST across one of its not (visited/tvisited)
-links and.
-
-Flooding: Each node receiving a STARTING_SEGMENT_REQUEST,
-if not (visited/tvisited),  forwards  to the attached links that are
-not already marked as visited/tvisited using a flooding mechanism.
-Each of these links is then marked as tvisited with the segment id
-associated to the packet. Note that a node that has already received a
-STARTING_SEGMENT_REQUEST packet can simply ignore further packets
-associated to the same request, since has already contributed to the
-flooding. Note also that each of these packets has a max_segment_hops
-field to prevent packets from travelling undefinitively.
-
-setup of the starting-segment: when this STARTING_SEGMENT_REQUEST packet reaches
-the starting node (from a different link, of course), the starting
-segment is found. Then the starting node sends back a SEGMENT_CONFIRM
-packet with the same id along the link from which it received the
-STARTING_SEGMENT_REQUEST. Each node do same by changing its own status
-from tvisited to visited. So the confirmation packet is sent back from
-node to node and the starting segment is created.
-
-Note: A node knows to be tvisited due a  STARTING_SEGMENT_REQUEST.
-Then, when receiving a SEGMENT_REQUEST for other (not the starting)
-segment, simply knows to cancel the tvisited status of the node and
-its links, since if a segment arrived it means that a starting segment
-has already been found a there’s no need to keep the tvisited status
-for those broadcast status. What happens to nodes not receiving these
-segment request? they simply remain tvisited and after a timeout reset
-their state as free. But they could also remain tvisited for the
-starting segment, since this doesn’t affect their behaviour for future
-segment requests.
-
-failure: [TODO] should we handle this case ? i.e.
-marking as terminal ?
-
-\subsection{Finding other segments}
-
-Injecting request: A node in the ASSIGNED state can initiate a search for a
-segment, by sending a SEGMENT_REQUEST with an across one of its free
-links. Note that, since this is not the starting segment, in this case
-the packet should not reach the initiator, but just another visited
-node
-
-setup of the segment: The find process is successfull when a visited
-node receives the SEGMENT_REQUEST packet. Then, a SEGMENT_CONFIRM is
-sent back along the path that originated the request.  Failing while
-searching a segment: a node received a SEGMENT_REQUEST packet but
-matched one of the following conditions: the node is free but has no
-more suitable free links (can’t forward the SEGMENT_REQUEST) the node
-is tvisited candidate for another find process the request packet
-exceeded the max_segment_hops limit.  In all these cases the node
-sends back a SEGMENT_CANCEL along the proper link modifying its state
-to free. Each of the subsequent nodes will forward this SEGMENT_CANCEL
-only if no more free links can be explored starting from them.
-
-\subsection{Intra-node vs Inter-node parallelism}
-In the processes described above, we assumed that each node in the
-READY_SEARCHING state can start a find segment process by injecting a
-SEGMENT_REQUEST. However, a more accurate decision when defining DiSR
-should be made in order to decide whether or not the node must
-actually perform this action. 
-The point above is is strictly related to the general question: which
-level of “parallelism” should we allow in DiSR ? The adopted approach
-is that, although the nature of DiSR itself is intrinsicly parallel,
-the use of parallelism makes things work in a more complex way. In
-other words, DiSR is parallel when needed, but it does not exploit
-parallelism as an “improving feature”. When not needed, things should
-be serialized. For example: when a node is “ready searching” could
-start several find segment process associated to the same segment, one
-for each free link. But serializing this by investigating the free
-links in order could be a simplest solution. We refer to this saying
-that we avoid intra-node parallelism.  Note that while intra-node
-parallelism can be avoided, trying to avoid inter-node parallelism
-could be more complex than allowing the parallelism itself. Imagine
-for example the effort of trying to coordinate nodes so that an unique
-finding node process is actually running in the whole subnet. Thus, in
-contrast to the intra-node parallelism, the inter-node parallelism is
-a structural property of the DiSR algorithm and should not be avoided.
-%------------------------------------------------------------------------------
-
-\section{Node behaviour Model}
-Assumption: when discussing of
-visited/tvisited nodes, we are assuming with an id corresponding to
-the same subnet. Nodes involved in other subnet processes can simply
-ignore these packets. (TBD: formalize more clearly in which cases
-inter-subnet packets must be ignored, probably this happens most of
-the times, but in some cases, e.g. when a terminal node is found, some
-kind of communication packets are needed in order to crearte the
-bridge between two subnets.)
-
-\subsection{Receiving a STARTING_SEGMENT_REQUEST}
-
-When a node receives a STARTING_SEGMENT_REQUEST, with id = X,  there are the following cases:
-
-The node is visited with the same segID = x, that is it was the
-initiator of the request (set visited by definition): a first segment
-was found and should be confirmed sending back a SEGMENT_CONFIRM
-packet.
-
-The node is tvisited, with the same segID of the packet: due
-the flooding mechanism, another starting segment packet reached a node
-which was previously marked as tvisited from the same starting segment
-search process. Since the node is tvisited with the same id, it means
-that it already accomplished in the task of propagating that kind
-packets, thus can simply ignore the event thrashing the packet.  If
-the node it's not visited/tvisited: it should set itself as tvisited
-and forward the packet along its free links, using flooding. TBD: how
-the status should be changed ? depend on the flooding mechanism. Note
-that these links don’t include the link from which the request was
-received.
-
-The node it's visited, with different id in the packet.
-CHECK:  it is not the initiator of the starting segment request, but
-is already assigned to some segment!? assuming again we are discussing
-of nodes belonging to the same subnet, this should NOT happen, since
-the only visited node of the subnet should be the initial node from
-which the STARTING_SEGMENT_REQUEST originated. Note again that we are
-assuming that if the the node is visited or tvisited with the id of
-another subnet can simply ignore the request.  The node it's tvisited
-but it's not the initiator of the request (different id): same as
-above, if we are assuming nodes of the same subnet, this shouldn’t
-happen. If the node is of another subnet, can simply ignore the event.
-
-\subsection{Receiving a SEGMENT_REQUEST}
-When a node receives a SEGMENT_REQUEST, the are the following cases:
-
-The node is visited (and belongs to the same subnet): a segment was
-found and it should be confirmed sending back a SEGMENT_CONFIRM
-packet.
-
-The node is tvisited: it should discard the packet sending
-back a SEGMENT_CANCEL
-
-The node it's not visited/tvisited and has free
-links: it marks itself as tvisited and forwards the SEGMENT_REQUEST
-(one request at time) to each of its free links, according to some
-ordering
-
-CHECK: the difference between confirming a STARTING_SEGMENT_REQUEST
-and confirming a SEGMENT_REQUEST is that in the first case the node
-itself it's included in the segment , while in the second case the
-receiving node DOES NOT belong to the segment found. The motivation is
-that in the second case the node was already marked as visited because
-of being assigned to some segment found before, while in the
-starting-segment case, by definition, the first segment of a subnet
-begins with the starting node, which is marked as visited by the SR
-algorithm when searching for the first (starting) segment. Remember
-that the first segment of a subnet is a loop beginning with the
-starting node.
-
-\subsection{Receiving a SEGMENT_CANCEL}
-When a node receives a SEGMENT_CANCEL packet it means that searching
-for a segment along that path was unsuccessful. But if the node still
-has other free links to try, it should forward a SEGMENT_REQUEST to
-the next link (next according to some internal ordering). So a node
-forwards back the SEGMENT_CANCEL packet along the link that originated
-the SEGMENT_REQUEST packet ONLY when there are no more free links to
-try. If this is the case, the node modifies its status from tvisited
-to free and fordwards the SEGMENT_CANCEL packet to the link from which
-the request was received. The process stops when the SEGMENT_CANCEL
-packet reach the starting node that originated the request.
-
-\section{Nanoxim and simulation environment}
-% - Architecture of the nanoxim simulator
-% - how simulations were conducted
-...
-
-%------------------------------------------------------------------------------
-
-\section{Experiments}
-% - Graphs, tables
-% - comparison against other approaches
-...
-
-%------------------------------------------------------------------------------
-
-\section{Conclusions}
-...
-
-%------------------------------------------------------------------------------
-
-\balance
-
-\bibliographystyle{IEEEtran} 
-\bibliography{bibliography}
-
-%------------------------------------------------------------------------------
-
-\end{document}
+Let us now look inside the \emph{DiSR} block. A formal description of
+DiSRalgorithm has already been given in Figure~\ref{alg:disr}, thus we
+will focus on the architectural elements to be implemented.

### 2013-07-10 trunk/PAPER/introduction.tex
- splitted

\section{Introduction and Motivation}

Exploring long term alternatives to the CMOS technology is gaining
more and more revelance as the scaling trend of such devices keeps
introducing new challenges. Power density, defect tolerance, testing
costs and wire delays are only a few of the many critical aspects
involved~\cite{}. While software parallelism and multicore
approaches~\cite{TODO} are partially mitigating the impact of such
constraints on performances, it is likely that the growing computing demand will
eventually need even more radical architectural modifications and new
paradigms in order to address the Computer Design challenges of the next
decades.

In the last years, Self-assembled nanoscale architectures~\cite{TOOD}
are emerging as a promising technology due their tera/peta scale of
integration, defect tolerance tolerance and huge potential computing
capabilities~\cite{TODO}. These technologies are certainly still at
their early stage of development, however different laboratory demos and
prof-of-concepts architectures have been presented~\cite{TODO}.
The main idea behind this approach is to exploit the physical regularity and
stabiliy of DNA structures in order to create a scaffold onto which
nano-devices (e.g. nanowires and nanotubes~\cite{TODO}) can be
attached. This can be achieved by designing approapriate complementary DNA tags for
each terminal to be placed, so that a nano device will be attached
only where its own DNA tag matches a complementary tag on the DNA grid
scaffold (see figure~\ref{fig:dna_tag}.
\begin{figure}
  \centering
    \includegraphics[width=0.40\textwidth]{pictures/dna_tag.ps}
  \caption{DNA tag matching}
  \label{fig:dna_tag}
\end{figure}
A detailed description of the chemical properties involved is far
beyond the scope of this paper (see also~\cite{}), so we will focus on
the three main challenges that this new fabrication process introduces
in Computer Design: (i)limited node complexity, (ii) large scale
randomness and (iii) high defect rates.

The \emph{limited node complexity} aspect is directly
related to the use of complementary DNA tags in order to place circuit
components. In a traditional CMOS process the complexity is introduced
using a photolithography mask, so that larger (more complex) circuits
only require larger masks; conversely, self-assembly achieves
complexity by increasing the number of unique DNA tags, since more
different tags means having more control on component placement. Ideally, by specifying a single
and unique tag for each nano transistor terminal, we could exactly
choose where each component would be placed. But the number of DNA
symbols forming the DNA sequence is limited (sequence of 4 nucleobases
G,A,T,C) and so creating many different tags (of a given lenght) would
mean make them more similar to each other, increasing the probability
of incorrect/partial matching. To avoid this problem we should limit
the number of unique tags, thus limiting the complexity at each node.

\emph{Large scale randomness} and \emph{high defect rates} are the other two fundaments
conditions of self-assembled technology: if, as seen, some complexity
can be introduced by designing tag sequences in the DNA grid of each
node, we have no control of where each of these grids will be placed
on the whole network. Further, as a consequence, we cannot guarantee
other typical properties of regular networks, like nodes being
connected to 4 neighbors, having a determined orientation and so on.

These aspects of a DNA-self assembly process lead to some important
architectural implications to be addressed when approaching to the
Computer Design: computational model must be founded on a distributed
network of small computing and storage nodes, randomly placed and
interconnected (see figure~\ref{fig:nana}).  Proof-of-concept of such kind of computational model
can be found in~\cite{}, where instructions and data operands travel
on packets and routed using a topology-agnostic strategy that avoids
deadlock, since no particular regularity can be assumed in such
network. Altought we will assume a similar scenario as background, it
is important to underline that the proposed approach to defect
tolerance is more general and not stricly dependent on any of these
architectures.
\begin{figure}
  \centering
    \includegraphics[width=0.40\textwidth]{pictures/nana.ps}
  \caption{Irregular architecture of computing and storage elements}
  \label{fig:nana}
\end{figure}

Several works~\cite{} have been presented addressing the problem of topology
agnostic routing. While they show interesting
performances, the requirement for virtual channels resources 
to avoid deadlock makes them not suitable for the specific DNA self
assembled networks we are assuming as background.
Other topology independent algorithms~\cite{} don't use virtual channels to
achieve deadlock freedom, but turn proibitions. However,
the centralized nature of these algorithms still makes it necessary to
provide a topology graph as input to generate a working set
of proibitions and routing tables.
Up-Down~\cite{} exploits the creation of a spanning tree of the
topology, then placing bidirectional restrictions by avoiding a packet
to traverse the same link in both up and down directions.
While the hierarchical nature of this approach can lead to uneven traffic
distribution, with many packets traversing upper links (near to the
root), this is quite acceptable in classical wide area networks
topologies with a limited number of nodes. Other approaches~\cite{} mitigate this
issue, but the set of turn restrictions is still prefixed,
striclty depending on the particular tree root selected, thus making these
approaches not scalable for the TODO(thousands) nodes scenario of DNA
self assembled technology.

Other solutions~\cite{} try to approach the issue of irregular
topologies by limiting the number and location of missing links. This
restriction is clearly unacceptable given the hight-defect rates of
DNA self-assembled networks scenario. For the same reason, we also
avoid considering solutions based on hardware-redundancy to
dynamically recover defects as in~\cite{}.

In~\cite{} authors present SR, an approach the solves these
limitations by allowing turn restrictions to be placed locally,
independently from other restrictions. The whole network is
partitioned into segments, and a each bidirectional turn
restriction can be freely chosen within a segment in order to guarantee
deadlock freedom and connected networks. This \emph{locality
independence} property, together with no requirement of any particular tree/root
choice, would make it the best choice for the given scenario;
however, its topology independency still requires the knowledge of the
whole network graph in order to find the segments.

The contribution presented in this paper is a first effort for a
Distributed Segment-based routing in nanoscale DNA based networks
(DiSR). Given the particular scenario assumed as background, is essential
avoiding non-scalable or resource hungry solutions such as
centralized node algorithms, tree-based approaches, virtual channels
or other expensive hardware implementations. While maintaining similar
properties to segment-based routing, the DiSR approach is not intended
to discover the "optimal" segment choice (ideally reachable with the
knowledge of the topology graph) but just to demonstrate a concrete
model that can fit into such complex, irregular and large sized
topologies.

The paper is organized as follows: in Section~\ref{sec:disr_concepts}
we introduce the main elements of the DiSR approach, describing  
a draft of the DiSR model in Section~\ref{sec:disr_model}
together with execution model details in Section~\ref{sec:disr_detaled_model}.
Finally, simulations are carried out with the opensource tool Nanoxim
to demostrate how DiSR preserves some of the main segment-based
properties and how compares to the tree-based approaches.

### 2013-07-10 PAPER/simulation.tex
- splitted

\section{Simulation environment}

In this section we will test the proposed DiSR approach to demonstrate
its effectiveness from two different perspectives:
\begin{itemize}
\item Against the centralized segment based approach (SR), to evaluate
if and how its known properties are still preserved in the new nano-scale distributed scenario
\item Against topology agnostic approaches based on spanning
trees and broadcasting, to measure how DiSR performs in discovering
the network structure 
\end{itemize}

\subsection{Nanoxim tool}

In order to quantitatively and qualitatively evaluate the proposed approach a
specific simulation environment has been developed, resulting in
the open source and freely available project called Nanoxim~\cite{}.
Nanoxim is a SystemC tool based on a almost rewritten
version of the Noxim Network-on-Chip simulator~\cite{}. While some
complex features have been removed (e.g. wormhole, congestion/topology
aware routing and selection strategies) new features specifically
taylored for nanoscale scenario were introduced, e.g. the ability to simulate a random
network, the implementation of the DiSR to obtain the segment topology
and the support for defective links and nodes.

%------------------------------------------------------------------------------
\subsection{Experimental setup}
The following parameters have been taken into account when
performing the DiSR simulation:
\begin{itemize}
\item {S}: Size of the network, intended as number of nodes, on a
range from 10x10 to 100x100 sized networks. 
\item {\% defective links}: the probability that each link is
disconnected or not present, from 0 the amount that yelds
no more segments.
\item {\% defective nodes}: the probability that a node is not
working, thus having all its attached links not useful for DiSR setup.
Same range as defective links parameter.
\item {Bootstrap node}: the node used from upper layer (e.g. microscale)
to inject the DiSR process. When not explicitly investigating the
impact of each single bootstrap choice, a set representative regions have been
considered, i.e. the central part of the network and the edge corners
\end{itemize}

The show the results, the following evaluation metrics have been adopted:
\begin{itemize}
\item{Node coverage}: this is the fraction of nodes that
are assigned to a segment. In the ideal case, all the non defective
nodes should be assigned, so this metric is useful to show how some
disconnected node regions can negativaly impact on the whole DiSR
effectiveness.
\item{Broadcast latency}: this measures how the time required to complete the
segment assignment scale for increasing network sizes and defect rates
\item{Bootstrap node effect}: this evaluates the impact of the chosen
bootstrap node on the node coverage.
\end{itemize}

Further, to evaluate how DiSR compares against the centralized segment
based algorithm, the following metrics have been adopted:
\begin{itemize}
\item {Average Path Lenght}:
\item {Average Link Weight}:
\item {Unidirectional restrictions:}
\item {Number of Segments}:
\end{itemize}

Since the distribution of defects and thus the resulting topology is randomly
generated, a set of simulations with different seeds has been run
for each system configuration. We found that TODO repetitions are
required in order to obtain statistically significant results.

\subsection{Other optimisations}
Some optimisation parameters, which demostrated to improve the DiSR
results have been fixed to some good values, but are not subject to
further investigation; once again the focus here is not the
optimal set of segments, but just demostrating a working approach. 
These are optimisations are:
\begin{itemize}
\item{cycle\_links}: max number of retries across the set of links of
each node. While searching for a free link due an incoming request,
the same request is cancelled after a given number of tries. This
gives to preceding node change to test a different paths. Default is set to 1.
\item{bootstrap\_timeout}: number of time units that a bootstrap node
should wait before assuming that a livelock in the starting segment
process has occurred. In the worst case, we can imagine that longest
path required is the one returning to the bootstrap node after having
travelled across all the links. So, althought this is just an extreme
situation, a good upper limit can be safely be set to NxN.
\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
setup process, a bootstrap node should not have defective links.
Enabling this optimisation, a bootstrap node is immune to defects.
We may think of a pre-boostrap phase that properly selects (from upper
layer via) a bootstrap node which is tested as properly connected. We
enabled this optimisation, however empirical tests showed us that only
simulations using bootstrap nodes placed on edges would be heavily
affected, since these are nodes starting with a lower number of links,
e.g. corner nodes could only have two connected direction, so even a
defective link could prevent starting segment packet to return to
bootstrap to close the loop a create the segment.

\end{itemize}

\section{Results}
\label{sec:results}

In Figure~\ref{fig:coverage} is shown node coverage using different
network sizes and bootstrap injection points. As can be seen,
increasing the \% of defective node, TODO COMMENT...

\begin{figure*}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_boot27_Xdefect_Ycoverage.eps} & 
    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_boot127_Xdefect_Ycoverage.eps} \\
    (a) & (b)
  \end{tabular}
  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
  \label{fig:coverage}
\end{figure*}

Figure~\ref{fig:bootstrap} shows the effect of bootstrap node position
on node coverage, for different defect rates. TODO COMMENT.

\begin{figure}
  \centering
  \begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_nodefect_Xbootstrap_Ycoverage.eps} & 
    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_nodefect_Xbootstrap_Ycoverage.eps} \\
    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_defect01_Xbootstrap_Ycoverage.eps} & 
    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_defect01_Xbootstrap_Ycoverage.eps} \\
    (a) & (b)
  \end{tabular}
  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
  \label{fig:bootstrap}
\end{figure}

Next, Figure~\ref{fig:latency_size} shows latency as function of
network size, with different defect rates, while Figure~\ref{fig:latency_defective}
shows the same latency when different bootstrap nodes are
considered.... TODO COMMENT

TODO: something like Broadcast Tree properties (sez.  5.4)

### 2013-07-16 trunk/PAPER/introduction.tex
- splitted intro and related works

@@
 costs and wire delays are only a few of the many critical aspects
-involved~\cite{}. While software parallelism and multicore
-approaches~\cite{TODO} are partially mitigating the impact of such
+involved~\cite{itrs12}. While software parallelism and multicore
+approaches~\cite{TODO1} are partially mitigating the impact of such
 constraints on performances, it is likely that the growing computing demand will
@@
 
-In the last years, Self-assembled nanoscale architectures~\cite{TOOD}
+In the last years, Self-assembled nanoscale architectures~\cite{TODO2}
 are emerging as a promising technology due their tera/peta scale of
 integration, defect tolerance tolerance and huge potential computing
-capabilities~\cite{TODO}. These technologies are certainly still at
+capabilities. These technologies are certainly still at
 their early stage of development, however different laboratory demos and
-prof-of-concepts architectures have been presented~\cite{TODO}.
+prof-of-concepts architectures have been presented~\cite{TODO3}.
 The main idea behind this approach is to exploit the physical regularity and
 stabiliy of DNA structures in order to create a scaffold onto which
-nano-devices (e.g. nanowires and nanotubes~\cite{TODO}) can be
+nano-devices (e.g. nanowires and nanotubes~\cite{TODO4}) can be
 attached. This can be achieved by designing approapriate complementary DNA tags for
@@
   \centering
-    \includegraphics[width=0.40\textwidth]{pictures/dna_tag.ps}
+    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps}
   \caption{DNA tag matching}
@@
 A detailed description of the chemical properties involved is far
-beyond the scope of this paper (see also~\cite{}), so we will focus on
+beyond the scope of this paper (see also~\cite{TODO5}), so we will focus on
 the three main challenges that this new fabrication process introduces
@@
 interconnected (see figure~\ref{fig:nana}).  Proof-of-concept of such kind of computational model
-can be found in~\cite{}, where instructions and data operands travel
+can be found in~\cite{TODO6}, where instructions and data operands travel
 on packets and routed using a topology-agnostic strategy that avoids
 deadlock, since no particular regularity can be assumed in such
-network. Altought we will assume a similar scenario as background, it
-is important to underline that the proposed approach to defect
-tolerance is more general and not stricly dependent on any of these
-architectures.
+network.
+
 \begin{figure}
   \centering
-    \includegraphics[width=0.40\textwidth]{pictures/nana.ps}
+    \includegraphics[width=0.40\textwidth]{pictures/dna1.eps}
   \caption{Irregular architecture of computing and storage elements}
@@
 
-Several works~\cite{} have been presented addressing the problem of topology
+In this paper we introduce DiSR, a first effort for a Distributed
+Segment-based Routing in large scale DNA self assembled networks.
+Given the irregular/high-defect rates scenario assumed as background, is essential
+avoiding non-scalable or resource hungry solutions such as
+centralized off-chip algorithms, tree-based approaches, virtual channels
+or expensive implementations based on hardware redundancy.
+Altought we will assume an architecture similar to the one depicted
+in~\ref{fig:nana} as background, it
+is important to underline that the proposed approach to topology
+discovery is more general and not stricly dependent on any of these
+architectures.
+
+\section{Related Works}
+
+Several works~\cite{TODO7} have been presented addressing the problem of topology
 agnostic routing. While they show interesting
@@
 assembled networks we are assuming as background.
-Other topology independent algorithms~\cite{} don't use virtual channels to
-achieve deadlock freedom, but turn proibitions. However,
-the centralized nature of these algorithms still makes it necessary to
-provide a topology graph as input to generate a working set
-of proibitions and routing tables.
-Up-Down~\cite{} exploits the creation of a spanning tree of the
+Other topology independent algorithms~\cite{TODO8} don't use virtual channels to
+achieve deadlock freedom, but turn proibitions. 
+In particular, up*/down* exploits the creation of a spanning tree of the
 topology, then placing bidirectional restrictions by avoiding a packet
@@
 root), this is quite acceptable in classical wide area networks
-topologies with a limited number of nodes. Other approaches~\cite{} mitigate this
+topologies with a limited number of nodes. Other approaches such as
+FX~\cite{TODO9} mitigate this
 issue, but the set of turn restrictions is still prefixed,
-striclty depending on the particular tree root selected, thus making these
-approaches not scalable for the TODO(thousands) nodes scenario of DNA
-self assembled technology.
-
-Other solutions~\cite{} try to approach the issue of irregular
-topologies by limiting the number and location of missing links. This
+striclty depending on the particular tree root selected. 
+Other solutions try to approach the issue of irregular
+topologies by limiting the number~\cite{TODO10} or the
+location~\cite{TODO11} of missing links. This
 restriction is clearly unacceptable given the hight-defect rates of
@@
 avoid considering solutions based on hardware-redundancy to
-dynamically recover defects as in~\cite{}.
+dynamically recover defects as in~\cite{TODO12}.
 
-In~\cite{} authors present SR, an approach the solves these
+In~\cite{mejia_ipdps06} authors present SR, an approach the solves these
 limitations by allowing turn restrictions to be placed locally,
@@
 
-The contribution presented in this paper is a first effort for a
-Distributed Segment-based routing in nanoscale DNA based networks
-(DiSR). Given the particular scenario assumed as background, is essential
-avoiding non-scalable or resource hungry solutions such as
-centralized node algorithms, tree-based approaches, virtual channels
-or other expensive hardware implementations. While maintaining similar
-properties to segment-based routing, the DiSR approach is not intended
-to discover the "optimal" segment choice (ideally reachable with the
-knowledge of the topology graph) but just to demonstrate a concrete
-model that can fit into such complex, irregular and large sized
-topologies.
+The contribution presented in this paper is to bring the advantages of
+segment-based turn prohibition without requiring any topology graph,
+external defect map or centralized algorithm execution.  While
+maintaining similar properties to segment-based routing, the DiSR
+approach is not intended to discover the "optimal" segment choice
+(ideally reachable with the knowledge of the topology graph) but just
+to demonstrate a concrete model that can fit into such complex,
+irregular and large sized topologies.
 

### 2013-08-18 PAPER/disr.tex
Added missing '}' character at the end of a 'subsection' definition

--- 2013-07-10 trunk/PAPER/disr.tex
@@
 
-\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}
+\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
 When received, if the node status is \emph{tvisited} with a segID corresponding to the one indicated in

### 2013-08-18 PAPER/introduction.tex
[NanoTask-2] Completed TODOs 2-12. Updated bibliography and introduction

--- 2013-07-16 trunk/PAPER/introduction.tex
@@
 
-In the last years, Self-assembled nanoscale architectures~\cite{TODO2}
+In the last years, Self-assembled nanoscale architectures~\cite{winfree1998, yan2003}
 are emerging as a promising technology due their tera/peta scale of
@@
 their early stage of development, however different laboratory demos and
-prof-of-concepts architectures have been presented~\cite{TODO3}.
+prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1, pistol2009}.
 The main idea behind this approach is to exploit the physical regularity and
 stabiliy of DNA structures in order to create a scaffold onto which
-nano-devices (e.g. nanowires and nanotubes~\cite{TODO4}) can be
+nano-devices (e.g. nanowires and nanotubes~\cite{bachtold2001, tans1998, cui2001}) can be
 attached. This can be achieved by designing approapriate complementary DNA tags for
@@
 A detailed description of the chemical properties involved is far
-beyond the scope of this paper (see also~\cite{TODO5}), so we will focus on
+beyond the scope of this paper (see also~\cite{braun1998, seeman1999}), so we will focus on
 the three main challenges that this new fabrication process introduces
@@
 interconnected (see figure~\ref{fig:nana}).  Proof-of-concept of such kind of computational model
-can be found in~\cite{TODO6}, where instructions and data operands travel
+can be found in~\cite{patwardhan2006_1}, where instructions and data operands travel
 on packets and routed using a topology-agnostic strategy that avoids
@@
 
-Several works~\cite{TODO7} have been presented addressing the problem of topology
+Several works~\cite{sancho2002, skeie2002, skeie2004, koibuchi2003} have been presented addressing the problem of topology
 agnostic routing. While they show interesting
@@
 assembled networks we are assuming as background.
-Other topology independent algorithms~\cite{TODO8} don't use virtual channels to
+Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} don't use virtual channels to
 achieve deadlock freedom, but turn proibitions. 
@@
 topologies with a limited number of nodes. Other approaches such as
-FX~\cite{TODO9} mitigate this
+FX~\cite{sancho2000} mitigate this
 issue, but the set of turn restrictions is still prefixed,
@@
 Other solutions try to approach the issue of irregular
-topologies by limiting the number~\cite{TODO10} or the
-location~\cite{TODO11} of missing links. This
+topologies by limiting the number~\cite{dally1994, duato1997, gomez2004, koibuchi2008} or the
+location~\cite{zhang2008, sui2000, flich2008, liu2011} of missing links. This
 restriction is clearly unacceptable given the hight-defect rates of
@@
 avoid considering solutions based on hardware-redundancy to
-dynamically recover defects as in~\cite{TODO12}.
+dynamically recover defects as in~\cite{constantinides2006, kohler2010, kim2006, park2006}.
 

### 2013-08-19 trunk/PAPER/introduction.tex
[NanoTask-2] Completed TODO 1. Updated bibliography and introduction

@@
 involved~\cite{itrs12}. While software parallelism and multicore
-approaches~\cite{TODO1} are partially mitigating the impact of such
+approaches~\cite{horowitz2004, mudge2001, powell2009} are partially mitigating the impact of such
 constraints on performances, it is likely that the growing computing demand will

### 2013-09-16 PAPER/implementation.tex
first draft of implementation

\section{Implementation Issues}
\label{sec:implementation}
Although a completed and detailed floorplan of the node is not the
focus of this work, in this section we want to give a basic idea of
which are the main elements required to support this kind of
architecture and the DiSR approach. There are three main classes of
node elements:
\begin{itemize}
\item Node-specific: components (such ALUs, memories) that are
strictly related to the node functionality and role inside a given
networks: e.g. is that a computation or storage node.
\item Node communication:  these are elements (such as transceivers,
buffers) required to the node to communicate with its neighbours,
independently from node functionality and DiSR implementation
\item DiSR-specific: all the hardware, such as control logic and
configuration, required to implement the proposed DiSR approach.
\end{itemize}

Let us now look inside the \emph{DiSR} block which implements the DiSR-specific
operation. In Fig.~\ref{fig:implementation} we shown a possible sketch of this 
last one, which mainly consist in the following building blocks:

\begin{itemize}
\item \emph{DBS block}: This block take trace of the dynamic behaviour status (DBS). 
      How discussed in the Sec.~\ref{ssec:disr_dstruct}, there are six possible status. 
      These status can be codified using only 3 bit implemented with a 3-bit register 
      and the required combinatory logic. This block is essentially designed as a state machine.
\item \emph{LED register}: Is a set of register useful as storage for local environment data (LED)
      described in Sec.~\ref{ssec:disr_dstruct}. In Fig.~\ref{fig:implementation} in their 
      respective block, are highlighted two table that represents the link\_visited 
      and link\_tvisited array. The implementation of this block is an array of register 
      (one for each direction) that can be implemented with an SRAM, in which are presents two 
      specific fields  for representing the segID (nodeID+linkID). 
\item \emph{Control circuitry}: This circuitry read the information from the incoming packet, 
      LED registers and the dynamic behaviour status (DBS block) and is able to write The LED
      informations and change the dynamic behaviour status. The output (Ctrl out), drive 
      the others communications resources (such as node transceivers) for actuating the DiSR 
      routing operation.
\end{itemize}

One of the main design challenge typical of DNA Self-Assembled systems is due to the
reduced available resource (such as the number of CNFET per node) for implementing both 
computations and routing decisions for each node. Considering the budget of $10^4$ CNFET 
for each network's node\cite{liu_jetcs} we must estimate the required resource useful 
for implementing the entire DiSR block (Fig.~\ref{fig:implementation}). For this purpose, 
after a description of the DiSR circuitry with an hardware description language (VHDL) 
we have synthesized at gate-level the required hardware. Furthermore, considering the 
specific layout of each single logic elements (such as NAND, full-adder, latch etc.), 
we are able to count the number of CNFET necessary for implementing the DiSR logic. 
With this approach we estimated 2452 CNFET for implementing that blocks which constitutes 
about the 25\% of the overall node budget. This number of resource can be certainly reducing 
applying more effort in the circuitry design of each building block exposed in this section.

\begin{figure}
  \centering
  \includegraphics[width=0.40\textwidth]{pictures/disr_imp.eps}
  \caption{\emph{DiSR} block architecture.}
 \label{fig:implementation}
\end{figure}

### 2013-09-17 PAPER/implementation.tex
other implementation values are addicted

@@
 \section{Implementation Issues}
+
 \label{sec:implementation}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.35\textwidth]{pictures/disr_imp.eps}
+  \caption{\emph{DiSR} block architecture.}
+ \label{fig:implementation}
+\end{figure}
+
 Let us now look inside the \emph{DiSR} block which implements the DiSR-specific
-operation. In Fig.~\ref{fig:implementation} we shown a possible sketch of this 
-last one, which mainly consist in the following building blocks:
+operation. In Fig.~\ref{fig:implementation} is shown a possible sketch of this 
+block, which mainly consist in the following building elements:
 
 \begin{itemize}
-\item \emph{DBS block}: This block take trace of the dynamic behaviour status (DBS). 
+\item \emph{DBS block}: It Takes trace of the dynamic behaviour status (DBS). 
       How discussed in the Sec.~\ref{ssec:disr_dstruct}, there are six possible status. 
@@
       and the required combinatory logic. This block is essentially designed as a state machine.
-\item \emph{LED register}: Is a set of register useful as storage for local environment data (LED)
-      described in Sec.~\ref{ssec:disr_dstruct}. In Fig.~\ref{fig:implementation} in their 
-      respective block, are highlighted two table that represents the link\_visited 
-      and link\_tvisited array. The implementation of this block is an array of register 
+\item \emph{LED register}: Is a set of register useful for storage the local environment data (LED)
+      described in Sec.~\ref{ssec:disr_dstruct}. In Fig.~\ref{fig:implementation}, in their 
+      respective block, are highlighted two table that represents the \emph{link\_visited[]} 
+      and \emph{link\_tvisited[]}. The implementation of this block is an array of register 
       (one for each direction) that can be implemented with an SRAM, in which are presents two 
-      specific fields  for representing the segID (nodeID+linkID). 
+      specific fields  for representing the \emph{segID} (nodeID+linkID). 
 \item \emph{Control circuitry}: This circuitry read the information from the incoming packet, 
       LED registers and the dynamic behaviour status (DBS block) and is able to write The LED
-      informations and change the dynamic behaviour status. The output (Ctrl out), drive 
+      informations and change the dynamic behaviour status. The output (Ctrl\_out), drive 
       the others communications resources (such as node transceivers) for actuating the DiSR 
@@
 
-One of the main design challenge typical of DNA Self-Assembled systems is due to the
-reduced available resource (such as the number of CNFET per node) for implementing both 
-computations and routing decisions for each node. Considering the budget of $10^4$ CNFET 
-for each network's node\cite{liu_jetcs} we must estimate the required resource useful 
-for implementing the entire DiSR block (Fig.~\ref{fig:implementation}). For this purpose, 
-after a description of the DiSR circuitry with an hardware description language (VHDL) 
-we have synthesized at gate-level the required hardware. Furthermore, considering the 
-specific layout of each single logic elements (such as NAND, full-adder, latch etc.), 
-we are able to count the number of CNFET necessary for implementing the DiSR logic. 
-With this approach we estimated 2452 CNFET for implementing that blocks which constitutes 
-about the 25\% of the overall node budget. This number of resource can be certainly reducing 
-applying more effort in the circuitry design of each building block exposed in this section.
+One of main design challenge typical of DNA Self-Assembled systems is due to the
+reduced available resource (such as the number of CNFETs per node) for implementing both 
+computations and routing decisions for each node. Thi is due to the limited feasibiliy
+of DNA grid were can be placed the single unit cells such as CNFETs and nanowires.
+For this reason, considering a budget of $10^4$ CNFETs for each network's node~\cite{liu_jetcs}
+we should estimate the required resource useful for implementing the entire DiSR block 
+(Fig.~\ref{fig:implementation}). For this purpose, after a description of the DiSR circuitry 
+with an hardware description language (VHDL) we have synthesized at gate-level the required 
+hardware. Furthermore, considering the specific layout of each single logic elements 
+(such as NAND, full-adder, latch etc.), we are able to count the number of CNFETs 
+(carbon nanotube field-effect transitor) necessary for implementing the DiSR logic. 
+In particular, in Fig.\ref{fig:imp_trend} is shown the results of synthesis in therms 
+of number of devices (CNFET) versus the number of network nodes while the network scale 
+up from $10\times10$ to $100\times100$ nodes. Can be observed tath, while the node increase 
+rapidly, the circuitry complexity wich implements the DiSR algorithm increase more slowly. 
+This means that the implemented system scale fine when the number of network's node. 
+In fact, when the number of node increase, the number of register for store the local 
+\emph{segID} for the router and the segment id within the table \emph{link\_visited[]} 
+and \emph{link\_tvisited[]} increase too. For example, the increment of the number of 
+register that implement the \emph{link\_visited[]} and \emph{link\_tvisited[]} table 
+follow the function:
+
+\begin{equation}
+  \label{eq:imp_trend}
+  N_{reg}=2\cdot N_{port} \cdot log_2(N)
+\end{equation}
+where $N_{port}$ is the number of the router's ports (4 in our cases), N is the number 
+of network's node and the therms 2 take in account that \emph{link\_visited[]} and 
+\emph{link\_tvisited[]} are two separate set o registers.
+
+%With this approach we estimated about 2000 CNFET for implementing that blocks when
+%it is implemented in a network with $100\times100$ nodes. 
+%This number of resource can be certainly reducing 
+%applying more effort in the circuitry design of each building block exposed in this section.
 
@@
   \centering
-  \includegraphics[width=0.40\textwidth]{pictures/disr_imp.eps}
+  \includegraphics[width=0.48\textwidth]{pictures/imp.eps}
   \caption{\emph{DiSR} block architecture.}
- \label{fig:implementation}
+ \label{fig:imp_trend}
 \end{figure}

### 2013-09-17 trunk/PAPER/implementation.tex
other stuff

@@
 \section{Implementation Issues}
+
 \label{sec:implementation}
-Althought a completed and detailed floorplan of the node is not the
+Although a completed and detailed floorplan of the node is not the
 focus of this work, in this section we want to give a basic idea of
@@
 strictly related to the node functionality and role inside a given
-networks: e.g. is that a computation or storage node ?
+networks: e.g. is that a computation or storage node.
 \item Node communication:  these are elements (such as transceivers,
-buffers) required to the node to communicate with its neighbors,
-indepentently from node functionality and DiSR implementation
+buffers) required to the node to communicate with its neighbours,
+independently from node functionality and DiSR implementation
 \item DiSR-specific: all the hardware, such as control logic and
@@
   \centering
-  \includegraphics[width=0.50\textwidth]{pictures/router_schematic.eps}
-  \caption{Schematic of the router. Top-level view (top). Block
-  implementing the routing algorithm (middle). Block implementing the
-  TODO
-  }
-  \label{fig:schematic}
+  \includegraphics[width=0.35\textwidth]{pictures/disr_imp.eps}
+  \caption{\emph{DiSR} block architecture.}
+ \label{fig:implementation}
 \end{figure}
 
-Figure~\ref{fig:schematic} shows the schematic of a router for
-a mesh based network topology implementing DiSR . As shown, the top level scheme of the router consists of a
-set of ...
+Let us now look inside the \emph{DiSR} block which implements the DiSR-specific
+operation. In Fig.~\ref{fig:implementation} is shown a possible sketch of this 
+block, which mainly consist in the following building elements:
 
-The content of a routing algorithm block is more accurately shown in
-the central part of Figure~\ref{fig:schematic}. Each routing algorithm
-block consists of ...
+\begin{itemize}
+\item \emph{DBS block}: It Takes trace of the dynamic behaviour status (DBS). 
+      How discussed in the Sec.~\ref{ssec:disr_dstruct}, there are six possible status. 
+      These status can be codified using only 3 bit implemented with a 3-bit register 
+      and the required combinational logic. This block is essentially designed as a state machine.
+\item \emph{LED register}: Is a set of register useful for storage the local environment data (LED)
+      described in Sec.~\ref{ssec:disr_dstruct}. In Fig.~\ref{fig:implementation}, in their 
+      respective block, are highlighted two table that represents the \emph{link\_visited[]} 
+      and \emph{link\_tvisited[]}. The implementation of this block is an array of register 
+      (one for each direction) that can be implemented with an SRAM, in which are presents two 
+      specific fields  for representing the \emph{segID} (nodeID+linkID). 
+\item \emph{Control circuitry}: This circuitry read the information from the incoming packet, 
+      LED registers and the dynamic behaviour status (DBS block) and is able to write The LED
+      informations and change the dynamic behaviour status. The output (Ctrl\_out), drive 
+      the others communications resources (such as node transceivers) for actuating the DiSR 
+      routing operation.
+\end{itemize}
 
-Let us now look inside the \emph{DiSR} block. A formal description of
-DiSRalgorithm has already been given in Figure~\ref{alg:disr}, thus we
-will focus on the architectural elements to be implemented.
+One of main design challenge typical of DNA Self-Assembled systems is due to the
+reduced available resource (such as the number of CNFETs per node) for implementing both 
+computations and routing decisions for each node. The reason, is the limited feasibility
+of DNA grids were can be placed the single unit cells such as CNFETs and nanowires.
+For this reason, considering a budget of $10^4$ CNFETs for each network's node~\cite{liu_jetcs}
+we should estimate the required resource useful for implementing the entire DiSR block 
+(Fig.~\ref{fig:implementation}). For this purpose, after a description of the DiSR circuitry 
+with an hardware description language (VHDL) we have synthesized at gate-level the required 
+hardware. Furthermore, considering the specific layout of each single logic elements 
+(such as NAND, full-adder, latch etc.), we are able to count the number of CNFETs 
+(carbon nanotube field-effect transistor) necessary for implementing the DiSR logic. 
+In particular, in Fig.\ref{fig:imp_trend} is shown the results of synthesis in therms 
+of number of devices (CNFET) versus the number of network nodes while the network scale 
+up from $10\times10$ to $100\times100$ nodes. Can be observed that, while the node have
+a squared increment, the circuitry complexity which implements the DiSR algorithm increase slowly. 
+This means that the implemented system scale fine whit the number of network's node. 
+For example, the increment of the number of register that implement the \emph{link\_visited[]} 
+and \emph{link\_tvisited[]} table follow the function:
+
+\begin{equation}
+  \label{eq:imp_trend}
+  N_{reg}=2\cdot N_{port} \cdot log_2(N)
+\end{equation}
+where $N_{port}$ is the number of the router's ports (4 in our cases), N is the number 
+of network's node and the therms 2 take in account that \emph{link\_visited[]} and 
+\emph{link\_tvisited[]} are two separate set o registers. While this number is fixed by 
+the number of network's node, the control circuitry can be optimized applying more effort 
+when designing this building block. However, observing the Fig.\ref{fig:imp_trend} can 
+be pointed out that the proposed implementation occupy only 20\% of the node budget.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.48\textwidth]{pictures/imp.eps}
+  \caption{\emph{DiSR} block architecture.}
+ \label{fig:imp_trend}
+\end{figure}

### 2013-09-17 trunk/PAPER/implementation.tex
synthesis graph name changed

@@
 \section{Implementation Issues}
+\label{sec:implementation}
 
-\label{sec:implementation}
 Although a completed and detailed floorplan of the node is not the
@@
       LED registers and the dynamic behaviour status (DBS block) and is able to write The LED
-      informations and change the dynamic behaviour status. The output (Ctrl\_out), drive 
+      informations and change the dynamic behaviour status. The output (Ctrl Out), drive 
       the others communications resources (such as node transceivers) for actuating the DiSR 
@@
 
-One of main design challenge typical of DNA Self-Assembled systems is due to the
-reduced available resource (such as the number of CNFETs per node) for implementing both 
-computations and routing decisions for each node. The reason, is the limited feasibility
-of DNA grids were can be placed the single unit cells such as CNFETs and nanowires.
+One of the main design challenge typical of DNA Self-Assembled systems is due to the
+reduced available resource  for implementing both computations and routing decisions for each node. 
+The reason is the limited feasibility of DNA grids were can be placed the single unit cells such 
+as CNFETs (carbon nanotube field-effect transistors) and nanowires.
 For this reason, considering a budget of $10^4$ CNFETs for each network's node~\cite{liu_jetcs}
-we should estimate the required resource useful for implementing the entire DiSR block 
+we should estimate the required resource for implementing the entire DiSR block 
 (Fig.~\ref{fig:implementation}). For this purpose, after a description of the DiSR circuitry 
@@
 (such as NAND, full-adder, latch etc.), we are able to count the number of CNFETs 
-(carbon nanotube field-effect transistor) necessary for implementing the DiSR logic. 
+necessary for implementing the DiSR logic. 
 In particular, in Fig.\ref{fig:imp_trend} is shown the results of synthesis in therms 
-of number of devices (CNFET) versus the number of network nodes while the network scale 
+of number of devices (CNFETs) versus the number of network nodes while the network scale 
 up from $10\times10$ to $100\times100$ nodes. Can be observed that, while the node have
@@
 when designing this building block. However, observing the Fig.\ref{fig:imp_trend} can 
-be pointed out that the proposed implementation occupy only 20\% of the node budget.
+be pointed out that the proposed implementation occupy  about 20\% of the node budget.
 
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{pictures/imp.eps}
-  \caption{\emph{DiSR} block architecture.}
+  \includegraphics[width=0.48\textwidth]{pictures/imp_rslt.eps}
+  \caption{DiSR synthesis results: N is the number of network's node.}
  \label{fig:imp_trend}

### 2013-09-17 PAPER/simulation.tex
- removed pics

@@
   \begin{tabular}{cc}
-    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_boot27_Xdefect_Ycoverage.eps} & 
-    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_boot127_Xdefect_Ycoverage.eps} \\
+    \includegraphics[width=0.40\textwidth]{pictures/set1.eps} & 
+    \includegraphics[width=0.40\textwidth]{pictures/set3.eps} \\
     (a) & (b)
@@
 
-\begin{figure}
-  \centering
-  \begin{tabular}{cc}
-    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_nodefect_Xbootstrap_Ycoverage.eps} & 
-    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_nodefect_Xbootstrap_Ycoverage.eps} \\
-    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_defect01_Xbootstrap_Ycoverage.eps} & 
-    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_defect01_Xbootstrap_Ycoverage.eps} \\
-    (a) & (b)
-  \end{tabular}
-  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
-  \label{fig:bootstrap}
-\end{figure}
+%\begin{figure}
+%  \centering
+%  \begin{tabular}{cc}
+%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_nodefect_Xbootstrap_Ycoverage.eps} & 
+%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_nodefect_Xbootstrap_Ycoverage.eps} \\
+%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_defect01_Xbootstrap_Ycoverage.eps} & 
+%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_defect01_Xbootstrap_Ycoverage.eps} \\
+%    (a) & (b)
+%  \end{tabular}
+%  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
+%  \label{fig:bootstrap}
+%\end{figure}
 

### 2013-09-17 trunk/PAPER/paper.tex
- minor updates

@@
 
-\title{A Distributed Segment-based Approach for Topology-agnostic
-Routing in Self-Assembled Nano Networks}
+\title{A First Effort for a Distributed Segment-based Approach on Topology-agnostic
+Self-Assembled Nano Networks}
 
-\author{Vincenzo~Catania, Salvatore Monteleone~and~Davide~Patti% 
+\author{Vincenzo~Catania, Andrea Mineo, Salvatore Monteleone~and~Davide~Patti% 
 \thanks{The authors are with the Dipartimento di Ingegneria
 Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
-(email: \{vcatania,dpatti\}@dieei.unict.it).}}
+(email: \{vincenzo.catania,amineo,salvatore.monteleone,davide.patti\}@dieei.unict.it).}}
 
@@
 In this paper we present DiSR, a first effort for a distributed
-segment-based approach to routing in a nano-scale, topology agnostic
+segment-based approach to routing and defect mapping in a nano-scale, topology agnostic
 scenario based on DNA self-assembly. The main aim is exploiting the
@@
 approach can be used to discover irregular network topology while
-estabilishing network segments. Finally, we perfomed some quantitive
-comparisons to demonstrate how DiSR compares against classic
-segment-based algorithm and other broadcasting based approaches.  The
-results shows how DiSR still preserves some important features
+estabilishing network segments.  The results shows how DiSR still
+preserves some important features
 (connectivity, defect tolerance, scalability)  while avoiding centralized
 tree-based broadcasting and resource hungry solutions such as virtual
-channels and hardware redundancy.
+channels and hardware redundancy. Finally, we analyzed a possible
+VHDL hardware implementation of the required control logic and storage for
+DiSR, demonstrating a relatively acceptable impact ranging from 15 to
+about 25\% of the budget of transistors available for each node.
 \end{abstract}

### 2013-09-18 trunk/PAPER/paper.tex
Added conclusion and fixed intro

@@
 In this paper we present DiSR, a first effort for a distributed
-segment-based approach to routing and defect mapping in a nano-scale, topology agnostic
-scenario based on DNA self-assembly. The main aim is exploiting the
-already-proven qualities of segment-based routing without neither requiring a
-topology graph as input, nor needing a centralized algorithm to
-configure network paths. 
-After introducing the conceptual elements and the execution model of
-DiSR, we developed the opensource Nanoxim tool to show how the proposed
-approach can be used to discover irregular network topology while
-estabilishing network segments.  The results shows how DiSR still
-preserves some important features
-(connectivity, defect tolerance, scalability)  while avoiding centralized
-tree-based broadcasting and resource hungry solutions such as virtual
-channels and hardware redundancy. Finally, we analyzed a possible
-VHDL hardware implementation of the required control logic and storage for
+segment-based approach to routing and defect mapping in a nano-scale,
+topology agnostic scenario based on DNA self-assembly. The main aim is
+exploiting the already-proven qualities of segment-based routing
+without neither requiring a topology graph as input, nor needing a
+centralized algorithm to configure network paths.  After introducing
+the conceptual elements and the execution model of DiSR, we show how
+the opensource Nanoxim platform has been used to evaluate the proposed
+approach in the process of discovering irregular network topology
+while estabilishing network segments.  Results show how DiSR still
+preserves some important properties (coverage, defect tolerance,
+scalability)  while avoiding centralized tree-based broadcasting and
+resource hungry solutions such as virtual channels and hardware
+redundancy. Finally, we analyzed a first, not yet optimised VHDL
+hardware implementation of the required control logic and storage for
 DiSR, demonstrating a relatively acceptable impact ranging from 15 to
@@
 \section{Conclusions}
-...
+In this work we presented DiSR, a initial attempt of porting a segment based
+approach to distributed self-assembled nanoscale scenario. We
+demostrated how DiSR can accomplish the aim of finding a segment
+coverage of the network withouth requiring any centralized approach
+that would request a graph topology as input. A draft hardware
+implementation has been presented to evalute the impact on the limited
+node size typical of the assumed scenario. Future works will focus on
+developing self tuning of DiSR to match a high coverage levels and the
+detailed low level hardware implementation on
+DNA grid using the appropriate nano devices models.
 

### 2013-09-18 trunk/PAPER/introduction.tex
lot of fixes

@@
 
-Exploring long term alternatives to the CMOS technology is gaining
-more and more revelance as the scaling trend of such devices keeps
-introducing new challenges. Power density, defect tolerance, testing
-costs and wire delays are only a few of the many critical aspects
-involved~\cite{itrs12}. While software parallelism and multicore
-approaches~\cite{horowitz2004, mudge2001, powell2009} are partially mitigating the impact of such
-constraints on performances, it is likely that the growing computing demand will
-eventually need even more radical architectural modifications and new
-paradigms in order to address the Computer Design challenges of the next
-decades.
+% TODO: re-enable on long paper
+%Exploring long term alternatives to the CMOS technology is gaining
+%more and more revelance as the scaling trend of such devices keeps
+%introducing new challenges. Power density, defect tolerance, testing
+%costs and wire delays are only a few of the many critical aspects
+%involved~\cite{itrs12}. While software parallelism and multicore
+%approaches~\cite{horowitz2004, mudge2001, powell2009} are partially mitigating the impact of such
+%constraints on performances, it is likely that the growing computing demand will
+%eventually need even more radical architectural modifications and new
+%paradigms in order to address the Computer Design challenges of the next
+%decades.
 
@@
 scaffold (see figure~\ref{fig:dna_tag}.
+
 \begin{figure}
@@
 \end{figure}
+
 A detailed description of the chemical properties involved is far
@@
 the number of unique tags, thus limiting the complexity at each node.
+In particular, a budget of about $10,000$ transistor per node has been
+estimated in~\cite{liu_jetcs}.
 
-\emph{Large scale randomness} and \emph{high defect rates} are the other two fundaments
-conditions of self-assembled technology: if, as seen, some complexity
-can be introduced by designing tag sequences in the DNA grid of each
-node, we have no control of where each of these grids will be placed
-on the whole network. Further, as a consequence, we cannot guarantee
-other typical properties of regular networks, like nodes being
-connected to 4 neighbors, having a determined orientation and so on.
+\emph{Large scale randomness} is the other fundamental condition of
+self-assembled technology: DNA tags allow a control placement inside
+node grid, but there is no control of where each of these  grids will
+be placed on the whole network. As a consequence, other typical
+properties of regular networks cannot be guaranteed, e.g. being
+connected to a fixed number of neighbors, having a determined
+orientation and so on.
+
+Finally, \emph{defect rates}: while they are very hardly tolerated in mask
+based top down design , the same nature of a bottom up self
+assembled process cannot assume such a deterministic device placement
+process.
 
 These aspects of a DNA-self assembly process lead to some important
-architectural implications to be addressed when approaching to the
-Computer Design: computational model must be founded on a distributed
-network of small computing and storage nodes, randomly placed and
-interconnected (see figure~\ref{fig:nana}).  Proof-of-concept of such kind of computational model
-can be found in~\cite{patwardhan2006_1}, where instructions and data operands travel
-on packets and routed using a topology-agnostic strategy that avoids
-deadlock, since no particular regularity can be assumed in such
-network.
+implications to be addressed when approaching to the design of
+computer architecture: a computational model should be founded on a
+distributed network of small computing and storage nodes, randomly
+placed and interconnected (see figure~\ref{fig:nana}).
+Proof-of-concept of such kind of computational model can be found for
+example in~\cite{patwardhan2006_1}.  Since no regularity can be
+assumed in such network, a topology agnostic strategy that avoids
+deadlock should be adopted in order to route packets (e.g.
+instructions and data operands) among nodes.  It is important to
+underline that, altought we can assume an architecture similar to the
+one depicted in~\ref{fig:nana} as background, the topology discovery
+problem is more general and not stricly dependent on any of the
+underlying computing architectures.
 
+%where instructions and data operands travel
+%on packets and routed using a topology-agnostic strategy that avoids
+%deadlock, 
 \begin{figure}
   \centering
-    \includegraphics[width=0.40\textwidth]{pictures/dna1.eps}
-  \caption{Irregular architecture of computing and storage elements}
+    \includegraphics[width=0.20\textwidth]{pictures/dna1.eps}
+  \caption{Irregular topology of computing and storage elements}
   \label{fig:nana}
@@
 
-In this paper we introduce DiSR, a first effort for a Distributed
+The contribution presented in this paper is to bring the advantages of
+a segment-based approach to deadlock freedom without requiring any topology graph,
+external defect map or centralized algorithm execution.  We introduce DiSR, a first effort for a Distributed
 Segment-based Routing in large scale DNA self assembled networks.
-Given the irregular/high-defect rates scenario assumed as background, is essential
+While maintaining similar properties to segment-based , the DiSR
+approach is not intended to discover the "optimal" segment choice
+(ideally reachable with the knowledge of the topology graph) but just
+to demonstrate a concrete model that can fit into such complex,
+irregular and large sized topologies.
+Given the irregular/high-defect rates scenario discussed above, is essential
 avoiding non-scalable or resource hungry solutions such as
@@
 or expensive implementations based on hardware redundancy.
-Altought we will assume an architecture similar to the one depicted
-in~\ref{fig:nana} as background, it
-is important to underline that the proposed approach to topology
-discovery is more general and not stricly dependent on any of these
-architectures.
 
@@
 
-The contribution presented in this paper is to bring the advantages of
-segment-based turn prohibition without requiring any topology graph,
-external defect map or centralized algorithm execution.  While
-maintaining similar properties to segment-based routing, the DiSR
-approach is not intended to discover the "optimal" segment choice
-(ideally reachable with the knowledge of the topology graph) but just
-to demonstrate a concrete model that can fit into such complex,
-irregular and large sized topologies.
+The DiSR approach presented in this works is a first attempt of
+reaching the same goal of SR (e.g. estabilishing segments) without
+requiring a topology graph and a centralized exectution.
 
@@
 together with execution model details in Section~\ref{sec:disr_detaled_model}.
-Finally, simulations are carried out with the opensource tool Nanoxim
+In Section~\ref{sec:simulatio} simulations are carried out with the opensource tool Nanoxim
 to demostrate how DiSR preserves some of the main segment-based
-properties and how compares to the tree-based approaches.
+properties and how compares to the tree-based approaches. Finally a
+draft of a VHDL hardware implementation is shown in
+Section~\ref{sec:implementation} to evaluate the feasibility of the
+approach in terms of node complexity.

### 2013-09-18 trunk/PAPER/disr.tex
Lot of fixes, rearrangements

@@
 \emph{Segment}: a Segment is basically a path of consecutive node
-and links. 
+and links. All segments start with a link attached to a node which
+belongs to different segment, ending with a link also attached to a
+node belonging to a different segment. A exception is the first
+segment estabilished in the network, called \emph{starting segment} which it's  a loop
+beginning/ending on a particular node defined as boostrap node.
+
 The idea is to partition the network in a set of disjoint segments, and then
-placing a turn restriction within each segment. It has been proved~\cite{}
+placing a turn restriction within each segment. It has been proved~\cite{mejia_ipdps06}
 that such a set of turn prohibitions guarantees dealock freedom and
@@
 is basically similar to the classic SR approach. This can be useful to
-give an initial idea of the approach, however, some important
-differences should be pointed out:(i) no centralized entity is
-globally aware of what is going on. The status of the DiSR execution
-is collectively distributed among the nodes (ii) no defect map and/or
+give an initial idea of the approach, however, some essential
+differences should be pointed out. First of all no centralized entity is
+globally aware of what is going on: the status of the DiSR execution
+is collectively distributed among the nodes; second, no defect map and/or
 topology graph is available as input, thus, the topology has to be
-discovered \emph{while} segments are created (iii) at the end of the
+discovered \emph{while} segments are created; finally, at the end of the
 execution, no segment list is created: Each node is only aware of
@@
 \begin{itemize}
-\item Injection of the DiSR process from upper layer into a bootstrap
+\item Injection of the DiSR process from upper layer to set a bootstrap
 node
-\item Bootstrap node broadcast to create first segment of the subnet
-\item Parallel requests creating other segments
-\item Turn proibition in each confirmed segment
-\item Draining of remaining packet due timeouts
+\item Bootstrap node broadcasting to create the first segment of the subnet
+\item Parallel requests starting from assigned node to discover other segments
+%\item Turn proibition in each confirmed segment
+%\item Draining of remaining packet due timeouts
 \end{itemize}
@@
 The DiSR approach works with a distributed mechanism which is build
-upon an exchange of small setup packets containing very simple data:
+upon an exchange of small packets containing the following fields:
 \begin{itemize}
+\item{packet\_type}: encodes the meaning of the control message respect
+to the whole DiSR process.
+\item{seg\_ID}: the id of the segment associated to the DiSR control message
 \item{src\_id}: the id of the node that initially originated the
 packet
-\item{packet\_type}: this encodes that particular meaning of the
-packet in the whole DiSR process.
 \end{itemize}
@@
 
+A quantitative analysis of the resources needed to implement these
+fields is presented in Section~\ref{sec:implementation} when
+discussing the impact of the DiSR control logic and storage on
+hardware implementation of the node.
+
 \subsection{DiSR Data Structures}
+\label{ssec:disr_dstruct}
 
-We distinct among two different kind of data stored at each node:
-local environment data (LED) and dynamic behaviour status (DBS).
+We distinct between two different kind of data stored at each node:
+\emph{Local Environment Data} (\emph{LED}) and \emph{Dynamic Behaviour
+Status} (\emph{DBS}).
 
-The LED is like a snapshot of the DiSR algorithm at each node,
+The \emph{LED} is like a snapshot of the DiSR algorithm at each node,
 consisting in the following variables:
@@
 \begin{itemize}
-\item{segID}:a value used to specify a segment id for the node. Depending on
-the values of \emph{visited}/\emph{tvisited} variables below, a node can be
-assigned to or candidate for a specific segment id.  
-\item{\emph{visited}}: a boolean value. If \emph{visited} is true
-and segID is different from NULL, then segID specifies the segment id
-to which the node has been assigne. Note that a value different from NULL does not
-necessarily mean the node has been assigned to some segment (e.g. when
-searching starting segment is set \emph{visited} by default even if not yet
-assigned to any segment). 
-\item{\emph{tvisited}}: a boolean value. If
-true, the node is being considered as candidate for a segment, and the
-segID value specifies the segment id for which the node it's candidate. 
+\item{\emph{segID}}:a value used to specify the segment to which the
+node has been assigned or is candidate for being assigned.
+\item{\emph{visited}}: a boolean value. When \emph{true}
+a \emph{segID} different from \texttt{NULL} specifies the segment 
+to which the node has been assigned.
+
+% TODO: the following it's true, but complicates things at this stage
+%Note that a value different from \emph{NULL} does not
+%necessarily mean the node has been assigned to some segment (e.g. when
+%searching starting segment is set \emph{visited} by default even if not yet
+%assigned to any segment).
+
+\item{\emph{tvisited}}: a boolean value. If \emph{true}, the node is
+being considered as candidate for a segment, and the \emph{segID} value
+specifies the segment id for which the node it's candidate. 
 \item{\emph{link\_visited[]}}: an array
 of values representing information about attached links, that is, the
-segID of the segment owning each link. When NULL, the corresponding link has not yet been
+segID of the segment owning each link. When \texttt{NULL}, the corresponding link has not yet been
 assigned.
@@
 \item{\emph{link\_tvisited[]}}: an array of
-values representing information about attached links, that is, the segID of
-the segment for which the link is candidate. When NULL, the link is
+values representing information about attached links, that is, the \emph{segID} of
+the segment for which the link is candidate. When \texttt{NULL}, the link is
 currently not \emph{tvisited}.  
-\item{\emph{starting}}: boolean, true if the node it's a
-starting node from which the whole process was initiated.
 \end{itemize}
+%\item{\emph{starting}}: boolean, \emph{true} if the node it's a
+%starting node from which the whole process was initiated.
+%\end{itemize}
 
-In addition to the LED variables described above, further information
-should be stored in order to capture the current dynamic behaviour of
-the node. This is represented by the dynamic behaviour status (DBS)
-variable, which strictly depends on the LED data and the events
-occurring at the node. The DBS can have the following values:
+In addition to the \emph{LED} variables described above, further
+information should be stored in order to capture the current dynamic
+behaviour of the node. This is represented by \emph{DBS} variable,
+which strictly depends on the \emph{LED} data and the events occurring
+at the node. The \emph{DBS} can have the following values:
 
@@
 \item{\emph{Free}}: a node that has  not been yet considered  by the DiSR algorithm.
-The node is not marked as \emph{visited}/\emph{tvisited}/terminal/starting.
+The node is not marked as \emph{visited}/\emph{tvisited}.
 \item{\emph{Boostrap}}: a node which has been explicitly set as bootstrap node from
-an upper layer via. This is required because a
-\texttt{STARTING\_SEGMENT\_REQUEST} packet should be injected in order to start
-the whole process.
+an upper layer via. 
+% TODO: this and all the other details on the items below should be
+% checked and moved elsewhere for a future long paper
+
+%This is required because a
+%\texttt{STARTING\_SEGMENT\_REQUEST} packet should be injected in order to start
+%the whole process.
 \item{\emph{ActiveSearching}}: a node from which a find process of new segments has
-been started and not yet cancelled or confirmed. This happens when all
-the following conditions are matched: the node is marked as \emph{visited},
-that is \emph{visited} = TRUE 
-TODO: segID is set to some value reflecting
-the segment request sent there is a link that is being investigated by
-the node, that is a tvisited\_link marked with the same id of the node 
+been started and not yet cancelled or confirmed. 
+%This happens when all
+%the following conditions are matched: the node is marked as \emph{visited},
+%that is \emph{visited} = TRUE 
+%TODO: \emph{segID} is set to some value reflecting
+%the segment request sent there is a link that is being investigated by
+%the node, that is a tvisited\_link marked with the same id of the node 
 \item{\emph{Candidate}}: a node currently candidate for belonging to some segment
 with id segid, not being itself the node from which the find process
-was started. The following conditions should be matched: \emph{tvisited} =
-true, with segID=X different from node's id.  Two links set as
-\emph{link\_tvisited} with id X. Let’s refer them as  links 'i' and 'j'. Then
-link\_tvisited[i] was set = X when the find process from an adjacent
-node reached the current node, while link\_tvisited[j] has been set to
-X when the node itself started to investigate its free links for the
-segment request with id X. Note that while investigating its attached
-links, if the find process fails along path 'j', the current node can
-investigate another free node 'k' if suitable.  
+was started.
+
+%The following conditions should be matched: \emph{tvisited} =
+%true, with segID=X different from node's id.  Two links set as
+%\emph{link\_tvisited} with id X. Let’s refer them as  links 'i' and 'j'. Then
+%link\_tvisited[i] was set = X when the find process from an adjacent
+%node reached the current node, while link\_tvisited[j] has been set to
+%X when the node itself started to investigate its free links for the
+%segment request with id X. Note that while investigating its attached
+%links, if the find process fails along path 'j', the current node can
+%investigate another free node 'k' if suitable.  
 \item{\emph{CandidateStarting}}: same as above, but the node is currently being considered as candidate
-for starting segment. Two main differences: Can confirm
-\texttt{STARTING\_SEGMENT\_CONFIRM} with the same segID when receiving a normal
-\texttt{SEGMENT\_REQUEST}: Overwrites its status setting it to \emph{Candidate} for the
-segID frees the links previously set as \emph{tvisited} during flooding
+for starting segment.
+
+%Two main differences: Can confirm
+%\texttt{STARTING\_SEGMENT\_CONFIRM} with the same \emph{segID} when receiving a normal
+%\texttt{SEGMENT\_REQUEST}: Overwrites its status setting it to \emph{Candidate} for the
+%segID frees the links previously set as \emph{tvisited} during flooding
 \item{\emph{Assigned}}: a node for which the segment has been determined.  The
-segment segID attribute value is set to some id X different from NULL.
-The \emph{visited} value is true NOTE: an \emph{Assigned} state is a quick temporary
-state, since it becomes \emph{ActiveSearching} if a not (\emph{visited}/tvisited)
-link is suitable for searching new segments (see next\_visited
-procedure on paper) 
+segment \emph{segID} attribute value is set to some id X different from \texttt{NULL}.
+%The \emph{visited} value is \emph{true} NOTE: an \emph{Assigned} state is a quick temporary
+%state, since it becomes \emph{ActiveSearching} if a not (\emph{visited}/tvisited)
+%link is suitable for searching new segments (see next\_visited
+%procedure on paper) 
 \end{itemize}
 
-\subsection{Creating the starting segment}
+\subsection{Sketch of DiSR}
 
@@
 
-\item{Injecting request}: all nodes have status \emph{Free}, except for a
-“bootstrap node” with status \emph{Boostrap}, set by some signal from an
-upper layer via. This bootstrap node sets itself as \emph{visited} and
+\item{\textbf{Injecting bootstrap request}}: all nodes have a initial
+\emph{DBS} status \emph{Free}, except for a
+ node with status \emph{Bootstrap}, set by some signal from an
+upper layer via. When starting, this bootstrap node sets itself as \emph{visited} and
 changes its status to \emph{ActiveSearching}, injecting a
@@
 
-\item{Flooding}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
-if not (\emph{visited}/\emph{tvisited}),  forwards it to its free links using a flooding mechanism.
+\item{\textbf{Flooding}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
+if not yet (\emph{visited}/\emph{tvisited}),  forwards it to its free links using a flooding mechanism.
 Each of these links is then marked as \emph{tvisited} with the segment id
@@
 associated to the same request, having already contributed to the
-flooding. Note also that each of these packets has a max\_segment\_hops
-field to prevent packets from travelling undefinitively.
+flooding. 
+%Note also that each of these packets has a max\_segment\_hops
+%field to prevent packets from travelling undefinitively.
 
-\item{Confirming the Starting Segment}: when this \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
+\item{\textbf{Confirming the Starting Segment}}: when this \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
 the starting node (from a different link, of course), the starting
@@
 \texttt{STARTING\_SEGMENT\_REQUEST}. Each node do same by changing its own status
-from \emph{tvisited} to \emph{visited}. So the confirmation packet is sent back from
+to \emph{Assigned}. So the confirmation packet is sent back from
 node to node and the starting segment is created.
 
-Note: A node knows to be \emph{tvisited} due a
+Note: A node knows to be \emph{Candidate} due a
 \texttt{STARTING\_SEGMENT\_REQUEST}.  Then, when receiving a simple
-(not starting) \texttt{SEGMENT\_REQUEST} , can simply cancel its
-\emph{tvisited} status and set its links as free, because the second
-request means that a starting segment has already been found a
-there’s no need to keep the \emph{tvisited} status for those broadcast
-status. What happens to nodes not receiving these segment request?
-they simply remain \emph{tvisited} and after a timeout reset their
-state as free. But they could also remain \emph{tvisited} for the
-starting segment, since this doesn’t affect their behaviour for future
-segment requests.
+(not starting) \texttt{SEGMENT\_REQUEST} , it can simply cancel its
+previous \emph{Candidate} status, since this second
+request means that the starting segment has already been found.
+
+%What happens to nodes not receiving these segment request?
+%they simply remain \emph{tvisited} and after a timeout reset their
+%state as free. But they could also remain \emph{tvisited} for the
+%starting segment, since this doesn’t affect their behaviour for future
+%segment requests.
 
 %failure: TODO should we handle this case ? i.e.  marking as terminal ?
-\end{itemize}
 
-\subsection{Finding other segments}
-
-\begin{itemize}
-\item{Injecting request}: Every node in the \emph{Assigned} status can initiate a search for a
+\item{\textbf{Injecting other request}}: Each node in the \emph{Assigned} status can initiate a search for a
 segment, by sending a \texttt{SEGMENT\_REQUEST} across one of its free
 links. Note that, since this is not the starting segment, in this case
-the packet should not reach the initiator, but just another visited
+the packet should not return back to the initiator, but just another visited
 node
-
-\item{setup of the segment}: The find process is successfull when a visited
-node receives the \texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
-sent back along the path that originated the request.  Failing while
-searching a segment: a node received a \texttt{SEGMENT\_REQUEST} packet but
+\item{\textbf{Setup of a segment}}: The find process is successfull
+when an \emph{Assigned} node receives the \texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
+sent back along the path that originated the request.  
+\item{\textbf{Failing while searching a segment}}: a node received a \texttt{SEGMENT\_REQUEST} packet but
 matched one of the following conditions: the node is free but has no
@@
 
-\subsection{Intra-node vs Inter-node parallelism}
-In the processes described above, we assumed that each node in the
-READY\_SEARCHING state can start a find segment process by injecting a
-\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when defining DiSR
-should be made in order to decide whether or not the node must
-actually perform this action. 
-The point above is is strictly related to the general question: which
-level of “parallelism” should we allow in DiSR ? The adopted approach
-is that, although the nature of DiSR itself is intrinsicly parallel,
-the use of parallelism makes things work in a more complex way. In
-other words, DiSR is parallel when needed, but it does not exploit
-parallelism as an “improving feature”. When not needed, things should
-be serialized. For example: when a node is “ready searching” could
-start several find segment process associated to the same segment, one
-for each free link. But serializing this by investigating the free
-links in order could be a simplest solution. We refer to this saying
-that we avoid intra-node parallelism.  Note that while intra-node
-parallelism can be avoided, trying to avoid inter-node parallelism
-could be more complex than allowing the parallelism itself. Imagine
-for example the effort of trying to coordinate nodes so that an unique
-finding node process is actually running in the whole subnet. Thus, in
-contrast to the intra-node parallelism, the inter-node parallelism is
-a structural property of the DiSR algorithm and should not be avoided.
+%\subsection{Intra-node vs Inter-node parallelism}
+%In the processes described above, we assumed that each node in the
+%READY\_SEARCHING state can start a find segment process by injecting a
+%\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when defining DiSR
+%should be made in order to decide whether or not the node must
+%actually perform this action. 
+%The point above is is strictly related to the general question: which
+%level of “parallelism” should we allow in DiSR ? The adopted approach
+%is that, although the nature of DiSR itself is intrinsicly parallel,
+%the use of parallelism makes things work in a more complex way. In
+%other words, DiSR is parallel when needed, but it does not exploit
+%parallelism as an “improving feature”. When not needed, things should
+%be serialized. For example: when a node is “ready searching” could
+%start several find segment process associated to the same segment, one
+%for each free link. But serializing this by investigating the free
+%links in order could be a simplest solution. We refer to this saying
+%that we avoid intra-node parallelism.  Note that while intra-node
+%parallelism can be avoided, trying to avoid inter-node parallelism
+%could be more complex than allowing the parallelism itself. Imagine
+%for example the effort of trying to coordinate nodes so that an unique
+%finding node process is actually running in the whole subnet. Thus, in
+%contrast to the intra-node parallelism, the inter-node parallelism is
+%a structural property of the DiSR algorithm and should not be avoided.
 %------------------------------------------------------------------------------
@@
 \section{Detailed Node behaviour Model}
+\label{sec:disr_detailed_model}
 
-The LED variables at each node are are initially set so the node and
+The \emph{LED} variables at each node are are initially set so the node and
 each of its links is set as free. The only node that makes exception
@@
 the subsequent events happening at each node are the consequence of
-its current dynamic status (DBS) and the packets received, as depicted
-in the Figure~\ref{fig:status_machine}.
+its current dynamic status (DBS) and the packets received.
 
-\label{sec:disr_detailed_model}
 %TODO: add state machines
@@
 
-The request for the first segment of a
-subnet should be managed differently since all nodes (except the starting
-one) must forward the packet using a flooding mechanism. This is
-necessary since the request packet must reach the starting node, which
-is the only node marked as \emph{visited}. As stated elsewhere, it should
-remembered that the first segment of each subnet it's  a loop that
-beginning/ending on the starting node.
-
-When a node receives a \texttt{STARTING\_SEGMENT\_REQUEST}, with SegID = X,  there
-are the following cases:
+The request for the first segment should be managed differently since
+all nodes (except the starting one) must forward the packet using a
+flooding mechanism. This is necessary since the request packet must
+return the bootstrap node.
+When a node receives a \texttt{STARTING\_SEGMENT\_REQUEST}, the
+following cases can happen:
 
 \begin{itemize}
-\item The node is visited with the same segID = x, that is it was the
-initiator of the request (set visited by definition): a first segment
-was found and should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
+\item The node it's not candidate or assigned: it should set itself as
+\emph{Candidate} and forward the packet along its free links, using
+flooding.  
+\item The node is \emph{Candidate} with the same
+\emph{segID} and \emph{src\_id} is equal to node id: this means the
+node was the initiator of the request, so a starting segment was found and
+should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
 packet.  
-\item The node is \emph{tvisited}, with the same segID of the packet: due
+\item The node is \emph{Candidate}, with the same \emph{segID} of the
+packet but \emph{src\_id} is different from node id: due
 the flooding mechanism, another starting segment packet reached a node
-which was previously marked as \emph{tvisited} from the same starting segment
-search process. Since the node is \emph{tvisited} with the same id, it means
+which was previously marked as \emph{Candidate} from the same starting segment
+search process. Since the node is candidate with the same id, it means
 that it already accomplished in the task of propagating that kind
-packets, thus can simply ignore the event thrashing the packet.  If
-the node it's not visited/\emph{tvisited}: it should set itself as \emph{tvisited}
-and forward the packet along its free links, using flooding. TBD: how
-the status should be changed ? depend on the flooding mechanism. Note
-that these links don’t include the link from which the request was
-received.  
-\item The node it's visited, with different id in the packet.
-CHECK:  it is not the initiator of the starting segment request, but
-is already assigned to some segment!? assuming again we are discussing
-of nodes belonging to the same subnet, this should NOT happen, since
-the only visited node of the subnet should be the initial node from
-which the \texttt{STARTING\_SEGMENT\_REQUEST} originated. Note again that we are
-assuming that if the the node is visited or \emph{tvisited} with the id of
-another subnet can simply ignore the request.  The node it's \emph{tvisited}
-but it's not the initiator of the request (different id): same as
-above, if we are assuming nodes of the same subnet, this shouldn’t
-happen. If the node is of another subnet, can simply ignore the event.
+packets, thus can simply ignore the event thrashing the packet.  
+%TBD: how the status should be changed ? depend on the flooding mechanism. Note
+%that these links don’t include the link from which the request was
+%received.  
+\item The node is \emph{Candidate}, with a different \emph{segID}: 
+this simply means that the starting segment received it's deprecated,
+because the node has already accepted non-starting segment requests
+originated from other \item{Assigned} nodes.
+\item The node it's \emph{Assigned}, with a different \emph{segID}:
+same as the previous case.
+
+% TODO: check and remove, the below it's not true
+%CHECK:  it is not the initiator of the starting segment request, but
+%is already assigned to some segment!? assuming again we are discussing
+%of nodes belonging to the same subnet, this should NOT happen, since
+%the only visited node of the subnet should be the initial node from
+%which the \texttt{STARTING\_SEGMENT\_REQUEST} originated. Note again that we are
+%assuming that if the the node is visited or \emph{tvisited} with the id of
+%another subnet can simply ignore the request.  The node it's \emph{tvisited}
+%but it's not the initiator of the request (different id): same as
+%above, if we are assuming nodes of the same subnet, this shouldn’t
+%happen. If the node is of another subnet, can simply ignore the event.
 
@@
 \begin{itemize}
-\item The node is \emph{visited} (and belongs to the same subnet): a segment was
+\item The node is \emph{Assigned}: a segment was
 found and it should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
 packet.  
-\item The node is \emph{tvisited}: it should discard the packet sending
+\item The node is \emph{Candidate}: it should discard the packet sending
 back a \texttt{SEGMENT\_CANCEL} 
-\item The node it's not \emph{visited}/\emph{tvisited} and has free
-links: it marks itself as \emph{tvisited} and forwards the \texttt{SEGMENT\_REQUEST}
-(one request at time) to each of its free links, according to some
-ordering
-\item NOTD: the difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
+\item The node it's not \emph{Assigned} or \emph{Candidate} and has free
+links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
+to one of its free links, according to some internal ordering
+\end{itemize}
+
+NOTE: the main difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
 and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
 itself it's included in the segment , while in the second case the
-receiving node DOES NOT belong to the segment found. The motivation is
-that in the second case the node was already marked as \emph{visited} because
-of being assigned to some segment found before, while in the
-starting-segment case, by definition, the first segment of a subnet
-begins with the starting node, which is marked as \emph{visited} by the SR
-algorithm when searching for the first (starting) segment. Remember
-that the first segment of a subnet is a loop beginning with the
-starting node. 
-\end{itemize}
+receiving node does not belong to the segment found.
 
-\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}
-When received, if the node status is \emph{tvisited} with a segID corresponding to the one indicated in
+%The motivation is
+%that in the second case the node was already marked as \emph{visited} because
+%of being assigned to some segment found before, while in the
+%starting-segment case, by definition, the first segment of a subnet
+%begins with the starting node, which is marked as \emph{visited} by the SR
+%algorithm when searching for the first (starting) segment. Remember
+%that the first segment of a subnet is a loop beginning with the
+%starting node.
+
+\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
+When received, if the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
 the packet, the node learns to belong to the segment associated to the
@@
 original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
-can learn the segment id they belong to.  LED shoud be
+can learn the segment id they belong to.  \emph{LED} shoud be
 updated: The state of the node changes from \emph{tvisited} to \emph{visited}.  the
-\emph{link\_tvisited} previously set with the segID should be invalidated the
+\emph{link\_tvisited} previously set with the \emph{segID} should be invalidated the
 \emph{link\_visited} variable associated to the incoming confirm should be set
@@
 forwards back the \texttt{SEGMENT\_CANCEL} packet along the link that originated
-the \texttt{SEGMENT\_REQUEST} packet ONLY when there are no more free links to
-try. If this is the case, the node modifies its status from \emph{tvisited}
-to free and fordwards the \texttt{SEGMENT\_CANCEL} packet to the link from which
+the \texttt{SEGMENT\_REQUEST} packet only when there are no more free links to
+try. If this is the case, the node modifies its status from
+\emph{Candidate} to \emph{Free} and forwards the \texttt{SEGMENT\_CANCEL} packet to the link from which
 the request was received. The process stops when the \texttt{SEGMENT\_CANCEL}
@@
 
-TODO REPEAT!!
-
-When a node discovers that the path that includes
-the node itself is no more suitable, a \texttt{SEGMENT\_CANCEL} is sent back
-across the link from which the \texttt{SEGMENT\_REQUEST} was received.  Possible
-reasons for that: The node it’s already candidate for another segment
-The node it’s free but can’t find a free link (according the
-cyclelinks timeout) The node it’s \emph{tvisited} for the same request id,
-previously forwarded that request along some free direction, but now
-it’s receiving a a cancel request and has no more free links
+%TODO REPEAT!!
+%When a node discovers that the path that includes
+%the node itself is no more suitable, a \texttt{SEGMENT\_CANCEL} is sent back
+%across the link from which the \texttt{SEGMENT\_REQUEST} was received.  Possible
+%reasons for that: The node it’s already candidate for another segment
+%The node it’s free but can’t find a free link (according the
+%cyclelinks timeout) The node it’s \emph{tvisited} for the same request id,
+%previously forwarded that request along some free direction, but now
+%it’s receiving a a cancel request and has no more free links

### 2013-09-19 PAPER/implementation.tex
Fixes

--- 2013-09-16 PAPER/implementation.tex
@@
 \label{sec:implementation}
+
 Although a completed and detailed floorplan of the node is not the
@@
 which are the main elements required to support this kind of
-architecture and the DiSR approach. There are three main classes of
-node elements:
+architecture thus giving an estimate of the overhead by the
+DiSR approach. There are three main classes of node elements:
 \begin{itemize}
@@
 strictly related to the node functionality and role inside a given
-networks: e.g. is that a computation or storage node.
+network, e.g. being a computation or storage node.
 \item Node communication:  these are elements (such as transceivers,
 buffers) required to the node to communicate with its neighbours,
-independently from node functionality and DiSR implementation
-\item DiSR-specific: all the hardware, such as control logic and
-configuration, required to implement the proposed DiSR approach.
+independently from node functionality and DiSR implementatio
+\item DiSR-specific: all the hardware, control logic and
+configuration registers, related to an implementation the proposed approach.
 \end{itemize}
-
-Let us now look inside the \emph{DiSR} block which implements the DiSR-specific
-operation. In Fig.~\ref{fig:implementation} we shown a possible sketch of this 
-last one, which mainly consist in the following building blocks:
-
-\begin{itemize}
-\item \emph{DBS block}: This block take trace of the dynamic behaviour status (DBS). 
-      How discussed in the Sec.~\ref{ssec:disr_dstruct}, there are six possible status. 
-      These status can be codified using only 3 bit implemented with a 3-bit register 
-      and the required combinatory logic. This block is essentially designed as a state machine.
-\item \emph{LED register}: Is a set of register useful as storage for local environment data (LED)
-      described in Sec.~\ref{ssec:disr_dstruct}. In Fig.~\ref{fig:implementation} in their 
-      respective block, are highlighted two table that represents the link\_visited 
-      and link\_tvisited array. The implementation of this block is an array of register 
-      (one for each direction) that can be implemented with an SRAM, in which are presents two 
-      specific fields  for representing the segID (nodeID+linkID). 
-\item \emph{Control circuitry}: This circuitry read the information from the incoming packet, 
-      LED registers and the dynamic behaviour status (DBS block) and is able to write The LED
-      informations and change the dynamic behaviour status. The output (Ctrl out), drive 
-      the others communications resources (such as node transceivers) for actuating the DiSR 
-      routing operation.
-\end{itemize}
-
-One of the main design challenge typical of DNA Self-Assembled systems is due to the
-reduced available resource (such as the number of CNFET per node) for implementing both 
-computations and routing decisions for each node. Considering the budget of $10^4$ CNFET 
-for each network's node\cite{liu_jetcs} we must estimate the required resource useful 
-for implementing the entire DiSR block (Fig.~\ref{fig:implementation}). For this purpose, 
-after a description of the DiSR circuitry with an hardware description language (VHDL) 
-we have synthesized at gate-level the required hardware. Furthermore, considering the 
-specific layout of each single logic elements (such as NAND, full-adder, latch etc.), 
-we are able to count the number of CNFET necessary for implementing the DiSR logic. 
-With this approach we estimated 2452 CNFET for implementing that blocks which constitutes 
-about the 25\% of the overall node budget. This number of resource can be certainly reducing 
-applying more effort in the circuitry design of each building block exposed in this section.
 
@@
   \centering
-  \includegraphics[width=0.40\textwidth]{pictures/disr_imp.eps}
+  \includegraphics[width=0.35\textwidth]{pictures/disr_imp.eps}
   \caption{\emph{DiSR} block architecture.}
@@
 \end{figure}
+
+Let's so focus to the \emph{DiSR} block. In
+Fig.~\ref{fig:implementation} is shown a possible sketch of this
+block, which mainly consist in the following building elements:
+
+\begin{itemize}
+\item \emph{DBS block}: It Takes trace of the DBS, and how already
+discussed in the Section~\ref{ssec:disr_dstruct}, there are six possible
+configurations. These values can be codified using 3 bit implemented
+with a 3-bit register and the required combinational logic. This block
+is essentially designed as a state machine.
+\item \emph{LED registers}: Is a set of registers useful for storing
+the local environment data (LED) described in
+Section~\ref{ssec:disr_dstruct}. In particular in
+fig.~\ref{fig:implementation}, are highlighted two tables representing
+the \emph{link\_visited[]} and \emph{link\_tvisited[]} values. This
+block consists of an array of registers (one for each
+direction) that can be implemented with an SRAM, in which are presents
+two specific fields  for representing the \emph{segID}. 
+\item \emph{Control circuitry}: This circuitry reads data
+from the fields of the incoming packet, LED registers and the
+\emph{DBS}, updating \emph{LED} and
+\emph{DBS} data when required. Then, the resulting \emph{Ctrl Out} output  drives the other
+communication resources (such as node transceivers) for actuating the
+DiSR routing operation.
+\end{itemize}
+
+As discussed above, one of the main design challenge of DNA
+Self-Assembled systems is the limited resource available for
+implementing both computations and routing decisions for each node.
+For this reason, assuming a budget of $10^4$ CNFETs for each network's
+node~\cite{liu_jetcs} we estimated the required resource for
+implementing the entire DiSR block. An not optimized VHDL description
+of the DiSR circuitry has been written and synthesized at gate-level.
+Considering the specific layout of each single logic elements ( NAND,
+full-adder, latch etc.), it has been possible to get a rough estimate
+of the number of transistors necessary for implementing the DiSR
+logic.  Figure~\ref{fig:imp_trend} shows the results of synthesis in
+terms of number of devices (CNFETs) versus the number of network nodes
+while the network scales up from $10\times10$ to $100\times100$ nodes.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.48\textwidth]{pictures/imp_rslt.eps}
+  \caption{DiSR synthesis results: N is the number of network's node.}
+ \label{fig:imp_trend}
+\end{figure}
+In particular, observing the Fig.\ref{fig:imp_trend} can 
+be pointed out that the proposed implementation occupy  about 20\% of the node budget. 
+Further, more than the absolute number of devices itself, it's interesting to
+observe that, while the node have a squared increment, the circuitry
+complexity which implements the DiSR algorithm increases with a slowly
+growing trend.  
+An intuitive explaination of this is the relatively simple logic of
+DiSR, whose behaviour is almost code on scalable storage structures.
+For example, the number of registers implementing the
+\emph{link\_visited[]} and \emph{link\_tvisited[]} table follow the
+logaritmic function:
+\begin{equation}
+  \label{eq:imp_trend}
+  N_{reg}=2\cdot N_{port} \cdot log_2(N)
+\end{equation}
+where $N_{port}$ is the number of the router's ports, $N$ is the number 
+of network's nodes while the term $2$ takes in account that \emph{link\_visited[]} and 
+\emph{link\_tvisited[]} are two separate set of registers. While this number is fixed by 
+the number of network's node, the control circuitry could be optimized applying more effort 
+in future designs of this building block.

### 2013-09-19 trunk/PAPER/simulation.tex
Fixes

--- 2013-09-17 PAPER/simulation.tex
@@
-\section{Simulation environment}
+\section{Simulation and Results}
 
@@
 
-\subsection{Nanoxim tool}
+\subsection{Nanoxim environment}
 
@@
 specific simulation environment has been developed, resulting in
-the open source and freely available project called Nanoxim~\cite{}.
+the open source and freely available project called
+Nanoxim~\cite{nanoxim}.
 Nanoxim is a SystemC tool based on a almost rewritten
-version of the Noxim Network-on-Chip simulator~\cite{}. While some
+version of the Noxim Network-on-Chip simulator~\cite{noxim}. While some
 complex features have been removed (e.g. wormhole, congestion/topology
@@
 \begin{itemize}
-\item {S}: Size of the network, intended as number of nodes, on a
+\item {\emph{Size of the network}}: number of nodes, on a
 range from 10x10 to 100x100 sized networks. 
-\item {\% defective links}: the probability that each link is
-disconnected or not present, from 0 the amount that yelds
-no more segments.
-\item {\% defective nodes}: the probability that a node is not
-working, thus having all its attached links not useful for DiSR setup.
-Same range as defective links parameter.
-\item {Bootstrap node}: the node used from upper layer (e.g. microscale)
+%\item {\% defective links}: the probability that each link is
+%disconnected or not present, from 0 the amount that yelds
+%no more segments.
+\item {\emph{\% defective nodes}}: the probability that a node is not
+working, thus having all its links cannot be utilized during DiSR setup.  
+%Same range as defective links parameter.
+\item {Bootstrap node}: the node used from upper layer 
 to inject the DiSR process. When not explicitly investigating the
@@
 \begin{itemize}
-\item {Average Path Lenght}:
-\item {Average Link Weight}:
+%\item {Average Path Lenght}:
+%\item {Average Link Weight}:
 \item {Unidirectional restrictions:}
@@
 generated, a set of simulations with different seeds has been run
-for each system configuration. We found that TODO repetitions are
+for each system configuration. We found that 20 repetitions are
 required in order to obtain statistically significant results.
 
-\subsection{Other optimisations}
-Some optimisation parameters, which demostrated to improve the DiSR
-results have been fixed to some good values, but are not subject to
-further investigation; once again the focus here is not the
-optimal set of segments, but just demostrating a working approach. 
-These are optimisations are:
-\begin{itemize}
-\item{cycle\_links}: max number of retries across the set of links of
-each node. While searching for a free link due an incoming request,
-the same request is cancelled after a given number of tries. This
-gives to preceding node change to test a different paths. Default is set to 1.
-\item{bootstrap\_timeout}: number of time units that a bootstrap node
-should wait before assuming that a livelock in the starting segment
-process has occurred. In the worst case, we can imagine that longest
-path required is the one returning to the bootstrap node after having
-travelled across all the links. So, althought this is just an extreme
-situation, a good upper limit can be safely be set to NxN.
-\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
-setup process, a bootstrap node should not have defective links.
-Enabling this optimisation, a bootstrap node is immune to defects.
-We may think of a pre-boostrap phase that properly selects (from upper
-layer via) a bootstrap node which is tested as properly connected. We
-enabled this optimisation, however empirical tests showed us that only
-simulations using bootstrap nodes placed on edges would be heavily
-affected, since these are nodes starting with a lower number of links,
-e.g. corner nodes could only have two connected direction, so even a
-defective link could prevent starting segment packet to return to
-bootstrap to close the loop a create the segment.
-
-\end{itemize}
+% TODO: long paper
+%\subsection{Other optimisations}
+%Some optimisation parameters, which demostrated to improve the DiSR
+%results have been fixed to some good values, but are not subject to
+%further investigation; once again the focus here is not the
+%optimal set of segments, but just demostrating a working approach. 
+%These are optimisations are:
+%\begin{itemize}
+%\item{cycle\_links}: max number of retries across the set of links of
+%each node. While searching for a free link due an incoming request,
+%the same request is cancelled after a given number of tries. This
+%gives to preceding node change to test a different paths. Default is set to 1.
+%\item{bootstrap\_timeout}: number of time units that a bootstrap node
+%should wait before assuming that a livelock in the starting segment
+%process has occurred. In the worst case, we can imagine that longest
+%path required is the one returning to the bootstrap node after having
+%travelled across all the links. So, althought this is just an extreme
+%situation, a good upper limit can be safely be set to NxN.
+%\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
+%setup process, a bootstrap node should not have defective links.
+%Enabling this optimisation, a bootstrap node is immune to defects.
+%We may think of a pre-boostrap phase that properly selects (from upper
+%layer via) a bootstrap node which is tested as properly connected. We
+%enabled this optimisation, however empirical tests showed us that only
+%simulations using bootstrap nodes placed on edges would be heavily
+%affected, since these are nodes starting with a lower number of links,
+%e.g. corner nodes could only have two connected direction, so even a
+%defective link could prevent starting segment packet to return to
+%bootstrap to close the loop a create the segment.
+%\end{itemize}
 

### 2013-09-20 trunk/PAPER/pictures/node_coverage/coverage_plot.m
node_coverage added

@@ -1,0 +1,12 @@
+%after that the workspace is loaded from file
+hold on;
+plot(def_node,ideal,'-');
+plot(def_node, trenta,'--o');
+plot(def_node,cinquanta,':.');
+plot(def_node,cento,'-.x');
+%plot(def_node,ottanta,':');
+
+
+xlabel('Node Defect Rate');
+ylabel('Node Coverage');
+legend('Ideal','30x30','50x50','100x100');

### 2013-09-20 PAPER/implementation.tex
Removed some contracted verbal forms, and typos

@@
 be pointed out that the proposed implementation occupy  about 20\% of the node budget. 
-Further, more than the absolute number of devices itself, it's interesting to
+Further, more than the absolute number of devices itself, it is interesting to
 observe that, while the node have a squared increment, the circuitry

### 2013-09-20 PAPER/introduction.tex
Removed some contracted verbal forms, and typos

@@
 
-Exploring long term alternatives to the CMOS technology is gaining
-more and more revelance as the scaling trend of such devices keeps
-introducing new challenges. Power density, defect tolerance, testing
-costs and wire delays are only a few of the many critical aspects
-involved~\cite{itrs12}. While software parallelism and multicore
-approaches~\cite{TODO1} are partially mitigating the impact of such
-constraints on performances, it is likely that the growing computing demand will
-eventually need even more radical architectural modifications and new
-paradigms in order to address the Computer Design challenges of the next
-decades.
+% TODO: re-enable on long paper
+%Exploring long term alternatives to the CMOS technology is gaining
+%more and more revelance as the scaling trend of such devices keeps
+%introducing new challenges. Power density, defect tolerance, testing
+%costs and wire delays are only a few of the many critical aspects
+%involved~\cite{itrs12}. While software parallelism and multicore
+%approaches~\cite{horowitz2004, mudge2001, powell2009} are partially mitigating the impact of such
+%constraints on performances, it is likely that the growing computing demand will
+%eventually need even more radical architectural modifications and new
+%paradigms in order to address the Computer Design challenges of the next
+%decades.
 
@@
 assembled networks we are assuming as background.
-Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} don't use virtual channels to
+Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} do not use virtual channels to
 achieve deadlock freedom, but turn proibitions. 

### 2013-09-20 trunk/PAPER/disr.tex
Removed some contracted verbal forms, and typos

@@
 node belonging to a different segment. A exception is the first
-segment estabilished in the network, called \emph{starting segment} which it's  a loop
-beginning/ending on a particular node defined as boostrap node.
+segment estabilished in the network, called \emph{starting segment} which is  a loop
+beginning/ending on a particular node defined as bootstrap node.
 
@@
 
-% TODO: the following it's true, but complicates things at this stage
+% TODO: the following is true, but complicates things at this stage
 %Note that a value different from \emph{NULL} does not
@@
 being considered as candidate for a segment, and the \emph{segID} value
-specifies the segment id for which the node it's candidate. 
+specifies the segment id for which the node is candidate. 
 \item{\emph{link\_visited[]}}: an array
@@
 \end{itemize}
-%\item{\emph{starting}}: boolean, \emph{true} if the node it's a
+%\item{\emph{starting}}: boolean, \emph{true} if the node is a
 %starting node from which the whole process was initiated.
@@
 The node is not marked as \emph{visited}/\emph{tvisited}.
-\item{\emph{Boostrap}}: a node which has been explicitly set as bootstrap node from
+\item{\emph{Bootstrap}}: a node which has been explicitly set as bootstrap node from
 an upper layer via. 
@@
 \begin{itemize}
-\item The node it's not candidate or assigned: it should set itself as
+\item The node is not candidate or assigned: it should set itself as
 \emph{Candidate} and forward the packet along its free links, using
@@
 %TBD: how the status should be changed ? depend on the flooding mechanism. Note
-%that these links don’t include the link from which the request was
+%that these links do not include the link from which the request was
 %received.  
 \item The node is \emph{Candidate}, with a different \emph{segID}: 
-this simply means that the starting segment received it's deprecated,
+this simply means that the starting segment received is deprecated,
 because the node has already accepted non-starting segment requests
-originated from other \item{Assigned} nodes.
-\item The node it's \emph{Assigned}, with a different \emph{segID}:
+originated from other \emph{Assigned} nodes.
+\item The node is \emph{Assigned}, with a different \emph{segID}:
 same as the previous case.
 
-% TODO: check and remove, the below it's not true
+% TODO: check and remove, the below is not true
 %CHECK:  it is not the initiator of the starting segment request, but
@@
 %assuming that if the the node is visited or \emph{tvisited} with the id of
-%another subnet can simply ignore the request.  The node it's \emph{tvisited}
-%but it's not the initiator of the request (different id): same as
-%above, if we are assuming nodes of the same subnet, this shouldn’t
+%another subnet can simply ignore the request.  The node is \emph{tvisited}
+%but it is not the initiator of the request (different id): same as
+%above, if we are assuming nodes of the same subnet, this should not
 %happen. If the node is of another subnet, can simply ignore the event.
@@
 back a \texttt{SEGMENT\_CANCEL} 
-\item The node it's not \emph{Assigned} or \emph{Candidate} and has free
+\item The node is not \emph{Assigned} or \emph{Candidate} and has free
 links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
@@
 and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
-itself it's included in the segment , while in the second case the
+itself is included in the segment , while in the second case the
 receiving node does not belong to the segment found.
@@
 as segID. Note that if the request was flooded across different links,
-the \emph{link\_visited} variable associated to the other paths shouldn’t be
+the \emph{link\_visited} variable associated to the other paths should not be
 set.  the \emph{link\_visited} variable associated to the link from which the

### 2013-09-20 PAPER/introduction.tex
Fixes

@@
 stabiliy of DNA structures in order to create a scaffold onto which
-nano-devices (e.g. nanowires and nanotubes~\cite{bachtold2001, tans1998, cui2001}) can be
+nano-devices (e.g. nanowires and CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be
 attached. This can be achieved by designing approapriate complementary DNA tags for
@@
 the number of unique tags, thus limiting the complexity at each node.
-In particular, a budget of about $10,000$ transistor per node has been
+In particular, a budget of about $10,000$ CNFETs per node has been
 estimated in~\cite{liu_jetcs}.
@@
 properties and how compares to the tree-based approaches. Finally a
-draft of a VHDL hardware implementation is shown in
+draft of a architectural implementation is shown in
 Section~\ref{sec:implementation} to evaluate the feasibility of the

### 2013-09-20 PAPER/paper.tex
Fixes

--- 2013-04-15 PAPER/paper.tex
@@
 
-\title{A Distribuited Segment-based Approach for Topology-agnostic Nano Networks Routing}
+\title{A First Effort for a Distributed Segment-based Approach on Self-Assembled Nano Networks}
 
-\author{
-  \IEEEauthorblockN{Vincenzo Catania} \IEEEauthorblockA{Affiliation3\\ email3}} \and
-  \IEEEauthorblockN{Davide Patti} \IEEEauthorblockA{Affiliation2\\ email2}
+\author{Vincenzo~Catania, Andrea Mineo, Salvatore Monteleone~and~Davide~Patti% 
+\thanks{The authors are with the Dipartimento di Ingegneria
+Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
+(email: \{vincenzo.catania,amineo,salvatore.monteleone,davide.patti\}@dieei.unict.it).}}
 
@@
 \begin{abstract}
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized setup
-phase.
+In this paper we present DiSR, a first effort for a distributed
+segment-based approach to routing and defect mapping in a nano-scale,
+topology agnostic scenario based on DNA self-assembly. The main aim is
+exploiting the already-proven qualities of segment-based routing
+without neither requiring a topology graph as input, nor needing a
+centralized algorithm to configure network paths.  After introducing
+the conceptual elements and the execution model of DiSR, we show how
+the opensource Nanoxim platform has been used to evaluate the proposed
+approach in the process of discovering irregular network topology
+while estabilishing network segments.  Results show how DiSR still
+preserves some important properties (coverage, defect tolerance,
+scalability)  while avoiding centralized tree-based broadcasting and
+resource hungry solutions such as virtual channels and hardware
+redundancy. Finally, we analyzed a first, not yet optimised gate-level
+hardware implementation of the required control logic and storage for
+DiSR, demonstrating a relatively acceptable impact ranging from 10 to
+about 20\% of the budget of transistors available for each node.
 \end{abstract}
@@
 %------------------------------------------------------------------------------
+%\IEEEkeywords{...}
 
-\IEEEkeywords{...}
-
+\begin{IEEEkeywords}
+Nanotechnology, DNA, Self-assembly, Routing
+\end{IEEEkeywords}
 %------------------------------------------------------------------------------
 
-\section{Introduction}
-Exploring long term alternatives to the CMOS technology is gaining
-more and more revelance as the scaling trend of such devices continue
-to introduce new challenges. Power density, defect tolerance, testing
-costs and many other issues are only partially mitigated by multicore
-approaches~\ref{TODO}, but growing computing requirements will eventually need
-even more radical architectural modifications and new paradigms in
-future computer design.
-
-DNA-self assembled nanoscale architectures~\ref{TOOD} are emerging as promising
-technology due its tera/peta scale of integration, defect tolerance
-tolerance and potential computing capabilities~\ref{TODO}. This
-technologies is certainly still at its early stage of development,
-however different laboratory demos and prof-of-concepts architectures
-have been presented~\ref{TODO}.
-
-The main idea beyond this approach is to exploit the regularity and
-stabiliy of DNA sequences in orders to create grids onto which
-nano-devices (e.g. nanowires and CNFET~\ref{TODO}) can be attached by
-designing approapriate DNA tags. A detailed description of the
-chemical properties involved is beyond the scope of this paper, since
-we focus of the main challenges that this new fabrication process
-introduces in Computer Design. These are:
-\begin{itemize}
-\item small scale control of placement and connectivity
-\item large scal randomness
-\item high defect rates
-\end{itemize}
-
-This aspects of a DNA-self assembled process leads some architectural implications
-when approaching to the Computer Design. Architecture must consist of
-a distributed network of small computing and storage nodes, randomly
-connected. Data will be travelling on packets that must be routed
-using a topology-agnostic strategy, since no particular regularity can
-be assumed in such network.
-
-In this paper we present a first effort for a distributed
-segment-based approach to routing which exploits the already-proven
-qualities of segment-based routing without requiring as graph
-topology as input, and also without requiring a centralized algorithm
-which perform a \"segment setup\" phase.
-
-% irregular topology -> how to route ?
-
-%------------------------------------------------------------------------------
-
-\section{Related Work}
-% - Up/Down etc..
-% - SR is ok (topology independent) but requires the knowledge of the
-% topology graph -> impossible in DNA self assembly
-% - Our contribution: a distribuited approach for a segment-based
-%   routing. Not the "optimal" SR, just a SR "that works" in such
-%   complex irregular topologies where a graph could never be
-%   available.
-...
-Different architectures using nano-scale devices have been presented.A
-general purpose architecture for Self-Assembled Nano-Electronics has
-been presented to demostrate the potential of
-DNA-selfassembly~\ref{TODO}
-
-%------------------------------------------------------------------------------
-
-\section{Proposal}
-% - Draft of the DiSR idea
-% - how it should work
-...
-%------------------------------------------------------------------------------
-
-\section{Detailed DiSR model}
-We distinct among two different kind of data stored at each node:
-local environment data (LED) and dynamic behaviour status (DBS).
-
-\subsection{Local Environment Data (LED)}
-
-The LED is like a snapshot of the DiSR algorithm on each node,
-consisting in the following variables:
-
-segID:a value used to specify a segment id for the node. Depending on
-the values of visited/tvisited variables below, the node can be
-assigned to or candidate for a specific segment id.
-
-visited : a boolean value corresponding to the visited status. If visited is true
-and segID is different from NULL, then segID specifies the segment id
-the node belongs to. Note that a value different from NULL does not
-necessarily mean the node has been assigned to some segment (e.g. when
-searching starting segment is set visited by default even if not yet
-assigned to any segment). When false, the node is not yet visited.
-
-tvisited: a boolean value corresponding to the tvisited status. If
-true, the node is being considered as candidate for a segment, and the
-segID specifies the segment id for which the node it's candidate. When
-false, the node is not currently tvisited.
-
-link_visited[]: an array
-of values representing information about attached links, that is, the
-ID of the segment owning each link. When NULL, a link has not yet been
-marked as visited. TDB: do we need to introduce some value for the
-“bridge” status ? (e.g. a node connecting the terminal node of a
-subnet with the starting one of another)
-
-link_tvisited[]: an array of
-values representing information about attached links, e.g. the ID of
-the segment for which the link is candidate. When NULL, the link is
-currently not tvisited.  starting: boolean, true if the node it's a
-starting node for the subnet terminal:boolean, true if the node it's a
-terminal node for the subnet.  subnet:the subnet the node belongs to.
-If NULL, none.
-
-\subsection{Dynamic Behaviour Status (DBS)}
-In addition to the LED variables
-described above, further information should be stored in order to
-capture the current dynamic behaviour of the node. This is represented
-by the dynamic behaviour status (DBS) variable, which strictly depends
-on the LED data and the events occurring at the node. The DBS can have
-the following values:
-
-FREE: a node that has  not been yet considered  by the DiSR algorithm.
-The node is not marked as visited/tvisited/terminal/starting.
-
-BOOTSTRAP: a node which has been explicitly set as bootstrap node from
-an upper layer via. This is required because a
-
-STARTING_SEGMENT_REQUEST packet should be injected in order to start
-the whole process.
-
-ACTIVE_SEARCHING: a node from which a find process of new segments has
-been started and not yet cancelled or confirmed. This happens when all
-the following conditions are matched: the node is marked as visited,
-that is visited = TRUE
-
-CHECK: segID is set to some value reflecting
-the segment request sent there is a link that is being investigated by
-the node, that is a tvisited_link marked with the same id of the node
-
-CANDIDATE: a node currently candidate for belonging to some segment
-with id segid, not being itself the node from which the find process
-was started. The following conditions should be matched: tvisited =
-true, with segID=X different from node's id.  Two links set as
-link_tvisited with id X. Let’s refer them as  links 'i' and 'j'. Then
-link_tvisited[i] was set = X when the find process from an adjacent
-node reached the current node, while link_tvisited[j] has been set to
-X when the node itself started to investigate its free links for the
-segment request with id X. Note that while investigating its attached
-links, if the find process fails along path 'j', the current node can
-investigate another free node 'k' if suitable.
-
-CANDIDATE_STARTING:
-same as above, but the node is currently being considered as candidate
-for starting segment. Two main differences: Can confirm
-STARTING_SEGMENT_CONFIRM with the same segID when receiving a normal
-SEGMENT_REQUEST: Overwrites its status setting it to CANDIDATE for the
-segID frees the links previously set as tvisited during flooding
-
-ASSIGNED: a node for which the segment has been determined.  The
-segment segID attribute value is set to some id X different from NULL.
-The visited value is true NOTE: an ASSIGNED state is a quick temporary
-state, since it becomes ACTIVE_SEARCHING if a not (visited/tvisited)
-link is suitable for searching new segments (see next_visited
-procedure on paper)
-
-PROCESSED: a node which should take no other
-action, since all its links have been investigated.
-
-\subsection{Packets types Required}
-TODO: a lot of description is already present elsewhere, make this
-section smaller...
-
-SEGMENT_REQUEST: used to search candidates for a segment (not the
-first of the subnet, managed separately as a starting segment).
-
-SEGMENT_CONFIRM: used to create a segment. When received, if the node
-status is tvisited with a segID corresponding to the one indicated in
-the packet, the node learns to belong to the segment associated to the
-id. Further, it should forward this packet to the link where the
-original SEGMENT_REQUEST packet came from, so that all candidate nodes
-can learn the segment id they belong to. The following LED shoud be
-updated: The state of the node changes from tvisited to visited.  the
-link_tvisited previously set with the segID should be invalidated the
-link_visited variable associated to the incoming confirm should be set
-as segID. Note that if the request was flooded across different links,
-the link_visited variable associated to the other paths shouldn’t be
-set.  the link_visited variable associated to the link from which the
-request was originated should be set segID
-
-STARTING_SEGMENT_REQUEST: the request for the first segment of a
-subnet should be differentiated since all nodes (except the starting
-one) must forward the packet using a flooding mechanism. This is
-necessary since the request packet must reach the starting node, which
-is the only node marked as visited. As stated elsewhere, it should
-remembered that the first segment of each subnet it's  a loop that
-beginning/ending on the starting node.
-
-SEGMENT_CANCEL: used when the process of searching a segment along a
-certain path fails. When a node discovers that the path that includes
-the node itself is no more suitable, a SEGMENT_CANCEL is sent back
-across the link from which the SEGMENT_REQUEST was received.  Possible
-reasons for that: The node it’s already candidate for another segment
-The node it’s free but can’t find a free link (according the
-cyclelinks timeout) The node it’s tvisited for the same request id,
-previously forwarded that request along some free direction, but now
-it’s receiving a a cancel request and has no more free links
-
-\section{DiSR Execution Phases}
-
-\subsection{Creating the starting segment}
-
-Injecting request: all nodes have status FREE, except for a
-“bootstrap node” with status BOOTSTRAP, set by some signal from an
-upper layer via. This bootstrap node sets itself as “visited” and
-changes its status to ACTIVE_SEARCHING, sending a
-STARTING_SEGMENT_REQUEST across one of its not (visited/tvisited)
-links and.
-
-Flooding: Each node receiving a STARTING_SEGMENT_REQUEST,
-if not (visited/tvisited),  forwards  to the attached links that are
-not already marked as visited/tvisited using a flooding mechanism.
-Each of these links is then marked as tvisited with the segment id
-associated to the packet. Note that a node that has already received a
-STARTING_SEGMENT_REQUEST packet can simply ignore further packets
-associated to the same request, since has already contributed to the
-flooding. Note also that each of these packets has a max_segment_hops
-field to prevent packets from travelling undefinitively.
-
-setup of the starting-segment: when this STARTING_SEGMENT_REQUEST packet reaches
-the starting node (from a different link, of course), the starting
-segment is found. Then the starting node sends back a SEGMENT_CONFIRM
-packet with the same id along the link from which it received the
-STARTING_SEGMENT_REQUEST. Each node do same by changing its own status
-from tvisited to visited. So the confirmation packet is sent back from
-node to node and the starting segment is created.
-
-Note: A node knows to be tvisited due a  STARTING_SEGMENT_REQUEST.
-Then, when receiving a SEGMENT_REQUEST for other (not the starting)
-segment, simply knows to cancel the tvisited status of the node and
-its links, since if a segment arrived it means that a starting segment
-has already been found a there’s no need to keep the tvisited status
-for those broadcast status. What happens to nodes not receiving these
-segment request? they simply remain tvisited and after a timeout reset
-their state as free. But they could also remain tvisited for the
-starting segment, since this doesn’t affect their behaviour for future
-segment requests.
-
-failure: [TODO] should we handle this case ? i.e.
-marking as terminal ?
-
-\subsection{Finding other segments}
-
-Injecting request: A node in the ASSIGNED state can initiate a search for a
-segment, by sending a SEGMENT_REQUEST with an across one of its free
-links. Note that, since this is not the starting segment, in this case
-the packet should not reach the initiator, but just another visited
-node
-
-setup of the segment: The find process is successfull when a visited
-node receives the SEGMENT_REQUEST packet. Then, a SEGMENT_CONFIRM is
-sent back along the path that originated the request.  Failing while
-searching a segment: a node received a SEGMENT_REQUEST packet but
-matched one of the following conditions: the node is free but has no
-more suitable free links (can’t forward the SEGMENT_REQUEST) the node
-is tvisited candidate for another find process the request packet
-exceeded the max_segment_hops limit.  In all these cases the node
-sends back a SEGMENT_CANCEL along the proper link modifying its state
-to free. Each of the subsequent nodes will forward this SEGMENT_CANCEL
-only if no more free links can be explored starting from them.
-
-\subsection{Intra-node vs Inter-node parallelism}
-In the processes described above, we assumed that each node in the
-READY_SEARCHING state can start a find segment process by injecting a
-SEGMENT_REQUEST. However, a more accurate decision when defining DiSR
-should be made in order to decide whether or not the node must
-actually perform this action. 
-The point above is is strictly related to the general question: which
-level of “parallelism” should we allow in DiSR ? The adopted approach
-is that, although the nature of DiSR itself is intrinsicly parallel,
-the use of parallelism makes things work in a more complex way. In
-other words, DiSR is parallel when needed, but it does not exploit
-parallelism as an “improving feature”. When not needed, things should
-be serialized. For example: when a node is “ready searching” could
-start several find segment process associated to the same segment, one
-for each free link. But serializing this by investigating the free
-links in order could be a simplest solution. We refer to this saying
-that we avoid intra-node parallelism.  Note that while intra-node
-parallelism can be avoided, trying to avoid inter-node parallelism
-could be more complex than allowing the parallelism itself. Imagine
-for example the effort of trying to coordinate nodes so that an unique
-finding node process is actually running in the whole subnet. Thus, in
-contrast to the intra-node parallelism, the inter-node parallelism is
-a structural property of the DiSR algorithm and should not be avoided.
-%------------------------------------------------------------------------------
-
-\section{Node behaviour Model}
-Assumption: when discussing of
-visited/tvisited nodes, we are assuming with an id corresponding to
-the same subnet. Nodes involved in other subnet processes can simply
-ignore these packets. (TBD: formalize more clearly in which cases
-inter-subnet packets must be ignored, probably this happens most of
-the times, but in some cases, e.g. when a terminal node is found, some
-kind of communication packets are needed in order to crearte the
-bridge between two subnets.)
-
-\subsection{Receiving a STARTING_SEGMENT_REQUEST}
-
-When a node receives a STARTING_SEGMENT_REQUEST, with id = X,  there are the following cases:
-
-The node is visited with the same segID = x, that is it was the
-initiator of the request (set visited by definition): a first segment
-was found and should be confirmed sending back a SEGMENT_CONFIRM
-packet.
-
-The node is tvisited, with the same segID of the packet: due
-the flooding mechanism, another starting segment packet reached a node
-which was previously marked as tvisited from the same starting segment
-search process. Since the node is tvisited with the same id, it means
-that it already accomplished in the task of propagating that kind
-packets, thus can simply ignore the event thrashing the packet.  If
-the node it's not visited/tvisited: it should set itself as tvisited
-and forward the packet along its free links, using flooding. TBD: how
-the status should be changed ? depend on the flooding mechanism. Note
-that these links don’t include the link from which the request was
-received.
-
-The node it's visited, with different id in the packet.
-CHECK:  it is not the initiator of the starting segment request, but
-is already assigned to some segment!? assuming again we are discussing
-of nodes belonging to the same subnet, this should NOT happen, since
-the only visited node of the subnet should be the initial node from
-which the STARTING_SEGMENT_REQUEST originated. Note again that we are
-assuming that if the the node is visited or tvisited with the id of
-another subnet can simply ignore the request.  The node it's tvisited
-but it's not the initiator of the request (different id): same as
-above, if we are assuming nodes of the same subnet, this shouldn’t
-happen. If the node is of another subnet, can simply ignore the event.
-
-\subsection{Receiving a SEGMENT_REQUEST}
-When a node receives a SEGMENT_REQUEST, the are the following cases:
-
-The node is visited (and belongs to the same subnet): a segment was
-found and it should be confirmed sending back a SEGMENT_CONFIRM
-packet.
-
-The node is tvisited: it should discard the packet sending
-back a SEGMENT_CANCEL
-
-The node it's not visited/tvisited and has free
-links: it marks itself as tvisited and forwards the SEGMENT_REQUEST
-(one request at time) to each of its free links, according to some
-ordering
-
-CHECK: the difference between confirming a STARTING_SEGMENT_REQUEST
-and confirming a SEGMENT_REQUEST is that in the first case the node
-itself it's included in the segment , while in the second case the
-receiving node DOES NOT belong to the segment found. The motivation is
-that in the second case the node was already marked as visited because
-of being assigned to some segment found before, while in the
-starting-segment case, by definition, the first segment of a subnet
-begins with the starting node, which is marked as visited by the SR
-algorithm when searching for the first (starting) segment. Remember
-that the first segment of a subnet is a loop beginning with the
-starting node.
-
-\subsection{Receiving a SEGMENT_CANCEL}
-When a node receives a SEGMENT_CANCEL packet it means that searching
-for a segment along that path was unsuccessful. But if the node still
-has other free links to try, it should forward a SEGMENT_REQUEST to
-the next link (next according to some internal ordering). So a node
-forwards back the SEGMENT_CANCEL packet along the link that originated
-the SEGMENT_REQUEST packet ONLY when there are no more free links to
-try. If this is the case, the node modifies its status from tvisited
-to free and fordwards the SEGMENT_CANCEL packet to the link from which
-the request was received. The process stops when the SEGMENT_CANCEL
-packet reach the starting node that originated the request.
-
-\section{Nanoxim and simulation environment}
-% - Architecture of the nanoxim simulator
-% - how simulations were conducted
-...
-
-%------------------------------------------------------------------------------
-
-\section{Experiments}
-% - Graphs, tables
-% - comparison against other approaches
-...
+\input{introduction.tex}
+\input{disr.tex}
+\input{simulation.tex}
+\input{implementation.tex}
 

### 2013-09-20 PAPER/simulation.tex
Fixes

--- 2013-07-10 PAPER/simulation.tex
@@
 generated, a set of simulations with different seeds has been run
-for each system configuration. We found that TODO repetitions are
+for each system configuration. We found that 20 repetitions are
 required in order to obtain statistically significant results.
 
-\subsection{Other optimisations}
-Some optimisation parameters, which demostrated to improve the DiSR
-results have been fixed to some good values, but are not subject to
-further investigation; once again the focus here is not the
-optimal set of segments, but just demostrating a working approach. 
-These are optimisations are:
-\begin{itemize}
-\item{cycle\_links}: max number of retries across the set of links of
-each node. While searching for a free link due an incoming request,
-the same request is cancelled after a given number of tries. This
-gives to preceding node change to test a different paths. Default is set to 1.
-\item{bootstrap\_timeout}: number of time units that a bootstrap node
-should wait before assuming that a livelock in the starting segment
-process has occurred. In the worst case, we can imagine that longest
-path required is the one returning to the bootstrap node after having
-travelled across all the links. So, althought this is just an extreme
-situation, a good upper limit can be safely be set to NxN.
-\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
-setup process, a bootstrap node should not have defective links.
-Enabling this optimisation, a bootstrap node is immune to defects.
-We may think of a pre-boostrap phase that properly selects (from upper
-layer via) a bootstrap node which is tested as properly connected. We
-enabled this optimisation, however empirical tests showed us that only
-simulations using bootstrap nodes placed on edges would be heavily
-affected, since these are nodes starting with a lower number of links,
-e.g. corner nodes could only have two connected direction, so even a
-defective link could prevent starting segment packet to return to
-bootstrap to close the loop a create the segment.
-
-\end{itemize}
+% TODO: long paper
+%\subsection{Other optimisations}
+%Some optimisation parameters, which demostrated to improve the DiSR
+%results have been fixed to some good values, but are not subject to
+%further investigation; once again the focus here is not the
+%optimal set of segments, but just demostrating a working approach. 
+%These are optimisations are:
+%\begin{itemize}
+%\item{cycle\_links}: max number of retries across the set of links of
+%each node. While searching for a free link due an incoming request,
+%the same request is cancelled after a given number of tries. This
+%gives to preceding node change to test a different paths. Default is set to 1.
+%\item{bootstrap\_timeout}: number of time units that a bootstrap node
+%should wait before assuming that a livelock in the starting segment
+%process has occurred. In the worst case, we can imagine that longest
+%path required is the one returning to the bootstrap node after having
+%travelled across all the links. So, althought this is just an extreme
+%situation, a good upper limit can be safely be set to NxN.
+%\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
+%setup process, a bootstrap node should not have defective links.
+%Enabling this optimisation, a bootstrap node is immune to defects.
+%We may think of a pre-bootstrap phase that properly selects (from upper
+%layer via) a bootstrap node which is tested as properly connected. We
+%enabled this optimisation, however empirical tests showed us that only
+%simulations using bootstrap nodes placed on edges would be heavily
+%affected, since these are nodes starting with a lower number of links,
+%e.g. corner nodes could only have two connected direction, so even a
+%defective link could prevent starting segment packet to return to
+%bootstrap to close the loop a create the segment.
+%\end{itemize}
 
@@
 
-\begin{figure*}
-  \centering
-  \begin{tabular}{cc}
-    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_boot27_Xdefect_Ycoverage.eps} & 
-    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_boot127_Xdefect_Ycoverage.eps} \\
-    (a) & (b)
-  \end{tabular}
-  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
-  \label{fig:coverage}
-\end{figure*}
-
-Figure~\ref{fig:bootstrap} shows the effect of bootstrap node position
-on node coverage, for different defect rates. TODO COMMENT.
-
 \begin{figure}
@@
   \begin{tabular}{cc}
-    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_nodefect_Xbootstrap_Ycoverage.eps} & 
-    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_nodefect_Xbootstrap_Ycoverage.eps} \\
-    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_defect01_Xbootstrap_Ycoverage.eps} & 
-    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_defect01_Xbootstrap_Ycoverage.eps} \\
+    \includegraphics[width=0.22\textwidth]{pictures/set1.eps} & 
+    \includegraphics[width=0.22\textwidth]{pictures/coverage.eps} \\
+    \includegraphics[width=0.22\textwidth]{pictures/set2.eps} & 
+    \includegraphics[width=0.22\textwidth]{pictures/set3.eps} \\
     (a) & (b)
@@
 \end{figure}
+
+Figure~\ref{fig:bootstrap} shows the effect of bootstrap node position
+on node coverage, for different defect rates. TODO COMMENT.
 

### 2013-09-20 trunk/PAPER/paper.tex
Title
added pics

@@
 \newcommand{\etc}{\emph{etc.}}
-
+%\renewcommand{\baselinestretch}{0.9}\normalsize
 %------------------------------------------------------------------------------
@@
 
-\title{A First Effort for a Distributed Segment-based Approach on Topology-agnostic
-Self-Assembled Nano Networks}
+\title{A First Effort for a Distributed Segment-based Approach on Self-Assembled Nano Networks}
 
@@
 resource hungry solutions such as virtual channels and hardware
-redundancy. Finally, we analyzed a first, not yet optimised VHDL
+redundancy. Finally, we analyzed a first, not yet optimised gate-level
 hardware implementation of the required control logic and storage for
-DiSR, demonstrating a relatively acceptable impact ranging from 15 to
-about 25\% of the budget of transistors available for each node.
+DiSR, demonstrating a relatively acceptable impact ranging from 10 to
+about 20\% of the budget of transistors available for each node.
 \end{abstract}

### 2013-09-20 trunk/PAPER/simulation.tex
Removed some contracted verbal forms, and typos
Added comments to results

@@
 \section{Simulation and Results}
+\label{sec:simulation}
 
 In this section we will test the proposed DiSR approach to demonstrate
-its effectiveness from two different perspectives:
-\begin{itemize}
-\item Against the centralized segment based approach (SR), to evaluate
-if and how its known properties are still preserved in the new nano-scale distributed scenario
-\item Against topology agnostic approaches based on spanning
-trees and broadcasting, to measure how DiSR performs in discovering
-the network structure 
-\end{itemize}
+its effectiveness and to compare it against topology agnostic approach
+based on spanning trees and
+broadcasting~\cite{Patwardhan05evaluatingthe}, to measure how DiSR
+performs in covering the network structure
+
+%\item Against the centralized segment based approach (SR), to evaluate
+%if and how its known properties are still preserved in the new nano-scale distributed scenario
 
@@
 %Same range as defective links parameter.
-\item {Bootstrap node}: the node used from upper layer 
+\item {\emph{Bootstrap node}}: the node used from upper layer 
 to inject the DiSR process. When not explicitly investigating the
@@
 effectiveness.
-\item{Broadcast latency}: this measures how the time required to complete the
-segment assignment scale for increasing network sizes and defect rates
-\item{Bootstrap node effect}: this evaluates the impact of the chosen
+\item{\emph{Latency}}: this measures how the cycles required to complete the
+segment assignment scales for increasing network sizes and defect rates
+\item{\emph{Bootstrap node effect}}: this evaluates the impact of the chosen
 bootstrap node on the node coverage.
@@
 
-Further, to evaluate how DiSR compares against the centralized segment
-based algorithm, the following metrics have been adopted:
-\begin{itemize}
-%\item {Average Path Lenght}:
-%\item {Average Link Weight}:
-\item {Unidirectional restrictions:}
-\item {Number of Segments}:
-\end{itemize}
+%Further, to evaluate how DiSR compares against the centralized segment
+%based algorithm, the following metrics have been adopted:
+%\begin{itemize}
+%%\item {Average Path Lenght}:
+%%\item {Average Link Weight}:
+%\item {Unidirectional restrictions:}
+%\item {Number of Segments}:
+%\end{itemize}
 
@@
 %Enabling this optimisation, a bootstrap node is immune to defects.
-%We may think of a pre-boostrap phase that properly selects (from upper
+%We may think of a pre-bootstrap phase that properly selects (from upper
 %layer via) a bootstrap node which is tested as properly connected. We
@@
 
-\section{Results}
+\subsection{Results}
 \label{sec:results}
 
-In Figure~\ref{fig:coverage} is shown node coverage using different
-network sizes and bootstrap injection points. As can be seen,
-increasing the \% of defective node, TODO COMMENT...
+Figure~\ref{fig:results} collects the results in terms of node
+coverage and latency at different network sizes, defect rates and
+bootstrap injection points.  In particular graphs (a) and (b) show
+node coverage for DiSR and RPF tree based approach respectively. While
+the first aim of DiSR is not to reach the optimal coverage, we still
+can observe a quite good performance as compared to tree based
+approach. Note that defect rates beyond 25\% lead to many disconnected
+regions of nodes that this first of DiSR cannot handle; however, these
+level of defects should be considered as worst case scenarios, so the
+achieved coverage of $0.5$ is satisfying results for this first
+version of DiSR. As regards the the network size it seems to have a
+limited impact when defect rate do not introduce to much disconnected
+regions.
 
-\begin{figure*}
+The number of cycles required to complete the segment mapping
+process is shown in latency graph (c). Comparison against tree-based
+has been omitted for space reasons, however similar numbers (in terms
+of upper bound) have been reported
+(see~\cite{Patwardhan05evaluatingthe} for details). What it's more
+interesting is to observe is how DiSR latency scales with network
+size. For example, going from 900 to 2500 nodes, at the medium defect
+rate of $0.15$, leads to an increse from 3000 to 4500 cycles. Note how
+the effect of defect rate is incresing until the threshold of $0.25$
+is reached, meaning that while DiSR finds it more difficult to
+complete the process due incresing defective paths, it still discover
+new segments when let running for a more extended amount of cycles.
+After that threshold, the impact of entire disconnected regions
+becomes predominant and DiSR more quickly complete the process
+covering the nodes that can be reached.
+
+\begin{figure}
   \centering
   \begin{tabular}{cc}
-    \includegraphics[width=0.40\textwidth]{pictures/set1.eps} & 
-    \includegraphics[width=0.40\textwidth]{pictures/set3.eps} \\
-    (a) & (b)
+    \includegraphics[width=0.22\textwidth]{pictures/set1.eps} & 
+    \includegraphics[width=0.22\textwidth]{pictures/coverage.eps} \\
+    \includegraphics[width=0.22\textwidth]{pictures/set2.eps} & 
+    \includegraphics[width=0.22\textwidth]{pictures/set3.eps} \\
+    (a) & (b) \\
+    (c) & (d) \\
   \end{tabular}
-  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
-  \label{fig:coverage}
-\end{figure*}
+  \caption{DiSR (a) and RPF (b) node coverage (c) Latency and effect
+  of bootstrap node (d)}
+  \label{fig:results}
+\end{figure}
 
-Figure~\ref{fig:bootstrap} shows the effect of bootstrap node position
-on node coverage, for different defect rates. TODO COMMENT.
-
-%\begin{figure}
-%  \centering
-%  \begin{tabular}{cc}
-%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_nodefect_Xbootstrap_Ycoverage.eps} & 
-%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_nodefect_Xbootstrap_Ycoverage.eps} \\
-%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_defect01_Xbootstrap_Ycoverage.eps} & 
-%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_defect01_Xbootstrap_Ycoverage.eps} \\
-%    (a) & (b)
-%  \end{tabular}
-%  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
-%  \label{fig:bootstrap}
-%\end{figure}
-
-Next, Figure~\ref{fig:latency_size} shows latency as function of
-network size, with different defect rates, while Figure~\ref{fig:latency_defective}
-shows the same latency when different bootstrap nodes are
-considered.... TODO COMMENT
-
-TODO: something like Broadcast Tree properties (sez.  5.4)
+Finally, picture (d) visually represent  the stability of the approach
+against different choices of the bootstrap node in a 10x10 network.
+This is an important aspect to evaluate when considering that one of
+the main advantages of DiSR against all the tree based approaches
+should be the ability of choosing whatever bootstrap node, without
+having to care of any particular \emph{root-node role} assumed in the future.
+In other words, after segments have been estabilished, the bootstrap node
+is like every other node, i.e. it is not center of a structure, and it
+is not an hotspot for the traffic distribution. The results in terms
+of coverage,  shown for low, medium and high defect profiles, seems to
+demostrate a relatively limited impact of the bootstrap choice in
+the low/medium scenarios, while a 30\%instability is found for very high defect
+rates. This also sounds acceptable, since when lot of defective nodes
+are present, the particular position of the bootstrap choice could
+lead to completely different evolution in the DiSR setup process.

### 2013-09-20 trunk/PAPER/introduction.tex
fixes refs moved contribution comments

@@
   \centering
-    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps}
+    \includegraphics[width=0.30\textwidth]{pictures/dna2b.eps}
   \caption{DNA tag matching}
@@
 
-The contribution presented in this paper is to bring the advantages of
+The main contribution presented in this paper is to bring the advantages of
 a segment-based approach to deadlock freedom without requiring any topology graph,
@@
 
+The paper is organized as follows: in Section~\ref{sec:related_works}
+we summarize the main approaches to topology agnostic routing. Next in
+Section~\ref{sec:disr_concepts} are described the main elements of the
+proposed approach, showing a the DiSR execution model in
+Section~\ref{sec:execution_model}.  In Section~\ref{sec:simulation}
+simulations are carried out with the opensource tool Nanoxim to
+demostrate how DiSR preserves some of the main segment-based
+properties and how compares to the tree-based approaches. Finally a
+draft of a architectural implementation is shown in
+Section~\ref{sec:implementation} to evaluate the feasibility of the
+approach in terms of node complexity.
+
 \section{Related Works}
-
+\label{sec:related_works}
 Several works~\cite{sancho2002, skeie2002, skeie2004, koibuchi2003} have been presented addressing the problem of topology
@@
 assembled networks we are assuming as background.
-Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} don't use virtual channels to
+Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} do not use virtual channels to
 achieve deadlock freedom, but turn proibitions. 
-In particular, up*/down* exploits the creation of a spanning tree of the
+In particular, authors of~\cite{Patwardhan05evaluatingthe} exploits the creation of a spanning tree of the
 topology, then placing bidirectional restrictions by avoiding a packet
@@
 
-The DiSR approach presented in this works is a first attempt of
-reaching the same goal of SR (e.g. estabilishing segments) without
-requiring a topology graph and a centralized exectution.
-
-The paper is organized as follows: in Section~\ref{sec:disr_concepts}
-we introduce the main elements of the DiSR approach, describing  
-a draft of the DiSR model in Section~\ref{sec:disr_model}
-together with execution model details in Section~\ref{sec:disr_detaled_model}.
-In Section~\ref{sec:simulatio} simulations are carried out with the opensource tool Nanoxim
-to demostrate how DiSR preserves some of the main segment-based
-properties and how compares to the tree-based approaches. Finally a
-draft of a VHDL hardware implementation is shown in
-Section~\ref{sec:implementation} to evaluate the feasibility of the
-approach in terms of node complexity.
+The DiSR approach presented in this work is a first attempt of
+reaching the same goal of a segment based approach, that is
+estabilishing segments, without requiring any topology graph or
+centralized execution.

### 2013-09-20 PAPER/disr.tex
label for the implementation added
label

--- 2013-07-10 trunk/PAPER/disr.tex
@@
 \emph{Segment}: a Segment is basically a path of consecutive node
-and links. 
+and links. All segments start with a link attached to a node which
+belongs to different segment, ending with a link also attached to a
+node belonging to a different segment. A exception is the first
+segment estabilished in the network, called \emph{starting segment} which is  a loop
+beginning/ending on a particular node defined as bootstrap node.
+
 The idea is to partition the network in a set of disjoint segments, and then
-placing a turn restriction within each segment. It has been proved~\cite{}
+placing a turn restriction within each segment. It has been proved~\cite{mejia_ipdps06}
 that such a set of turn prohibitions guarantees dealock freedom and
@@
 \begin{itemize}
-\item{segID}:a value used to specify a segment id for the node. Depending on
-the values of \emph{visited}/\emph{tvisited} variables below, a node can be
-assigned to or candidate for a specific segment id.  
-\item{\emph{visited}}: a boolean value. If \emph{visited} is true
-and segID is different from NULL, then segID specifies the segment id
-to which the node has been assigne. Note that a value different from NULL does not
-necessarily mean the node has been assigned to some segment (e.g. when
-searching starting segment is set \emph{visited} by default even if not yet
-assigned to any segment). 
-\item{\emph{tvisited}}: a boolean value. If
-true, the node is being considered as candidate for a segment, and the
-segID value specifies the segment id for which the node it's candidate. 
+\item{\emph{segID}}:a value used to specify the segment to which the
+node has been assigned or is candidate for being assigned.
+\item{\emph{visited}}: a boolean value. When \emph{true}
+a \emph{segID} different from \texttt{NULL} specifies the segment 
+to which the node has been assigned.
+
+% TODO: the following is true, but complicates things at this stage
+%Note that a value different from \emph{NULL} does not
+%necessarily mean the node has been assigned to some segment (e.g. when
+%searching starting segment is set \emph{visited} by default even if not yet
+%assigned to any segment).
+
+\item{\emph{tvisited}}: a boolean value. If \emph{true}, the node is
+being considered as candidate for a segment, and the \emph{segID} value
+specifies the segment id for which the node is candidate. 
 \item{\emph{link\_visited[]}}: an array
 of values representing information about attached links, that is, the
-segID of the segment owning each link. When NULL, the corresponding link has not yet been
+segID of the segment owning each link. When \texttt{NULL}, the corresponding link has not yet been
 assigned.
@@
 \item{\emph{link\_tvisited[]}}: an array of
-values representing information about attached links, that is, the segID of
-the segment for which the link is candidate. When NULL, the link is
+values representing information about attached links, that is, the \emph{segID} of
+the segment for which the link is candidate. When \texttt{NULL}, the link is
 currently not \emph{tvisited}.  
-\item{\emph{starting}}: boolean, true if the node it's a
-starting node from which the whole process was initiated.
 \end{itemize}
+%\item{\emph{starting}}: boolean, \emph{true} if the node is a
+%starting node from which the whole process was initiated.
+%\end{itemize}
 
-In addition to the LED variables described above, further information
-should be stored in order to capture the current dynamic behaviour of
-the node. This is represented by the dynamic behaviour status (DBS)
-variable, which strictly depends on the LED data and the events
-occurring at the node. The DBS can have the following values:
+In addition to the \emph{LED} variables described above, further
+information should be stored in order to capture the current dynamic
+behaviour of the node. This is represented by \emph{DBS} variable,
+which strictly depends on the \emph{LED} data and the events occurring
+at the node. The \emph{DBS} can have the following values:
 
@@
 \item{\emph{Free}}: a node that has  not been yet considered  by the DiSR algorithm.
-The node is not marked as \emph{visited}/\emph{tvisited}/terminal/starting.
-\item{\emph{Boostrap}}: a node which has been explicitly set as bootstrap node from
-an upper layer via. This is required because a
-\texttt{STARTING\_SEGMENT\_REQUEST} packet should be injected in order to start
-the whole process.
+The node is not marked as \emph{visited}/\emph{tvisited}.
+\item{\emph{Bootstrap}}: a node which has been explicitly set as bootstrap node from
+an upper layer via. 
+% TODO: this and all the other details on the items below should be
+% checked and moved elsewhere for a future long paper
+
+%This is required because a
+%\texttt{STARTING\_SEGMENT\_REQUEST} packet should be injected in order to start
+%the whole process.
 \item{\emph{ActiveSearching}}: a node from which a find process of new segments has
-been started and not yet cancelled or confirmed. This happens when all
-the following conditions are matched: the node is marked as \emph{visited},
-that is \emph{visited} = TRUE 
-TODO: segID is set to some value reflecting
-the segment request sent there is a link that is being investigated by
-the node, that is a tvisited\_link marked with the same id of the node 
+been started and not yet cancelled or confirmed. 
+%This happens when all
+%the following conditions are matched: the node is marked as \emph{visited},
+%that is \emph{visited} = TRUE 
+%TODO: \emph{segID} is set to some value reflecting
+%the segment request sent there is a link that is being investigated by
+%the node, that is a tvisited\_link marked with the same id of the node 
 \item{\emph{Candidate}}: a node currently candidate for belonging to some segment
 with id segid, not being itself the node from which the find process
-was started. The following conditions should be matched: \emph{tvisited} =
-true, with segID=X different from node's id.  Two links set as
-\emph{link\_tvisited} with id X. Let’s refer them as  links 'i' and 'j'. Then
-link\_tvisited[i] was set = X when the find process from an adjacent
-node reached the current node, while link\_tvisited[j] has been set to
-X when the node itself started to investigate its free links for the
-segment request with id X. Note that while investigating its attached
-links, if the find process fails along path 'j', the current node can
-investigate another free node 'k' if suitable.  
+was started.
+
+%The following conditions should be matched: \emph{tvisited} =
+%true, with segID=X different from node's id.  Two links set as
+%\emph{link\_tvisited} with id X. Let’s refer them as  links 'i' and 'j'. Then
+%link\_tvisited[i] was set = X when the find process from an adjacent
+%node reached the current node, while link\_tvisited[j] has been set to
+%X when the node itself started to investigate its free links for the
+%segment request with id X. Note that while investigating its attached
+%links, if the find process fails along path 'j', the current node can
+%investigate another free node 'k' if suitable.  
 \item{\emph{CandidateStarting}}: same as above, but the node is currently being considered as candidate
-for starting segment. Two main differences: Can confirm
-\texttt{STARTING\_SEGMENT\_CONFIRM} with the same segID when receiving a normal
-\texttt{SEGMENT\_REQUEST}: Overwrites its status setting it to \emph{Candidate} for the
-segID frees the links previously set as \emph{tvisited} during flooding
+for starting segment.
+
+%Two main differences: Can confirm
+%\texttt{STARTING\_SEGMENT\_CONFIRM} with the same \emph{segID} when receiving a normal
+%\texttt{SEGMENT\_REQUEST}: Overwrites its status setting it to \emph{Candidate} for the
+%segID frees the links previously set as \emph{tvisited} during flooding
 \item{\emph{Assigned}}: a node for which the segment has been determined.  The
-segment segID attribute value is set to some id X different from NULL.
-The \emph{visited} value is true NOTE: an \emph{Assigned} state is a quick temporary
-state, since it becomes \emph{ActiveSearching} if a not (\emph{visited}/tvisited)
-link is suitable for searching new segments (see next\_visited
-procedure on paper) 
+segment \emph{segID} attribute value is set to some id X different from \texttt{NULL}.
+%The \emph{visited} value is \emph{true} NOTE: an \emph{Assigned} state is a quick temporary
+%state, since it becomes \emph{ActiveSearching} if a not (\emph{visited}/tvisited)
+%link is suitable for searching new segments (see next\_visited
+%procedure on paper) 
 \end{itemize}
 
-\subsection{Creating the starting segment}
+\subsection{Sketch of DiSR}
 
@@
 \section{Detailed Node behaviour Model}
+\label{sec:execution_model}
 
-The LED variables at each node are are initially set so the node and
+The \emph{LED} variables at each node are are initially set so the node and
 each of its links is set as free. The only node that makes exception
@@
 the subsequent events happening at each node are the consequence of
-its current dynamic status (DBS) and the packets received, as depicted
-in the Figure~\ref{fig:status_machine}.
+its current dynamic status (DBS) and the packets received.
 
-\label{sec:disr_detailed_model}
+\begin{figure}
+  \centering
+    \includegraphics[width=0.30\textwidth]{pictures/state_machine.eps}
+  \caption{DiSR node execution model}
+  \label{fig:dna_tag}
+\end{figure}
+
 %TODO: add state machines
@@
 
-The request for the first segment of a
-subnet should be managed differently since all nodes (except the starting
-one) must forward the packet using a flooding mechanism. This is
-necessary since the request packet must reach the starting node, which
-is the only node marked as \emph{visited}. As stated elsewhere, it should
-remembered that the first segment of each subnet it's  a loop that
-beginning/ending on the starting node.
-
-When a node receives a \texttt{STARTING\_SEGMENT\_REQUEST}, with SegID = X,  there
-are the following cases:
+The request for the first segment should be managed differently since
+all nodes (except the starting one) must forward the packet using a
+flooding mechanism. This is necessary since the request packet must
+return the bootstrap node.
+When a node receives a \texttt{STARTING\_SEGMENT\_REQUEST}, the
+following cases can happen:
 
 \begin{itemize}
-\item The node is visited with the same segID = x, that is it was the
-initiator of the request (set visited by definition): a first segment
-was found and should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
+\item The node is not candidate or assigned: it should set itself as
+\emph{Candidate} and forward the packet along its free links, using
+flooding.  
+\item The node is \emph{Candidate} with the same
+\emph{segID} and \emph{src\_id} is equal to node id: this means the
+node was the initiator of the request, so a starting segment was found and
+should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
 packet.  
-\item The node is \emph{tvisited}, with the same segID of the packet: due
+\item The node is \emph{Candidate}, with the same \emph{segID} of the
+packet but \emph{src\_id} is different from node id: due
 the flooding mechanism, another starting segment packet reached a node
-which was previously marked as \emph{tvisited} from the same starting segment
-search process. Since the node is \emph{tvisited} with the same id, it means
+which was previously marked as \emph{Candidate} from the same starting segment
+search process. Since the node is candidate with the same id, it means
 that it already accomplished in the task of propagating that kind
-packets, thus can simply ignore the event thrashing the packet.  If
-the node it's not visited/\emph{tvisited}: it should set itself as \emph{tvisited}
-and forward the packet along its free links, using flooding. TBD: how
-the status should be changed ? depend on the flooding mechanism. Note
-that these links don’t include the link from which the request was
-received.  
-\item The node it's visited, with different id in the packet.
-CHECK:  it is not the initiator of the starting segment request, but
-is already assigned to some segment!? assuming again we are discussing
-of nodes belonging to the same subnet, this should NOT happen, since
-the only visited node of the subnet should be the initial node from
-which the \texttt{STARTING\_SEGMENT\_REQUEST} originated. Note again that we are
-assuming that if the the node is visited or \emph{tvisited} with the id of
-another subnet can simply ignore the request.  The node it's \emph{tvisited}
-but it's not the initiator of the request (different id): same as
-above, if we are assuming nodes of the same subnet, this shouldn’t
-happen. If the node is of another subnet, can simply ignore the event.
+packets, thus can simply ignore the event thrashing the packet.  
+%TBD: how the status should be changed ? depend on the flooding mechanism. Note
+%that these links do not include the link from which the request was
+%received.  
+\item The node is \emph{Candidate}, with a different \emph{segID}: 
+this simply means that the starting segment received is deprecated,
+because the node has already accepted non-starting segment requests
+originated from other \emph{Assigned} nodes.
+\item The node is \emph{Assigned}, with a different \emph{segID}:
+same as the previous case.
+
+% TODO: check and remove, the below is not true
+%CHECK:  it is not the initiator of the starting segment request, but
+%is already assigned to some segment!? assuming again we are discussing
+%of nodes belonging to the same subnet, this should NOT happen, since
+%the only visited node of the subnet should be the initial node from
+%which the \texttt{STARTING\_SEGMENT\_REQUEST} originated. Note again that we are
+%assuming that if the the node is visited or \emph{tvisited} with the id of
+%another subnet can simply ignore the request.  The node is \emph{tvisited}
+%but it is not the initiator of the request (different id): same as
+%above, if we are assuming nodes of the same subnet, this should not
+%happen. If the node is of another subnet, can simply ignore the event.
 
@@
 \begin{itemize}
-\item The node is \emph{visited} (and belongs to the same subnet): a segment was
+\item The node is \emph{Assigned}: a segment was
 found and it should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
 packet.  
-\item The node is \emph{tvisited}: it should discard the packet sending
+\item The node is \emph{Candidate}: it should discard the packet sending
 back a \texttt{SEGMENT\_CANCEL} 
-\item The node it's not \emph{visited}/\emph{tvisited} and has free
-links: it marks itself as \emph{tvisited} and forwards the \texttt{SEGMENT\_REQUEST}
-(one request at time) to each of its free links, according to some
-ordering
-\item NOTD: the difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
-and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
-itself it's included in the segment , while in the second case the
-receiving node DOES NOT belong to the segment found. The motivation is
-that in the second case the node was already marked as \emph{visited} because
-of being assigned to some segment found before, while in the
-starting-segment case, by definition, the first segment of a subnet
-begins with the starting node, which is marked as \emph{visited} by the SR
-algorithm when searching for the first (starting) segment. Remember
-that the first segment of a subnet is a loop beginning with the
-starting node. 
+\item The node is not \emph{Assigned} or \emph{Candidate} and has free
+links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
+to one of its free links, according to some internal ordering
 \end{itemize}
 
-\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}
-When received, if the node status is \emph{tvisited} with a segID corresponding to the one indicated in
+NOTE: the main difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
+and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
+itself is included in the segment , while in the second case the
+receiving node does not belong to the segment found.
+
+%The motivation is
+%that in the second case the node was already marked as \emph{visited} because
+%of being assigned to some segment found before, while in the
+%starting-segment case, by definition, the first segment of a subnet
+%begins with the starting node, which is marked as \emph{visited} by the SR
+%algorithm when searching for the first (starting) segment. Remember
+%that the first segment of a subnet is a loop beginning with the
+%starting node.
+
+\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
+When received, if the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
 the packet, the node learns to belong to the segment associated to the
@@
 original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
-can learn the segment id they belong to.  LED shoud be
+can learn the segment id they belong to.  \emph{LED} shoud be
 updated: The state of the node changes from \emph{tvisited} to \emph{visited}.  the
-\emph{link\_tvisited} previously set with the segID should be invalidated the
+\emph{link\_tvisited} previously set with the \emph{segID} should be invalidated the
 \emph{link\_visited} variable associated to the incoming confirm should be set
 as segID. Note that if the request was flooded across different links,
-the \emph{link\_visited} variable associated to the other paths shouldn’t be
+the \emph{link\_visited} variable associated to the other paths should not be
 set.  the \emph{link\_visited} variable associated to the link from which the

### 2013-09-20 PAPER/introduction.tex
added pics
Removed pic for space

@@
 their early stage of development, however different laboratory demos and
-prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1, pistol2009}.
+prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006_1, pistol2009}.
+%, patwardhan2006
 The main idea behind this approach is to exploit the physical regularity and
@@
 only where its own DNA tag matches a complementary tag on the DNA grid
-scaffold (see figure~\ref{fig:dna_tag}.
-
-\begin{figure}
-  \centering
-    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps}
-  \caption{DNA tag matching}
-  \label{fig:dna_tag}
-\end{figure}
-
+scaffold.
+%(see figure~\ref{fig:dna_tag}.
+%
+%\begin{figure}
+%  \centering
+%    \includegraphics[width=0.30\textwidth]{pictures/dna2b.eps}
+%  \caption{DNA tag matching}
+%  \label{fig:dna_tag}
+%\end{figure}
 A detailed description of the chemical properties involved is far
@@
 the three main challenges that this new fabrication process introduces
-in Computer Design: (i)limited node complexity, (ii) large scale
-randomness and (iii) high defect rates.
+in Computer Design: \emph{(i) limited node complexity}, \emph{(ii) large scale
+randomness} and \emph{(iii) high defect rates}.
 
@@
 achieve deadlock freedom, but turn proibitions. 
-In particular, up*/down* exploits the creation of a spanning tree of the
+In particular, authors of~\cite{Patwardhan05evaluatingthe} exploits the creation of a spanning tree of the
 topology, then placing bidirectional restrictions by avoiding a packet
@@
 
-The DiSR approach presented in this works is a first attempt of
-reaching the same goal of SR (e.g. estabilishing segments) without
-requiring a topology graph and a centralized exectution.
-
-The paper is organized as follows: in Section~\ref{sec:disr_concepts}
-we introduce the main elements of the DiSR approach, describing  
-a draft of the DiSR model in Section~\ref{sec:disr_model}
-together with execution model details in Section~\ref{sec:disr_detaled_model}.
-In Section~\ref{sec:simulatio} simulations are carried out with the opensource tool Nanoxim
-to demostrate how DiSR preserves some of the main segment-based
-properties and how compares to the tree-based approaches. Finally a
-draft of a architectural implementation is shown in
-Section~\ref{sec:implementation} to evaluate the feasibility of the
-approach in terms of node complexity.
+The DiSR approach presented in this work is a first attempt of
+reaching the same goal of a segment based approach, that is
+estabilishing segments, without requiring any topology graph or
+centralized execution.

### 2013-09-20 trunk/PAPER/disr.tex
added pics
Final strechting

@@
 The main concept behind of the original SR approach is the
-\emph{Segment}: a Segment is basically a path of consecutive node
-and links. All segments start with a link attached to a node which
-belongs to different segment, ending with a link also attached to a
-node belonging to a different segment. A exception is the first
-segment estabilished in the network, called \emph{starting segment} which is  a loop
-beginning/ending on a particular node defined as bootstrap node.
-
+\emph{segment}: a segment is basically a path of consecutive node and
+links. A segment $S_1$ starts with a link attached to a node which
+belongs to different segment $S_2$, ending with a link attached to a
+node belonging to a different segment $s_3$. In other words, a segment
+a path between connecting two other different segments.A exception is
+the first segment estabilished in the network, called \emph{starting
+segment} which is  a loop beginning/ending on a particular node
+defined as \emph{bootstrap node}.
 The idea is to partition the network in a set of disjoint segments, and then
@@
 Roughly speaking, the execution of can be described as the execution
-of the following phases:
-\begin{itemize}
-\item Injection of the DiSR process from upper layer to set a bootstrap
-node
-\item Bootstrap node broadcasting to create the first segment of the subnet
-\item Parallel requests starting from assigned node to discover other segments
+of the following phases: (1) Injection of the DiSR process from upper layer to set a bootstrap
+node (2) Bootstrap node broadcasting to create the first segment of the subnet
+(3) Parallel requests starting from assigned node to discover other
+segments. The following subsection describe the data structure and
+execution model required at each node.
 %\item Turn proibition in each confirmed segment
 %\item Draining of remaining packet due timeouts
-\end{itemize}
 
-Once again, it should be pointed out that nowhere in the network there
-is such a global vision of these exection phases. A more detailed
-description of the exection model at each node is discussed in the
-next section.
+%Once again, it should be pointed out that nowhere in the network there
+%is such a global vision of these exection phases. A more detailed
+%description of the exection model at each node is discussed in the
+%next section.
 
@@
 consisting in the following variables:
-
 \begin{itemize}
@@
 to which the node has been assigned. 
-
 % TODO: the following is true, but complicates things at this stage
@@
 %assigned to any segment). 
-
 \item{\emph{tvisited}}: a boolean value. If \emph{true}, the node is
@@
 % checked and moved elsewhere for a future long paper
-
 %This is required because a
@@
 for starting segment. 
-
 %Two main differences: Can confirm
@@
 
-\subsection{Sketch of DiSR}
+\subsection{DiSR Execution Model}
 
+In Figure~\ref{fig:state_machine} are depicted the main events
+representing the execution model at each node. The DiSR control
+packets described in the previous subsection trigger node events,
+which eventually change $DBS$ status according to the current value of
+$LED$ variables and the type of the packet received. The main DiSR
+phases, together with a reference to the particular status transition
+shown in Figure~\ref{fig:state_machine} are described in the
+following.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.30\textwidth]{pictures/state_machine.eps}
+  \caption{DiSR node execution model}
+  \label{fig:state_machine}
+\end{figure}
 \begin{itemize}
@@
  node with status \emph{Bootstrap}, set by some signal from an
-upper layer via. When starting, this bootstrap node sets itself as \emph{visited} and
-changes its status to \emph{ActiveSearching}, injecting a
+upper layer via (a). When starting, this bootstrap node 
+changes its status to \emph{ActiveSearching} (b), injecting a
 \texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links.
@@
 \item{\textbf{Flooding}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
-if not yet (\emph{visited}/\emph{tvisited}),  forwards it to its free links using a flooding mechanism.
-Each of these links is then marked as \emph{tvisited} with the segment id
+if $Free$ forwards it to its free links using a flooding mechanism and
+becoming $CandidateStarting$ (g).
+Each of its free links is then marked as \emph{tvisited} with the segment id
 associated to the request. Note that a node that has already received a
@@
 
-\item{\textbf{Confirming the Starting Segment}}: when this \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
-the starting node (from a different link, of course), the starting
-segment is found. Then the starting node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
-packet with the same id along the link from which it received the
-\texttt{STARTING\_SEGMENT\_REQUEST}. Each node do same by changing its own status
-to \emph{Assigned}. So the confirmation packet is sent back from
+\item{\textbf{Confirming the Starting Segment}}: when the \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
+the bootstrap node (from a different link, of course), the starting
+segment is found. Then the boostrap node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
+packet along the link from which it received the
+\texttt{STARTING\_SEGMENT\_REQUEST} and becomes $Assigned$ (c). Each
+node receiving the confirm do same by changing its own status
+to \emph{Assigned} (l). So the confirmation packet is sent back from
 node to node and the starting segment is created.
 
-Note: A node knows to be \emph{Candidate} due a
-\texttt{STARTING\_SEGMENT\_REQUEST}.  Then, when receiving a simple
-(not starting) \texttt{SEGMENT\_REQUEST} , it can simply cancel its
-previous \emph{Candidate} status, since this second
+Note: A node being \emph{CandidateStarting}, when receiving a simple
+(not starting) \texttt{SEGMENT\_REQUEST} , can simply cancel its
+previous \emph{CandidateStarting} status and set itself as
+$Candidate$ for that request (h), since this new
 request means that the starting segment has already been found.
@@
 
-\item{\textbf{Injecting other request}}: Each node in the \emph{Assigned} status can initiate a search for a
-segment, by sending a \texttt{SEGMENT\_REQUEST} across one of its free
-links. Note that, since this is not the starting segment, in this case
-the packet should not return back to the initiator, but just another visited
-node
+\item{\textbf{Injecting other requests}}: Each node in the
+\emph{Assigned} status can initiate a search for a segment, by sending
+a \texttt{SEGMENT\_REQUEST} across one of its free links (d). Note
+that since this is not the starting segment in this case the packet
+should not reach the initiator, but just another \emph{Assigned} node.
+
 \item{\textbf{Setup of a segment}}: The find process is successfull
-when an \emph{Assigned} node receives the \texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
-sent back along the path that originated the request.  
+when an already \emph{Assigned} node receives the
+\texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
+sent back along the path that originated the request (e), while the
+node remain $Assigned$ (since it could confirm more segments). Each node
+previously set as $Candidate$ for that segment id, when receiving the
+confirm packet changes its status to $Assigned$ (m) and forwards back
+the same confirm until it reaches the initator of the request, which
+changes from $ActiveSearching$ to $Assigned$ (c).
+
 \item{\textbf{Failing while searching a segment}}: a node received a \texttt{SEGMENT\_REQUEST} packet but
-matched one of the following conditions: the node is free but has no
-more suitable free links (can’t forward the \texttt{SEGMENT\_REQUEST}) the node
-is \emph{tvisited} candidate for another find process the request packet
-exceeded the max\_segment\_hops limit.  In all these cases the node
-sends back a \texttt{SEGMENT\_CANCEL} along the proper link modifying its state
-to free. Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
-only if no more free links can be explored starting from them.
+matched one of two the following conditions: the node is $Free$ but has no
+more suitable free links (thus can’t forward the
+\texttt{SEGMENT\_REQUEST})(f); the node
+is candidate for another find process(i).  In all these cases the node
+sends back a \texttt{SEGMENT\_CANCEL} along the proper link. 
+%Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
+%only if no more free links can be explored starting from them.
 \end{itemize}
@@
 
-\section{Detailed Node behaviour Model}
-\label{sec:disr_detailed_model}
+% TODO: FIX and RE-enable in long paper
 
-The \emph{LED} variables at each node are are initially set so the node and
-each of its links is set as free. The only node that makes exception
-is the bootstrap node, initialized in the \emph{Bootstrap} status. All
-the subsequent events happening at each node are the consequence of
-its current dynamic status (DBS) and the packets received.
-
-%TODO: add state machines
-
-% TODO: fix, move elsewhere or delete
-%Assumption: when discussing of visited/\emph{tvisited} nodes, we are assuming
-%with an id corresponding to the same subnet. Nodes involved in other
-%subnet processes can simply ignore these packets. (TBD: formalize more
-%clearly in which cases inter-subnet packets must be ignored, probably
-%this happens most of the times, but in some cases, e.g. when a
-%terminal node is found, some kind of communication packets are needed
-%in order to crearte the bridge between two subnets.)
-
-\subsection{Receiving a \texttt{STARTING\_SEGMENT\_REQUEST}}
-
-The request for the first segment should be managed differently since
-all nodes (except the starting one) must forward the packet using a
-flooding mechanism. This is necessary since the request packet must
-return the bootstrap node.
-When a node receives a \texttt{STARTING\_SEGMENT\_REQUEST}, the
-following cases can happen:
-
-\begin{itemize}
-\item The node is not candidate or assigned: it should set itself as
-\emph{Candidate} and forward the packet along its free links, using
-flooding.  
-\item The node is \emph{Candidate} with the same
-\emph{segID} and \emph{src\_id} is equal to node id: this means the
-node was the initiator of the request, so a starting segment was found and
-should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
-packet.  
-\item The node is \emph{Candidate}, with the same \emph{segID} of the
-packet but \emph{src\_id} is different from node id: due
-the flooding mechanism, another starting segment packet reached a node
-which was previously marked as \emph{Candidate} from the same starting segment
-search process. Since the node is candidate with the same id, it means
-that it already accomplished in the task of propagating that kind
-packets, thus can simply ignore the event thrashing the packet.  
-%TBD: how the status should be changed ? depend on the flooding mechanism. Note
-%that these links do not include the link from which the request was
-%received.  
-\item The node is \emph{Candidate}, with a different \emph{segID}: 
-this simply means that the starting segment received is deprecated,
-because the node has already accepted non-starting segment requests
-originated from other \emph{Assigned} nodes.
-\item The node is \emph{Assigned}, with a different \emph{segID}:
-same as the previous case.
-
-% TODO: check and remove, the below is not true
-%CHECK:  it is not the initiator of the starting segment request, but
-%is already assigned to some segment!? assuming again we are discussing
-%of nodes belonging to the same subnet, this should NOT happen, since
-%the only visited node of the subnet should be the initial node from
-%which the \texttt{STARTING\_SEGMENT\_REQUEST} originated. Note again that we are
-%assuming that if the the node is visited or \emph{tvisited} with the id of
-%another subnet can simply ignore the request.  The node is \emph{tvisited}
-%but it is not the initiator of the request (different id): same as
-%above, if we are assuming nodes of the same subnet, this should not
-%happen. If the node is of another subnet, can simply ignore the event.
-
-\end{itemize}
-
-\subsection{Receiving a \texttt{SEGMENT\_REQUEST}}
-When a node receives a \texttt{SEGMENT\_REQUEST}, the are the following cases:
-
-\begin{itemize}
-\item The node is \emph{Assigned}: a segment was
-found and it should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
-packet.  
-\item The node is \emph{Candidate}: it should discard the packet sending
-back a \texttt{SEGMENT\_CANCEL} 
-\item The node is not \emph{Assigned} or \emph{Candidate} and has free
-links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
-to one of its free links, according to some internal ordering
-\end{itemize}
-
-NOTE: the main difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
-and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
-itself is included in the segment , while in the second case the
-receiving node does not belong to the segment found.
-
-%The motivation is
-%that in the second case the node was already marked as \emph{visited} because
-%of being assigned to some segment found before, while in the
-%starting-segment case, by definition, the first segment of a subnet
-%begins with the starting node, which is marked as \emph{visited} by the SR
-%algorithm when searching for the first (starting) segment. Remember
-%that the first segment of a subnet is a loop beginning with the
-%starting node.
-
-\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
-When received, if the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
-the packet, the node learns to belong to the segment associated to the
-id. Further, it should forward this packet to the link where the
-original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
-can learn the segment id they belong to.  \emph{LED} shoud be
-updated: The state of the node changes from \emph{tvisited} to \emph{visited}.  the
-\emph{link\_tvisited} previously set with the \emph{segID} should be invalidated the
-\emph{link\_visited} variable associated to the incoming confirm should be set
-as segID. Note that if the request was flooded across different links,
-the \emph{link\_visited} variable associated to the other paths should not be
-set.  the \emph{link\_visited} variable associated to the link from which the
-request was originated should be set segID
-
-\subsection{Receiving a \texttt{SEGMENT\_CANCEL}}
-When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that searching
-for a segment along that path was unsuccessful. But if the node still
-has other free links to try, it should forward a \texttt{SEGMENT\_REQUEST} to
-the next link (next according to some internal ordering). So a node
-forwards back the \texttt{SEGMENT\_CANCEL} packet along the link that originated
-the \texttt{SEGMENT\_REQUEST} packet only when there are no more free links to
-try. If this is the case, the node modifies its status from
-\emph{Candidate} to \emph{Free} and forwards the \texttt{SEGMENT\_CANCEL} packet to the link from which
-the request was received. The process stops when the \texttt{SEGMENT\_CANCEL}
-packet reach the starting node that originated the request.
+%\section{Detailed Node behaviour Model}
+%\label{sec:execution_model}
+%
+%The \emph{LED} variables at each node are are initially set so the node and
+%each of its links is set as free. The only node that makes exception
+%is the bootstrap node, initialized in the \emph{Bootstrap} status. All
+%the subsequent events happening at each node are the consequence of
+%its current dynamic status (DBS) and the packets received.
+%
+%
+%%TODO: add state machines
+%
+%% TODO: fix, move elsewhere or delete
+%%Assumption: when discussing of visited/\emph{tvisited} nodes, we are assuming
+%%with an id corresponding to the same subnet. Nodes involved in other
+%%subnet processes can simply ignore these packets. (TBD: formalize more
+%%clearly in which cases inter-subnet packets must be ignored, probably
+%%this happens most of the times, but in some cases, e.g. when a
+%%terminal node is found, some kind of communication packets are needed
+%%in order to crearte the bridge between two subnets.) 
+%
+%\subsection{Receiving a \texttt{STARTING\_SEGMENT\_REQUEST}}
+%
+%The request for the first segment should be managed differently since
+%all nodes (except the starting one) must forward the packet using a
+%flooding mechanism. This is necessary since the request packet must
+%return the bootstrap node.
+%When a node receives a \texttt{STARTING\_SEGMENT\_REQUEST}, the
+%following cases can happen:
+%
+%\begin{itemize}
+%\item The node is not candidate or assigned: it should set itself as
+%\emph{Candidate} and forward the packet along its free links, using
+%flooding.  
+%\item The node is \emph{Candidate} with the same
+%\emph{segID} and \emph{src\_id} is equal to node id: this means the
+%node was the initiator of the request, so a starting segment was found and
+%should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
+%packet.  
+%\item The node is \emph{Candidate}, with the same \emph{segID} of the
+%packet but \emph{src\_id} is different from node id: due
+%the flooding mechanism, another starting segment packet reached a node
+%which was previously marked as \emph{Candidate} from the same starting segment
+%search process. Since the node is candidate with the same id, it means
+%that it already accomplished in the task of propagating that kind
+%packets, thus can simply ignore the event thrashing the packet.  
+%%TBD: how the status should be changed ? depend on the flooding mechanism. Note
+%%that these links do not include the link from which the request was
+%%received.  
+%\item The node is \emph{Candidate}, with a different \emph{segID}: 
+%this simply means that the starting segment received is deprecated,
+%because the node has already accepted non-starting segment requests
+%originated from other \emph{Assigned} nodes.
+%\item The node is \emph{Assigned}, with a different \emph{segID}:
+%same as the previous case. 
+%
+%% TODO: check and remove, the below is not true
+%%CHECK:  it is not the initiator of the starting segment request, but
+%%is already assigned to some segment!? assuming again we are discussing
+%%of nodes belonging to the same subnet, this should NOT happen, since
+%%the only visited node of the subnet should be the initial node from
+%%which the \texttt{STARTING\_SEGMENT\_REQUEST} originated. Note again that we are
+%%assuming that if the the node is visited or \emph{tvisited} with the id of
+%%another subnet can simply ignore the request.  The node is \emph{tvisited}
+%%but it is not the initiator of the request (different id): same as
+%%above, if we are assuming nodes of the same subnet, this should not
+%%happen. If the node is of another subnet, can simply ignore the event.
+%
+%\end{itemize}
+%
+%\subsection{Receiving a \texttt{SEGMENT\_REQUEST}}
+%When a node receives a \texttt{SEGMENT\_REQUEST}, the are the following cases:
+%
+%\begin{itemize}
+%\item The node is \emph{Assigned}: a segment was
+%found and it should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
+%packet.  
+%\item The node is \emph{Candidate}: it should discard the packet sending
+%back a \texttt{SEGMENT\_CANCEL} 
+%\item The node is not \emph{Assigned} or \emph{Candidate} and has free
+%links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
+%to one of its free links, according to some internal ordering
+%\end{itemize}
+%
+%NOTE: the main difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
+%and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
+%itself is included in the segment , while in the second case the
+%receiving node does not belong to the segment found. 
+%
+%%The motivation is
+%%that in the second case the node was already marked as \emph{visited} because
+%%of being assigned to some segment found before, while in the
+%%starting-segment case, by definition, the first segment of a subnet
+%%begins with the starting node, which is marked as \emph{visited} by the SR
+%%algorithm when searching for the first (starting) segment. Remember
+%%that the first segment of a subnet is a loop beginning with the
+%%starting node. 
+%
+%\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
+%When received, if the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
+%the packet, the node learns to belong to the segment associated to the
+%id. Further, it should forward this packet to the link where the
+%original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
+%can learn the segment id they belong to.  \emph{LED} shoud be
+%updated from \emph{tvisited} to \emph{visited}.  the
+%\emph{link\_tvisited} previously set with the \emph{segID} should be invalidated the
+%\emph{link\_visited} variable associated to the incoming confirm should be set
+%as segID. Note that if the request was flooded across different links,
+%the \emph{link\_visited} variable associated to the other paths should not be
+%set.  the \emph{link\_visited} variable associated to the link from which the
+%request was originated should be set segID
+%
+%\subsection{Receiving a \texttt{SEGMENT\_CANCEL}}
+%When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that searching
+%for a segment along that path was unsuccessful. But if the node still
+%has other free links to try, it should forward a \texttt{SEGMENT\_REQUEST} to
+%the next link (next according to some internal ordering). So a node
+%forwards back the \texttt{SEGMENT\_CANCEL} packet along the link that originated
+%the \texttt{SEGMENT\_REQUEST} packet only when there are no more free links to
+%try. If this is the case, the node modifies its status from
+%\emph{Candidate} to \emph{Free} and forwards the \texttt{SEGMENT\_CANCEL} packet to the link from which
+%the request was received. The process stops when the \texttt{SEGMENT\_CANCEL}
+%packet reach the starting node that originated the request.
 

### 2013-09-20 PAPER/introduction.tex
Final strechting

@@
 assembled process cannot assume such a deterministic device placement
-process.
+process, thus defect tolerance is something like a design requirement
+more than a exception to be avoided.
 
@@
 one depicted in~\ref{fig:nana} as background, the topology discovery
-problem is more general and not stricly dependent on any of the
-underlying computing architectures.
+problem faced in this work is more general and not stricly dependent on any of the
+underlying computing architecture.
 
@@
 
-The main contribution presented in this paper is to bring the advantages of
+In this paper we introduce DiSR, a first effort for a Distributed
+Segment-based Routing in large scale DNA self assembled networks.
+The main contribution is to bring the advantages of
 a segment-based approach to deadlock freedom without requiring any topology graph,
-external defect map or centralized algorithm execution.  We introduce DiSR, a first effort for a Distributed
-Segment-based Routing in large scale DNA self assembled networks.
+external defect map or centralized algorithm execution. 
 While maintaining similar properties to segment-based , the DiSR
@@
 The DiSR approach presented in this work is a first attempt of
-reaching the same goal of a segment based approach, that is
+reaching the same goals of a segment based approach, that is
 estabilishing segments, without requiring any topology graph or

### 2013-09-20 trunk/PAPER/disr.tex
Final fix to typos

@@
 a path between connecting two other different segments.A exception is
-the first segment estabilished in the network, called \emph{starting
+the first segment established in the network, called \emph{starting
 segment} which is  a loop beginning/ending on a particular node
@@
 placing a turn restriction within each segment. It has been proved~\cite{mejia_ipdps06}
-that such a set of turn prohibitions guarantees dealock freedom and
+that such a set of turn prohibitions guarantees deadlock freedom and
 while preserving connectivity of the network.
@@
 node to when searching for the first segment. 
-\item{\texttt{STARTING\_SEGMENT\_CONFIRM}}: used when estabilishing
+\item{\texttt{STARTING\_SEGMENT\_CONFIRM}}: used when establishing
 the starting  segment. 
@@
 first)
-\item{\texttt{SEGMENT\_CONFIRM}}: used to estabilish a segment. 
+\item{\texttt{SEGMENT\_CONFIRM}}: used to establish a segment. 
 \item{\texttt{SEGMENT\_CANCEL}}: used to cancel the process of searching a segment along a
@@
 
-\item{\textbf{Injecting bootstrap request}}: all nodes have a initial
+\item{\textbf{Injecting bootstrap request}}: all nodes have an initial
 \emph{DBS} status \emph{Free}, except for a
@@
 \item{\textbf{Flooding}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
-if $Free$ forwards it to its free links using a flooding mechanism and
+when $Free$ forwards it to its free links using a flooding mechanism and
 becoming $CandidateStarting$ (g).
@@
 the bootstrap node (from a different link, of course), the starting
-segment is found. Then the boostrap node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
+segment is found. Then the bootstrap node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
 packet along the link from which it received the
@@
 
-\item{\textbf{Setup of a segment}}: The find process is successfull
+\item{\textbf{Setup of a segment}}: The find process is successful
 when an already \emph{Assigned} node receives the
@@
 confirm packet changes its status to $Assigned$ (m) and forwards back
-the same confirm until it reaches the initator of the request, which
+the same confirm until it reaches the initiator of the request, which
 changes from $ActiveSearching$ to $Assigned$ (c).

### 2013-09-20 PAPER/implementation.tex
Fixes
added pics
Final fix to typos

@@
   \centering
-  \includegraphics[width=0.35\textwidth]{pictures/disr_imp.eps}
+  \includegraphics[width=0.25\textwidth]{pictures/disr_imp.eps}
   \caption{\emph{DiSR} block architecture.}
@@
 node~\cite{liu_jetcs} we estimated the required resource for
-implementing the entire DiSR block. An not optimized VHDL description
-of the DiSR circuitry has been written and synthesized at gate-level.
+implementing the entire DiSR block. A not optimized behavioural
+HDL of the DiSR circuitry has been written and synthesized at gate-level.
 Considering the specific layout of each single logic elements ( NAND,
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{pictures/imp_rslt.eps}
+  \includegraphics[width=0.25\textwidth]{pictures/imp_rslt.eps}
   \caption{DiSR synthesis results: N is the number of network's node.}
@@
 growing trend.  
-An intuitive explaination of this is the relatively simple logic of
+An intuitive explanation of this is the relatively simple logic of
 DiSR, whose behaviour is almost code on scalable storage structures.
@@
 \emph{link\_visited[]} and \emph{link\_tvisited[]} table follow the
-logaritmic function:
+logarithmic function:
 \begin{equation}

### 2013-09-20 PAPER/introduction.tex
Final fix to typos

@@
 The main idea behind this approach is to exploit the physical regularity and
-stabiliy of DNA structures in order to create a scaffold onto which
+stability of DNA structures in order to create a scaffold onto which
 nano-devices (e.g. nanowires and CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be
-attached. This can be achieved by designing approapriate complementary DNA tags for
+attached. This can be achieved by designing appropriate complementary DNA tags for
 each terminal to be placed, so that a nano device will be attached
@@
 process, thus defect tolerance is something like a design requirement
-more than a exception to be avoided.
+more than an exception to be avoided.
 
@@
 instructions and data operands) among nodes.  It is important to
-underline that, altought we can assume an architecture similar to the
+underline that, altougth we can assume an architecture similar to the
 one depicted in~\ref{fig:nana} as background, the topology discovery
-problem faced in this work is more general and not stricly dependent on any of the
+problem faced in this work is more general and not strictly dependent on any of the
 underlying computing architecture.
@@
 we summarize the main approaches to topology agnostic routing. Next in
-Section~\ref{sec:disr_concepts} are described the main elements of the
-proposed approach, showing a the DiSR execution model in
-Section~\ref{sec:execution_model}.  In Section~\ref{sec:simulation}
+Section~\ref{sec:disr_concepts} are described the main elements and
+the execution model of the proposed approach.  In Section~\ref{sec:simulation}
 simulations are carried out with the opensource tool Nanoxim to
-demostrate how DiSR preserves some of the main segment-based
+demonstrate how DiSR preserves some of the main segment-based
 properties and how compares to the tree-based approaches. Finally a
@@
 Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} do not use virtual channels to
-achieve deadlock freedom, but turn proibitions. 
+achieve deadlock freedom, but turn prohibitions. 
 In particular, authors of~\cite{Patwardhan05evaluatingthe} exploits the creation of a spanning tree of the
@@
 issue, but the set of turn restrictions is still prefixed,
-striclty depending on the particular tree root selected. 
+strictly depending on the particular tree root selected. 
 Other solutions try to approach the issue of irregular
@@
 independently from other restrictions. The whole network is
-partitioned into segments, and a each bidirectional turn
+partitioned into segments, and each bidirectional turn
 restriction can be freely chosen within a segment in order to guarantee
@@
 reaching the same goals of a segment based approach, that is
-estabilishing segments, without requiring any topology graph or
+establishing segments, without requiring any topology graph or
 centralized execution.

### 2013-09-20 PAPER/paper.tex
Final fix to typos

@@
 \newcommand{\etc}{\emph{etc.}}
-
+\renewcommand{\baselinestretch}{0.98}\normalsize
 %------------------------------------------------------------------------------
@@
 approach in the process of discovering irregular network topology
-while estabilishing network segments.  Results show how DiSR still
+while establishing network segments.  Results show how DiSR still
 preserves some important properties (coverage, defect tolerance,
@@
 \section{Conclusions}
-In this work we presented DiSR, a initial attempt of porting a segment based
+In this work we presented DiSR, an initial attempt of porting a segment based
 approach to distributed self-assembled nanoscale scenario. We
-demostrated how DiSR can accomplish the aim of finding a segment
-coverage of the network withouth requiring any centralized approach
+demonstrated how DiSR can accomplish the aim of finding a segment
+coverage of the network without requiring any centralized approach
 that would request a graph topology as input. A draft hardware
-implementation has been presented to evalute the impact on the limited
+implementation has been presented to evaluate the impact on the limited
 node size typical of the assumed scenario. Future works will focus on

### 2013-09-20 PAPER/simulation.tex
Final fix to typos

@@
 nodes should be assigned, so this metric is useful to show how some
-disconnected node regions can negativaly impact on the whole DiSR
+disconnected node regions can negatively impact on the whole DiSR
 effectiveness.
-\item{Broadcast latency}: this measures how the time required to complete the
-segment assignment scale for increasing network sizes and defect rates
-\item{Bootstrap node effect}: this evaluates the impact of the chosen
+\item{\emph{Latency}}: this measures how the cycles required to complete the
+segment assignment scales for increasing network sizes and defect rates
+\item{\emph{Bootstrap node effect}}: this evaluates the impact of the chosen
 bootstrap node on the node coverage.
@@
 
-\section{Results}
+\subsection{Results}
 \label{sec:results}
 
-In Figure~\ref{fig:coverage} is shown node coverage using different
-network sizes and bootstrap injection points. As can be seen,
-increasing the \% of defective node, TODO COMMENT...
+Figure~\ref{fig:results} collects the results in terms of node
+coverage and latency at different network sizes, defect rates and
+bootstrap injection points.  In particular graphs (a) and (b) show
+node coverage for DiSR and RPF tree based approach respectively. While
+the first aim of DiSR is not to reach the optimal coverage, we still
+can observe a quite good performance as compared to tree based
+approach. Note that defect rates beyond 25\% lead to many disconnected
+regions of nodes that this first of DiSR cannot handle; however, these
+level of defects should be considered as worst case scenarios, so the
+achieved coverage of $0.5$ is satisfying results for this first
+version of DiSR. As regards the the network size it seems to have a
+limited impact when defect rate do not introduce to much disconnected
+regions.
+
+The number of cycles required to complete the segment mapping
+process is shown in latency graph (c). Comparison against tree-based
+has been omitted for space reasons, however similar numbers (in terms
+of upper bound) have been reported
+(see~\cite{Patwardhan05evaluatingthe} for details). What it's more
+interesting is to observe is how DiSR latency scales with network
+size. For example, going from 900 to 2500 nodes, at the medium defect
+rate of $0.15$, leads to an increase from 3000 to 4500 cycles. Note how
+the effect of defect rate is increasing until the threshold of $0.25$
+is reached, meaning that while DiSR finds it more difficult to
+complete the process due increasing defective paths, it still discover
+new segments when let running for a more extended amount of cycles.
+After that threshold, the impact of entire disconnected regions
+becomes predominant and DiSR more quickly complete the process
+covering the nodes that can be reached.
 
@@
 \includegraphics[width=0.22\textwidth]{pictures/coverage.eps} \\
+(a) & (b) \\
 \includegraphics[width=0.22\textwidth]{pictures/set2.eps} & 
 \includegraphics[width=0.22\textwidth]{pictures/set3.eps} \\
-    (a) & (b)
+(c) & (d)
 \end{tabular}
-  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
-  \label{fig:bootstrap}
+\caption{DiSR (a) and RPF (b) node coverage (c) Latency and effect
+of bootstrap node (d)}
+\label{fig:results}
 \end{figure}
 
-Figure~\ref{fig:bootstrap} shows the effect of bootstrap node position
-on node coverage, for different defect rates. TODO COMMENT.
-
-Next, Figure~\ref{fig:latency_size} shows latency as function of
-network size, with different defect rates, while Figure~\ref{fig:latency_defective}
-shows the same latency when different bootstrap nodes are
-considered.... TODO COMMENT
-
-TODO: something like Broadcast Tree properties (sez.  5.4)
+Finally, picture (d) visually represent  the stability of the approach
+against different choices of the bootstrap node in a 10x10 network.
+This is an important aspect to evaluate when considering that one of
+the main advantages of DiSR against all the tree based approaches
+should be the ability of choosing whatever bootstrap node, without
+having to care of any particular \emph{root-node role} assumed in the future.
+In other words, after segments have been established, the bootstrap node
+is like every other node, i.e. it is not center of a structure, and it
+is not an hotspot for the traffic distribution. The results in terms
+of coverage,  shown for low, medium and high defect profiles, seems to
+demonstrate a relatively limited impact of the bootstrap choice in
+the low/medium scenarios, while a 30\%instability is found for very high defect
+rates. This also sounds acceptable, since when lot of defective nodes
+are present, the particular position of the bootstrap choice could
+lead to completely different evolution in the DiSR setup process.

### 2013-10-16 trunk/PAPER/implementation.tex
NocArc review fixes

--- 2013-07-10 trunk/PAPER/implementation.tex
@@
 \label{sec:implementation}
-Althought a completed and detailed floorplan of the node is not the
+
+Although a completed and detailed floorplan of the node is not the
 focus of this work, in this section we want to give a basic idea of
 which are the main elements required to support this kind of
-architecture and the DiSR approach. There are three main classes of
-node elements:
+architecture thus giving an estimate of the overhead by the
+DiSR approach. There are three main classes of node elements:
 \begin{itemize}
@@
 strictly related to the node functionality and role inside a given
-networks: e.g. is that a computation or storage node ?
+network, e.g. being a computation or storage node.
 \item Node communication:  these are elements (such as transceivers,
-buffers) required to the node to communicate with its neighbors,
-indepentently from node functionality and DiSR implementation
-\item DiSR-specific: all the hardware, such as control logic and
-configuration, required to implement the proposed DiSR approach.
+buffers) required to the node to communicate with its neighbours,
+independently from node functionality and DiSR implementatio
+\item DiSR-specific: all the hardware, control logic and
+configuration registers, related to an implementation the proposed approach.
 \end{itemize}
@@
   \centering
-  \includegraphics[width=0.50\textwidth]{pictures/router_schematic.eps}
-  \caption{Schematic of the router. Top-level view (top). Block
-  implementing the routing algorithm (middle). Block implementing the
-  TODO
-  }
-  \label{fig:schematic}
+  \includegraphics[width=0.25\textwidth]{pictures/disr_imp.eps}
+  \caption{\emph{DiSR} block architecture.}
+ \label{fig:implementation}
 \end{figure}
 
-Figure~\ref{fig:schematic} shows the schematic of a router for
-a mesh based network topology implementing DiSR . As shown, the top level scheme of the router consists of a
-set of ...
+Let's so focus to the \emph{DiSR} block. In
+Fig.~\ref{fig:implementation} is shown a possible sketch of this
+block, which mainly consist in the following building elements:
 
-The content of a routing algorithm block is more accurately shown in
-the central part of Figure~\ref{fig:schematic}. Each routing algorithm
-block consists of ...
+\begin{itemize}
+\item \emph{DBS block}: It Takes trace of the DBS, and how already
+discussed in the Section~\ref{ssec:disr_dstruct}, there are six possible
+configurations. These values can be codified using 3 bit implemented
+with a 3-bit register and the required combinational logic. This block
+is essentially designed as a state machine.
+\item \emph{LED registers}: Is a set of registers useful for storing
+the local environment data (LED) described in
+Section~\ref{ssec:disr_dstruct}. In particular in
+fig.~\ref{fig:implementation}, are highlighted two tables representing
+the \emph{link\_visited[]} and \emph{link\_tvisited[]} values. This
+block consists of an array of registers (one for each
+direction) that can be implemented with an SRAM, in which are presents
+two specific fields  for representing the \emph{segID}. 
+\item \emph{Control circuitry}: This circuitry reads data
+from the fields of the incoming packet, LED registers and the
+\emph{DBS}, updating \emph{LED} and
+\emph{DBS} data when required. Then, the resulting \emph{Ctrl Out} output  drives the other
+communication resources (such as node transceivers) for actuating the
+DiSR routing operation.
+\end{itemize}
 
-Let us now look inside the \emph{DiSR} block. A formal description of
-DiSRalgorithm has already been given in Figure~\ref{alg:disr}, thus we
-will focus on the architectural elements to be implemented.
+As discussed above, one of the main design challenge of DNA
+Self-Assembled systems is the limited resource available for
+implementing both computations and routing decisions for each node.
+For this reason, assuming a budget of $10^4$ CNFETs for each network's
+node~\cite{liu_jetcs} we estimated the required resource for
+implementing the entire DiSR block. A not optimized behavioural
+HDL of the DiSR circuitry has been written and synthesized at gate-level.
+Considering the specific layout of each single logic elements ( NAND,
+full-adder, latch etc.), it has been possible to get a rough estimate
+of the number of transistors necessary for implementing the DiSR
+logic.  Figure~\ref{fig:imp_trend} shows the results of synthesis in
+terms of number of devices (CNFETs) versus the number of network nodes
+while the network scales up from $10\times10$ to $100\times100$ nodes.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.25\textwidth]{pictures/imp_rslt.eps}
+  \caption{Number of network's node (N) vs number of CNFETs.}
+ \label{fig:imp_trend}
+\end{figure}
+In particular, observing the Fig.\ref{fig:imp_trend} can 
+be pointed out that the proposed implementation occupy  about 20\% of the node budget. 
+Further, more than the absolute number of devices itself, it is interesting to
+observe that, while the node have a squared increment, the circuitry
+complexity which implements the DiSR algorithm increases with a slowly
+growing trend.  
+An intuitive explanation of this is the relatively simple logic of
+DiSR, whose behaviour is almost code on scalable storage structures.
+For example, the number of registers implementing the
+\emph{link\_visited[]} and \emph{link\_tvisited[]} table follow the
+logarithmic function:
+\begin{equation}
+  \label{eq:imp_trend}
+  N_{reg}=2\cdot N_{port} \cdot log_2(N)
+\end{equation}
+where $N_{port}$ is the number of the router's ports, $N$ is the number 
+of network's nodes while the term $2$ takes in account that \emph{link\_visited[]} and 
+\emph{link\_tvisited[]} are two separate set of registers. While this number is fixed by 
+the number of network's node, the control circuitry could be optimized applying more effort 
+in future designs of this building block.

### 2013-10-16 PAPER/introduction.tex
NocArc review fixes

@@
 are emerging as a promising technology due their tera/peta scale of
-integration, defect tolerance tolerance and huge potential computing
+integration, defect tolerance and huge potential computing
 capabilities. These technologies are certainly still at
@@
 underline that, altougth we can assume an architecture similar to the
-one depicted in~\ref{fig:nana} as background, the topology discovery
+one depicted in Figure~\ref{fig:nana} as background, the topology discovery
 problem faced in this work is more general and not strictly dependent on any of the
@@
 The main contribution is to bring the advantages of
-a segment-based approach to deadlock freedom without requiring any topology graph,
+a segment-based approach~\cite{mejia_ipdps06} to deadlock freedom without requiring any topology graph,
 external defect map or centralized algorithm execution. 

### 2013-10-16 trunk/PAPER/introduction.tex
Adding missing reference

@@
 are emerging as a promising technology due their tera/peta scale of
-integration, defect tolerance tolerance and huge potential computing
+integration, defect tolerance and huge potential computing
 capabilities. These technologies are certainly still at
 their early stage of development, however different laboratory demos and
-prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1, pistol2009}.
+prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006_1, pistol2009}.
+%, patwardhan2006
 The main idea behind this approach is to exploit the physical regularity and
-stabiliy of DNA structures in order to create a scaffold onto which
+stability of DNA structures in order to create a scaffold onto which
 nano-devices (e.g. nanowires and CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be
-attached. This can be achieved by designing approapriate complementary DNA tags for
+attached. This can be achieved by designing appropriate complementary DNA tags for
 each terminal to be placed, so that a nano device will be attached
 only where its own DNA tag matches a complementary tag on the DNA grid
-scaffold (see figure~\ref{fig:dna_tag}.
-
-\begin{figure}
-  \centering
-    \includegraphics[width=0.30\textwidth]{pictures/dna2b.eps}
-  \caption{DNA tag matching}
-  \label{fig:dna_tag}
-\end{figure}
-
+scaffold.
+%(see figure~\ref{fig:dna_tag}.
+%
+%\begin{figure}
+%  \centering
+%    \includegraphics[width=0.30\textwidth]{pictures/dna2b.eps}
+%  \caption{DNA tag matching}
+%  \label{fig:dna_tag}
+%\end{figure}
 A detailed description of the chemical properties involved is far
@@
 assembled process cannot assume such a deterministic device placement
-process.
+process, thus defect tolerance is something like a design requirement
+more than an exception to be avoided.
 
@@
 instructions and data operands) among nodes.  It is important to
-underline that, altought we can assume an architecture similar to the
-one depicted in~\ref{fig:nana} as background, the topology discovery
-problem is more general and not stricly dependent on any of the
-underlying computing architectures.
+underline that, altougth we can assume an architecture similar to the
+one depicted in Figure~\ref{fig:nana} as background, the topology discovery
+problem faced in this work is more general and not strictly dependent on any of the
+underlying computing architecture.
 
@@
 
-The main contribution presented in this paper is to bring the advantages of
-a segment-based approach to deadlock freedom without requiring any topology graph,
-external defect map or centralized algorithm execution.  We introduce DiSR, a first effort for a Distributed
+In this paper we introduce DiSR, a first effort for a Distributed
 Segment-based Routing in large scale DNA self assembled networks.
+The main contribution is to bring the advantages of
+a segment-based approach~\cite{mejia_ipdps06} to deadlock freedom without requiring any topology graph,
+external defect map or centralized algorithm execution. 
 While maintaining similar properties to segment-based , the DiSR
@@
 avoid considering solutions based on hardware-redundancy to
-dynamically recover defects as in~\cite{constantinides2006, kohler2010, kim2006, park2006}.
+dynamically recover defects as in~\cite{constantinides2006, kohler2010, kim2006, park2006, ebrahimi2013}.
 
@@
 The DiSR approach presented in this work is a first attempt of
-reaching the same goal of a segment based approach, that is
-estabilishing segments, without requiring any topology graph or
+reaching the same goals of a segment based approach, that is
+establishing segments, without requiring any topology graph or
 centralized execution.

### 2013-10-18 trunk/PAPER/paper.tex
Final strechting
Streching lines

@@
 \newcommand{\etc}{\emph{etc.}}
-%\renewcommand{\baselinestretch}{0.9}\normalsize
+\renewcommand{\baselinestretch}{0.97}\normalsize
 %------------------------------------------------------------------------------

### 2013-11-04 trunk/PAPER/disr.tex
Synced to after-conferences updates

--- 2013-09-20 trunk/PAPER/disr.tex
@@
 \subsection{Basic Idea}
-The main concept behind of the original SR approach is the
-\emph{Segment}: a Segment is basically a path of consecutive node
-and links. All segments start with a link attached to a node which
-belongs to different segment, ending with a link also attached to a
-node belonging to a different segment. A exception is the first
-segment estabilished in the network, called \emph{starting segment} which is  a loop
-beginning/ending on a particular node defined as bootstrap node.
-
+The main concept behind the kind of turn prohibition we want to
+achieve is the \emph{Segment}: it is basically a path of consecutive
+nodes and links. A segment $S_1$ starts with a link attached to a node which
+belongs to different segment $S_2$, ending with a link attached to a
+node belonging to a different segment $S_3$. In other words, a segment
+a path between connecting two other different segments.A exception is
+the first segment established in the network, called \emph{starting
+segment} which is  a loop beginning/ending on a particular node
+defined as \emph{bootstrap node}.
 The idea is to partition the network in a set of disjoint segments, and then
 placing a turn restriction within each segment. It has been proved~\cite{mejia_ipdps06}
-that such a set of turn prohibitions guarantees dealock freedom and
+that such a set of turn prohibitions guarantees deadlock freedom and
 while preserving connectivity of the network.
@@
 Roughly speaking, the execution of can be described as the execution
-of the following phases:
-\begin{itemize}
-\item Injection of the DiSR process from upper layer to set a bootstrap
-node
-\item Bootstrap node broadcasting to create the first segment of the subnet
-\item Parallel requests starting from assigned node to discover other segments
-%\item Turn proibition in each confirmed segment
+of the following phases: (1) Injection of the DiSR process from upper layer to set a bootstrap
+node (2) Bootstrap node broadcasting to create the first segment of the subnet
+(3) Parallel requests starting from assigned node to discover other
+segments. The following subsection describe the data structure and
+execution model required at each node. (4) Turn proibition in each
+confirmed segment.
 %\item Draining of remaining packet due timeouts
-\end{itemize}
 
-Once again, it should be pointed out that nowhere in the network there
-is such a global vision of these exection phases. A more detailed
-description of the exection model at each node is discussed in the
-next section.
+%Once again, it should be pointed out that nowhere in the network there
+%is such a global vision of these exection phases. A more detailed
+%description of the exection model at each node is discussed in the
+%next section.
 
-\subsection{Packets types Required}
+\subsection{Signal Types Required}
 
@@
 
-\subsection{Sketch of DiSR}
+\subsection{DiSR Execution Model}
 
+In Figure~\ref{fig:state_machine} are depicted the main events
+representing the execution model at each node. The DiSR control
+packets described in the previous subsection trigger node events,
+which eventually change $DBS$ status according to the current value of
+$LED$ variables and the type of the packet received. The main DiSR
+phases, together with a reference to the particular status transition
+shown in Figure~\ref{fig:state_machine} are described in the
+following.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.40\textwidth]{pictures/state_machine.eps}
+  \caption{DiSR node execution model}
+  \label{fig:state_machine}
+\end{figure}
 \begin{itemize}
 
-\item{\textbf{Injecting bootstrap request}}: all nodes have a initial
+\item{\textbf{Injecting bootstrap request}}: all nodes have an initial
 \emph{DBS} status \emph{Free}, except for a
  node with status \emph{Bootstrap}, set by some signal from an
-upper layer via. When starting, this bootstrap node sets itself as \emph{visited} and
-changes its status to \emph{ActiveSearching}, injecting a
+upper layer via (a). When starting, this bootstrap node 
+changes its status to \emph{ActiveSearching} (b), injecting a
 \texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links.
@@
 \item{\textbf{Flooding}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
-if not yet (\emph{visited}/\emph{tvisited}),  forwards it to its free links using a flooding mechanism.
-Each of these links is then marked as \emph{tvisited} with the segment id
+when $Free$ forwards it to its free links using a flooding mechanism and
+becoming $CandidateStarting$ (g).
+Each of its free links is then marked as \emph{tvisited} with the segment id
 associated to the request. Note that a node that has already received a
@@
 
-\item{\textbf{Confirming the Starting Segment}}: when this \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
-the starting node (from a different link, of course), the starting
-segment is found. Then the starting node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
-packet with the same id along the link from which it received the
-\texttt{STARTING\_SEGMENT\_REQUEST}. Each node do same by changing its own status
-to \emph{Assigned}. So the confirmation packet is sent back from
+\item{\textbf{Confirming the Starting Segment}}: when the \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
+the bootstrap node (from a different link, of course), the starting
+segment is found. Then the bootstrap node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
+packet along the link from which it received the
+\texttt{STARTING\_SEGMENT\_REQUEST} and becomes $Assigned$ (c). Each
+node receiving the confirm do same by changing its own status
+to \emph{Assigned} (l). So the confirmation packet is sent back from
 node to node and the starting segment is created.
 
-Note: A node knows to be \emph{Candidate} due a
-\texttt{STARTING\_SEGMENT\_REQUEST}.  Then, when receiving a simple
-(not starting) \texttt{SEGMENT\_REQUEST} , it can simply cancel its
-previous \emph{Candidate} status, since this second
+Note: A node being \emph{CandidateStarting}, when receiving a simple
+(not starting) \texttt{SEGMENT\_REQUEST} , can simply cancel its
+previous \emph{CandidateStarting} status and set itself as
+$Candidate$ for that request (h), since this new
 request means that the starting segment has already been found.
@@
 
-\item{\textbf{Injecting other request}}: Each node in the \emph{Assigned} status can initiate a search for a
-segment, by sending a \texttt{SEGMENT\_REQUEST} across one of its free
-links. Note that, since this is not the starting segment, in this case
-the packet should not return back to the initiator, but just another visited
-node
-\item{\textbf{Setup of a segment}}: The find process is successfull
-when an \emph{Assigned} node receives the \texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
-sent back along the path that originated the request.  
+\item{\textbf{Injecting other requests}}: Each node in the
+\emph{Assigned} status can initiate a search for a segment, by sending
+a \texttt{SEGMENT\_REQUEST} across one of its free links (d). Note
+that since this is not the starting segment in this case the packet
+should not reach the initiator, but just another \emph{Assigned} node.
+
+\item{\textbf{Setup of a segment}}: The find process is successful
+when an already \emph{Assigned} node receives the
+\texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
+sent back along the path that originated the request (e), while the
+node remain $Assigned$ (since it could confirm more segments). Each node
+previously set as $Candidate$ for that segment id, when receiving the
+confirm packet changes its status to $Assigned$ (m) and forwards back
+the same confirm until it reaches the initiator of the request, which
+changes from $ActiveSearching$ to $Assigned$ (c).
+
 \item{\textbf{Failing while searching a segment}}: a node received a \texttt{SEGMENT\_REQUEST} packet but
-matched one of the following conditions: the node is free but has no
-more suitable free links (can’t forward the \texttt{SEGMENT\_REQUEST}) the node
-is \emph{tvisited} candidate for another find process the request packet
-exceeded the max\_segment\_hops limit.  In all these cases the node
-sends back a \texttt{SEGMENT\_CANCEL} along the proper link modifying its state
-to free. Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
-only if no more free links can be explored starting from them.
+matched one of two the following conditions: the node is $Free$ but has no
+more suitable free links (thus can’t forward the
+\texttt{SEGMENT\_REQUEST})(f); the node
+is candidate for another find process(i).  In all these cases the node
+sends back a \texttt{SEGMENT\_CANCEL} along the proper link. 
+%Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
+%only if no more free links can be explored starting from them.
 \end{itemize}
 
-%\subsection{Intra-node vs Inter-node parallelism}
-%In the processes described above, we assumed that each node in the
-%READY\_SEARCHING state can start a find segment process by injecting a
-%\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when defining DiSR
-%should be made in order to decide whether or not the node must
-%actually perform this action. 
-%The point above is is strictly related to the general question: which
-%level of “parallelism” should we allow in DiSR ? The adopted approach
-%is that, although the nature of DiSR itself is intrinsicly parallel,
-%the use of parallelism makes things work in a more complex way. In
-%other words, DiSR is parallel when needed, but it does not exploit
-%parallelism as an “improving feature”. When not needed, things should
-%be serialized. For example: when a node is “ready searching” could
-%start several find segment process associated to the same segment, one
-%for each free link. But serializing this by investigating the free
-%links in order could be a simplest solution. We refer to this saying
-%that we avoid intra-node parallelism.  Note that while intra-node
-%parallelism can be avoided, trying to avoid inter-node parallelism
-%could be more complex than allowing the parallelism itself. Imagine
-%for example the effort of trying to coordinate nodes so that an unique
-%finding node process is actually running in the whole subnet. Thus, in
-%contrast to the intra-node parallelism, the inter-node parallelism is
-%a structural property of the DiSR algorithm and should not be avoided.
+\subsection{Intra-node vs Inter-node parallelism}
+In the processes described above, we assumed that each node in the
+READY\_SEARCHING state can start a find segment process by injecting a
+\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when defining DiSR
+should be made in order to decide whether or not the node must
+actually perform this action. 
+The point above is is strictly related to the general question: which
+level of “parallelism” should we allow in DiSR ? The adopted approach
+is that, although the nature of DiSR itself is intrinsicly parallel,
+the use of parallelism makes things work in a more complex way. In
+other words, DiSR is parallel when needed, but it does not exploit
+parallelism as an “improving feature”. When not needed, things should
+be serialized. For example: when a node is “ready searching” could
+start several find segment process associated to the same segment, one
+for each free link. But serializing this by investigating the free
+links in order could be a simplest solution. We refer to this saying
+that we avoid intra-node parallelism.  Note that while intra-node
+parallelism can be avoided, trying to avoid inter-node parallelism
+could be more complex than allowing the parallelism itself. Imagine
+for example the effort of trying to coordinate nodes so that an unique
+finding node process is actually running in the whole subnet. Thus, in
+contrast to the intra-node parallelism, the inter-node parallelism is
+a structural property of the DiSR algorithm and should not be avoided.
 %------------------------------------------------------------------------------
 
+% TODO: FIX and RE-enable in long paper
+
 \section{Detailed Node behaviour Model}
-\label{sec:disr_detailed_model}
+\label{sec:execution_model}
 
@@
 can learn the segment id they belong to.  \emph{LED} shoud be
-updated: The state of the node changes from \emph{tvisited} to \emph{visited}.  the
+updated from \emph{tvisited} to \emph{visited}.  the
 \emph{link\_tvisited} previously set with the \emph{segID} should be invalidated the

### 2013-11-04 PAPER/implementation.tex
Synced to after-conferences updates

@@
-\section{Implementation Issues}
+\section{Hardware Implementation}
 \label{sec:implementation}
@@
   \centering
-  \includegraphics[width=0.25\textwidth]{pictures/disr_imp.eps}
+  \includegraphics[width=0.40\textwidth]{pictures/implementation.eps}
   \caption{\emph{DiSR} block architecture.}
@@
 
-Let's so focus to the \emph{DiSR} block. In
-Fig.~\ref{fig:implementation} is shown a possible sketch of this
-block, which mainly consist in the following building elements:
+To give a basic estimate of the overhead needed we will focus on
+DiSR-specific components, that is, the control logic and configuration
+registers needed to implement DiSR. In
+Figure~\ref{fig:implementation} is shown a sketch of this block, which
+mainly consist in the following building element: 
+\begin{itemize}
+	\item \textbf{DBS block:} It takes trace of the DBS state machine, 
+	consisting of a 3-bit register (to cover six DBS values) and the 
+	required combinational logic. This block receives signals from 
+	stored packets to decode the packet type, and from 
+	the control circuitry to change its status.
+	The bootstrap node is selected by setting the boot signal to high
+	during the initialization phase.  
+	\item \textbf{LED registers:} A set of registers storing 
+	the Local Environment Data (LED) listed in the section
+	\ref{sec:disr_concepts}. It should be pointed out that, while the \emph{visited} 
+	and \emph{tvisited} data must be implemented with two distinct
+	elements, the \emph{tvisited} and \emph{visited} table can be implemented with 
+	a single RAM file for storing the segment id of each link.
+	This can be done adding a special register named \emph{Tflag}
+	indicating whether the \emph{SegID} value refers to \emph{visited} or to 
+	\emph{tvisited}. When SegID's register is set to 0, it means that the link
+	is neither visited nor tvisited.
 
-\begin{itemize}
-\item \emph{DBS block}: It Takes trace of the DBS, and how already
-discussed in the Section~\ref{ssec:disr_dstruct}, there are six possible
-configurations. These values can be codified using 3 bit implemented
-with a 3-bit register and the required combinational logic. This block
-is essentially designed as a state machine.
-\item \emph{LED registers}: Is a set of registers useful for storing
-the local environment data (LED) described in
-Section~\ref{ssec:disr_dstruct}. In particular in
-fig.~\ref{fig:implementation}, are highlighted two tables representing
-the \emph{link\_visited[]} and \emph{link\_tvisited[]} values. This
-block consists of an array of registers (one for each
-direction) that can be implemented with an SRAM, in which are presents
-two specific fields  for representing the \emph{segID}. 
-\item \emph{Control circuitry}: This circuitry reads data
-from the fields of the incoming packet, LED registers and the
-\emph{DBS}, updating \emph{LED} and
-\emph{DBS} data when required. Then, the resulting \emph{Ctrl Out} output  drives the other
-communication resources (such as node transceivers) for actuating the
-DiSR routing operation.
+    \item \textbf{Control circuitry:} This circuitry reads data from
+	the incoming packet, the LED registers and the DBS,
+	updating them when required. This block drives the LED register 
+	for storing or, for reading the LED data according with
+	\emph{write enable (WE)} or \emph{read enable (RE)}
+	signals. Then, the resulting Ctrl-Out output drives the other
+	communication resources for actuating the DiSR routing operation.
 \end{itemize}
+
+Each building block reacts with the rising edge  of
+the\emph{clock signal} shown in Figure. An asynchronous system
+\emph{reset} signal is also present for restoring all registers to
+their default values. When this last signal is
+set, the DBS state machines for each network's node are set as
+\emph{Free}.
 
@@
 implementing both computations and routing decisions for each node.
-For this reason, assuming a budget of $10^4$ CNFETs for each network's
+Assuming a budget of $10^4$ CNFETs for each network's
 node~\cite{liu_jetcs}  we estimated the required resource for
-implementing the entire DiSR block. A not optimized behavioural
-HDL of the DiSR circuitry has been written and synthesized at gate-level.
-Considering the specific layout of each single logic elements ( NAND,
-full-adder, latch etc.), it has been possible to get a rough estimate
-of the number of transistors necessary for implementing the DiSR
-logic.  Figure~\ref{fig:imp_trend} shows the results of synthesis in
+implementing the entire DiSR block.  A not optimized RTL description
+(with an hardware description language)  of the DiSR circuitry has
+been written and synthesized at gate-level. Considering the specific
+layout of each single logic elements (NAND, full-adder, latch etc.),
+it has been possible to get a rough estimate of the number of
+transistors necessary for implementing the DiSR logic.
+
+Figure~\ref{fig:imp_trend} shows the results of synthesis in
 terms of number of devices (CNFETs) versus the number of network nodes
@@
   \centering
-  \includegraphics[width=0.25\textwidth]{pictures/imp_rslt.eps}
-  \caption{DiSR synthesis results: N is the number of network's node.}
+  \includegraphics[width=0.40\textwidth]{pictures/imp_rslt.eps}
+  \caption{Number of network's node (N) vs number of CNFETs.}
  \label{fig:imp_trend}
 \end{figure}
-In particular, observing the Fig.\ref{fig:imp_trend} can 
-be pointed out that the proposed implementation occupy  about 20\% of the node budget. 
+In particular, observing the Figure~\ref{fig:imp_trend} can 
+be pointed out that the proposed implementation occupy  about 17\% of the node budget. 
 Further, more than the absolute number of devices itself, it is interesting to
@@
 An intuitive explanation of this is the relatively simple logic of
-DiSR, whose behaviour is almost code on scalable storage structures.
-For example, the number of registers implementing the
-\emph{link\_visited[]} and \emph{link\_tvisited[]} table follow the
-logarithmic function:
-\begin{equation}
-  \label{eq:imp_trend}
-  N_{reg}=2\cdot N_{port} \cdot log_2(N)
-\end{equation}
-where $N_{port}$ is the number of the router's ports, $N$ is the number 
-of network's nodes while the term $2$ takes in account that \emph{link\_visited[]} and 
-\emph{link\_tvisited[]} are two separate set of registers. While this number is fixed by 
-the number of network's node, the control circuitry could be optimized applying more effort 
-in future designs of this building block.
+DiSR, whose behaviour is al4ost code on scalable storage structures.
+For example, the number of registers
+implementing the \emph{link\_visited[]} and \emph{link\_tvisited[]}
+table follow the logarithmic function $N_{reg}=N_{port} \cdot
+log_2(N)$ where \emph{Nport} is the number of the router’s ports, N is
+the number of network’s nodes.  While $N_{reg}$ is fixed by the number
+of network’s node,  the control circuitry could be optimized applying
+more effort in future designs of this building block.

### 2013-11-04 PAPER/introduction.tex
Synced to after-conferences updates

@@
 
-% TODO: re-enable on long paper
-%Exploring long term alternatives to the CMOS technology is gaining
-%more and more revelance as the scaling trend of such devices keeps
-%introducing new challenges. Power density, defect tolerance, testing
-%costs and wire delays are only a few of the many critical aspects
-%involved~\cite{itrs12}. While software parallelism and multicore
-%approaches~\cite{horowitz2004, mudge2001, powell2009} are partially mitigating the impact of such
-%constraints on performances, it is likely that the growing computing demand will
-%eventually need even more radical architectural modifications and new
-%paradigms in order to address the Computer Design challenges of the next
-%decades.
+ TODO: re-enable on long paper
+Exploring long term alternatives to the CMOS technology is gaining
+more and more revelance as the scaling trend of such devices keeps
+introducing new challenges. Power density, defect tolerance, testing
+costs and wire delays are only a few of the many critical aspects
+involved~\cite{itrs12}. While software parallelism and multicore
+approaches~\cite{horowitz2004, mudge2001, powell2009} are partially mitigating the impact of such
+constraints on performances, it is likely that the growing computing demand will
+eventually need even more radical architectural modifications and new
+paradigms in order to address the Computer Design challenges of the next
+decades.
 
@@
 scaffold.
-%(see figure~\ref{fig:dna_tag}.
-%
-%\begin{figure}
-%  \centering
-%    \includegraphics[width=0.30\textwidth]{pictures/dna2b.eps}
-%  \caption{DNA tag matching}
-%  \label{fig:dna_tag}
-%\end{figure}
 A detailed description of the chemical properties involved is far
@@
 
+\begin{figure}
+\centering
+\begin{tabular}{cc}
+    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps} &
+    \includegraphics[width=0.40\textwidth]{pictures/dna1_complex2.eps} \\
+ (a) & (b)
+ \end{tabular}
+  \caption{DNA tag matching and Resulting Irregualr Topology}
+  \label{fig:nana}
+\end{figure}
 These aspects of a DNA-self assembly process lead to some important
@@
 underlying computing architecture.
-
-%where instructions and data operands travel
-%on packets and routed using a topology-agnostic strategy that avoids
-%deadlock, 
-\begin{figure}
-  \centering
-    \includegraphics[width=0.20\textwidth]{pictures/dna1.eps}
-  \caption{Irregular topology of computing and storage elements}
-  \label{fig:nana}
-\end{figure}
 

### 2013-11-04 PAPER/simulation.tex
NocArc review fixes
Synced to after-conferences updates

@@
 \begin{itemize}
-\item {\emph{Size of the network}}: number of nodes, on a
-range from 10x10 to 100x100 sized networks. 
+\item {\emph{Size of the network}}: number of nodes, on a range from
+10x10 to 100x100 sized networks. 
 %\item {\% defective links}: the probability that each link is
@@
 % TODO: long paper
-%\subsection{Other optimisations}
-%Some optimisation parameters, which demostrated to improve the DiSR
-%results have been fixed to some good values, but are not subject to
-%further investigation; once again the focus here is not the
-%optimal set of segments, but just demostrating a working approach. 
-%These are optimisations are:
-%\begin{itemize}
-%\item{cycle\_links}: max number of retries across the set of links of
-%each node. While searching for a free link due an incoming request,
-%the same request is cancelled after a given number of tries. This
-%gives to preceding node change to test a different paths. Default is set to 1.
-%\item{bootstrap\_timeout}: number of time units that a bootstrap node
-%should wait before assuming that a livelock in the starting segment
-%process has occurred. In the worst case, we can imagine that longest
-%path required is the one returning to the bootstrap node after having
-%travelled across all the links. So, althought this is just an extreme
-%situation, a good upper limit can be safely be set to NxN.
-%\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
-%setup process, a bootstrap node should not have defective links.
-%Enabling this optimisation, a bootstrap node is immune to defects.
-%We may think of a pre-bootstrap phase that properly selects (from upper
-%layer via) a bootstrap node which is tested as properly connected. We
-%enabled this optimisation, however empirical tests showed us that only
-%simulations using bootstrap nodes placed on edges would be heavily
-%affected, since these are nodes starting with a lower number of links,
-%e.g. corner nodes could only have two connected direction, so even a
-%defective link could prevent starting segment packet to return to
-%bootstrap to close the loop a create the segment.
-%\end{itemize}
+\subsection{Other Optimisations}
+Some optimisation parameters, which demostrated to improve the DiSR
+results have been fixed to some good values, but are not subject to
+further investigation; once again the focus here is not the
+optimal set of segments, but just demostrating a working approach. 
+These are optimisations are:
+\begin{itemize}
+\item{cycle\_links}: max number of retries across the set of links of
+each node. While searching for a free link due an incoming request,
+the same request is cancelled after a given number of tries. This
+gives to preceding node change to test a different paths. Default is set to 1.
+\item{bootstrap\_timeout}: number of time units that a bootstrap node
+should wait before assuming that a livelock in the starting segment
+process has occurred. In the worst case, we can imagine that longest
+path required is the one returning to the bootstrap node after having
+travelled across all the links. So, althought this is just an extreme
+situation, a good upper limit can be safely be set to NxN.
+\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
+setup process, a bootstrap node should not have defective links.
+Enabling this optimisation, a bootstrap node is immune to defects.
+We may think of a pre-bootstrap phase that properly selects (from upper
+layer via) a bootstrap node which is tested as properly connected. We
+enabled this optimisation, however empirical tests showed us that only
+simulations using bootstrap nodes placed on edges would be heavily
+affected, since these are nodes starting with a lower number of links,
+e.g. corner nodes could only have two connected direction, so even a
+defective link could prevent starting segment packet to return to
+bootstrap to close the loop a create the segment.
+\end{itemize}
 
@@
 
-Figure~\ref{fig:results} collects the results in terms of node
+In this section we analyze the results in terms of node
 coverage and latency at different network sizes, defect rates and
-bootstrap injection points.  In particular graphs (a) and (b) show
+bootstrap injection points.  In particular
+Figure~\ref{fig:results_coverage} shows
 node coverage for DiSR and RPF tree based approach respectively. While
 the first aim of DiSR is not to reach the optimal coverage, we still
-can observe a quite good performance as compared to tree based
+can observe a quite good performance as compared to the tree based
 approach. Note that defect rates beyond 25\% lead to many disconnected
-regions of nodes that this first of DiSR cannot handle; however, these
-level of defects should be considered as worst case scenarios, so the
-achieved coverage of $0.5$ is satisfying results for this first
-version of DiSR. As regards the the network size it seems to have a
-limited impact when defect rate do not introduce to much disconnected
+regions of nodes that DiSR currently cannot handle.
+For example Figure~\ref{fig:net} show a 30x30 network with a 25\%
+defect in which the bottom-left part cannot be reached due
+disconnected regions. Note that remaining defective nodes belonging to
+connected regions are successfully surrounded by DiSR coverage; in any
+case, these defect levels should be considered as worst case scenarios, so the
+achieved coverage of $0.5$ is a satisfying result for this first
+version of DiSR. On the other hand, the network size seems to have a
+limited impact when defect rate do not introduce too much disconnected
 regions. 
+\begin{figure}
+\centering
+\begin{tabular}{cc}
+\includegraphics[width=0.48\textwidth]{pictures/set1.eps} & 
+\includegraphics[width=0.48\textwidth]{pictures/coverage.eps} \\
+(a) & (b) 
+\end{tabular}
+\caption{DiSR (a) and RPF (b) node coverage}
+\label{fig:results_coverage}
+\end{figure}
 
-The number of cycles required to complete the segment mapping
-process is shown in latency graph (c). Comparison against tree-based
-has been omitted for space reasons, however similar numbers (in terms
-of upper bound) have been reported
-(see~\cite{Patwardhan05evaluatingthe} for details). What it's more
-interesting is to observe is how DiSR latency scales with network
-size. For example, going from 900 to 2500 nodes, at the medium defect
-rate of $0.15$, leads to an increase from 3000 to 4500 cycles. Note how
-the effect of defect rate is increasing until the threshold of $0.25$
-is reached, meaning that while DiSR finds it more difficult to
-complete the process due increasing defective paths, it still discover
-new segments when let running for a more extended amount of cycles.
-After that threshold, the impact of entire disconnected regions
-becomes predominant and DiSR more quickly complete the process
-covering the nodes that can be reached.
+\begin{figure}
+\centering
+\includegraphics[width=0.70\textwidth]{pictures/net.ps}
+\caption{Covered regions in a 30x30 network with 25\% defects}
+\label{fig:net}
+\end{figure}
 
@@
 \begin{tabular}{cc}
-\includegraphics[width=0.22\textwidth]{pictures/set1.eps} & 
-\includegraphics[width=0.22\textwidth]{pictures/coverage.eps} \\
-(a) & (b) \\
-\includegraphics[width=0.22\textwidth]{pictures/set2.eps} & 
-\includegraphics[width=0.22\textwidth]{pictures/set3.eps} \\
-(c) & (d)
+\includegraphics[width=0.48\textwidth]{pictures/set2.eps} & 
+\includegraphics[width=0.48\textwidth]{pictures/set2_rpf.eps} \\
+(a) & (b)
 \end{tabular}
-\caption{DiSR (a) and RPF (b) node coverage (c) Latency and effect
-of bootstrap node (d)}
-\label{fig:results}
+\caption{Latency of DiSR (a) vs tree based RPF (b) }
+\label{fig:results_latency}
 \end{figure}
 
-Finally, picture (d) visually represent  the stability of the approach
-against different choices of the bootstrap node in a 10x10 network.
-This is an important aspect to evaluate when considering that one of
-the main advantages of DiSR against all the tree based approaches
-should be the ability of choosing whatever bootstrap node, without
-having to care of any particular \emph{root-node role} assumed in the future.
-In other words, after segments have been established, the bootstrap node
-is like every other node, i.e. it is not center of a structure, and it
-is not an hotspot for the traffic distribution. The results in terms
-of coverage,  shown for low, medium and high defect profiles, seems to
-demonstrate a relatively limited impact of the bootstrap choice in
-the low/medium scenarios, while a 30\%instability is found for very high defect
-rates. This also sounds acceptable, since when lot of defective nodes
-are present, the particular position of the bootstrap choice could
-lead to completely different evolution in the DiSR setup process.
+The number of cycles required to complete segment mapping process
+is shown in Figure~\ref{fig:results_latency}. In this case comparison
+against tree-based shows better (lower) values at different defect
+rates.  Rather than the absolute numbers, what it's more interesting
+to observe is how DiSR latency scales with network size. For example,
+going from 900 to 2500 nodes, at the medium defect rate of $0.15$,
+leads to an increase from 3000 to 4500 cycles. It should be noticed
+also how the effect of defect rate is increasing until the threshold
+of $0.25$ is reached, meaning that until that limit DiSR finds it more
+and more difficult to complete the process due increasing defective
+paths, but still discover new segments when let running for a more
+extended amount of cycles. This behavior is not reported in the RPF
+based approach, meaning that a tree based approach, although starting
+from higher values, is less affected by defect rates (when low rates
+are considered).
+After the $0.25$ threshold, the impact of entire disconnected regions
+becomes predominant and both approaches become faster in completing
+the covering process, since far less nodes can be actually reached.
+
+Finally, Figure~\ref{fig:results_bootstrap} visually represents  the
+stability of the approach against choices of a different bootstrap
+node in a 10x10 network.  This is an important aspect to evaluate when
+considering that one of the main advantages of DiSR against all the
+tree based approaches should be the ability of choosing whatever
+bootstrap node, without having to care about the role assumed in the
+future by the chosen root node.  In other words, after segments have
+been established, the bootstrap node is like every other node, i.e. it
+is not center of a structure, and it is not an hotspot for the traffic
+distribution. The results in terms of coverage,  shown for low, medium
+and high defect profiles, demonstrate a relatively limited
+impact of the bootstrap choice in the low/medium scenarios, while a
+$30\%$ instability is found for very high defect rates. This also
+sounds acceptable, since when a lot of defective nodes are present, the
+particular position of the bootstrap node could lead to a completely
+different evolution in the DiSR setup process.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth]{pictures/set3.eps}
+\caption{Effect of bootstrap node}
+\label{fig:results_bootstrap}
+\end{figure}

### 2013-11-04 trunk/PAPER/pictures/set2_script.m
updated/new pics

@@ -1,0 +1,9 @@
+plot(coverage,dieci,'-+')
+xlabel('Node Defect Rate')
+ylabel('Latency')
+hold on
+plot(coverage,trenta,'--o')
+plot(coverage,cinquanta,':*')
+plot(coverage,cento,'-.x')
+
+legend('100x100','50x50','30x30','10x10')

### 2013-11-04 trunk/PAPER/implementation.tex
monteleone's fixes

@@
 
-Let's so focus to the \emph{DiSR} block. In
-Fig.~\ref{fig:implementation} is shown a possible sketch of this
-block, which mainly consist in the following building elements:
+To give a basic estimate of the overhead needed we will focus on
+DiSR-specific components, that is, the control logic and configuration
+registers needed to implement DiSR. In
+Figure~\ref{fig:implementation} is shown a sketch of a possible
+implementation, which mainly consist in the following building
+elements: 
+\begin{itemize}
+	\item \textbf{DBS block:} It takes trace of the DBS state machine, 
+	consisting of a 3-bit register (to cover six DBS values) and the 
+	required combinational logic. This block receives signals from 
+	stored packets to decode the packet type, and from 
+	the control circuitry to change its status.
+	The bootstrap node is selected by setting the boot signal to high
+	during the initialization phase.  
+	\item \textbf{LED registers:} A set of registers storing 
+	the \emph{LED} listed in the section
+	\ref{sec:disr_concepts}. It should be pointed out that, while the \emph{visited} 
+	and \emph{tvisited} data must be implemented with two distinct
+	elements, the \emph{tvisited} and \emph{visited} table can be implemented with 
+	a single RAM file for storing the segment id of each link.
+	This can be done adding a special register named \emph{Tflag}
+	indicating whether the \emph{SegID} value refers to \emph{visited} or to 
+	\emph{tvisited}. When SegID's register is set to 0, it means that the link
+	is neither visited nor tvisited.
 
-\begin{itemize}
-\item \emph{DBS block}: It Takes trace of the DBS, and how already
-discussed in the Section~\ref{ssec:disr_dstruct}, there are six possible
-configurations. These values can be codified using 3 bit implemented
-with a 3-bit register and the required combinational logic. This block
-is essentially designed as a state machine.
-\item \emph{LED registers}: Is a set of registers useful for storing
-the local environment data (LED) described in
-Section~\ref{ssec:disr_dstruct}. In particular in
-fig.~\ref{fig:implementation}, are highlighted two tables representing
-the \emph{link\_visited[]} and \emph{link\_tvisited[]} values. This
-block consists of an array of registers (one for each
-direction) that can be implemented with an SRAM, in which are presents
-two specific fields  for representing the \emph{segID}. 
-\item \emph{Control circuitry}: This circuitry reads data
-from the fields of the incoming packet, LED registers and the
-\emph{DBS}, updating \emph{LED} and
-\emph{DBS} data when required. Then, the resulting \emph{Ctrl Out} output  drives the other
-communication resources (such as node transceivers) for actuating the
-DiSR routing operation.
+    \item \textbf{Control circuitry:} This circuitry reads data from
+	the incoming packet, the LED registers and the DBS,
+	updating them when required. This block drives the LED register 
+	for storing or, for reading the LED data according with
+	\emph{write enable (WE)} or \emph{read enable (RE)}
+	signals. Then, the resulting \emph{Ctrl-Out} drives the other
+	communication resources for actuating the DiSR routing operation.
 \end{itemize}
+
+Each building block reacts with the rising edge  of
+the\emph{clock signal} shown in Figure. An asynchronous system
+\emph{reset} signal is also present for restoring all registers to
+their default values. When this last signal is
+set, the DBS state machines for each network's node are set as
+\emph{Free}.
 
@@
 implementing both computations and routing decisions for each node.
-For this reason, assuming a budget of $10^4$ CNFETs for each network's
-node~\cite{liu_jetcs} we estimated the required resource for
-implementing the entire DiSR block. A not optimized behavioural
-HDL of the DiSR circuitry has been written and synthesized at gate-level.
-Considering the specific layout of each single logic elements ( NAND,
-full-adder, latch etc.), it has been possible to get a rough estimate
-of the number of transistors necessary for implementing the DiSR
-logic.  Figure~\ref{fig:imp_trend} shows the results of synthesis in
+Assuming a budget of $10^4$ CNFETs for each network's
+node~\cite{liu_jetcs}  we estimated the required resources for
+implementing the entire DiSR block.  A not optimized RTL description
+(with an hardware description language)  of the DiSR circuitry has
+been written and synthesized at gate-level. Considering the specific
+layout of each single logic elements (NAND, full-adder, latch etc.),
+it has been possible to get a rough estimate of the number of
+transistors necessary to implement the DiSR logic.
+
+Figure~\ref{fig:imp_trend} shows the results of synthesis in
 terms of number of devices (CNFETs) versus the number of network nodes
@@
   \centering
-  \includegraphics[width=0.25\textwidth]{pictures/imp_rslt.eps}
+  \includegraphics[width=0.40\textwidth]{pictures/imp_rslt.eps}
   \caption{Number of network's node (N) vs number of CNFETs.}
@@
 \end{figure}
-In particular, observing the Fig.\ref{fig:imp_trend} can 
-be pointed out that the proposed implementation occupy  about 20\% of the node budget. 
+In particular, observing the Figure~\ref{fig:imp_trend} can 
+be pointed out that the proposed implementation occupies about 17\% of the node budget. 
 Further, more than the absolute number of devices itself, it is interesting to

### 2013-11-04 trunk/PAPER/introduction.tex
monteleone's fixes

@@
 
+\begin{figure}
+\centering
+\begin{tabular}{cc}
+    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps} &
+    \includegraphics[width=0.40\textwidth]{pictures/dna1_complex2.eps} \\
+ (a) & (b)
+ \end{tabular}
+  \caption{DNA tag matching and Resulting Irregualr Topology}
+  \label{fig:nana}
+\end{figure}
 These aspects of a DNA-self assembly process lead to some important
 implications to be addressed when approaching to the design of
-computer architecture: a computational model should be founded on a
+computer architecture: a computational model should be based on a
 distributed network of small computing and storage nodes, randomly
-placed and interconnected (see figure~\ref{fig:nana}).
+placed and interconnected (see Figure~\ref{fig:nana}).
 Proof-of-concept of such kind of computational model can be found for
@@
 
-%where instructions and data operands travel
-%on packets and routed using a topology-agnostic strategy that avoids
-%deadlock, 
-\begin{figure}
-  \centering
-    \includegraphics[width=0.20\textwidth]{pictures/dna1.eps}
-  \caption{Irregular topology of computing and storage elements}
-  \label{fig:nana}
-\end{figure}
-
-In this paper we introduce DiSR, a first effort for a Distributed
-Segment-based Routing in large scale DNA self assembled networks.
-The main contribution is to bring the advantages of
-a segment-based approach~\cite{mejia_ipdps06} to deadlock freedom without requiring any topology graph,
-external defect map or centralized algorithm execution. 
-While maintaining similar properties to segment-based , the DiSR
-approach is not intended to discover the "optimal" segment choice
-(ideally reachable with the knowledge of the topology graph) but just
-to demonstrate a concrete model that can fit into such complex,
-irregular and large sized topologies.
-Given the irregular/high-defect rates scenario discussed above, is essential
-avoiding non-scalable or resource hungry solutions such as
-centralized off-chip algorithms, tree-based approaches, virtual channels
-or expensive implementations based on hardware redundancy.
+In this work we introduce DiSR, a Distributed Segment-based approach
+to deadlock freedom in large scale DNA self assembled networks. Our
+contribution aims to achieve the classical properties of a
+segment-based approach~\cite{mejia_ipdps06} without requiring any
+topology graph, external defect map or centralized algorithm
+execution.  So the DiSR approach is not intended to discover the
+``optimal'' segment choice (ideally reachable with the knowledge of
+the topology graph) but just to demonstrate a concrete model that can
+fit into such complex, irregular and large sized networks.
 

### 2013-11-04 trunk/PAPER/simulation.tex
Fixes pic captions
monteleone's fixes

--- 2013-09-17 PAPER/simulation.tex
@@
-\section{Simulation environment}
+\section{Simulation and Results}
+\label{sec:simulation}
 
 In this section we will test the proposed DiSR approach to demonstrate
-its effectiveness from two different perspectives:
-\begin{itemize}
-\item Against the centralized segment based approach (SR), to evaluate
-if and how its known properties are still preserved in the new nano-scale distributed scenario
-\item Against topology agnostic approaches based on spanning
-trees and broadcasting, to measure how DiSR performs in discovering
-the network structure 
-\end{itemize}
+its effectiveness and compare it against topology agnostic approach
+based on spanning trees and
+broadcasting~\cite{Patwardhan05evaluatingthe}, to measure how DiSR
+performs in covering the network structure.
 
-\subsection{Nanoxim tool}
+%\item Against the centralized segment based approach (SR), to evaluate
+%if and how its known properties are still preserved in the new nano-scale distributed scenario
+
+\subsection{Nanoxim Environment}
 
@@
 specific simulation environment has been developed, resulting in
-the open source and freely available project called Nanoxim~\cite{}.
+the open source and freely available project called
+Nanoxim~\cite{nanoxim}.
 Nanoxim is a SystemC tool based on a almost rewritten
-version of the Noxim Network-on-Chip simulator~\cite{}. While some
+version of the Noxim Network-on-Chip simulator~\cite{noxim}. While some
 complex features have been removed (e.g. wormhole, congestion/topology
 aware routing and selection strategies) new features specifically
-taylored for nanoscale scenario were introduced, e.g. the ability to simulate a random
+taylored for the nanoscale scenario were introduced, e.g. the ability to simulate a random
 network, the implementation of the DiSR to obtain the segment topology
@@
 \begin{itemize}
-\item {S}: Size of the network, intended as number of nodes, on a
-range from 10x10 to 100x100 sized networks. 
-\item {\% defective links}: the probability that each link is
-disconnected or not present, from 0 the amount that yelds
-no more segments.
-\item {\% defective nodes}: the probability that a node is not
-working, thus having all its attached links not useful for DiSR setup.
-Same range as defective links parameter.
-\item {Bootstrap node}: the node used from upper layer (e.g. microscale)
+\item {\emph{Size of the network}}: number of nodes, on a range from
+10x10 to 100x100 sized networks. 
+%\item {\% defective links}: the probability that each link is
+%disconnected or not present, from 0 the amount that yelds
+%no more segments.
+\item {\emph{\% defective nodes}}: the probability that a node is not
+working, thus having all its links cannot be utilized during DiSR setup.  
+%Same range as defective links parameter.
+\item {\emph{Bootstrap node}}: the node used from upper layer 
 to inject the DiSR process. When not explicitly investigating the
 impact of each single bootstrap choice, a set representative regions have been
-considered, i.e. the central part of the network and the edge corners
+considered, e.g. the central part of the network and the edge corners.
 \end{itemize}
-
-The show the results, the following evaluation metrics have been adopted:
+To present the results, the following evaluation metrics have been adopted:
 \begin{itemize}
@@
 nodes should be assigned, so this metric is useful to show how some
-disconnected node regions can negativaly impact on the whole DiSR
+disconnected regions can negatively impact on the whole DiSR
 effectiveness.
-\item{Broadcast latency}: this measures how the time required to complete the
-segment assignment scale for increasing network sizes and defect rates
-\item{Bootstrap node effect}: this evaluates the impact of the chosen
+\item{\emph{Latency}}: this measures how the cycles required to complete the
+segment assignment scales for increasing network sizes and defect rates
+\item{\emph{Bootstrap node effect}}: this evaluates the impact of the chosen
 bootstrap node on the node coverage.
@@
 
-Further, to evaluate how DiSR compares against the centralized segment
-based algorithm, the following metrics have been adopted:
-\begin{itemize}
-\item {Average Path Lenght}:
-\item {Average Link Weight}:
-\item {Unidirectional restrictions:}
-\item {Number of Segments}:
-\end{itemize}
+%Further, to evaluate how DiSR compares against the centralized segment
+%based algorithm, the following metrics have been adopted:
+%\begin{itemize}
+%%\item {Average Path Lenght}:
+%%\item {Average Link Weight}:
+%\item {Unidirectional restrictions:}
+%\item {Number of Segments}:
+%\end{itemize}
 
@@
 generated, a set of simulations with different seeds has been run
-for each system configuration. We found that TODO repetitions are
+for each system configuration. We found that 20 repetitions are
 required in order to obtain statistically significant results.
 
-\subsection{Other optimisations}
+% TODO: long paper
+\subsection{Other Optimisations}
 Some optimisation parameters, which demostrated to improve the DiSR
@@
 Enabling this optimisation, a bootstrap node is immune to defects.
-We may think of a pre-boostrap phase that properly selects (from upper
+We may think of a pre-bootstrap phase that properly selects (from upper
 layer via) a bootstrap node which is tested as properly connected. We
@@
 bootstrap to close the loop a create the segment.
-
 \end{itemize}
 
-\section{Results}
+\subsection{Results}
 \label{sec:results}
 
-In Figure~\ref{fig:coverage} is shown node coverage using different
-network sizes and bootstrap injection points. As can be seen,
-increasing the \% of defective node, TODO COMMENT...
-
-\begin{figure*}
+In this section we analyze the results in terms of node
+coverage and latency at different network sizes, defect rates and
+bootstrap injection points.  In particular
+Figure~\ref{fig:results_coverage} shows
+node coverage for DiSR and RPF tree based approach respectively. While
+the first aim of DiSR is not to reach the optimal coverage, we still
+can observe a quite good performance as compared to the tree based
+approach. Note that defect rates beyond 25\% lead to many disconnected
+regions of nodes that DiSR currently cannot handle.
+For example Figure~\ref{fig:net} show a 30x30 network with a 25\%
+defect in which the bottom-left part cannot be reached due
+disconnected regions. Note that remaining defective nodes belonging to
+connected regions are successfully surrounded by DiSR coverage; in any
+case, these defect levels should be considered as worst case scenarios, so the
+achieved coverage of $0.5$ is a satisfying result for this first
+version of DiSR. On the other hand, the network size seems to have a
+limited impact when defect rate do not introduce too much disconnected
+regions. 
+\begin{figure}
 \centering
 \begin{tabular}{cc}
-    \includegraphics[width=0.40\textwidth]{pictures/set1.eps} & 
-    \includegraphics[width=0.40\textwidth]{pictures/set3.eps} \\
+\includegraphics[width=0.48\textwidth]{pictures/set1.eps} & 
+\includegraphics[width=0.48\textwidth]{pictures/coverage.eps} \\
 (a) & (b) 
 \end{tabular}
-  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
-  \label{fig:coverage}
-\end{figure*}
+\caption{DiSR (a) and RPF (b) node coverage}
+\label{fig:results_coverage}
+\end{figure}
 
-Figure~\ref{fig:bootstrap} shows the effect of bootstrap node position
-on node coverage, for different defect rates. TODO COMMENT.
+\begin{figure}
+\centering
+\includegraphics[width=0.70\textwidth]{pictures/net.ps}
+\caption{Covered regions in a 30x30 network with 25\% defects}
+\label{fig:net}
+\end{figure}
 
-%\begin{figure}
-%  \centering
-%  \begin{tabular}{cc}
-%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_nodefect_Xbootstrap_Ycoverage.eps} & 
-%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_nodefect_Xbootstrap_Ycoverage.eps} \\
-%    \includegraphics[width=0.40\textwidth]{pictures/sim8x8_defect01_Xbootstrap_Ycoverage.eps} & 
-%    \includegraphics[width=0.40\textwidth]{pictures/sim15x15_defect01_Xbootstrap_Ycoverage.eps} \\
-%    (a) & (b)
-%  \end{tabular}
-%  \caption{Node coverage in function of Node defect rates at 8x8 (a) and 15x15 (b) network sizes}
-%  \label{fig:bootstrap}
-%\end{figure}
+\begin{figure}
+\centering
+\begin{tabular}{cc}
+\includegraphics[width=0.48\textwidth]{pictures/set2.eps} & 
+\includegraphics[width=0.48\textwidth]{pictures/set2_rpf.eps} \\
+(a) & (b)
+\end{tabular}
+\caption{Latency of DiSR (a) vs tree based RPF (b) }
+\label{fig:results_latency}
+\end{figure}
 
-Next, Figure~\ref{fig:latency_size} shows latency as function of
-network size, with different defect rates, while Figure~\ref{fig:latency_defective}
-shows the same latency when different bootstrap nodes are
-considered.... TODO COMMENT
+The number of cycles required to complete segment mapping process
+is shown in Figure~\ref{fig:results_latency}. In this case comparison
+against tree-based shows better (lower) values at different defect
+rates.  Rather than the absolute numbers, what it's more interesting
+to observe is how DiSR latency scales with network size. For example,
+going from 900 to 2500 nodes, at the medium defect rate of $0.15$,
+leads to an increase from 3000 to 4500 cycles. It should be noticed
+also how the effect of defect rate is increasing until the threshold
+of $0.25$ is reached, meaning that until that limit DiSR finds it more
+and more difficult to complete the process due increasing defective
+paths, but still discover new segments when let running for a more
+extended amount of cycles. This behavior is not reported in the RPF
+based approach, meaning that a tree based approach, although starting
+from higher values, is less affected by defect rates (when low rates
+are considered).
+After the $0.25$ threshold, the impact of entire disconnected regions
+becomes predominant and both approaches become faster in completing
+the covering process, since far less nodes can be actually reached.
 
-TODO: something like Broadcast Tree properties (sez.  5.4)
+Finally, Figure~\ref{fig:results_bootstrap} visually represents  the
+stability of the approach against choices of a different bootstrap
+node in a 10x10 network.  This is an important aspect to evaluate when
+considering that one of the main advantages of DiSR against all the
+tree based approaches should be the ability of choosing whatever
+bootstrap node, without having to care about the role assumed in the
+future by the chosen root node.  In other words, after segments have
+been established, the bootstrap node is like every other node, i.e. it
+is not center of a structure, and it is not an hotspot for the traffic
+distribution. The results in terms of coverage,  shown for low, medium
+and high defect profiles, demonstrate a relatively limited
+impact of the bootstrap choice in the low/medium scenarios, while a
+$30\%$ instability is found for very high defect rates. This also
+sounds acceptable, since when a lot of defective nodes are present, the
+particular position of the bootstrap node could lead to a completely
+different evolution in the DiSR setup process.
+
+\begin{figure}
+\centering
+\includegraphics[width=0.48\textwidth]{pictures/set3.eps}
+\caption{Effect of bootstrap node}
+\label{fig:results_bootstrap}
+\end{figure}

### 2013-11-05 trunk/PAPER/introduction.tex
Removed figure/text overlapping

@@
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
   \label{fig:nana}
-\end{figure}
+\end{figure*}
 These aspects of a DNA-self assembly process lead to some important

### 2014-02-12 trunk/PAPER/implementation.tex
bibliography updated

@@
 
-Although a completed and detailed floorplan of the node is not the
-focus of this work, in this section we want to give a basic idea of
-which are the main elements required to support this kind of
-architecture thus giving an estimate of the overhead by the
-DiSR approach. There are three main classes of node elements:
-\begin{itemize}
-\item Node-specific: components (such ALUs, memories) that are
-strictly related to the node functionality and role inside a given
-network, e.g. being a computation or storage node.
-\item Node communication:  these are elements (such as transceivers,
-buffers) required to the node to communicate with its neighbours,
-independently from node functionality and DiSR implementatio
-\item DiSR-specific: all the hardware, control logic and
-configuration registers, related to an implementation the proposed approach.
-\end{itemize}
+A possible hardware implementation of the DiSR algorithm will be
+described in this section.  Before enter in to detail of  DiSR
+architecture,  an idea of node structure tailored for this particular
+scenario, can be found depicted in Fig.~\ref{fig:node_structure}. In
+particular, such node should have the following foundamental elements:
+
+\begin{itemize}%----Start Itemize------
+
+\item I/O Buffers-Trasceivers: These elements, one for
+each port,  are responsible of data transmission between neighbours
+nodes. The packets received or sent are stored in specifieds buffers
+named input and output buffers respectivelly.
+
+\item Switch Matrix: driven by a switch controller, enables the
+reciprocal connections beetween the devices inside the node. Before
+the creation of segments, such controller receives information from
+DiSR block.  After this phase, the switch controller will be driven by
+the block wich implements the routing algorithm. The Switch matrix is
+essentially a series of multiplexers and demultiplexers.
+
+\item : Processing Element (PE):Is strictly related to the node
+functionality  and role inside a given network, e.g. being a
+computation or storage node.
+
+\item DiSR-Routing: The DiSR block contains all the hardware, control
+logic and configuration registers, related to the implementation of the
+proposed approach. The routing algorithm receives information
+from DiSR  wich indicates the status of the segments that interests a
+particular node. The routing operation will take in account of these
+informations in order to perform a deadlock-free routing. Both Routing
+and DiSR are connected to the switch matrix in order to receive
+packets from the input buffer. Since the packets are processed one at
+a time, a specific arbiter should be present within the switch matrix
+controller.
+
+\end{itemize}%------End Itemize------
 
@@
   \centering
-  \includegraphics[width=0.40\textwidth]{pictures/implementation.eps}
+  \includegraphics[width=0.45\textwidth]{pictures/node_structure.eps}
+  \caption{A possible node structure tailored for a DNA nanonetwork.}
+ \label{fig:node_structure}
+\end{figure}
+%--------------------------------------------------------------------
+\subsection{DiSR Architecture}
+\label{ssec:disr_architecture}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.40\textwidth]{pictures/disr_rtl_updated.eps}
   \caption{\emph{DiSR} block architecture.}
@@
 
-To give a basic estimate of the overhead needed we will focus on
-DiSR-specific components, that is, the control logic and configuration
-registers needed to implement DiSR. In
-Figure~\ref{fig:implementation} is shown a sketch of a possible
-implementation, which mainly consist in the following building
-elements: 
+To give a basic estimate of the overhead needed we will focus on DiSR-
+specific components, that is, the control logic and configuration
+registers needed to implement DiSR. In Figure~\ref{fig:implementation}
+is shown a sketch of the  architecture, which mainly consist in the
+following building elements:
+
 \begin{itemize}
-	\item \textbf{DBS block:} It takes trace of the DBS state machine, 
+
+	\item \textbf{DBS block:} 
+	It takes trace of the DBS state machine, 
 	consisting of a 3-bit register (to cover six DBS values) and the 
 	required combinational logic. This block receives signals from 
-	stored packets to decode the packet type, and from 
+	stored packets  in order to decode the packet type, and from 
 	the control circuitry to change its status.
@@
 	during the initialization phase.
-	\item \textbf{LED registers:} A set of registers storing 
-	the \emph{LED} listed in the section
-	\ref{sec:disr_concepts}. It should be pointed out that, while the \emph{visited} 
-	and \emph{tvisited} data must be implemented with two distinct
-	elements, the \emph{tvisited} and \emph{visited} table can be implemented with 
-	a single RAM file for storing the segment id of each link.
-	This can be done adding a special register named \emph{Tflag}
-	indicating whether the \emph{SegID} value refers to \emph{visited} or to 
-	\emph{tvisited}. When SegID's register is set to 0, it means that the link
-	is neither visited nor tvisited.
 
-    \item \textbf{Control circuitry:} This circuitry reads data from
-	the incoming packet, the LED registers and the DBS,
-	updating them when required. This block drives the LED register 
-	for storing or, for reading the LED data according with
-	\emph{write enable (WE)} or \emph{read enable (RE)}
+	\item \textbf{LED registers:} 
+	A set of registers store the \emph{LED} listed in the
+	section~\ref{sec:disr_concepts}.  In particular, in the
+	link\_visited[] table, can be pointed out the presence of two  
+	particular registernamed \emph{tflag} and \emph{busy}.  The Latter
+	is used to indicate if a specific port is alredy visited or tvisited and
+	the former indicates specifically if the node is visited or tvisited.
+
+    \item \textbf{Control circuitry:}
+    This circuitry decodes the the      incoming packet, the LED
+	registers and the DBS,     updating them when required. This block
+	drives the LED register   to store or, to read the LED data
+	according with     \emph{write enable (WE)} or \emph{read enable (RE)}
 	signals. Then, the resulting \emph{Ctrl-Out} drives the other
 	communication resources for actuating the DiSR routing operation.
+
+	\item \textbf{Packager:}
+	Essentially is a set of registers and multiplexers. Starting from
+	an incoming packet stored in the input buffer, it updates the
+	content of the packet before the retransmission to   a destination
+	node.  In some cases, this circuitry build the packet from the
+	scratch.  For example this happens when a node is bootsrap and for
+	the first time it should inject a
+	\emph{strating\_segment\_request}. In Fig.~\ref{fig:packager} is
+	shown the architecture of such packager block. When a packet is
+	created for the first time, the multiplexers driven by the
+	controller select the information coming from the internal node
+	such as the \emph{soruce\_ID}. In this situation the TTL field
+	should be resetted to its initial value and the \emph{segment\_ID}
+	is composed by the node ID and by the output port identification 
+	number.
+
 \end{itemize}
 
-Each building block reacts with the rising edge  of
-the\emph{clock signal} shown in Figure. An asynchronous system
-\emph{reset} signal is also present for restoring all registers to
-their default values. When this last signal is
-set, the DBS state machines for each network's node are set as
-\emph{Free}.
+While the elements mentioned above are part of the DiSR circuitry, 
+the other devices depicted in Fig.~\ref{fig:implementation} like the 
+multiplexer and demultiplexer are implemented outside DiSR.
+In particular, such components will be within the switch matrix 
+(refers to the Fig~\ref{fig:node_structure}).
 
-As discussed above, one of the main design challenge of DNA
-Self-Assembled systems is the limited resource available for
-implementing both computations and routing decisions for each node.
-Assuming a budget of $10^4$ CNFETs for each network's
-node~\cite{liu_jetcs}  we estimated the required resources for
-implementing the entire DiSR block.  A not optimized RTL description
-(with an hardware description language)  of the DiSR circuitry has
-been written and synthesized at gate-level. Considering the specific
-layout of each single logic elements (NAND, full-adder, latch etc.),
-it has been possible to get a rough estimate of the number of
-transistors necessary to implement the DiSR logic.
-
-Figure~\ref{fig:imp_trend} shows the results of synthesis in
-terms of number of devices (CNFETs) versus the number of network nodes
-while the network scales up from $10\times10$ to $100\times100$ nodes.
 \begin{figure}
   \centering
-  \includegraphics[width=0.40\textwidth]{pictures/imp_rslt.eps}
+  \includegraphics[width=0.40\textwidth]{pictures/packager.eps}
+  \caption{Packager block}
+ \label{fig:packager}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.40\textwidth]{pictures/pipeline.eps}
+  \caption{Pipeline description of DiSR operations}
+ \label{fig:pipeline}
+\end{figure}
+
+Each just described building block, reacts with the rising edge  of
+the\emph{clock signal}. An asynchronous system \emph{reset} signal is
+also present for restoring all registers to their default values. When
+this last signal is set, the DBS state machines for each network's
+node are set as \emph{Free}.  
+In Fig.~\ref{fig:pipeline} is described the pipeline structure of the
+DiSR architecture. The packet incoming from the neighbours node, or
+locally generated will be send to the DBS state machine in order to te
+ensure the status commutation. While the DBS update its state,  in the
+next clock cycle the control circuitry will update the Led status and
+will drive the sitch matrix in order to send eventually the packets to
+the  right output buffer.
+%--------------------------------------------------------------------
+\subsection{Synthesis results}
+
+As discussed above, one of the main design challenge of DNA Self-
+Assembled systems is the limited resource available to implement both
+computations and routing decisions for each node. Assuming a budget of
+$10^4$ CNFETs for each network's node~\cite{liu_jetcs}  we estimated
+the required resources for implementing the entire DiSR block. The RTL
+description of the circuitry described in the last section (with an
+hardware description language)  of the DiSR circuitry has been written
+and synthesized at gate-level. Considering the specific layout of each
+single logic elements (NAND, full-adder, latch etc.), it has been
+possible to get a rough estimate of the number of transistors
+necessary to implement the DiSR logic. Figure~\ref{fig:imp_trend}
+shows the results of synthesis in terms of number of devices (CNFETs)
+versus the number of network nodes while the network scales up from
+$10\times10$ to $100\times100$ nodes.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.50\textwidth]{pictures/synthesis.eps}
   \caption{Number of network's node (N) vs number of CNFETs.}
- \label{fig:imp_trend}
+ \label{fig:synthesys}
 \end{figure}
+
 In particular, observing the Figure~\ref{fig:imp_trend} can 
-be pointed out that the proposed implementation occupies about 17\% of the node budget. 
+be pointed out that the proposed implementation occupies about 17,5\% of the node budget. In particular the main contribution is due to the controller circuitry followed by LED registers.
 Further, more than the absolute number of devices itself, it is interesting to
-observe that, while the node have a squared increment, the circuitry
+observe that the circuitry
 complexity which implements the DiSR algorithm increases with a slowly
@@
 An intuitive explanation of this is the relatively simple logic of
-DiSR, whose behaviour is al4ost code on scalable storage structures.
+DiSR, whose behaviour is almost code on scalable storage structures.
 For example, the number of registers
@@
 log_2(N)$ where \emph{Nport} is the number of the router’s ports, N is
-the number of network’s nodes.  While $N_{reg}$ is fixed by the number
-of network’s node,  the control circuitry could be optimized applying
-more effort in future designs of this building block.
+the number of network’s nodes.
+
+In order ha have estimate the maximum working clock frequency for the implemented
+circuitry, the \cite{deng_isscc07}

### 2014-02-12 trunk/PAPER/implementation.tex
implementation updated

@@
 
-\item I/O Buffers-Trasceivers: These elements, one for
+\item \textbf{I/O Buffers-Trasceivers:} These elements, one for
 each port,  are responsible of data transmission between neighbours
@@
 
-\item Switch Matrix: driven by a switch controller, enables the
+\item \textbf{Switch Matrix:} Driven by a switch controller, enables the
 reciprocal connections beetween the devices inside the node. Before
@@
 
-\item : Processing Element (PE):Is strictly related to the node
+\item  \textbf{Processing Element (PE):} Is strictly related to the node
 functionality  and role inside a given network, e.g. being a
@@
 
-\item DiSR-Routing: The DiSR block contains all the hardware, control
+\item \textbf{DiSR-Routing:} The DiSR block contains all the hardware, control
 logic and configuration registers, related to the implementation of the
@@
 hardware description language)  of the DiSR circuitry has been written
-and synthesized at gate-level. Considering the specific layout of each
-single logic elements (NAND, full-adder, latch etc.), it has been
-possible to get a rough estimate of the number of transistors
-necessary to implement the DiSR logic. Figure~\ref{fig:imp_trend}
-shows the results of synthesis in terms of number of devices (CNFETs)
-versus the number of network nodes while the network scales up from
-$10\times10$ to $100\times100$ nodes.
+and synthesized at gate-level using \emph{Synopsys Design Compiler} with 
+a generic technology library (GTECH).
+Considering the specific layout of each single logic elements  (NAND,
+full-adder, latch etc.), it has been possible to get a rough estimate
+of the number of transistors necessary to implement the DiSR logic.
+Figure~\ref{fig:synthesys} shows the results of synthesis in terms of
+number of devices (CNFETs) versus the number of network nodes while
+the network scales up from $10\times10$ to $100\times100$ nodes.
 
@@
   \includegraphics[width=0.50\textwidth]{pictures/synthesis.eps}
-  \caption{Number of network's node (N) vs number of CNFETs.}
+  \caption{Number of network's node (N) vs number of CNFETs necassary to implement
+  the DiSR circuitry.}
  \label{fig:synthesys}
@@
 
-In particular, observing the Figure~\ref{fig:imp_trend} can 
-be pointed out that the proposed implementation occupies about 17,5\% of the node budget. In particular the main contribution is due to the controller circuitry followed by LED registers.
-Further, more than the absolute number of devices itself, it is interesting to
-observe that the circuitry
-complexity which implements the DiSR algorithm increases with a slowly
-growing trend.  
-An intuitive explanation of this is the relatively simple logic of
-DiSR, whose behaviour is almost code on scalable storage structures.
-For example, the number of registers
+In particular, observing the Figure~\ref{fig:synthesys} can  be
+pointed out that the proposed implementation occupies about 17,5\% of
+the node budget. In particular the main contribution is due to the
+controller circuitry followed by LED registers. Further, more than the
+absolute number of devices itself, it is interesting to observe that
+the circuitry complexity which implements the DiSR algorithm increases
+with a slowly growing trend.   An intuitive explanation of this is the
+relatively simple logic of DiSR, whose behaviour is almost code on
+scalable storage structures. For example, the number of registers
 implementing the \emph{link\_visited[]} and \emph{link\_tvisited[]}
@@
 
-In order ha have estimate the maximum working clock frequency for the implemented
-circuitry, the \cite{deng_isscc07}
+In order to have an idea of the maximum working clock frequency for the
+implemented circuitry, we can obtain the timing results from a gate-
+level netlist. Since a complete technology library usefull for 
+commercial synthesis tool (like Design Compiler) doesn't exist for the this particular technology
+(at the best that we know), we have synthesized the RTL description of DiSR
+with a standard 32nm CMOS library obtain 
+a delay of about $\mathrm{\tau_{DiSR}=10} FO4$ (fan-out of four).
+Considering the results obtained in~\cite{deng_isscc07}, wich reports the
+ratio in therms of FO4 between a standard 32nm CMOS technology and a
+carbon nanotube ones, we can have a rough delay estimation.
+In particolar has been reported a ratio R of: 
+\begin{equation}
+\mathrm{R=\frac{FO4_{CMOS}}{FO4_{CNFET}}=2} 
+\end{equation}
+Considering that F04 CMOS is about 30 ps, and the results of  
+last equation thedelay of one FO4 for the CNFET case is about of
+15 ps an then the working frequency can be cmputed as:
+
+\begin{equation}
+\mathrm{f_{clk}=\frac{1}{T_{max}}=\frac{1}{\tau_{DiSR} \cdot FO4_{CNFET}}}=
+\frac{1}{10\cdot 15 \cdot 10^{-12}}=6,6 GHz
+\end{equation}
+
+where $\mathrm{\tau_{DiSR}}$ was expressed in therms of FO4.
+
+Regards the power
+consumption of the entire DiSR devices, we can skip to perform an a

### 2014-02-12 PAPER/implementation.tex
Fixed DiSR word

@@
 
-Although a completed and detailed floorplan of the node is not the
-focus of this work, in this section we want to give a basic idea of
-which are the main elements required to support this kind of
-architecture thus giving an estimate of the overhead by the
-DiSR approach. There are three main classes of node elements:
-\begin{itemize}
-\item Node-specific: components (such ALUs, memories) that are
-strictly related to the node functionality and role inside a given
-network, e.g. being a computation or storage node.
-\item Node communication:  these are elements (such as transceivers,
-buffers) required to the node to communicate with its neighbours,
-independently from node functionality and DiSR implementatio
-\item DiSR-specific: all the hardware, control logic and
-configuration registers, related to an implementation the proposed approach.
-\end{itemize}
+A possible hardware implementation of the \disr{} algorithm will be
+described in this section.  Before enter in to detail of  \disr{}
+architecture,  an idea of node structure tailored for this particular
+scenario, can be found depicted in Fig.~\ref{fig:node_structure}. In
+particular, such node should have the following foundamental elements:
+
+\begin{itemize}%----Start Itemize------
+
+\item \textbf{I/O Buffers-Trasceivers:} These elements, one for
+each port,  are responsible of data transmission between neighbours
+nodes. The packets received or sent are stored in specifieds buffers
+named input and output buffers respectivelly.
+
+\item \textbf{Switch Matrix:} Driven by a switch controller, enables the
+reciprocal connections beetween the devices inside the node. Before
+the creation of segments, such controller receives information from
+\disr{} block.  After this phase, the switch controller will be driven by
+the block wich implements the routing algorithm. The Switch matrix is
+essentially a series of multiplexers and demultiplexers.
+
+\item  \textbf{Processing Element (PE):} Is strictly related to the node
+functionality  and role inside a given network, e.g. being a
+computation or storage node.
+
+\item \textbf{\disr{}-Routing:} The \disr{} block contains all the hardware, control
+logic and configuration registers, related to the implementation of the
+proposed approach. The routing algorithm receives information
+from \disr{}  wich indicates the status of the segments that interests a
+particular node. The routing operation will take in account of these
+informations in order to perform a deadlock-free routing. Both Routing
+and \disr{} are connected to the switch matrix in order to receive
+packets from the input buffer. Since the packets are processed one at
+a time, a specific arbiter should be present within the switch matrix
+controller.
+
+\end{itemize}%------End Itemize------
 
@@
   \centering
-  \includegraphics[width=0.40\textwidth]{pictures/implementation.eps}
-  \caption{\emph{DiSR} block architecture.}
+  \includegraphics[width=0.45\textwidth]{pictures/node_structure.eps}
+  \caption{A possible node structure tailored for a DNA nanonetwork.}
+ \label{fig:node_structure}
+\end{figure}
+%--------------------------------------------------------------------
+\subsection{\disr{} Architecture}
+\label{ssec:disr_architecture}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.40\textwidth]{pictures/disr_rtl_updated.eps}
+  \caption{\emph{\disr{}} block architecture.}
  \label{fig:implementation}
@@
 
-To give a basic estimate of the overhead needed we will focus on
-DiSR-specific components, that is, the control logic and configuration
-registers needed to implement DiSR. In
-Figure~\ref{fig:implementation} is shown a sketch of this block, which
-mainly consist in the following building element: 
+To give a basic estimate of the overhead needed we will focus on \disr{}-
+specific components, that is, the control logic and configuration
+registers needed to implement \disr{}. In Figure~\ref{fig:implementation}
+is shown a sketch of the  architecture, which mainly consist in the
+following building elements:
+
 \begin{itemize}
-	\item \textbf{DBS block:} It takes trace of the DBS state machine, 
+
+	\item \textbf{DBS block:} 
+	It takes trace of the DBS state machine, 
 	consisting of a 3-bit register (to cover six DBS values) and the 
 	required combinational logic. This block receives signals from 
-	stored packets to decode the packet type, and from 
+	stored packets  in order to decode the packet type, and from 
 	the control circuitry to change its status.
@@
 	during the initialization phase.
-	\item \textbf{LED registers:} A set of registers storing 
-	the Local Environment Data (LED) listed in the section
-	\ref{sec:disr_concepts}. It should be pointed out that, while the \emph{visited} 
-	and \emph{tvisited} data must be implemented with two distinct
-	elements, the \emph{tvisited} and \emph{visited} table can be implemented with 
-	a single RAM file for storing the segment id of each link.
-	This can be done adding a special register named \emph{Tflag}
-	indicating whether the \emph{SegID} value refers to \emph{visited} or to 
-	\emph{tvisited}. When SegID's register is set to 0, it means that the link
-	is neither visited nor tvisited.
 
-    \item \textbf{Control circuitry:} This circuitry reads data from
-	the incoming packet, the LED registers and the DBS,
-	updating them when required. This block drives the LED register 
-	for storing or, for reading the LED data according with
-	\emph{write enable (WE)} or \emph{read enable (RE)}
-	signals. Then, the resulting Ctrl-Out output drives the other
-	communication resources for actuating the DiSR routing operation.
+	\item \textbf{LED registers:} 
+	A set of registers store the \emph{LED} listed in the
+	section~\ref{sec:disr_concepts}.  In particular, in the
+	link\_visited[] table, can be pointed out the presence of two  
+	particular registernamed \emph{tflag} and \emph{busy}.  The Latter
+	is used to indicate if a specific port is alredy visited or tvisited and
+	the former indicates specifically if the node is visited or tvisited.
+
+    \item \textbf{Control circuitry:}
+    This circuitry decodes the the      incoming packet, the LED
+	registers and the DBS,     updating them when required. This block
+	drives the LED register   to store or, to read the LED data
+	according with     \emph{write enable (WE)} or \emph{read enable (RE)}
+	signals. Then, the resulting \emph{Ctrl-Out} drives the other
+	communication resources for actuating the \disr{} routing operation.
+
+	\item \textbf{Packager:}
+	Essentially is a set of registers and multiplexers. Starting from
+	an incoming packet stored in the input buffer, it updates the
+	content of the packet before the retransmission to   a destination
+	node.  In some cases, this circuitry build the packet from the
+	scratch.  For example this happens when a node is bootsrap and for
+	the first time it should inject a
+	\emph{strating\_segment\_request}. In Fig.~\ref{fig:packager} is
+	shown the architecture of such packager block. When a packet is
+	created for the first time, the multiplexers driven by the
+	controller select the information coming from the internal node
+	such as the \emph{soruce\_ID}. In this situation the TTL field
+	should be resetted to its initial value and the \emph{segment\_ID}
+	is composed by the node ID and by the output port identification 
+	number.
+
 \end{itemize}
 
-Each building block reacts with the rising edge  of
-the\emph{clock signal} shown in Figure. An asynchronous system
-\emph{reset} signal is also present for restoring all registers to
-their default values. When this last signal is
-set, the DBS state machines for each network's node are set as
-\emph{Free}.
+While the elements mentioned above are part of the \disr{} circuitry, 
+the other devices depicted in Fig.~\ref{fig:implementation} like the 
+multiplexer and demultiplexer are implemented outside \disr{}.
+In particular, such components will be within the switch matrix 
+(refers to the Fig~\ref{fig:node_structure}).
 
-As discussed above, one of the main design challenge of DNA
-Self-Assembled systems is the limited resource available for
-implementing both computations and routing decisions for each node.
-Assuming a budget of $10^4$ CNFETs for each network's
-node~\cite{liu_jetcs}  we estimated the required resource for
-implementing the entire DiSR block.  A not optimized RTL description
-(with an hardware description language)  of the DiSR circuitry has
-been written and synthesized at gate-level. Considering the specific
-layout of each single logic elements (NAND, full-adder, latch etc.),
-it has been possible to get a rough estimate of the number of
-transistors necessary for implementing the DiSR logic.
-
-Figure~\ref{fig:imp_trend} shows the results of synthesis in
-terms of number of devices (CNFETs) versus the number of network nodes
-while the network scales up from $10\times10$ to $100\times100$ nodes.
 \begin{figure}
   \centering
-  \includegraphics[width=0.40\textwidth]{pictures/imp_rslt.eps}
-  \caption{Number of network's node (N) vs number of CNFETs.}
- \label{fig:imp_trend}
+  \includegraphics[width=0.40\textwidth]{pictures/packager.eps}
+  \caption{Packager block}
+ \label{fig:packager}
 \end{figure}
-In particular, observing the Figure~\ref{fig:imp_trend} can 
-be pointed out that the proposed implementation occupy  about 17\% of the node budget. 
-Further, more than the absolute number of devices itself, it is interesting to
-observe that, while the node have a squared increment, the circuitry
-complexity which implements the DiSR algorithm increases with a slowly
-growing trend.  
-An intuitive explanation of this is the relatively simple logic of
-DiSR, whose behaviour is al4ost code on scalable storage structures.
-For example, the number of registers
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.40\textwidth]{pictures/pipeline.eps}
+  \caption{Pipeline description of \disr{} operations}
+ \label{fig:pipeline}
+\end{figure}
+
+Each just described building block, reacts with the rising edge  of
+the\emph{clock signal}. An asynchronous system \emph{reset} signal is
+also present for restoring all registers to their default values. When
+this last signal is set, the DBS state machines for each network's
+node are set as \emph{Free}.  
+In Fig.~\ref{fig:pipeline} is described the pipeline structure of the
+\disr{} architecture. The packet incoming from the neighbours node, or
+locally generated will be send to the DBS state machine in order to te
+ensure the status commutation. While the DBS update its state,  in the
+next clock cycle the control circuitry will update the Led status and
+will drive the sitch matrix in order to send eventually the packets to
+the  right output buffer.
+%--------------------------------------------------------------------
+\subsection{Synthesis results}
+
+As discussed above, one of the main design challenge of DNA Self-
+Assembled systems is the limited resource available to implement both
+computations and routing decisions for each node. Assuming a budget of
+$10^4$ CNFETs for each network's node~\cite{liu_jetcs}  we estimated
+the required resources for implementing the entire \disr{} block. The RTL
+description of the circuitry described in the last section (with an
+hardware description language)  of the \disr{} circuitry has been written
+and synthesized at gate-level using \emph{Synopsys Design Compiler} with 
+a generic technology library (GTECH).
+Considering the specific layout of each single logic elements  (NAND,
+full-adder, latch etc.), it has been possible to get a rough estimate
+of the number of transistors necessary to implement the \disr{} logic.
+Figure~\ref{fig:synthesys} shows the results of synthesis in terms of
+number of devices (CNFETs) versus the number of network nodes while
+the network scales up from $10\times10$ to $100\times100$ nodes.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.50\textwidth]{pictures/synthesis.eps}
+  \caption{Number of network's node (N) vs number of CNFETs necassary to implement
+  the \disr{} circuitry.}
+ \label{fig:synthesys}
+\end{figure}
+
+In particular, observing the Figure~\ref{fig:synthesys} can  be
+pointed out that the proposed implementation occupies about 17,5\% of
+the node budget. In particular the main contribution is due to the
+controller circuitry followed by LED registers. Further, more than the
+absolute number of devices itself, it is interesting to observe that
+the circuitry complexity which implements the \disr{} algorithm increases
+with a slowly growing trend.   An intuitive explanation of this is the
+relatively simple logic of \disr{}, whose behaviour is almost code on
+scalable storage structures. For example, the number of registers
 implementing the \emph{link\_visited[]} and \emph{link\_tvisited[]}
@@
 log_2(N)$ where \emph{Nport} is the number of the router’s ports, N is
-the number of network’s nodes.  While $N_{reg}$ is fixed by the number
-of network’s node,  the control circuitry could be optimized applying
-more effort in future designs of this building block.
+the number of network’s nodes.
+
+In order to have an idea of the maximum working clock frequency for the
+implemented circuitry, we can obtain the timing results from a gate-
+level netlist. Since a complete technology library usefull for 
+commercial synthesis tool (like Design Compiler) doesn't exist for the this particular technology
+(at the best that we know), we have synthesized the RTL description of \disr{}
+with a standard 32nm CMOS library obtain 
+a delay of about $\mathrm{\tau_{\disr{}}=10} FO4$ (fan-out of four).
+Considering the results obtained in~\cite{deng_isscc07}, wich reports the
+ratio in therms of FO4 between a standard 32nm CMOS technology and a
+carbon nanotube ones, we can have a rough delay estimation.
+In particolar has been reported a ratio R of: 
+\begin{equation}
+\mathrm{R=\frac{FO4_{CMOS}}{FO4_{CNFET}}=2} 
+\end{equation}
+Considering that F04 CMOS is about 30 ps, and the results of  
+last equation thedelay of one FO4 for the CNFET case is about of
+15 ps an then the working frequency can be cmputed as:
+
+\begin{equation}
+\mathrm{f_{clk}=\frac{1}{T_{max}}=\frac{1}{\tau_{\disr{}} \cdot FO4_{CNFET}}}=
+\frac{1}{10\cdot 15 \cdot 10^{-12}}=6,6 GHz
+\end{equation}
+
+where $\mathrm{\tau_{\disr{}}}$ was expressed in therms of FO4.
+
+Regards the power
+consumption of the entire \disr{} devices, we can skip to perform an a

### 2014-02-12 PAPER/introduction.tex
Fixed DiSR word

@@
 
- TODO: re-enable on long paper
 Exploring long term alternatives to the CMOS technology is gaining
@@
 involved~\cite{itrs12}. While software parallelism and multicore
-approaches~\cite{horowitz2004, mudge2001, powell2009} are partially mitigating the impact of such
+approaches~\cite{horowitz2004, powell2009} are partially mitigating the impact of such
 constraints on performances, it is likely that the growing computing demand will
@@
 
-In the last years, Self-assembled nanoscale architectures~\cite{winfree1998, yan2003}
-are emerging as a promising technology due their tera/peta scale of
+In the last years, Self-assembled nanoscale architectures~\cite{yan2003}
+emerged as a promising technology due their tera/peta scale of
 integration, defect tolerance and huge potential computing
@@
   \label{fig:nana}
-\end{figure}
+\end{figure*}
 These aspects of a DNA-self assembly process lead to some important
 implications to be addressed when approaching to the design of
-computer architecture: a computational model should be founded on a
+computer architecture: a computational model should be based on a
 distributed network of small computing and storage nodes, randomly
-placed and interconnected (see figure~\ref{fig:nana}).
+placed and interconnected (see Figure~\ref{fig:nana}).
 Proof-of-concept of such kind of computational model can be found for
@@
 
-In this paper we introduce DiSR, a first effort for a Distributed
-Segment-based Routing in large scale DNA self assembled networks.
-The main contribution is to bring the advantages of
-a segment-based approach~\cite{mejia_ipdps06} to deadlock freedom without requiring any topology graph,
-external defect map or centralized algorithm execution. 
-While maintaining similar properties to segment-based , the DiSR
-approach is not intended to discover the "optimal" segment choice
-(ideally reachable with the knowledge of the topology graph) but just
-to demonstrate a concrete model that can fit into such complex,
-irregular and large sized topologies.
-Given the irregular/high-defect rates scenario discussed above, is essential
-avoiding non-scalable or resource hungry solutions such as
-centralized off-chip algorithms, tree-based approaches, virtual channels
-or expensive implementations based on hardware redundancy.
+In this work we introduce \disr{}, a Distributed Segment-based approach
+to deadlock freedom in large scale DNA self assembled networks. Our
+contribution aims to achieve the classical properties of a
+segment-based approach~\cite{mejia_ipdps06} without requiring any
+topology graph, external defect map or centralized algorithm
+execution.  So the \disr{} approach is not intended to discover the
+``optimal'' segment choice (ideally reachable with the knowledge of
+the topology graph) but just to demonstrate a concrete model that can
+fit into such complex, irregular and large sized networks.
 
@@
 simulations are carried out with the opensource tool Nanoxim to
-demonstrate how DiSR preserves some of the main segment-based
+demonstrate how \disr{} preserves some of the main segment-based
 properties and how compares to the tree-based approaches. Finally a
@@
 
-The DiSR approach presented in this work is a first attempt of
+The \disr{} approach presented in this work is a first attempt of
 reaching the same goals of a segment based approach, that is

### 2014-02-12 PAPER/simulation.tex
Fixed DiSR word

@@
 
-In this section we will test the proposed DiSR approach to demonstrate
-its effectiveness and to compare it against topology agnostic approach
+In this section we will test the proposed \disr{} approach to demonstrate
+its effectiveness and compare it against topology agnostic approach
 based on spanning trees and
-broadcasting~\cite{Patwardhan05evaluatingthe}, to measure how DiSR
-performs in covering the network structure
+broadcasting~\cite{Patwardhan05evaluatingthe}, to measure how \disr{}
+performs in covering the network structure.
 
@@
 
-\subsection{Nanoxim environment}
+\subsection{Nanoxim Environment}
 
@@
 aware routing and selection strategies) new features specifically
-taylored for nanoscale scenario were introduced, e.g. the ability to simulate a random
-network, the implementation of the DiSR to obtain the segment topology
+taylored for the nanoscale scenario were introduced, e.g. the ability to simulate a random
+network, the implementation of the \disr{} to obtain the segment topology
 and the support for defective links and nodes.
@@
 The following parameters have been taken into account when
-performing the DiSR simulation:
+performing the \disr{} simulation:
 \begin{itemize}
@@
 \item {\emph{\% defective nodes}}: the probability that a node is not
-working, thus having all its links cannot be utilized during DiSR setup.  
+working, thus having all its links cannot be utilized during \disr{} setup.  
 %Same range as defective links parameter.
 \item {\emph{Bootstrap node}}: the node used from upper layer 
-to inject the DiSR process. When not explicitly investigating the
+to inject the \disr{} process. When not explicitly investigating the
 impact of each single bootstrap choice, a set representative regions have been
-considered, i.e. the central part of the network and the edge corners
+considered, e.g. the central part of the network and the edge corners.
 \end{itemize}
-
-The show the results, the following evaluation metrics have been adopted:
+To present the results, the following evaluation metrics have been adopted:
 \begin{itemize}
@@
 nodes should be assigned, so this metric is useful to show how some
-disconnected node regions can negatively impact on the whole DiSR
+disconnected regions can negatively impact on the whole \disr{}
 effectiveness.
@@
 
-%Further, to evaluate how DiSR compares against the centralized segment
+%Further, to evaluate how \disr{} compares against the centralized segment
 %based algorithm, the following metrics have been adopted:
@@
 \subsection{Other Optimisations}
-Some optimisation parameters, which demostrated to improve the DiSR
+Some optimisation parameters, which demostrated to improve the \disr{}
 results have been fixed to some good values, but are not subject to
@@
 situation, a good upper limit can be safely be set to NxN.
-\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
+\item{bootstrap\_immunity}: in order to avoid the failure of the whole \disr{}
 setup process, a bootstrap node should not have defective links.
@@
 Figure~\ref{fig:results_coverage} shows
-node coverage for DiSR and RPF tree based approach respectively. While
-the first aim of DiSR is not to reach the optimal coverage, we still
+node coverage for \disr{} and RPF tree based approach respectively. While
+the first aim of \disr{} is not to reach the optimal coverage, we still
 can observe a quite good performance as compared to the tree based
 approach. Note that defect rates beyond 25\% lead to many disconnected
-regions of nodes that DiSR currently cannot handle.
+regions of nodes that \disr{} currently cannot handle.
 For example Figure~\ref{fig:net} show a 30x30 network with a 25\%
@@
 disconnected regions. Note that remaining defective nodes belonging to
-connected regions are successfully surrounded by DiSR coverage; in any
+connected regions are successfully surrounded by \disr{} coverage; in any
 case, these defect levels should be considered as worst case scenarios, so the
 achieved coverage of $0.5$ is a satisfying result for this first
-version of DiSR. On the other hand, the network size seems to have a
+version of \disr{}. On the other hand, the network size seems to have a
 limited impact when defect rate do not introduce too much disconnected
 regions. 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \end{tabular}
-\caption{DiSR (a) and RPF (b) node coverage}
+\caption{\disr{} (a) and RPF (b) node coverage}
 \label{fig:results_coverage}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \label{fig:net}
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \end{tabular}
-\caption{Latency of DiSR (a) vs tree based RPF (b) }
+\caption{Latency of \disr{} (a) vs tree based RPF (b) }
 \label{fig:results_latency}
-\end{figure}
+\end{figure*}
 
@@
 rates.  Rather than the absolute numbers, what it's more interesting
-to observe is how DiSR latency scales with network size. For example,
+to observe is how \disr{} latency scales with network size. For example,
 going from 900 to 2500 nodes, at the medium defect rate of $0.15$,
@@
 also how the effect of defect rate is increasing until the threshold
-of $0.25$ is reached, meaning that until that limit DiSR finds it more
+of $0.25$ is reached, meaning that until that limit \disr{} finds it more
 and more difficult to complete the process due increasing defective
@@
 node in a 10x10 network.  This is an important aspect to evaluate when
-considering that one of the main advantages of DiSR against all the
+considering that one of the main advantages of \disr{} against all the
 tree based approaches should be the ability of choosing whatever
@@
 particular position of the bootstrap node could lead to a completely
-different evolution in the DiSR setup process.
+different evolution in the \disr{} setup process.
 

### 2014-02-12 trunk/PAPER/paper.tex
Synced to after-conferences updates
Fixed DiSR word

@@
-\documentclass[final,journal,letterpaper]{IEEEtran}
+\documentclass[final,journal]{IEEEtran}
 %\IEEEoverridecommandlockouts
@@
 
-\usepackage{listings}
 \usepackage{listings}
@@
 \newcommand{\etc}{\emph{etc.}}
-\renewcommand{\baselinestretch}{0.97}\normalsize
+\newcommand{\disr}{{\sf DiSR}}
+%\renewcommand{\baselinestretch}{0.97}\normalsize
 %------------------------------------------------------------------------------
@@
 
-\title{A First Effort for a Distributed Segment-based Approach on Self-Assembled Nano Networks}
+\title{Distributed Topology Discovery in Self-Assembled Nano Networks}
 
@@
 \begin{abstract}
-In this paper we present DiSR, a first effort for a distributed
+In this paper we present \disr{}, a first effort for a distributed
 segment-based approach to routing and defect mapping in a nano-scale,
@@
 centralized algorithm to configure network paths.  After introducing
-the conceptual elements and the execution model of DiSR, we show how
+the conceptual elements and the execution model of \disr{}, we show how
 the opensource Nanoxim platform has been used to evaluate the proposed
 approach in the process of discovering irregular network topology
-while establishing network segments.  Results show how DiSR still
+while establishing network segments.  Results show how \disr{} still
 preserves some important properties (coverage, defect tolerance,
@@
 hardware implementation of the required control logic and storage for
-DiSR, demonstrating a relatively acceptable impact ranging from 10 to
+\disr{}, demonstrating a relatively acceptable impact ranging from 10 to
 about 20\% of the budget of transistors available for each node.
@@
 \begin{IEEEkeywords}
-Nanotechnology, DNA, Self-assembly, Routing
+Nanotechnology, DNA, Self-assembly, Routing, Deadlock
 \end{IEEEkeywords}
@@
 \section{Conclusions}
-In this work we presented DiSR, an initial attempt of porting a segment based
+In this work we presented \disr{}, an initial attempt of porting a segment based
 approach to distributed self-assembled nanoscale scenario. We
-demonstrated how DiSR can accomplish the aim of finding a segment
+demonstrated how \disr{} can accomplish the aim of finding a segment
 coverage of the network without requiring any centralized approach
@@
 node size typical of the assumed scenario. Future works will focus on
-developing self tuning of DiSR to match a high coverage levels and the
+developing self tuning of \disr{} to match a high coverage levels and the
 detailed low level hardware implementation on

### 2014-02-12 PAPER/disr.tex
General text reorganization/fixes

@@
 %------------------------------------------------------------------------------
-\section{Preliminary concepts}
+\section{\disr{} Sketch}
 %------------------------------------------------------------------------------
+
 \label{sec:disr_concepts}
+The main concept behind the kind of turn prohibition we want to
+achieve is the \emph{Segment}. A segment is basically a path of consecutive
+nodes and links, starts with a link attached to a node of a different
+segment and ending with a link attached to a
+node belonging another. In other words, a segment
+a path between connecting two other different segments. The example
+in Figure~\ref{fig:segments} shows the segment with id $1.4$, starting
+with a link connected to the node $9$, the going trought nodes
+$4$,$3$,$2$ and ending with the link connected to the node $1$. Other
+segments depicted are $9.2$ (link,node $10$,link) and $9.3$
+(link from $9$ ,$8$,link,$7$,link,$6$,link,$5$,link to the $1$). Note
+also that start/ending link can coincide and a segment can also be
+formed by one single link (e.g. in $7.2$ or $5.4$).
+An exception to the rule that a segment must connect two other
+segments is the first segment established in the network, called
+\emph{starting segment} which is a loop beginning/ending on the same
+node.
 
-\subsection{Basic Idea}
-The main concept behind of the original SR approach is the
-\emph{Segment}: a Segment is basically a path of consecutive node
-and links. All segments start with a link attached to a node which
-belongs to different segment, ending with a link also attached to a
-node belonging to a different segment. A exception is the first
-segment estabilished in the network, called \emph{starting segment} which is  a loop
-beginning/ending on a particular node defined as bootstrap node.
+\begin{figure}
+\centering
+    \includegraphics[width=0.25\textwidth]{pictures/network_slice.eps}
+  \caption{Example of Segments}
+  \label{fig:segments}
+\end{figure}
 
-The idea is to partition the network in a set of disjoint segments, and then
-placing a turn restriction within each segment. It has been proved~\cite{mejia_ipdps06}
-that such a set of turn prohibitions guarantees dealock freedom and
-while preserving connectivity of the network.
+A detailed description of the \disr{} execution model as depicted in
+the Figure~\ref{fig:disr_events} will be discussed in
+Subsection~\ref{sub:phases}. Roughly speaking, the execution of can be described as the execution
+of the following phases: 
+\begin{enumerate}
+\item Injection of the \disr{} process from an upper layer to set a \emph{bootstrap
+node} 
+\item Broadcasting and confirmation to create the first segment of the subnet
+\item Parallel requests starting from assigned node to discover other
+segments. 
+\item Turn proibition in each confirmed segment.
+\item Draining of remaining packet due timeouts
+\end{enumerate}
 
-Describing the execution phases of DiSR from a top level point-of-view
-is basically similar to the classic SR approach. This can be useful to
-give an initial idea of the approach, however, some essential
-differences should be pointed out. First of all no centralized entity is
-globally aware of what is going on: the status of the DiSR execution
-is collectively distributed among the nodes; second, no defect map and/or
-topology graph is available as input, thus, the topology has to be
-discovered \emph{while} segments are created; finally, at the end of the
-execution, no segment list is created: Each node is only aware of
-belonging to some segment, ignoring the presence of other nodes
-in the same segment and even the presence of other segments in the
-network.
+\section{Detailed Description of \disr{}}
+\subsection{Message Types Required}
 
-Roughly speaking, the execution of can be described as the execution
-of the following phases:
+The \disr{} approach works with a distributed mechanism which is build
+upon an exchange of small packets containing the following fields:
 \begin{itemize}
-\item Injection of the DiSR process from upper layer to set a bootstrap
-node
-\item Bootstrap node broadcasting to create the first segment of the subnet
-\item Parallel requests starting from assigned node to discover other segments
-%\item Turn proibition in each confirmed segment
-%\item Draining of remaining packet due timeouts
+\item \emph{packet\_type}: encodes the meaning of the control message
+\item \emph{seg\_ID}: the id of the segment associated to the \disr{} control message
+\item \emph{src\_id}: the id of the node that originated the packet
 \end{itemize}
 
-Once again, it should be pointed out that nowhere in the network there
-is such a global vision of these exection phases. A more detailed
-description of the exection model at each node is discussed in the
-next section.
-
-\subsection{Packets types Required}
-
-The DiSR approach works with a distributed mechanism which is build
-upon an exchange of small packets containing the following fields:
-\begin{itemize}
-\item{packet\_type}: encodes the meaning of the control message respect
-to the whole DiSR process.
-\item{seg\_ID}: the id of the segment associated to the DiSR control message
-\item{src\_id}: the id of the node that initially originated the
-packet
-\end{itemize}
-
-As regards packet\_type, we can have the following control packets:
+As regards \emph{packet\_type} field, we can have the following control packets:
 \begin{itemize}
@@
 
-A quantitative analysis of the resources needed to implement these
-fields is presented in Section~\ref{sec:implementation} when
-discussing the impact of the DiSR control logic and storage on
-hardware implementation of the node.
-
-\subsection{DiSR Data Structures}
+\subsection{\disr{} Data Structures}
 \label{ssec:disr_dstruct}
@@
 
-The \emph{LED} is like a snapshot of the DiSR algorithm at each node,
+The \emph{LED} is like a snapshot of the \disr{} algorithm at each node,
 consisting in the following variables:
-
 \begin{itemize}
@@
 \begin{itemize}
-\item{\emph{Free}}: a node that has  not been yet considered  by the DiSR algorithm.
-The node is not marked as \emph{visited}/\emph{tvisited}.
+\item{\emph{Free}}: a node that has  not been yet considered  by the \disr{} algorithm.
 \item{\emph{Bootstrap}}: a node which has been explicitly set as bootstrap node from
 an upper layer via. 
-% TODO: this and all the other details on the items below should be
-% checked and moved elsewhere for a future long paper
-
-%This is required because a
-%\texttt{STARTING\_SEGMENT\_REQUEST} packet should be injected in order to start
-%the whole process.
 \item{\emph{ActiveSearching}}: a node from which a find process of new segments has
@@
 \item{\emph{Candidate}}: a node currently candidate for belonging to some segment
-with id segid, not being itself the node from which the find process
-was started.
+, but not being itself the node from which the find process was started.
 
@@
 %segID frees the links previously set as \emph{tvisited} during flooding
-\item{\emph{Assigned}}: a node for which the segment has been determined.  The
-segment \emph{segID} attribute value is set to some id X different from \texttt{NULL}.
+\item{\emph{Assigned}}: a node for which the segment has been determined.  
 %The \emph{visited} value is \emph{true} NOTE: an \emph{Assigned} state is a quick temporary
@@
 
-\subsection{Sketch of DiSR}
+A quantitative analysis of the resources needed to implement these
+fields is presented in Section~\ref{sec:implementation} when
+discussing the impact of the \disr{} control logic and storage on
+hardware implementation of the node.
 
+\subsection{Execution Model}
+\label{sub:phases}
+
+The \disr{} control packets described in the previous subsection trigger
+node events, which eventually change $DBS$ status according to the
+current value of $LED$ variables and the type of the packet received.
+The main \disr{} phases, together with a reference to the particular
+status transition involved are described in the following. As a
+convention, we used single letters to refer to one of the \emph{DBS} transitions in
+Figure~\ref{fig:state_machine} while the phases are visually
+represented in~\ref{fig:disr_events}.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.25\textwidth]{pictures/dbs_updated.eps}
+  \caption{\disr{} node execution model}
+  \label{fig:state_machine}
+\end{figure}
 \begin{itemize}
 
-\item{\textbf{Injecting bootstrap request}}: all nodes have a initial
-\emph{DBS} status \emph{Free}, except for a
- node with status \emph{Bootstrap}, set by some signal from an
-upper layer via. When starting, this bootstrap node sets itself as \emph{visited} and
-changes its status to \emph{ActiveSearching}, injecting a
-\texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links.
+\begin{figure*}
+\centering
+\begin{tabular}{cccc}
+\includegraphics[width=0.23\textwidth]{pictures/seq01.eps} & 
+\includegraphics[width=0.23\textwidth]{pictures/seq02.eps} &
+\includegraphics[width=0.23\textwidth]{pictures/seq03.eps} & 
+\includegraphics[width=0.23\textwidth]{pictures/seq04.eps} \\
+(a) & (b) & (c) & (d) \\
+\includegraphics[width=0.23\textwidth]{pictures/seq05.eps} &
+\includegraphics[width=0.23\textwidth]{pictures/seq06.eps} &
+\includegraphics[width=0.23\textwidth]{pictures/seq07.eps} & 
+\includegraphics[width=0.23\textwidth]{pictures/seq08.eps} \\
+(e) & (f) & (g) & (h) \\
+\end{tabular}
+\caption{\disr{} (a) and RPF (b) node coverage}
+\label{fig:disr_events}
+\end{figure*}
 
-\item{\textbf{Flooding}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
-if not yet (\emph{visited}/\emph{tvisited}),  forwards it to its free links using a flooding mechanism.
-Each of these links is then marked as \emph{tvisited} with the segment id
+\item{\textbf{Injecting bootstrap request}}: all nodes have an initial
+\emph{DBS} status set to \emph{Free}, except for a
+ node with status \emph{Bootstrap}, set by some control signal from an
+upper layer via $(a)$. When starting, this bootstrap node 
+changes its status to \emph{CandidateStarting} $(b)$, injecting a
+\texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links
+(Figure~\ref{fig:disr_events}-a).
+
+\item{\textbf{Bootnode Broadcasting}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
+when $Free$, forwards it to its free links using a flooding mechanism and
+becoming $CandidateStarting$ $(g)$.
+Each of its free links is then marked as \emph{tvisited} with the segment id
 associated to the request. Note that a node that has already received a
@@
 associated to the same request, having already contributed to the
-flooding. 
+flooding (Figure~\ref{fig:disr_events}-b).
 %Note also that each of these packets has a max\_segment\_hops
@@
 
-\item{\textbf{Confirming the Starting Segment}}: when this \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
-the starting node (from a different link, of course), the starting
-segment is found. Then the starting node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
-packet with the same id along the link from which it received the
-\texttt{STARTING\_SEGMENT\_REQUEST}. Each node do same by changing its own status
-to \emph{Assigned}. So the confirmation packet is sent back from
-node to node and the starting segment is created.
-
-Note: A node knows to be \emph{Candidate} due a
-\texttt{STARTING\_SEGMENT\_REQUEST}.  Then, when receiving a simple
-(not starting) \texttt{SEGMENT\_REQUEST} , it can simply cancel its
-previous \emph{Candidate} status, since this second
-request means that the starting segment has already been found.
+\item{\textbf{Confirming the Starting Segment}}: when a \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
+the bootstrap node (from a different link, of course), the starting
+segment is found. Then the bootstrap node sends back a \texttt{STARTING\_SEGMENT\_CONFIRM}
+packet along the link from which it received the
+\texttt{STARTING\_SEGMENT\_REQUEST} and becomes $Assigned$ $(l)$. Each
+node receiving the confirm do same by changing its own status
+to \emph{Assigned}(Figure~\ref{fig:disr_events}-c). So the confirmation packet is sent back from
+node to node and the starting segment is created (Figure~\ref{fig:disr_events}-d).
 
@@
 
-\item{\textbf{Injecting other request}}: Each node in the \emph{Assigned} status can initiate a search for a
-segment, by sending a \texttt{SEGMENT\_REQUEST} across one of its free
-links. Note that, since this is not the starting segment, in this case
-the packet should not return back to the initiator, but just another visited
-node
-\item{\textbf{Setup of a segment}}: The find process is successfull
-when an \emph{Assigned} node receives the \texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
-sent back along the path that originated the request.  
-\item{\textbf{Failing while searching a segment}}: a node received a \texttt{SEGMENT\_REQUEST} packet but
-matched one of the following conditions: the node is free but has no
-more suitable free links (can’t forward the \texttt{SEGMENT\_REQUEST}) the node
-is \emph{tvisited} candidate for another find process the request packet
-exceeded the max\_segment\_hops limit.  In all these cases the node
-sends back a \texttt{SEGMENT\_CANCEL} along the proper link modifying its state
-to free. Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
-only if no more free links can be explored starting from them.
+\item{\textbf{Injecting Segment Requests}: Each node in the
+\emph{Assigned} status can initiate a search for a segment, by sending
+a \texttt{SEGMENT\_REQUEST} across one of its free links $(c)$ (see
+Figure~\ref{fig:disr_events}-e). 
+Note that each \emph{Assigned} note can inject the request just after
+becoming assigned, i.e. it is not needed that the whole confirmation
+process in completed (Figure~\ref{disr_events}-f).
+Note also that nodes previosly set as \emph{CandidateStarting}, when receiving 
+a \texttt{SEGMENT\_REQUEST} can simply cancel their
+status and set as $Candidate$ for that request, since this new
+request means that the first starting segment has already been found $(h)$. 
+\item{\textbf{Segment Confirmation}}: The find process is successful
+when an already \emph{Assigned} node receives the
+\texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
+sent back along the path that originated the request
+(Figure~\ref{fig:disr_events}-g), while the
+node remain $Assigned$ (since it could confirm more segments). Each node
+previously set as $Candidate$ for that segment id, when receiving the
+a confirmation packet changes its status to $Assigned$ $(m)$ and forwards back
+the same confirmation until it reaches the initiator of the request,
+which then changes from $ActiveSearching$ to $Assigned$ $(d)$.
+
+\item{\textbf{Failing while searching a segment}}: this happen when a node received a \texttt{SEGMENT\_REQUEST} packet but
+matches one of two the following conditions: first, the node is $Free$ but has no
+more suitable free links (thus can’t forward the
+\texttt{SEGMENT\_REQUEST})$(f)$; the node
+is already \emph{Candidate} with another segment id, i.e. another find
+process.  In all these cases the node
+sends back a \texttt{SEGMENT\_CANCEL} along the incoming link (see at
+the bottom of Figure~\ref{fig:disr_events}).
+%Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
+%only if no more free links can be explored starting from them.
 \end{itemize}
 
-%\subsection{Intra-node vs Inter-node parallelism}
-%In the processes described above, we assumed that each node in the
-%READY\_SEARCHING state can start a find segment process by injecting a
-%\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when defining DiSR
-%should be made in order to decide whether or not the node must
-%actually perform this action. 
-%The point above is is strictly related to the general question: which
-%level of “parallelism” should we allow in DiSR ? The adopted approach
-%is that, although the nature of DiSR itself is intrinsicly parallel,
-%the use of parallelism makes things work in a more complex way. In
-%other words, DiSR is parallel when needed, but it does not exploit
-%parallelism as an “improving feature”. When not needed, things should
-%be serialized. For example: when a node is “ready searching” could
-%start several find segment process associated to the same segment, one
-%for each free link. But serializing this by investigating the free
-%links in order could be a simplest solution. We refer to this saying
-%that we avoid intra-node parallelism.  Note that while intra-node
-%parallelism can be avoided, trying to avoid inter-node parallelism
-%could be more complex than allowing the parallelism itself. Imagine
-%for example the effort of trying to coordinate nodes so that an unique
-%finding node process is actually running in the whole subnet. Thus, in
-%contrast to the intra-node parallelism, the inter-node parallelism is
-%a structural property of the DiSR algorithm and should not be avoided.
-%------------------------------------------------------------------------------
+% TODO: FIX and RE-enable in long paper
 
@@
 its current dynamic status (DBS) and the packets received.
-
-\begin{figure}
-  \centering
-    \includegraphics[width=0.30\textwidth]{pictures/state_machine.eps}
-  \caption{DiSR node execution model}
-  \label{fig:dna_tag}
-\end{figure}
 
@@
 %it’s receiving a a cancel request and has no more free links
+\subsection{Intra-node vs Inter-node parallelism}
+In the processes described above, we assumed that each node in the
+\emph{Assigned} status can start a find segment process by injecting a
+\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when
+defining \disr{} should be made in order to decide whether or not the
+node must actually perform this action.  The point above is is
+strictly related to the general question: which level of “parallelism”
+should we allow in \disr{} ? The adopted approach is that, although
+the nature of \disr{} itself is intrinsicly parallel, the use of
+parallelism makes things work in a more complex way. In other words,
+\disr{} is parallel when needed, but it does not exploit parallelism
+as an “improving feature”. When not needed, things should be
+serialized. For example: when a node is “ready searching” could start
+several find segment process associated to the same segment, one for
+each free link. But serializing this by investigating the free links
+in order could be a simplest solution. We refer to this saying that we
+avoid intra-node parallelism.  Note that while intra-node parallelism
+can be avoided, trying to avoid inter-node parallelism could be more
+complex than allowing the parallelism itself. Imagine for example the
+effort of trying to coordinate nodes so that an unique finding node
+process is actually running in the whole subnet. Thus, in contrast to
+the intra-node parallelism, the inter-node parallelism is a structural
+property of the \disr{} algorithm and should not be avoided.
+%------------------------------------------------------------------------------

### 2014-02-12 PAPER/introduction.tex
General text reorganization/fixes

@@
 
-\section{Related Works}
+\section{Related Works and Contribution}
 \label{sec:related_works}
@@
 
-In~\cite{mejia_ipdps06} authors present SR, an approach the solves these
+In~\cite{mejia_ipdps06} authors present an approach the solves these
 limitations by allowing turn restrictions to be placed locally,
 independently from other restrictions. The whole network is
-partitioned into segments, and each bidirectional turn
+partitioned into segments, and a bidirectional turn
 restriction can be freely chosen within a segment in order to guarantee
-deadlock freedom and connected networks. This \emph{locality
-independence} property, together with no requirement of any particular tree/root
+deadlock freedom while preserving network connectivity. This \emph{locality
+independence} property, avoiding the requirement of any particular tree/root
 choice, would make it the best choice for the given scenario;
-however, its topology independency still requires the knowledge of the
+however, it still requires the knowledge of the
 whole network graph in order to find the segments.
@@
 The \disr{} approach presented in this work is a first attempt of
-reaching the same goals of a segment based approach, that is
-establishing segments, without requiring any topology graph or
-centralized execution.
+reaching the same goals of a segment based turn prohibition  without
+requiring any topology graph or centralized execution.  In particular
+\disr{} aims to obtain a segment network partitioning using a
+completely different mechanism, based on a distributed exchange of
+small setup packets. The following main features distinguish \disr{}
+from classic approaches to segment partitioning: 
+\begin{itemize}
+\item No centralized entity is globally responsible and/or aware of
+what is going on, i.e. the status of the \disr{} execution is
+collectively distributed among the nodes
+\item  No defect map and/or topology graph is used as input,
+thus, the topology has to be discovered \emph{while} segments are
+created
+\item At the end of the execution, no segment list is created or
+stored anywhere: each node is only aware of belonging to some segment,
+ignoring the presence of other nodes in the same segment and even the
+presence of other segments in the network
+\end{itemize}

### 2014-02-12 PAPER/simulation.tex
General text reorganization/fixes

@@
 required in order to obtain statistically significant results.
-
-% TODO: long paper
-\subsection{Other Optimisations}
-Some optimisation parameters, which demostrated to improve the \disr{}
-results have been fixed to some good values, but are not subject to
-further investigation; once again the focus here is not the
-optimal set of segments, but just demostrating a working approach. 
-These are optimisations are:
-\begin{itemize}
-\item{cycle\_links}: max number of retries across the set of links of
-each node. While searching for a free link due an incoming request,
-the same request is cancelled after a given number of tries. This
-gives to preceding node change to test a different paths. Default is set to 1.
-\item{bootstrap\_timeout}: number of time units that a bootstrap node
-should wait before assuming that a livelock in the starting segment
-process has occurred. In the worst case, we can imagine that longest
-path required is the one returning to the bootstrap node after having
-travelled across all the links. So, althought this is just an extreme
-situation, a good upper limit can be safely be set to NxN.
-\item{bootstrap\_immunity}: in order to avoid the failure of the whole \disr{}
-setup process, a bootstrap node should not have defective links.
-Enabling this optimisation, a bootstrap node is immune to defects.
-We may think of a pre-bootstrap phase that properly selects (from upper
-layer via) a bootstrap node which is tested as properly connected. We
-enabled this optimisation, however empirical tests showed us that only
-simulations using bootstrap nodes placed on edges would be heavily
-affected, since these are nodes starting with a lower number of links,
-e.g. corner nodes could only have two connected direction, so even a
-defective link could prevent starting segment packet to return to
-bootstrap to close the loop a create the segment.
-\end{itemize}
 
@@
 \end{figure}
+
+% TODO: long paper
+\subsection{Other Optimisations}
+Some optimisation parameters, which demostrated to improve the \disr{}
+results have been fixed to some good values, but are not subject to
+further investigation; once again the focus here is not the
+optimal set of segments, but just demostrating a working approach. 
+These are optimisations are:
+\begin{itemize}
+\item \emph{cycle\_links}: max number of retries across the set of links of
+each node. While searching for a free link due an incoming request,
+the same request is cancelled after a given number of tries. This
+gives to preceding node change to test a different paths. Default is set to 1.
+\item \emph{bootstrap\_timeout}: number of time units that a bootstrap node
+should wait before assuming that a livelock in the starting segment
+process has occurred. In the worst case, we can imagine that longest
+path required is the one returning to the bootstrap node after having
+travelled across all the links. So, althought this is just an extreme
+situation, a good upper limit can be safely be set to NxN.
+\item \emph{bootstrap\_immunity}: in order to avoid the failure of the whole \disr{}
+setup process, a bootstrap node should not have defective links.
+Enabling this optimisation, a bootstrap node is immune to defects.
+We may think of a pre-bootstrap phase that properly selects (from upper
+layer via) a bootstrap node which is tested as properly connected. We
+enabled this optimisation, however empirical tests showed us that only
+simulations using bootstrap nodes placed on edges would be heavily
+affected, since these are nodes starting with a lower number of links,
+e.g. corner nodes could only have two connected direction, so even a
+defective link could prevent starting segment packet to return to
+bootstrap to close the loop a create the segment.
+\end{itemize}

### 2014-02-13 trunk/PAPER/implementation.tex
implementation update

@@
 (at the best that we know), we have synthesized the RTL description of DiSR
-with a standard 32nm CMOS library obtain 
+with a standard 32nm CMOS library obtaining 
 a delay of about $\mathrm{\tau_{DiSR}=10} FO4$ (fan-out of four).
@@
 last equation thedelay of one FO4 for the CNFET case is about of
-15 ps an then the working frequency can be cmputed as:
+15 ps an then the working frequency can be computed as:
 
@@
 Regards the power
-consumption of the entire DiSR devices, we can skip to perform an a
+consumption of the entire DiSR devices, we can skip to perform an accurate
+power analysis with the switch activity annotation because the DiSR circuitry
+will be active only once a time a the system startup. Indeed, after the setup
+phase when all segments are mapped in to the network, the DiSR block will stop
+its activity giving as output the fixed status of segments to the routing
+algorithm. For this reason the dynamic power will goingo to zero and the only
+cosumption will be eventually only due to the leackage consumption.

### 2014-02-14 PAPER/implementation.tex
Final implementation

@@
 
-A possible hardware implementation of the \disr{} algorithm will be
-described in this section.  Before enter in to detail of  \disr{}
+A possible hardware implementation of the DiSR algorithm will be
+described in this section.  Before to enter in to detail of  DiSR
 architecture,  an idea of node structure tailored for this particular
-scenario, can be found depicted in Fig.~\ref{fig:node_structure}. In
+scenario can be found depicted in Fig.~\ref{fig:node_structure}. In
 particular, such node should have the following foundamental elements:
@@
 	each port,  are responsible of data transmission between neighbours
-nodes. The packets received or sent are stored in specifieds buffers
+	nodes. The packets received or sent will be stored in specified buffers
 	named input and output buffers respectivelly.
@@
 	\item \textbf{Switch Matrix:} Driven by a switch controller, enables the
-reciprocal connections beetween the devices inside the node. Before
+	reciprocal connections beetween		 devices inside the node. Before
 	the creation of segments, such controller receives information from
-\disr{} block.  After this phase, the switch controller will be driven by
+	DiSR block.  After this phase, the switch controller will be driven by
 	the block wich implements the routing algorithm. The Switch matrix is
@@
 
-\item \textbf{\disr{}-Routing:} The \disr{} block contains all the hardware, control
+	\item \textbf{DiSR-Routing:} The DiSR block contains all the hardware, control
 	logic and configuration registers, related to the implementation of the
 	proposed approach. The routing algorithm receives information
-from \disr{}  wich indicates the status of the segments that interests a
+	from DiSR  wich indicates the status of the segments that interests a
 	particular node. The routing operation will take in account of these
 	informations in order to perform a deadlock-free routing. Both Routing
-and \disr{} are connected to the switch matrix in order to receive
+	and DiSR are connected to the switch matrix in order to receive
 	packets from the input buffer. Since the packets are processed one at
@@
 %--------------------------------------------------------------------
-\subsection{\disr{} Architecture}
+\subsection{DiSR Architecture}
 \label{ssec:disr_architecture}
@@
   \includegraphics[width=0.40\textwidth]{pictures/disr_rtl_updated.eps}
-  \caption{\emph{\disr{}} block architecture.}
+  \caption{\emph{DiSR} block architecture.}
  \label{fig:implementation}
@@
 
-To give a basic estimate of the overhead needed we will focus on \disr{}-
+To give a basic estimate of the overhead needed we will focus on DiSR-
 specific components, that is, the control logic and configuration
-registers needed to implement \disr{}. In Figure~\ref{fig:implementation}
+registers needed to implement DiSR. In Figure~\ref{fig:implementation}
 is shown a sketch of the  architecture, which mainly consist in the
@@
 	\item \textbf{DBS block:}
-	It takes trace of the DBS state machine, 
-	consisting of a 3-bit register (to cover six DBS values) and the 
-	required combinational logic. This block receives signals from 
-	stored packets  in order to decode the packet type, and from 
-	the control circuitry to change its status.
-	The bootstrap node is selected by setting the boot signal to high
-	during the initialization phase.
+
+	It takes trace of the DBS state machine,  consisting of a 3-bit
+	register (to cover six DBS values) and the  required combinational
+	logic. This block receives signals from  stored packets  in order
+	to decode the packet type, and from  the control circuitry to
+	change its status. The bootstrap node is selected by setting the
+	boot signal to high during the initialization phase.
 
@@
 	particular registernamed \emph{tflag} and \emph{busy}.  The Latter
-	is used to indicate if a specific port is alredy visited or tvisited and
-	the former indicates specifically if the node is visited or tvisited.
+	is used to indicate if a specific port is alredy visited or
+	tvisited while the former indicates specifically if the specific
+	port is alredy candidate or  assigned for a specific segment.
 
@@
 	signals. Then, the resulting \emph{Ctrl-Out} drives the other
-	communication resources for actuating the \disr{} routing operation.
+	communication resources for actuating the DiSR routing operation.
 
@@
 	content of the packet before the retransmission to   a destination
-	node.  In some cases, this circuitry build the packet from the
+	node.  In some cases, this circuitry builds the packet from the
 	scratch.  For example this happens when a node is bootsrap and for
-	the first time it should inject a
-	\emph{strating\_segment\_request}. In Fig.~\ref{fig:packager} is
-	shown the architecture of such packager block. When a packet is
-	created for the first time, the multiplexers driven by the
-	controller select the information coming from the internal node
-	such as the \emph{soruce\_ID}. In this situation the TTL field
-	should be resetted to its initial value and the \emph{segment\_ID}
+	the first time it should inject a \emph{strating\_segment\_request}. 
+	In Fig.~\ref{fig:packager} is shown the architecture of such packager 
+	block. When a packet is created for the first time, the multiplexers 
+	driven by the controller, will select the information incoming from the 
+	internal node such as the \emph{soruce\_ID}. In this situation the 
+	TTL field should be resetted to its initial value and the \emph{segment\_ID}
 	is composed by the node ID and by the output port identification 
@@
 
-While the elements mentioned above are part of the \disr{} circuitry, 
+While the elements mentioned above are part of the DiSR circuitry,
 the other devices depicted in Fig.~\ref{fig:implementation} like the
-multiplexer and demultiplexer are implemented outside \disr{}.
-In particular, such components will be within the switch matrix 
-(refers to the Fig~\ref{fig:node_structure}).
+multiplexer and demultiplexer are implemented outside DiSR. In
+particular, such components will be inside the switch matrix  (refers
+to the Fig~\ref{fig:node_structure}).
 
@@
   \includegraphics[width=0.40\textwidth]{pictures/pipeline.eps}
-  \caption{Pipeline description of \disr{} operations}
+  \caption{Pipeline description of DiSR operations}
  \label{fig:pipeline}
@@
 
-Each just described building block, reacts with the rising edge  of
-the\emph{clock signal}. An asynchronous system \emph{reset} signal is
-also present for restoring all registers to their default values. When
-this last signal is set, the DBS state machines for each network's
+Each of just described building block, reacts with the rising edge  of
+the \emph{clock signal}. An asynchronous system \emph{reset} signal is
+also present to restore all registers to their default values. When
+this signal is set, the DBS state machines for each network
 node are set as \emph{Free}.  
 In Fig.~\ref{fig:pipeline} is described the pipeline structure of the
-\disr{} architecture. The packet incoming from the neighbours node, or
+DiSR architecture. The packets incoming from the neighbours node, or
 locally generated will be send to the DBS state machine in order to te
-ensure the status commutation. While the DBS update its state,  in the
+ensure the status commutation. While the DBS updates its state,  in the
 next clock cycle the control circuitry will update the Led status and
-will drive the sitch matrix in order to send eventually the packets to
+will drive the switch matrix in order to send eventually the packets to
 the  right output buffer.
@@
 As discussed above, one of the main design challenge of DNA Self-
-Assembled systems is the limited resource available to implement both
+Assembled systems is the limited number of resources available to implement both
 computations and routing decisions for each node. Assuming a budget of
 $10^4$ CNFETs for each network's node~\cite{liu_jetcs}  we estimated
-the required resources for implementing the entire \disr{} block. The RTL
+the required resources to implement the entire DiSR block. The RTL
 description of the circuitry described in the last section (with an
-hardware description language)  of the \disr{} circuitry has been written
+hardware description language)  of the DiSR circuitry has been written
 and synthesized at gate-level using \emph{Synopsys Design Compiler} with 
@@
 full-adder, latch etc.), it has been possible to get a rough estimate
-of the number of transistors necessary to implement the \disr{} logic.
+of the number of transistors necessary to implement the DiSR logic.
 Figure~\ref{fig:synthesys} shows the results of synthesis in terms of
@@
   \caption{Number of network's node (N) vs number of CNFETs necassary to implement
-  the \disr{} circuitry.}
+  the DiSR circuitry.}
  \label{fig:synthesys}
@@
 absolute number of devices itself, it is interesting to observe that
-the circuitry complexity which implements the \disr{} algorithm increases
+the circuitry complexity which implements the DiSR algorithm increases
 with a slowly growing trend.   An intuitive explanation of this is the
-relatively simple logic of \disr{}, whose behaviour is almost code on
+relatively simple logic of DiSR, whose behaviour is almost code on
 scalable storage structures. For example, the number of registers
@@
 
-In order to have an idea of the maximum working clock frequency for the
-implemented circuitry, we can obtain the timing results from a gate-
+In order to have an idea of the maximum working clock frequency for
+the implemented circuitry, timing results can be obtained from a gate-
 level netlist. Since a complete technology library usefull for
-commercial synthesis tool (like Design Compiler) doesn't exist for the this particular technology
-(at the best that we know), we have synthesized the RTL description of \disr{}
-with a standard 32nm CMOS library obtain 
-a delay of about $\mathrm{\tau_{\disr{}}=10} FO4$ (fan-out of four).
-Considering the results obtained in~\cite{deng_isscc07}, wich reports the
-ratio in therms of FO4 between a standard 32nm CMOS technology and a
-carbon nanotube ones, we can have a rough delay estimation.
-In particolar has been reported a ratio R of: 
+commercial synthesis tool (like Design Compiler) doesn't exist for 
+this particular technology (at the best that we know), we have
+synthesized the RTL description of DiSR with a standard 32nm CMOS
+library obtaining  a delay of about $\mathrm{\tau_{DiSR}=10} FO4$
+(fan-out of four). Considering the results obtained
+in~\cite{deng_isscc07}, wich reports the ratio in therms of FO4
+between a standard 32nm CMOS technology and a carbon nanotube ones, 
+rough delay estimation can be obtained. In particolar has been reported a
+ratio R of:  
 \begin{equation}
@@
 \end{equation}
-Considering that F04 CMOS is about 30 ps, and the results of  
-last equation thedelay of one FO4 for the CNFET case is about of
-15 ps an then the working frequency can be cmputed as:
-
+Considering that F04 CMOS is about 30 ps, and the results of last
+equation, a FO4 for the CNFET case is equal to about 15 ps, and
+then the working frequency can be computed as:
 \begin{equation}
-\mathrm{f_{clk}=\frac{1}{T_{max}}=\frac{1}{\tau_{\disr{}} \cdot FO4_{CNFET}}}=
+\mathrm{f_{clk}=\frac{1}{T_{max}}=\frac{1}{\tau_{DiSR} \cdot FO4_{CNFET}}}=
 \frac{1}{10\cdot 15 \cdot 10^{-12}}=6,6 GHz
 \end{equation}
+where $\mathrm{\tau_{DiSR}}$ was expressed in therms of FO4.
 
-where $\mathrm{\tau_{\disr{}}}$ was expressed in therms of FO4.
-
-Regards the power
-consumption of the entire \disr{} devices, we can skip to perform an a
+Regards the power consumption of the entire DiSR devices, 
+an accurate power analysis with the switch activity
+annotation can be avoided because the DiSR circuitry will be active 
+only once at the system startup. Indeed, after the setup phase, when all segments
+are mapped in to the network, the DiSR block will stop its activity
+giving as output the fixed status of segments to the routing
+algorithm. For this reason the dynamic power will going  to zero and
+the only cosumption will be eventually only due to the leackage
+consumption.

### 2014-02-14 PAPER/implementation.tex
DiSR logo

@@
 
-A possible hardware implementation of the DiSR algorithm will be
-described in this section.  Before to enter in to detail of  DiSR
+A possible hardware implementation of the \disr{} algorithm will be
+described in this section.  Before to enter in to detail of  \disr{}
 architecture,  an idea of node structure tailored for this particular
@@
 	the creation of segments, such controller receives information from
-	DiSR block.  After this phase, the switch controller will be driven by
+	\disr{} block.  After this phase, the switch controller will be driven by
 	the block wich implements the routing algorithm. The Switch matrix is
@@
 
-	\item \textbf{DiSR-Routing:} The DiSR block contains all the hardware, control
+	\item \textbf{\disr{}-Routing:} The \disr{} block contains all the hardware, control
 	logic and configuration registers, related to the implementation of the
 	proposed approach. The routing algorithm receives information
-	from DiSR  wich indicates the status of the segments that interests a
+	from \disr{}  wich indicates the status of the segments that interests a
 	particular node. The routing operation will take in account of these
 	informations in order to perform a deadlock-free routing. Both Routing
-	and DiSR are connected to the switch matrix in order to receive
+	and \disr{} are connected to the switch matrix in order to receive
 	packets from the input buffer. Since the packets are processed one at
@@
 %--------------------------------------------------------------------
-\subsection{DiSR Architecture}
+\subsection{\disr{} Architecture}
 \label{ssec:disr_architecture}
@@
   \includegraphics[width=0.40\textwidth]{pictures/disr_rtl_updated.eps}
-  \caption{\emph{DiSR} block architecture.}
+  \caption{\emph{\disr{}} block architecture.}
  \label{fig:implementation}
@@
 
-To give a basic estimate of the overhead needed we will focus on DiSR-
+To give a basic estimate of the overhead needed we will focus on \disr{}-
 specific components, that is, the control logic and configuration
-registers needed to implement DiSR. In Figure~\ref{fig:implementation}
+registers needed to implement \disr{}. In Figure~\ref{fig:implementation}
 is shown a sketch of the  architecture, which mainly consist in the
@@
 	signals. Then, the resulting \emph{Ctrl-Out} drives the other
-	communication resources for actuating the DiSR routing operation.
+	communication resources for actuating the \disr{} routing operation.
 
@@
 
-While the elements mentioned above are part of the DiSR circuitry,
+While the elements mentioned above are part of the \disr{} circuitry,
 the other devices depicted in Fig.~\ref{fig:implementation} like the
-multiplexer and demultiplexer are implemented outside DiSR. In
+multiplexer and demultiplexer are implemented outside \disr{}. In
 particular, such components will be inside the switch matrix  (refers
@@
   \includegraphics[width=0.40\textwidth]{pictures/pipeline.eps}
-  \caption{Pipeline description of DiSR operations}
+  \caption{Pipeline description of \disr{} operations}
  \label{fig:pipeline}
@@
 In Fig.~\ref{fig:pipeline} is described the pipeline structure of the
-DiSR architecture. The packets incoming from the neighbours node, or
+\disr{} architecture. The packets incoming from the neighbours node, or
 locally generated will be send to the DBS state machine in order to te
@@
 $10^4$ CNFETs for each network's node~\cite{liu_jetcs}  we estimated
-the required resources to implement the entire DiSR block. The RTL
+the required resources to implement the entire \disr{} block. The RTL
 description of the circuitry described in the last section (with an
-hardware description language)  of the DiSR circuitry has been written
+hardware description language)  of the \disr{} circuitry has been written
 and synthesized at gate-level using \emph{Synopsys Design Compiler} with 
@@
 full-adder, latch etc.), it has been possible to get a rough estimate
-of the number of transistors necessary to implement the DiSR logic.
+of the number of transistors necessary to implement the \disr{} logic.
 Figure~\ref{fig:synthesys} shows the results of synthesis in terms of
@@
   \caption{Number of network's node (N) vs number of CNFETs necassary to implement
-  the DiSR circuitry.}
+  the \disr{} circuitry.}
  \label{fig:synthesys}
@@
 absolute number of devices itself, it is interesting to observe that
-the circuitry complexity which implements the DiSR algorithm increases
+the circuitry complexity which implements the \disr{} algorithm increases
 with a slowly growing trend.   An intuitive explanation of this is the
-relatively simple logic of DiSR, whose behaviour is almost code on
+relatively simple logic of \disr{}, whose behaviour is almost code on
 scalable storage structures. For example, the number of registers
@@
 this particular technology (at the best that we know), we have
-synthesized the RTL description of DiSR with a standard 32nm CMOS
-library obtaining  a delay of about $\mathrm{\tau_{DiSR}=10} FO4$
+synthesized the RTL description of \disr{} with a standard 32nm CMOS
+library obtaining  a delay of about $\mathrm{\tau_{\disr{}}=10} FO4$
 (fan-out of four). Considering the results obtained
@@
 \begin{equation}
-\mathrm{f_{clk}=\frac{1}{T_{max}}=\frac{1}{\tau_{DiSR} \cdot FO4_{CNFET}}}=
+\mathrm{f_{clk}=\frac{1}{T_{max}}=\frac{1}{\tau_{\disr{}} \cdot FO4_{CNFET}}}=
 \frac{1}{10\cdot 15 \cdot 10^{-12}}=6,6 GHz
 \end{equation}
-where $\mathrm{\tau_{DiSR}}$ was expressed in therms of FO4.
+where $\mathrm{\tau_{\disr{}}}$ was expressed in therms of FO4.
 
-Regards the power consumption of the entire DiSR devices, 
+Regards the power consumption of the entire \disr{} devices, 
 an accurate power analysis with the switch activity
-annotation can be avoided because the DiSR circuitry will be active 
+annotation can be avoided because the \disr{} circuitry will be active 
 only once at the system startup. Indeed, after the setup phase, when all segments
-are mapped in to the network, the DiSR block will stop its activity
+are mapped in to the network, the \disr{} block will stop its activity
 giving as output the fixed status of segments to the routing

### 2014-02-14 PAPER/implementation.tex
implementation new update

@@
   \includegraphics[width=0.40\textwidth]{pictures/packager.eps}
-  \caption{Packager block}
+  \caption{Packager block.}
  \label{fig:packager}
@@
   \includegraphics[width=0.40\textwidth]{pictures/pipeline.eps}
-  \caption{Pipeline description of \disr{} operations}
+  \caption{Pipeline description of \disr{} operations.}
  \label{fig:pipeline}
@@
   \includegraphics[width=0.50\textwidth]{pictures/synthesis.eps}
-  \caption{Number of network's node (N) vs number of CNFETs necassary to implement
+  \caption{Network size vs number of CNFETs necassary to implement
   the \disr{} circuitry.}
@@
 In order to have an idea of the maximum working clock frequency for
-the implemented circuitry, timing results can be obtained from a gate-
-level netlist. Since a complete technology library usefull for
+the implemented circuitry, timing results can be obtained from a 
+gate-level netlist. Since a complete technology library usefull for
 commercial synthesis tool (like Design Compiler) doesn't exist for 
 this particular technology (at the best that we know), we have
-synthesized the RTL description of \disr{} with a standard 32nm CMOS
-library obtaining  a delay of about $\mathrm{\tau_{\disr{}}=10} FO4$
+synthesized the RTL description of \disr{} with a standard 32 nm CMOS
+library obtaining  a delay of about $\mathrm{\tau_{\disr{}}=10} \ FO4$
 (fan-out of four). Considering the results obtained
 in~\cite{deng_isscc07}, wich reports the ratio in therms of FO4
-between a standard 32nm CMOS technology and a carbon nanotube ones, 
-rough delay estimation can be obtained. In particolar has been reported a
-ratio R of:  
+between a standard 32 nm CMOS technology and a carbon nanotube ones, 
+rough delay estimation can be obtained. In particolar in such work 
+has been reported a ratio of:  
 \begin{equation}
-\mathrm{R=\frac{FO4_{CMOS}}{FO4_{CNFET}}=2}  
+\mathrm{\frac{FO4_{CMOS}}{FO4_{CNFET}}=2}  
 \end{equation}

### 2014-02-14 trunk/PAPER/disr.tex
monteleone's fixes
DiSR sequence pics and dbs
Misc fixes

@@
 %------------------------------------------------------------------------------
-\section{Preliminary concepts}
+\section{\disr{} Overview}
 %------------------------------------------------------------------------------
+
 \label{sec:disr_concepts}
+The main concept behind the kind of turn prohibition we want to
+achieve is the \emph{segment}. A segment $S_y$ is basically a path of consecutive
+nodes and links, starting with a link attached to a node belonging to
+a different segment $S_x$ and ending with a link attached to a
+node of another segment $S_z$. In other words, a segment
+a path between connecting two other different segments. The example
+in Figure~\ref{fig:segments} shows the segment with id $1.4$, starting
+with a link connected to the node $9$, the going trought nodes
+$4$,$3$,$2$ and ending with the link connected to the node $1$. Other
+segments depicted are $9.2$ (link,node $10$,link) and $9.3$
+(link from $9$ ,$8$,link,$7$,link,$6$,link,$5$,link to the $1$). Note
+also that start/ending link can coincide and a segment can also be
+formed by one single link (e.g. in $7.2$ or $5.4$).
+An exception to the rule that a segment must connect two other
+segments is the first segment established in the network, called
+\emph{starting segment} which is a loop beginning/ending on the same
+node.
 
-\subsection{Basic Idea}
-The main concept behind the kind of turn prohibition we want to
-achieve is the \emph{Segment}: it is basically a path of consecutive
-nodes and links. A segment $S_1$ starts with a link attached to a node which
-belongs to different segment $S_2$, ending with a link attached to a
-node belonging to a different segment $S_3$. In other words, a segment
-a path between connecting two other different segments.A exception is
-the first segment established in the network, called \emph{starting
-segment} which is  a loop beginning/ending on a particular node
-defined as \emph{bootstrap node}.
-The idea is to partition the network in a set of disjoint segments, and then
-placing a turn restriction within each segment. It has been proved~\cite{mejia_ipdps06}
-that such a set of turn prohibitions guarantees deadlock freedom and
-while preserving connectivity of the network.
+\begin{figure}
+\centering
+    \includegraphics[width=0.25\textwidth]{pictures/network_slice.eps}
+  \caption{Example of Segments}
+  \label{fig:segments}
+\end{figure}
 
-Describing the execution phases of DiSR from a top level point-of-view
-is basically similar to the classic SR approach. This can be useful to
-give an initial idea of the approach, however, some essential
-differences should be pointed out. First of all no centralized entity is
-globally aware of what is going on: the status of the DiSR execution
-is collectively distributed among the nodes; second, no defect map and/or
-topology graph is available as input, thus, the topology has to be
-discovered \emph{while} segments are created; finally, at the end of the
-execution, no segment list is created: Each node is only aware of
-belonging to some segment, ignoring the presence of other nodes
-in the same segment and even the presence of other segments in the
-network.
+A detailed description of the \disr{} execution model as depicted in
+the Figure~\ref{fig:disr_events} will be discussed in
+Subsection~\ref{sub:phases}. Roughly speaking, the execution of can be described as the execution
+of the following phases: 
+\begin{enumerate}
+\item Injection of the \disr{} process from an upper layer to set a \emph{bootstrap
+node} 
+\item Broadcasting and confirmation to create the first segment of the subnet
+\item Parallel requests starting from assigned node to discover other
+segments. 
+\item Turn proibition in each confirmed segment.
+\item Draining of remaining packet due timeouts
+\end{enumerate}
 
-Roughly speaking, the execution of can be described as the execution
-of the following phases: (1) Injection of the DiSR process from upper layer to set a bootstrap
-node (2) Bootstrap node broadcasting to create the first segment of the subnet
-(3) Parallel requests starting from assigned node to discover other
-segments. The following subsection describe the data structure and
-execution model required at each node. (4) Turn proibition in each
-confirmed segment.
-%\item Draining of remaining packet due timeouts
+\section{Detailed Description of \disr{}}
+\subsection{Message Types Required}
 
-%Once again, it should be pointed out that nowhere in the network there
-%is such a global vision of these exection phases. A more detailed
-%description of the exection model at each node is discussed in the
-%next section.
-
-\subsection{Signal Types Required}
-
-The DiSR approach works with a distributed mechanism which is build
+The \disr{} approach works with a distributed mechanism which is build
 upon an exchange of small packets containing the following fields:
 \begin{itemize}
-\item{packet\_type}: encodes the meaning of the control message respect
-to the whole DiSR process.
-\item{seg\_ID}: the id of the segment associated to the DiSR control message
-\item{src\_id}: the id of the node that initially originated the
-packet
+\item \emph{packet\_type}: encodes the meaning of the control message
+\item \emph{seg\_ID}: the id of the segment associated to the \disr{} control message
+\item \emph{src\_id}: the id of the node that originated the packet
 \end{itemize}
 
-As regards packet\_type, we can have the following control packets:
+As regards \emph{packet\_type} field, we can have the following control packets:
 \begin{itemize}
@@
 
-The \emph{LED} is like a snapshot of the DiSR algorithm at each node,
+The \emph{LED} is like a snapshot of the \disr{} algorithm at each node,
 consisting in the following variables:
@@
 \begin{itemize}
-\item{\emph{Free}}: a node that has  not been yet considered  by the DiSR algorithm.
-The node is not marked as \emph{visited}/\emph{tvisited}.
+\item{\emph{Free}}: a node that has  not been yet considered  by the \disr{} algorithm.
 \item{\emph{Bootstrap}}: a node which has been explicitly set as bootstrap node from
 an upper layer via. 
-% TODO: this and all the other details on the items below should be
-% checked and moved elsewhere for a future long paper
-%This is required because a
-%\texttt{STARTING\_SEGMENT\_REQUEST} packet should be injected in order to start
-%the whole process.
 \item{\emph{ActiveSearching}}: a node from which a find process of new segments has
@@
 
-\subsection{DiSR Execution Model}
+A quantitative analysis of the resources needed to implement these
+fields is presented in Section~\ref{sec:implementation} when
+discussing the impact of the \disr{} control logic and storage on
+hardware implementation of the node.
 
-In Figure~\ref{fig:state_machine} are depicted the main events
-representing the execution model at each node. The DiSR control
-packets described in the previous subsection trigger node events,
-which eventually change $DBS$ status according to the current value of
-$LED$ variables and the type of the packet received. The main DiSR
-phases, together with a reference to the particular status transition
-shown in Figure~\ref{fig:state_machine} are described in the
-following.
+\subsection{Execution Model}
+\label{sub:phases}
+
+The \disr{} control packets described in the previous subsection trigger
+node events, which eventually change $DBS$ status according to the
+current value of $LED$ variables and the type of the packet received.
+The main \disr{} phases, together with a reference to the particular
+status transition involved are described in the following. As a
+convention, we used single letters to refer to one of the \emph{DBS} transitions in
+Figure~\ref{fig:state_machine} while the phases are visually
+represented in~\ref{fig:disr_events}.
 
@@
   \centering
-    \includegraphics[width=0.40\textwidth]{pictures/state_machine.eps}
-  \caption{DiSR node execution model}
+    \includegraphics[width=0.25\textwidth]{pictures/dbs_updated.eps}
+  \caption{\disr{} node execution model}
   \label{fig:state_machine}
 \end{figure}
+
+\begin{figure*}
+\centering
+\begin{tabular}{cccc}
+\includegraphics[width=0.23\textwidth]{pictures/seq01.eps} & 
+\includegraphics[width=0.23\textwidth]{pictures/seq02.eps} &
+\includegraphics[width=0.23\textwidth]{pictures/seq03.eps} & 
+\includegraphics[width=0.23\textwidth]{pictures/seq04.eps} \\
+(a) & (b) & (c) & (d) \\
+\includegraphics[width=0.23\textwidth]{pictures/seq05.eps} &
+\includegraphics[width=0.23\textwidth]{pictures/seq06.eps} &
+\includegraphics[width=0.23\textwidth]{pictures/seq07.eps} & 
+\includegraphics[width=0.23\textwidth]{pictures/seq08.eps} \\
+(e) & (f) & (g) & (h) \\
+\end{tabular}
+\caption{Example of \disr{} segment setup: Nodes status are labeled as CandidateStarting($Cs$), Candidate ($C$), Free ($F$), Assigned ($A$) and Boostrap ($B$)}
+\label{fig:disr_events}
+\end{figure*}
+
 \begin{itemize}
+\item{\textbf{Injecting bootstrap request}}: all nodes have an initial
+\emph{DBS} status set to \emph{Free}, except for a
+ node with status \emph{Bootstrap}, set by some control signal from an
+upper layer via $(a)$. When starting, this bootstrap node 
+changes its status to \emph{CandidateStarting} $(b)$, injecting a
+\texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links
+(Figure~\ref{fig:disr_events}-a).
 
-\item{\textbf{Injecting bootstrap request}}: all nodes have an initial
-\emph{DBS} status \emph{Free}, except for a
- node with status \emph{Bootstrap}, set by some signal from an
-upper layer via (a). When starting, this bootstrap node 
-changes its status to \emph{ActiveSearching} (b), injecting a
-\texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links.
-
-\item{\textbf{Flooding}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
-when $Free$ forwards it to its free links using a flooding mechanism and
-becoming $CandidateStarting$ (g).
+\item{\textbf{Bootnode Broadcasting}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
+when $Free$, forwards it to its free links using a flooding mechanism and
+becoming $CandidateStarting$ $(g)$.
 Each of its free links is then marked as \emph{tvisited} with the segment id
@@
 
-\item{\textbf{Confirming the Starting Segment}}: when the \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
+\item{\textbf{Confirming the Starting Segment}}: when a \texttt{STARTING\_SEGMENT\_REQUEST} packet reaches
 the bootstrap node (from a different link, of course), the starting
@@
 packet along the link from which it received the
-\texttt{STARTING\_SEGMENT\_REQUEST} and becomes $Assigned$ (c). Each
+\texttt{STARTING\_SEGMENT\_REQUEST} and becomes $Assigned$ $(l)$. Each
 node receiving the confirm do same by changing its own status
-to \emph{Assigned} (l). So the confirmation packet is sent back from
-node to node and the starting segment is created.
-
-Note: A node being \emph{CandidateStarting}, when receiving a simple
-(not starting) \texttt{SEGMENT\_REQUEST} , can simply cancel its
-previous \emph{CandidateStarting} status and set itself as
-$Candidate$ for that request (h), since this new
-request means that the starting segment has already been found.
+to \emph{Assigned}(Figure~\ref{fig:disr_events}-c). So the confirmation packet is sent back from
+node to node and the starting segment is created (Figure~\ref{fig:disr_events}-d).
 
@@
 
-\item{\textbf{Injecting other requests}}: Each node in the
+\item{\textbf{Injecting Segment Requests}}: Each node in the
 \emph{Assigned} status can initiate a search for a segment, by sending
-a \texttt{SEGMENT\_REQUEST} across one of its free links (d). Note
-that since this is not the starting segment in this case the packet
-should not reach the initiator, but just another \emph{Assigned} node.
-
-\item{\textbf{Setup of a segment}}: The find process is successful
+a \texttt{SEGMENT\_REQUEST} across one of its free links $(c)$ (see
+Figure~\ref{fig:disr_events}-e). 
+Note that each \emph{Assigned} note can inject the request just after
+becoming assigned, i.e. it is not needed that the whole confirmation
+process in completed (Figure~\ref{disr_events}-f).
+Note also that nodes previosly set as \emph{CandidateStarting}, when receiving 
+a \texttt{SEGMENT\_REQUEST} can simply cancel their
+status and set as $Candidate$ for that request, since this new
+request means that the first starting segment has already been found $(h)$. 
+\item{\textbf{Segment Confirmation}}: The find process is successful
 when an already \emph{Assigned} node receives the
 \texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
-sent back along the path that originated the request (e), while the
+sent back along the path that originated the request
+(Figure~\ref{fig:disr_events}-g), while the
 node remain $Assigned$ (since it could confirm more segments). Each node
 previously set as $Candidate$ for that segment id, when receiving the
-confirm packet changes its status to $Assigned$ (m) and forwards back
-the same confirm until it reaches the initiator of the request, which
-changes from $ActiveSearching$ to $Assigned$ (c).
+a confirmation packet changes its status to $Assigned$ $(m)$ and forwards back
+the same confirmation until it reaches the initiator of the request,
+which then changes from $ActiveSearching$ to $Assigned$ $(d)$.
 
-\item{\textbf{Failing while searching a segment}}: a node received a \texttt{SEGMENT\_REQUEST} packet but
-matched one of two the following conditions: the node is $Free$ but has no
+\item{\textbf{Failing while searching a segment}}: this happen when a node received a \texttt{SEGMENT\_REQUEST} packet but
+matches one of two the following conditions: first, the node is $Free$ but has no
 more suitable free links (thus can’t forward the
-\texttt{SEGMENT\_REQUEST})(f); the node
-is candidate for another find process(i).  In all these cases the node
-sends back a \texttt{SEGMENT\_CANCEL} along the proper link. 
+\texttt{SEGMENT\_REQUEST})$(f)$; the node
+is already \emph{Candidate} with another segment id, i.e. another find
+process.  In all these cases the node
+sends back a \texttt{SEGMENT\_CANCEL} along the incoming link (see at
+the bottom of Figure~\ref{fig:disr_events}).
 %Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
@@
 \end{itemize}
-
-\subsection{Intra-node vs Inter-node parallelism}
-In the processes described above, we assumed that each node in the
-READY\_SEARCHING state can start a find segment process by injecting a
-\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when defining DiSR
-should be made in order to decide whether or not the node must
-actually perform this action. 
-The point above is is strictly related to the general question: which
-level of “parallelism” should we allow in DiSR ? The adopted approach
-is that, although the nature of DiSR itself is intrinsicly parallel,
-the use of parallelism makes things work in a more complex way. In
-other words, DiSR is parallel when needed, but it does not exploit
-parallelism as an “improving feature”. When not needed, things should
-be serialized. For example: when a node is “ready searching” could
-start several find segment process associated to the same segment, one
-for each free link. But serializing this by investigating the free
-links in order could be a simplest solution. We refer to this saying
-that we avoid intra-node parallelism.  Note that while intra-node
-parallelism can be avoided, trying to avoid inter-node parallelism
-could be more complex than allowing the parallelism itself. Imagine
-for example the effort of trying to coordinate nodes so that an unique
-finding node process is actually running in the whole subnet. Thus, in
-contrast to the intra-node parallelism, the inter-node parallelism is
-a structural property of the DiSR algorithm and should not be avoided.
-%------------------------------------------------------------------------------
 

### 2014-02-14 trunk/PAPER/disr.tex
Rearranged, fixed

@@
 
-\section{Detailed Description of \disr{}}
+\subsection{\disr{} Data Structures}
+\label{ssec:disr_data}
+
+We distinct between two different kind of data stored at each node:
+\emph{Dynamic Behaviour Status} (\emph{DBS}) and \emph{Local
+Environment Data} (\emph{LED}).
+
+The \emph{DBS} stores information in order to capture the dynamic
+behaviour of the node  in the context of the whole
+\disr{} execution phased. The \emph{DBS} can have the following values:
+
+\begin{itemize}
+\item{\emph{Free}}: a node that has  not been yet considered  by the \disr{} algorithm.
+\item{\emph{Bootstrap}}: a node which has been explicitly set as bootstrap node from
+an upper layer via. 
+\item{\emph{ActiveSearching}}: a node from which a find process of new segments has
+been started and not yet cancelled or confirmed. 
+\item{\emph{Candidate}}: a node currently candidate for belonging to some segment
+, but not being itself the node from which the find process was started. 
+\item{\emph{CandidateStarting}}: same as above, but the node is currently being considered as candidate
+for starting segment. 
+\item{\emph{Assigned}}: a node for which the segment has been determined.  
+\end{itemize}
+
+The \emph{LED} are like a instanst snapshot of the \disr{} algorithm at each node,
+consisting in the following variables:
+\begin{itemize}
+\item{\emph{segID}}:a value used to specify the segment to which the
+node has been assigned or is candidate for being assigned.
+\item{\emph{visited}}: a boolean value. When \emph{true}
+then a \emph{segID} different from \texttt{NULL} specifies the segment 
+to which the node has been assigned. 
+\item{\emph{tvisited}}: a boolean value. If \emph{true}, the node is
+being considered as candidate for a segment, and the \emph{segID} value
+specifies the segment id for which the node is candidate. 
+\item{\emph{link\_visited[]}}: an array
+of values representing information about attached links, that is, the
+segID of the segment owning each link. When \texttt{NULL}, the corresponding link has not yet been
+assigned.
+\item{\emph{link\_tvisited[]}}: an array of
+values representing information about attached links, that is, the \emph{segID} of
+the segment for which the link is candidate. When \texttt{NULL}, the link is
+not candidate for any segment, i.e. maybe already assigned
+or free.
+\end{itemize}
+
 \subsection{Message Types Required}
@@
 
-\subsection{\disr{} Data Structures}
-\label{ssec:disr_dstruct}
-
-We distinct between two different kind of data stored at each node:
-\emph{Local Environment Data} (\emph{LED}) and \emph{Dynamic Behaviour
-Status} (\emph{DBS}).
-
-The \emph{LED} is like a snapshot of the \disr{} algorithm at each node,
-consisting in the following variables:
-\begin{itemize}
-\item{\emph{segID}}:a value used to specify the segment to which the
-node has been assigned or is candidate for being assigned.
-\item{\emph{visited}}: a boolean value. When \emph{true}
-a \emph{segID} different from \texttt{NULL} specifies the segment 
-to which the node has been assigned. 
-% TODO: the following is true, but complicates things at this stage
-%Note that a value different from \emph{NULL} does not
-%necessarily mean the node has been assigned to some segment (e.g. when
-%searching starting segment is set \emph{visited} by default even if not yet
-%assigned to any segment). 
-\item{\emph{tvisited}}: a boolean value. If \emph{true}, the node is
-being considered as candidate for a segment, and the \emph{segID} value
-specifies the segment id for which the node is candidate. 
-\item{\emph{link\_visited[]}}: an array
-of values representing information about attached links, that is, the
-segID of the segment owning each link. When \texttt{NULL}, the corresponding link has not yet been
-assigned.
-%TDB: do we need to introduce some value for the
-%“bridge” status ? (e.g. a node connecting the terminal node of a
-%subnet with the starting one of another) 
-\item{\emph{link\_tvisited[]}}: an array of
-values representing information about attached links, that is, the \emph{segID} of
-the segment for which the link is candidate. When \texttt{NULL}, the link is
-currently not \emph{tvisited}.  
-\end{itemize}
-%\item{\emph{starting}}: boolean, \emph{true} if the node is a
-%starting node from which the whole process was initiated.
-%\end{itemize}
-
-In addition to the \emph{LED} variables described above, further
-information should be stored in order to capture the current dynamic
-behaviour of the node. This is represented by \emph{DBS} variable,
-which strictly depends on the \emph{LED} data and the events occurring
-at the node. The \emph{DBS} can have the following values:
-
-\begin{itemize}
-\item{\emph{Free}}: a node that has  not been yet considered  by the \disr{} algorithm.
-\item{\emph{Bootstrap}}: a node which has been explicitly set as bootstrap node from
-an upper layer via. 
-\item{\emph{ActiveSearching}}: a node from which a find process of new segments has
-been started and not yet cancelled or confirmed. 
-%This happens when all
-%the following conditions are matched: the node is marked as \emph{visited},
-%that is \emph{visited} = TRUE 
-%TODO: \emph{segID} is set to some value reflecting
-%the segment request sent there is a link that is being investigated by
-%the node, that is a tvisited\_link marked with the same id of the node 
-\item{\emph{Candidate}}: a node currently candidate for belonging to some segment
-, but not being itself the node from which the find process was started.
-
-%The following conditions should be matched: \emph{tvisited} =
-%true, with segID=X different from node's id.  Two links set as
-%\emph{link\_tvisited} with id X. Let’s refer them as  links 'i' and 'j'. Then
-%link\_tvisited[i] was set = X when the find process from an adjacent
-%node reached the current node, while link\_tvisited[j] has been set to
-%X when the node itself started to investigate its free links for the
-%segment request with id X. Note that while investigating its attached
-%links, if the find process fails along path 'j', the current node can
-%investigate another free node 'k' if suitable.  
-\item{\emph{CandidateStarting}}: same as above, but the node is currently being considered as candidate
-for starting segment. 
-%Two main differences: Can confirm
-%\texttt{STARTING\_SEGMENT\_CONFIRM} with the same \emph{segID} when receiving a normal
-%\texttt{SEGMENT\_REQUEST}: Overwrites its status setting it to \emph{Candidate} for the
-%segID frees the links previously set as \emph{tvisited} during flooding
-\item{\emph{Assigned}}: a node for which the segment has been determined.  
-%The \emph{visited} value is \emph{true} NOTE: an \emph{Assigned} state is a quick temporary
-%state, since it becomes \emph{ActiveSearching} if a not (\emph{visited}/tvisited)
-%link is suitable for searching new segments (see next\_visited
-%procedure on paper) 
-\end{itemize}
-
-A quantitative analysis of the resources needed to implement these
-fields is presented in Section~\ref{sec:implementation} when
+A quantitative analysis of the resources needed to implement and
+manage these structures is presented in Section~\ref{sec:implementation} when
 discussing the impact of the \disr{} control logic and storage on
@@
 the bottom of Figure~\ref{fig:disr_events}).
-%Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
-%only if no more free links can be explored starting from them.
 \end{itemize}
-
-% TODO: FIX and RE-enable in long paper
 
@@
 
-The \emph{LED} variables at each node are are initially set so the node and
-each of its links is set as free. The only node that makes exception
-is the bootstrap node, initialized in the \emph{Bootstrap} status. All
-the subsequent events happening at each node are the consequence of
-its current dynamic status (DBS) and the packets received.
+In this Section we provide further details about \disr{}
+execution model, describing the internal behavior implemented at
+each node. Note that this also corresponds exactly to what should be
+implemented from the node-hardware perspective, as discussed in
+Section~\ref{sec:implementation}.
 
-%TODO: add state machines
-
-% TODO: fix, move elsewhere or delete
-%Assumption: when discussing of visited/\emph{tvisited} nodes, we are assuming
-%with an id corresponding to the same subnet. Nodes involved in other
-%subnet processes can simply ignore these packets. (TBD: formalize more
-%clearly in which cases inter-subnet packets must be ignored, probably
-%this happens most of the times, but in some cases, e.g. when a
-%terminal node is found, some kind of communication packets are needed
-%in order to crearte the bridge between two subnets.)
+The \emph{LED} variables at each node
+($segID$,$visited$,$tvisited$,\emph{link\_visited[]},\emph{link\_tvisited[]})
+are initially set as \texttt{NULL}, so the node and each of its links
+are considered as free.
+The only node that makes exception is the bootstrap node, initialized
+in the \emph{Bootstrap} status. All the subsequent events happening at
+each node are the consequence of its current dynamic status (DBS), the
+packets received and the internal status represented by the
+\emph{LED}. Note that in the following, when using expression like
+``has a free link'' or ``free node'' we will assume the relationship beetween 
+$LED$ and $DBS$ discussed in Section~\ref{sec:disr_data}. Further, for
+each packet type all the cases not explicitly listed can simply be
+ignored since are associated to invalid/inconsistent events of the
+\disr{} execution model. A complete list of these cases can be checked
+in the environment simulator source code at~\ref{nanoxim}.
 
@@
 The request for the first segment should be managed differently since
-all nodes (except the starting one) must forward the packet using a
-flooding mechanism. This is necessary since the request packet must
+all nodes (except the bootstrap one) must forward the packet using a
+broadcasting mechanism. This is necessary since the request packet must
 return the bootstrap node.
@@
 \begin{itemize}
-\item The node is not candidate or assigned: it should set itself as
-\emph{Candidate} and forward the packet along its free links, using
-flooding.  
-\item The node is \emph{Candidate} with the same
-\emph{segID} and \emph{src\_id} is equal to node id: this means the
-node was the initiator of the request, so a starting segment was found and
-should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
+\item The node is $Free$: it should set itself as
+\emph{CandidateStarting} and forward the packet along its free links, using
+broadcasting and marking these links as $tvisited$ with $segID$ found
+in the packet.
+\item The node is \emph{CandidateStarting} with the same
+\emph{segID} and \emph{src\_id} of the packet is equal to node id:
+this means that the node was the initiator of the request, thus a starting segment has
+just been found and should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
 packet.  
-\item The node is \emph{Candidate}, with the same \emph{segID} of the
-packet but \emph{src\_id} is different from node id: due
-the flooding mechanism, another starting segment packet reached a node
-which was previously marked as \emph{Candidate} from the same starting segment
-search process. Since the node is candidate with the same id, it means
-that it already accomplished in the task of propagating that kind
+\item The node is \emph{CandidateStarting}, with the same \emph{segID} of the
+packet but the \emph{src\_id} field is different from node id: since the node is candidate with the same id, it means
+that it already accomplished the task of propagating that kind of
 packets, thus can simply ignore the event thrashing the packet.  
-%TBD: how the status should be changed ? depend on the flooding mechanism. Note
-%that these links do not include the link from which the request was
-%received.  
 \item The node is \emph{Candidate}, with a different \emph{segID}: 
-this simply means that the starting segment received is deprecated,
-because the node has already accepted non-starting segment requests
-originated from other \emph{Assigned} nodes.
+this simply means that the starting segment request just received is deprecated,
+because the node has already accepted a non-starting segment request
+that originated from another \emph{Assigned} nodes.
 \item The node is \emph{Assigned}, with a different \emph{segID}:
@@
 \begin{itemize}
-\item The node is \emph{Assigned}: a segment was
-found and it should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
-packet.  
+\item The node is \emph{Assigned}: a segment should be confirmed
+sending back a \texttt{SEGMENT\_CONFIRM} packet.
 \item The node is \emph{Candidate}: it should discard the packet sending
 back a \texttt{SEGMENT\_CANCEL} 
-\item The node is not \emph{Assigned} or \emph{Candidate} and has free
+\item The node is \emph{Free} and has free
 links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
-to one of its free links, according to some internal ordering
+to one of its free links, according to some internal ordering.
+\item The node is \emph{CandidateStarting}: same as being $Free$,
+since a segment request circulating in the network indicates that the
+starting segment process has been completed.
 \end{itemize}
 
-NOTE: the main difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
+Note that the main difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
 and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
-itself is included in the segment , while in the second case the
-receiving node does not belong to the segment found.
+itself is included in the segment.
 
@@
 \subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
-When received, if the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
-the packet, the node learns to belong to the segment associated to the
-id. Further, it should forward this packet to the link where the
+When the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
+the packet: the node set itself as $Assigned$ to the segment $SegID$. Further, it should forward this packet to the link where the
 original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
 can learn the segment id they belong to. \emph{LED} shoud be
-updated from \emph{tvisited} to \emph{visited}.  the
-\emph{link\_tvisited} previously set with the \emph{segID} should be invalidated the
-\emph{link\_visited} variable associated to the incoming confirm should be set
-as segID. Note that if the request was flooded across different links,
-the \emph{link\_visited} variable associated to the other paths should not be
-set.  the \emph{link\_visited} variable associated to the link from which the
-request was originated should be set segID
+updated from \emph{tvisited} to \emph{visited}.
 
 \subsection{Receiving a \texttt{SEGMENT\_CANCEL}}
-When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that searching
-for a segment along that path was unsuccessful. But if the node still
-has other free links to try, it should forward a \texttt{SEGMENT\_REQUEST} to
-the next link (next according to some internal ordering). So a node
-forwards back the \texttt{SEGMENT\_CANCEL} packet along the link that originated
-the \texttt{SEGMENT\_REQUEST} packet only when there are no more free links to
-try. If this is the case, the node modifies its status from
-\emph{Candidate} to \emph{Free} and forwards the \texttt{SEGMENT\_CANCEL} packet to the link from which
-the request was received. The process stops when the \texttt{SEGMENT\_CANCEL}
-packet reach the starting node that originated the request.
+When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that
+searching for a segment along that path was unsuccessful. But if the
+node still has some other free link to try, it should forward a
+\texttt{SEGMENT\_REQUEST} to the that link. So a node forwards back
+the \texttt{SEGMENT\_CANCEL} packet along the link that originated the
+\texttt{SEGMENT\_REQUEST} packet $only$ when there are no more free
+links to try. If this is the case, the node modifies its status from
+\emph{Candidate} to \emph{Free} and forwards the
+\texttt{SEGMENT\_CANCEL} packet to the link from which the request was
+received. The process stops when the \texttt{SEGMENT\_CANCEL} packet
+reach the starting node that originated the request.
 
-%TODO REPEAT!!
-%When a node discovers that the path that includes
-%the node itself is no more suitable, a \texttt{SEGMENT\_CANCEL} is sent back
-%across the link from which the \texttt{SEGMENT\_REQUEST} was received.  Possible
-%reasons for that: The node it’s already candidate for another segment
-%The node it’s free but can’t find a free link (according the
-%cyclelinks timeout) The node it’s \emph{tvisited} for the same request id,
-%previously forwarded that request along some free direction, but now
-%it’s receiving a a cancel request and has no more free links
 \subsection{Intra-node vs Inter-node parallelism}

### 2014-02-14 PAPER/introduction.tex
Fixes

@@
 more and more revelance as the scaling trend of such devices keeps
-introducing new challenges. Power density, defect tolerance, testing
+introducing new challenges: power density, defect tolerance, testing
 costs and wire delays are only a few of the many critical aspects
-involved~\cite{itrs12}. While software parallelism and multicore
+involved~\cite{itrs13}. 
+While software parallelism and multicore
 approaches~\cite{horowitz2004, powell2009} are partially mitigating the impact of such
@@
 only where its own DNA tag matches a complementary tag on the DNA grid
-scaffold.
+scaffold (see Figure~\ref{fig:nana}-a).
 A detailed description of the chemical properties involved is far
@@
  \end{tabular}
-  \caption{DNA tag matching and Resulting Irregualr Topology}
+  \caption{(a) DNA tag matching and (b) resulting trregualr topology}
   \label{fig:nana}
@@
 implications to be addressed when approaching to the design of
-computer architecture: a computational model should be based on a
-distributed network of small computing and storage nodes, randomly
-placed and interconnected (see Figure~\ref{fig:nana}).
-Proof-of-concept of such kind of computational model can be found for
-example in~\cite{patwardhan2006_1}.  Since no regularity can be
-assumed in such network, a topology agnostic strategy that avoids
-deadlock should be adopted in order to route packets (e.g.
-instructions and data operands) among nodes.  It is important to
-underline that, altougth we can assume an architecture similar to the
-one depicted in Figure~\ref{fig:nana} as background, the topology discovery
-problem faced in this work is more general and not strictly dependent on any of the
-underlying computing architecture.
+a computer architecture: computational model should be based on a
+distributed network of small processing and storage nodes, randomly
+placed and interconnected (see Figure~\ref{fig:nana}-b).
+Proof-of-concept of such architectures can be found for
+example in~\cite{patwardhan2006_1}, where instruction and data
+operands are move around the network in order to be processed.
+Indepentedly from the particular policy chosen for routing packets,
+such networks must be able to guarantee deadlock freedom without any
+prior assumption on topology.
 
@@
 fit into such complex, irregular and large sized networks.
+It is important to
+underline that, altougth we can assume an architecture similar to the
+one depicted in Figure~\ref{fig:nana} as background, the topology discovery
+problem faced in this work is more general and not strictly dependent on any of the
+underlying computing architecture.
 
@@
 
-\section{Related Works and Contribution}
+\section{Background and Contribution}
 \label{sec:related_works}
-Several works~\cite{sancho2002, skeie2002, skeie2004, koibuchi2003} have been presented addressing the problem of topology
-agnostic routing. While they show interesting
-performances, the requirement for virtual channels resources 
-to avoid deadlock makes them not suitable for the specific DNA self
-assembled networks we are assuming as background.
-Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} do not use virtual channels to
-achieve deadlock freedom, but turn prohibitions. 
+Several worksaddressed the problem of topology agnostic deadlock
+freedom introducing virtual channels~\cite{sancho2002, skeie2002,
+skeie2004, koibuchi2003}, but while they show interesting
+performances, the low resources deadlock makes them not suitable for
+the specific DNA self assembled networks we are assuming as
+background.
+Other topology independent algorithms~\cite{schroeder1991,
+koibuchi2001, cherkasova1996} do not require any virtual channels but
+exploit the concept of ``turn prohibition''.
 In particular, authors of~\cite{Patwardhan05evaluatingthe} exploits the creation of a spanning tree of the
-topology, then placing bidirectional restrictions by avoiding a packet
+topology, placing bidirectional restrictions by avoiding a packet
 to traverse the same link in both up and down directions.
-While the hierarchical nature of this approach can lead to uneven traffic
+The hierarchical nature of this approach can lead to uneven traffic
 distribution, with many packets traversing upper links (near to the
-root), this is quite acceptable in classical wide area networks
+root), but this is quite acceptable in classical wide area networks
 topologies with a limited number of nodes. Other approaches such as
@@
 Other solutions try to approach the issue of irregular
-topologies by limiting the number~\cite{dally1994, duato1997, gomez2004, koibuchi2008} or the
-location~\cite{zhang2008, sui2000, flich2008, liu2011} of missing links. This
+topologies by limiting the number~\cite{duato1997, gomez2004, koibuchi2008} or the
+location~\cite{zhang2008, flich2008, liu2011} of missing links. This
 restriction is clearly unacceptable given the hight-defect rates of
@@
 avoid considering solutions based on hardware-redundancy to
-dynamically recover defects as in~\cite{constantinides2006, kohler2010, kim2006, park2006, ebrahimi2013}.
+dynamically recover defects as in~\cite{constantinides2006, kohler2010,  park2006, ebrahimi2013}.
 
@@
 The \disr{} approach presented in this work is a first attempt of
-reaching the same goals of a segment based turn prohibition  without
+achieving the same goals of a segment based turn prohibition  without
 requiring any topology graph or centralized execution. In particular
-\disr{} aims to obtain a segment network partitioning using a
+\disr{} implements segment discovery and turn prohibition using a
 completely different mechanism, based on a distributed exchange of
-small setup packets. The following main features distinguish \disr{}
+small setup packets requiring on average $15\%$ of the available
+resource budget. The following main features distinguish \disr{}
 from classic approaches to segment partitioning: 

### 2014-02-14 PAPER/paper.tex
Fixes

@@
 \newcommand{\etc}{\emph{etc.}}
-\renewcommand{\baselinestretch}{0.98}\normalsize
+\newcommand{\disr}{{\sf DiSR}}
+%\renewcommand{\baselinestretch}{0.97}\normalsize
 %------------------------------------------------------------------------------
@@
 \begin{abstract}
-In this paper we present DiSR, a first effort for a distributed
-segment-based approach to routing and defect mapping in a nano-scale,
-topology agnostic scenario based on DNA self-assembly. The main aim is
-exploiting the already-proven qualities of segment-based routing
-without neither requiring a topology graph as input, nor needing a
-centralized algorithm to configure network paths.  After introducing
-the conceptual elements and the execution model of DiSR, we show how
-the opensource Nanoxim platform has been used to evaluate the proposed
-approach in the process of discovering irregular network topology
-while establishing network segments.  Results show how DiSR still
-preserves some important properties (coverage, defect tolerance,
-scalability)  while avoiding centralized tree-based broadcasting and
-resource hungry solutions such as virtual channels and hardware
-redundancy. Finally, we analyzed a first, not yet optimised gate-level
-hardware implementation of the required control logic and storage for
-DiSR, demonstrating a relatively acceptable impact ranging from 10 to
-about 20\% of the budget of transistors available for each node.
+In this paper we present \disr{}, a distributed approach to topology
+discovery and defect mapping in a self-assembled nano
+networks-on-chip. The main aim is achieving the already-proven
+properties of segment-based deadlock freedom without neither requiring
+a topology graph as input, nor needing a centralized algorithm to
+configure network paths.  After introducing the conceptual elements
+and the execution model of \disr{}, we show how the opensource Nanoxim
+platform has been used to evaluate the proposed approach in the
+process of discovering irregular network topology while establishing
+network segments. Comparison against a tree-based approach show how
+\disr{} still preserves some important properties (coverage, defect
+tolerance, scalability) while avoiding resource hungry solutions such
+as virtual channels and hardware redundancy. Finally, we propose a
+gate-level hardware implementation of the required control logic and
+storage for \disr{}, demonstrating a relatively acceptable impact
+ranging from 10 to about 20\% of the budget of transistors available
+for each node.
 \end{abstract}
@@
 \section{Conclusions}
-In this work we presented DiSR, an initial attempt of porting a segment based
-approach to distributed self-assembled nanoscale scenario. We
-demonstrated how DiSR can accomplish the aim of finding a segment
+In this work we presented \disr{}, an initial attempt of achieving a segment based
+topology discovery into distributed self-assembled nanoscale scenario. We
+demonstrated how \disr{} can accomplish the aim of finding a segment
 coverage of the network without requiring any centralized approach
@@
 implementation has been presented to evaluate the impact on the limited
-node size typical of the assumed scenario. Future works will focus on
-developing self tuning of DiSR to match a high coverage levels and the
-detailed low level hardware implementation on
+node size typical of the assumed scenario. From an high-level
+perspective future works will focus on
+investigating \disr{} resulting network in order to support the
+execution of massively parallel applications, while keeping into
+developing a detailed low level hardware implementation on
 DNA grid using the appropriate nano devices models.

### 2014-02-14 PAPER/implementation.tex
Rephrased some parts. Removed spotted typos

@@
 
-A possible hardware implementation of the \disr{} algorithm will be
-described in this section.  Before to enter in to detail of  \disr{}
-architecture,  an idea of node structure tailored for this particular
-scenario can be found depicted in Fig.~\ref{fig:node_structure}. In
-particular, such node should have the following foundamental elements:
+A possible hardware implementation of \disr{} algorithm will be
+described in this section. Figure~\ref{fig:node_structure} depicts the general
+structure of a node in this particular scenario. In particular such a node
+is composed by the following fundamental elements:
 
@@
 
-	\item \textbf{I/O Buffers-Trasceivers:} These elements, one for
-	each port,  are responsible of data transmission between neighbours
-	nodes. The packets received or sent will be stored in specified buffers
-	named input and output buffers respectivelly.
+	\item \textbf{I/O Buffers-Transceivers:} These elements, one for
+	each port,  are responsible for data transmission with neighbors
+	nodes. The packets received or sent are stored in specific buffers
+	named input and output buffers respectively.
 
-	\item \textbf{Switch Matrix:} Driven by a switch controller, enables the
-	reciprocal connections beetween		 devices inside the node. Before
-	the creation of segments, such controller receives information from
+	\item \textbf{Switch Matrix:} Driven by a switch controller, it enables the
+	reciprocal connections among devices inside the node. Before segments'
+	creation, this controller receives information from
 	\disr{} block. After this phase, the switch controller will be driven by
-	the block wich implements the routing algorithm. The Switch matrix is
-	essentially a series of multiplexers and demultiplexers.
+	the block implementing the routing algorithm. The \emph{Switch Matrix} is
+	essentially composed of a series of multiplexers and demultiplexers.
 
-	\item  \textbf{Processing Element (PE):} Is strictly related to the node
-	functionality  and role inside a given network, e.g. being a
-	computation or storage node.
+	\item  \textbf{Processing Element (PE):} Is strictly related to the
+	functionality and role that the node cover inside a given network (e.g. being a
+	computation or storage node).
 
 	\item \textbf{\disr{}-Routing:} The \disr{} block contains all the hardware, control
-	logic and configuration registers, related to the implementation of the
+	logic and configuration registers, needed by the implementation of the
 	proposed approach. The routing algorithm receives information
-	from \disr{}  wich indicates the status of the segments that interests a
-	particular node. The routing operation will take in account of these
-	informations in order to perform a deadlock-free routing. Both Routing
-	and \disr{} are connected to the switch matrix in order to receive
+	from \disr{}  which indicates the status of segments related to a
+	particular node. Routing operations will take into account these
+	information to obtain deadlock freedom. Both Routing
+	and \disr{} are connected to the \emph{Switch Matrix} in order to receive
 	packets from the input buffer. Since the packets are processed one at
-	a time, a specific arbiter should be present within the switch matrix
+	a time, a specific arbiter should be present within the \emph{Switch Matrix}
 	controller.
@@
 
-To give a basic estimate of the overhead needed we will focus on \disr{}-
-specific components, that is, the control logic and configuration
-registers needed to implement \disr{}. In Figure~\ref{fig:implementation}
-is shown a sketch of the  architecture, which mainly consist in the
+To give a basic estimate of the overhead needed we focus on \disr{}-
+specific components namely the control logic and configuration
+registers needed to implement \disr{}. Figure~\ref{fig:implementation}
+shows an architecture sketch, which mainly consist in the
 following building elements:
@@
 	\item \textbf{LED registers:}
-	A set of registers store the \emph{LED} listed in the
-	section~\ref{sec:disr_concepts}.  In particular, in the
-	link\_visited[] table, can be pointed out the presence of two
-	particular registernamed \emph{tflag} and \emph{busy}.  The Latter
-	is used to indicate if a specific port is alredy visited or
-	tvisited while the former indicates specifically if the specific
-	port is alredy candidate or  assigned for a specific segment.
+	A set of registers store the \emph{LED} defined in
+	section~\ref{sec:disr_concepts}.  In the
+	link\_visited[] table, we defined two specific registers named
+	\emph{tflag} and \emph{busy}. While the first one indicates
+    if the specific port of a segment is already candidate or assigned,
+    the second one records if a specific port is already visited or tvisited
 
     \item \textbf{Control circuitry:}
-    This circuitry decodes the the      incoming packet, the LED
-	registers and the DBS,     updating them when required. This block
-	drives the LED register   to store or, to read the LED data
-	according with \emph{write enable (WE)} or \emph{read enable (RE)}
+    This circuitry decodes incoming packet, LED
+	registers and DBS, updating them when required. This block
+	drives LED register according with \emph{write enable (WE)} or \emph{read enable (RE)}
 	signals. Then, the resulting \emph{Ctrl-Out} drives the other
-	communication resources for actuating the \disr{} routing operation.
+	communication resources to actuate \disr{} routing operations.
 
 	\item \textbf{Packager:}
-	Essentially is a set of registers and multiplexers. Starting from
-	an incoming packet stored in the input buffer, it updates the
-	content of the packet before the retransmission to   a destination
-	node.  In some cases, this circuitry builds the packet from the
-	scratch.  For example this happens when a node is bootsrap and for
-	the first time it should inject a \emph{strating\_segment\_request}. 
-	In Fig.~\ref{fig:packager} is shown the architecture of such packager 
+	Essentially it is a set of registers and multiplexers. Starting from
+	an incoming packet stored in the input buffer, it updates packet's
+	content before retransmission to a destination
+	node.  In some cases, this circuitry builds the packet from
+	scratch e.g. when a node is bootstrap and for
+	the first time it should inject a \emph{starting\_segment\_request}. 
+	Figure~\ref{fig:packager} depicts the architecture of this
 	block. When a packet is created for the first time, the multiplexers 
-	driven by the controller, will select the information incoming from the 
-	internal node such as the \emph{soruce\_ID}. In this situation the 
-	TTL field should be resetted to its initial value and the \emph{segment\_ID}
+	driven by the controller, will select information incoming from an internal 
+    node such as the \emph{source\_ID}. In this situation the 
+	TTL field should be reset to its initial value and the \emph{segment\_ID}
 	is composed by the node ID and by the output port identification 
@@
 While the elements mentioned above are part of the \disr{} circuitry,
-the other devices depicted in Fig.~\ref{fig:implementation} like the
+the other devices depicted in Figure~\ref{fig:implementation} like the
 multiplexer and demultiplexer are implemented outside \disr{}. In
-particular, such components will be inside the switch matrix  (refers
-to the Fig~\ref{fig:node_structure}).
+particular, such components will be inside the \emph{Switch Matrix} (see Figure~\ref{fig:node_structure}).
 
@@
 
-Each of just described building block, reacts with the rising edge  of
+All the blocks described above, reacts with the rising edge of
 the \emph{clock signal}. An asynchronous system \emph{reset} signal is
 also present to restore all registers to their default values. When
-this signal is set, the DBS state machines for each network
+this signal is set, DBS state machines for each network
 node are set as \emph{Free}.  
-In Fig.~\ref{fig:pipeline} is described the pipeline structure of the
-\disr{} architecture. The packets incoming from the neighbours node, or
-locally generated will be send to the DBS state machine in order to te
-ensure the status commutation. While the DBS updates its state,  in the
-next clock cycle the control circuitry will update the Led status and
-will drive the switch matrix in order to send eventually the packets to
+Figure~\ref{fig:pipeline} is shows the pipeline structure of the
+\disr{} architecture. Packets incoming from neighbor nodes (or
+generated locally) are sent to the DBS state machine in order to
+ensure the status commutation. While DBS updates its state, in the
+next clock cycle the control circuitry will update LED registers status and
+will drive the \emph{Switch Matrix} in order to send eventually the packets to
 the right output buffer.
@@
 
-As discussed above, one of the main design challenge of DNA Self-
+As discussed above, one of the main design challenges of DNA Self-
 Assembled systems is the limited number of resources available to implement both
@@
 full-adder, latch etc.), it has been possible to get a rough estimate
-of the number of transistors necessary to implement the \disr{} logic.
+of the number of transistors necessary to implement \disr{} logic.
 Figure~\ref{fig:synthesys} shows the results of synthesis in terms of
@@
   \includegraphics[width=0.50\textwidth]{pictures/synthesis.eps}
-  \caption{Network size vs number of CNFETs necassary to implement
+  \caption{Network size vs number of CNFETs necessary to implement
   the \disr{} circuitry.}
@@
 
-In particular, observing the Figure~\ref{fig:synthesys} can  be
-pointed out that the proposed implementation occupies about 17,5\% of
-the node budget. In particular the main contribution is due to the
-controller circuitry followed by LED registers. Further, more than the
+In particular, Figure~\ref{fig:synthesys} shows that the proposed 
+implementation occupies about 17,5\% of our node budget. 
+The main contribution is due to the controller circuitry followed by LED registers. 
+Further, more than the
 absolute number of devices itself, it is interesting to observe that
-the circuitry complexity which implements the \disr{} algorithm increases
+the circuitry complexity which implements \disr{} algorithm increases
 with a slowly growing trend. An intuitive explanation of this is the
-relatively simple logic of \disr{}, whose behaviour is almost code on
+relatively simple logic of \disr{}, whose behavior is almost coded on
 scalable storage structures. For example, the number of registers
@@
 table follow the logarithmic function $N_{reg}=N_{port} \cdot
-log_2(N)$ where \emph{Nport} is the number of the router’s ports, N is
+log_2(N)$ where \emph{Nport} is the number of the router’s ports and N is
 the number of network’s nodes.
@@
 the implemented circuitry, timing results can be obtained from a 
-gate-level netlist. Since a complete technology library usefull for
-commercial synthesis tool (like Design Compiler) doesn't exist for 
-this particular technology (at the best that we know), we have
-synthesized the RTL description of \disr{} with a standard 32 nm CMOS
-library obtaining  a delay of about $\mathrm{\tau_{\disr{}}=10} \ FO4$
+gate-level netlist. Since a complete technology library useful for
+commercial synthesis tool (e.g. Design Compiler) is not available for
+this particular technology, we have
+synthesized the RTL description of \disr{}, with a standard 32~nm CMOS
+library, obtaining a delay of about $\mathrm{\tau_{\disr{}}=10} \ FO4$
 (fan-out of four). Considering the results obtained
-in~\cite{deng_isscc07}, wich reports the ratio in therms of FO4
-between a standard 32 nm CMOS technology and a carbon nanotube ones, 
-rough delay estimation can be obtained. In particolar in such work 
+in~\cite{deng_isscc07}, which reports the ratio in terms of FO4
+between a standard 32~nm CMOS technology and a carbon nanotube ones, 
+rough delay estimation can be obtained. In particular in such work 
 has been reported a ratio of:  
@@
 \end{equation}
-Considering that F04 CMOS is about 30 ps, and the results of last
-equation, a FO4 for the CNFET case is equal to about 15 ps, and
-then the working frequency can be computed as:
+Considering that F04 CMOS is about 30~ps, and the results of last
+equation, a FO4 for the CNFET case is equal to about 15~ps, the working 
+frequency can be computed as:
 \begin{equation}
@@
 \end{equation}
-where $\mathrm{\tau_{\disr{}}}$ was expressed in therms of FO4.
+where $\mathrm{\tau_{\disr{}}}$ is expressed in terms of FO4.
 
-Regards the power consumption of the entire \disr{} devices, 
-an accurate power analysis with the switch activity
-annotation can be avoided because the \disr{} circuitry will be active 
-only once at the system startup. Indeed, after the setup phase, when all segments
-are mapped in to the network, the \disr{} block will stop its activity
-giving as output the fixed status of segments to the routing
-algorithm. For this reason the dynamic power will going  to zero and
-the only cosumption will be eventually only due to the leackage
+Regarding the power consumption of whole \disr{} devices, 
+we avoided an accurate power analysis with the switch activity
+annotation due to the fact that \disr{} circuitry will be active 
+only once during system startup. Indeed, after the setup phase, 
+when all segments are mapped, the \disr{} block will stop its activity 
+passing all the information related to segments to the routing
+algorithm. For this reason the dynamic power falls to zero and
+the only consumption could be due to the leakage
 consumption.

### 2014-02-17 trunk/PAPER/introduction.tex
Elsevier style

@@
 
- TODO: re-enable on long paper
 Exploring long term alternatives to the CMOS technology is gaining
 more and more revelance as the scaling trend of such devices keeps
-introducing new challenges. Power density, defect tolerance, testing
+introducing new challenges: power density, defect tolerance, testing
 costs and wire delays are only a few of the many critical aspects
-involved~\cite{itrs12}. While software parallelism and multicore
-approaches~\cite{horowitz2004, mudge2001, powell2009} are partially mitigating the impact of such
+involved~\cite{itrs13}. 
+While software parallelism and multicore
+approaches~\cite{horowitz2004} and \cite{powell2009} are partially mitigating the impact of such
 constraints on performances, it is likely that the growing computing demand will
@@
 implications to be addressed when approaching to the design of
-computer architecture: a computational model should be based on a
-distributed network of small computing and storage nodes, randomly
-placed and interconnected (see Figure~\ref{fig:nana}).
-Proof-of-concept of such kind of computational model can be found for
-example in~\cite{patwardhan2006_1}.  Since no regularity can be
-assumed in such network, a topology agnostic strategy that avoids
-deadlock should be adopted in order to route packets (e.g.
-instructions and data operands) among nodes.  It is important to
+a computer architecture: computational model should be based on a
+distributed network of small processing and storage nodes, randomly
+placed and interconnected (see Figure~\ref{fig:nana}-b).
+Proof-of-concept of such architectures can be found for
+example in~\cite{patwardhan2006_1}, where instruction and data
+operands are move around the network in order to be processed.
+Indepentedly from the particular policy chosen for routing packets,
+such networks must be able to guarantee deadlock freedom without any
+prior assumption on topology.
+
+In this work we introduce \disr{}, a Distributed Segment-based approach
+to deadlock freedom in large scale DNA self assembled networks. Our
+contribution aims to achieve the classical properties of a
+segment-based approach~\cite{mejia_ipdps06} without requiring any
+topology graph, external defect map or centralized algorithm
+execution.  So the \disr{} approach is not intended to discover the
+``optimal'' segment choice (ideally reachable with the knowledge of
+the topology graph) but just to demonstrate a concrete model that can
+fit into such complex, irregular and large sized networks.
+It is important to
 underline that, altougth we can assume an architecture similar to the
@@
 underlying computing architecture.
-
-In this work we introduce DiSR, a Distributed Segment-based approach
-to deadlock freedom in large scale DNA self assembled networks. Our
-contribution aims to achieve the classical properties of a
-segment-based approach~\cite{mejia_ipdps06} without requiring any
-topology graph, external defect map or centralized algorithm
-execution.  So the DiSR approach is not intended to discover the
-``optimal'' segment choice (ideally reachable with the knowledge of
-the topology graph) but just to demonstrate a concrete model that can
-fit into such complex, irregular and large sized networks.
 
@@
 
-\section{Related Works}
+\section{Background and Contribution}
 \label{sec:related_works}
-Several works~\cite{sancho2002, skeie2002, skeie2004, koibuchi2003} have been presented addressing the problem of topology
-agnostic routing. While they show interesting
-performances, the requirement for virtual channels resources 
-to avoid deadlock makes them not suitable for the specific DNA self
-assembled networks we are assuming as background.
-Other topology independent algorithms~\cite{schroeder1991, koibuchi2001, cherkasova1996} do not use virtual channels to
-achieve deadlock freedom, but turn prohibitions. 
+Several worksaddressed the problem of topology agnostic deadlock
+freedom introducing virtual channels~\cite{sancho2002, skeie2002,
+skeie2004, koibuchi2003}, but while they show interesting
+performances, the low resources deadlock makes them not suitable for
+the specific DNA self assembled networks we are assuming as
+background.
+Other topology independent algorithms~\cite{schroeder1991,
+koibuchi2001, cherkasova1996} do not require any virtual channels but
+exploit the concept of ``turn prohibition''.
 In particular, authors of~\cite{Patwardhan05evaluatingthe} exploits the creation of a spanning tree of the
-topology, then placing bidirectional restrictions by avoiding a packet
+topology, placing bidirectional restrictions by avoiding a packet
 to traverse the same link in both up and down directions.
-While the hierarchical nature of this approach can lead to uneven traffic
+The hierarchical nature of this approach can lead to uneven traffic
 distribution, with many packets traversing upper links (near to the
-root), this is quite acceptable in classical wide area networks
+root), but this is quite acceptable in classical wide area networks
 topologies with a limited number of nodes. Other approaches such as
@@
 avoid considering solutions based on hardware-redundancy to
-dynamically recover defects as in~\cite{constantinides2006, kohler2010, kim2006, park2006, ebrahimi2013}.
+dynamically recover defects as in~\cite{constantinides2006, kohler2010,  park2006, ebrahimi2013}.
 
-In~\cite{mejia_ipdps06} authors present SR, an approach the solves these
+In~\cite{mejia_ipdps06} authors present an approach the solves these
 limitations by allowing turn restrictions to be placed locally,
 independently from other restrictions. The whole network is
-partitioned into segments, and each bidirectional turn
+partitioned into segments, and a bidirectional turn
 restriction can be freely chosen within a segment in order to guarantee
-deadlock freedom and connected networks. This \emph{locality
-independence} property, together with no requirement of any particular tree/root
+deadlock freedom while preserving network connectivity. This \emph{locality
+independence} property, avoiding the requirement of any particular tree/root
 choice, would make it the best choice for the given scenario;
-however, its topology independency still requires the knowledge of the
+however, it still requires the knowledge of the
 whole network graph in order to find the segments.
 
-The DiSR approach presented in this work is a first attempt of
-reaching the same goals of a segment based approach, that is
-establishing segments, without requiring any topology graph or
-centralized execution.
+The \disr{} approach presented in this work is a first attempt of
+achieving the same goals of a segment based turn prohibition  without
+requiring any topology graph or centralized execution. In particular
+\disr{} implements segment discovery and turn prohibition using a
+completely different mechanism, based on a distributed exchange of
+small setup packets requiring on average $15\%$ of the available
+resource budget. The following main features distinguish \disr{}
+from classic approaches to segment partitioning: 
+\begin{itemize}
+\item No centralized entity is globally responsible and/or aware of
+what is going on, i.e. the status of the \disr{} execution is
+collectively distributed among the nodes
+\item  No defect map and/or topology graph is used as input,
+thus, the topology has to be discovered \emph{while} segments are
+created
+\item At the end of the execution, no segment list is created or
+stored anywhere: each node is only aware of belonging to some segment,
+ignoring the presence of other nodes in the same segment and even the
+presence of other segments in the network
+\end{itemize}

### 2014-02-17 trunk/PAPER/paper.tex
Elsevier style

@@
-\documentclass[final,journal]{IEEEtran}
+%\documentclass[final,journal]{IEEEtran}
 %\IEEEoverridecommandlockouts
 
+% Elsevier specific styles
 %------------------------------------------------------------------------------
+\documentclass[a4]{article}
+%\documentclass[review]{elsarticle}
+\usepackage{lineno,hyperref}
 
-\usepackage{cite}
+\modulolinenumbers[5]
+
+\journal{Journal of \LaTeX\ Templates}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+%\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
+%------------------------------------------------------------------------------
+%\usepackage{cite}
 \usepackage{amsmath}
@@
 \usepackage{url}
-\usepackage{cite}
 \usepackage{balance}
@@
 
+\begin{frontmatter}
 %------------------------------------------------------------------------------
@@
 
-\author{Vincenzo~Catania, Andrea Mineo, Salvatore Monteleone~and~Davide~Patti% 
-\thanks{The authors are with the Dipartimento di Ingegneria
-Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
-(email: \{vincenzo.catania,amineo,salvatore.monteleone,davide.patti\}@dieei.unict.it).}}
+%% Group authors per affiliation:
+\author{Elsevier\fnref{myfootnote}}
+\address{Radarweg 29, Amsterdam}
+\fntext[myfootnote]{Since 1880.}
 
-\maketitle
+%% or include affiliations in footnotes:
+%\author[mymainaddress,mysecondaryaddress]{Elsevier Inc}
+%\ead[url]{www.elsevier.com}
+
+%\author{Vincenzo~Catania, Andrea Mineo, Salvatore Monteleone~and~Davide~Patti% 
+%\thanks{The authors are with the Dipartimento di Ingegneria
+%Elettrica, Elettronica ed Informatica, Universit\`a di Catania, Italy
+%(email: \{vincenzo.catania,amineo,salvatore.monteleone,davide.patti\}@dieei.unict.it).}}
 
@@
 \begin{abstract}
-In this paper we present \disr{}, a first effort for a distributed
-segment-based approach to routing and defect mapping in a nano-scale,
-topology agnostic scenario based on DNA self-assembly. The main aim is
-exploiting the already-proven qualities of segment-based routing
-without neither requiring a topology graph as input, nor needing a
-centralized algorithm to configure network paths.  After introducing
-the conceptual elements and the execution model of \disr{}, we show how
-the opensource Nanoxim platform has been used to evaluate the proposed
-approach in the process of discovering irregular network topology
-while establishing network segments.  Results show how \disr{} still
-preserves some important properties (coverage, defect tolerance,
-scalability)  while avoiding centralized tree-based broadcasting and
-resource hungry solutions such as virtual channels and hardware
-redundancy. Finally, we analyzed a first, not yet optimised gate-level
-hardware implementation of the required control logic and storage for
-\disr{}, demonstrating a relatively acceptable impact ranging from 10 to
-about 20\% of the budget of transistors available for each node.
+In this paper we present \disr{}, a distributed approach to topology
+discovery and defect mapping in a self-assembled nano
+networks-on-chip. The main aim is achieving the already-proven
+properties of segment-based deadlock freedom without neither requiring
+a topology graph as input, nor needing a centralized algorithm to
+configure network paths.  After introducing the conceptual elements
+and the execution model of \disr{}, we show how the opensource Nanoxim
+platform has been used to evaluate the proposed approach in the
+process of discovering irregular network topology while establishing
+network segments. Comparison against a tree-based approach show how
+\disr{} still preserves some important properties (coverage, defect
+tolerance, scalability) while avoiding resource hungry solutions such
+as virtual channels and hardware redundancy. Finally, we propose a
+gate-level hardware implementation of the required control logic and
+storage for \disr{}, demonstrating a relatively acceptable impact
+ranging from 10 to about 20\% of the budget of transistors available
+for each node.
 \end{abstract}
@@
 %------------------------------------------------------------------------------
-%\IEEEkeywords{...}
-
-\begin{IEEEkeywords}
-Nanotechnology, DNA, Self-assembly, Routing, Deadlock
-\end{IEEEkeywords}
+\begin{keyword}
+Nanotechnology \sep DNA \sep Self-assembly \sep Routing \sep Deadlock
+\end{keyword}
+\end{frontmatter}
 %------------------------------------------------------------------------------
@@
 \section{Conclusions}
-In this work we presented \disr{}, an initial attempt of porting a segment based
-approach to distributed self-assembled nanoscale scenario. We
+In this work we presented \disr{}, an initial attempt of achieving a segment based
+topology discovery into distributed self-assembled nanoscale scenario. We
 demonstrated how \disr{} can accomplish the aim of finding a segment
@@
 implementation has been presented to evaluate the impact on the limited
-node size typical of the assumed scenario. Future works will focus on
-developing self tuning of \disr{} to match a high coverage levels and the
-detailed low level hardware implementation on
+node size typical of the assumed scenario. From an high-level
+perspective future works will focus on
+investigating \disr{} resulting network in order to support the
+execution of massively parallel applications, while keeping into
+developing a detailed low level hardware implementation on
 DNA grid using the appropriate nano devices models.
@@
 
-\balance
+%\balance
+%
+%\bibliographystyle{IEEEtran} 
+%\bibliography{bibliography}
 
-\bibliographystyle{IEEEtran} 
+%\bibliographystyle{elsarticle-num}
+\section*{References}
 \bibliography{bibliography}
-
 %------------------------------------------------------------------------------

### 2014-02-18 trunk/PAPER/simulation.tex
Removed figure/text overlapping
Removed some typos

@@
 
-In this section we will test the proposed DiSR approach to demonstrate
+In this section we will test the proposed \disr{} approach to demonstrate
 its effectiveness and compare it against topology agnostic approach
 based on spanning trees and
-broadcasting~\cite{Patwardhan05evaluatingthe}, to measure how DiSR
+broadcasting~\cite{Patwardhan05evaluatingthe}, to measure how \disr{}
 performs in covering the network structure.
@@
 aware routing and selection strategies) new features specifically
-taylored for the nanoscale scenario were introduced, e.g. the ability to simulate a random
-network, the implementation of the DiSR to obtain the segment topology
+tailored for the nanoscale scenario were introduced, e.g. the ability to simulate a random
+network, the implementation of the \disr{} to obtain the segment topology
 and the support for defective links and nodes.
@@
 %\item {\% defective links}: the probability that each link is
-%disconnected or not present, from 0 the amount that yelds
+%disconnected or not present, from 0 the amount that yields
 %no more segments.
 \item {\emph{\% defective nodes}}: the probability that a node is not
-working, thus having all its links cannot be utilized during DiSR setup.  
+working, thus having all its links cannot be utilized during \disr{} setup.  
 %Same range as defective links parameter.
 \item {\emph{Bootstrap node}}: the node used from upper layer 
-to inject the DiSR process. When not explicitly investigating the
+to inject the \disr{} process. When not explicitly investigating the
 impact of each single bootstrap choice, a set representative regions have been
@@
 nodes should be assigned, so this metric is useful to show how some
-disconnected regions can negatively impact on the whole DiSR
+disconnected regions can negatively impact on the whole \disr{}
 effectiveness.
@@
 
-%Further, to evaluate how DiSR compares against the centralized segment
+%Further, to evaluate how \disr{} compares against the centralized segment
 %based algorithm, the following metrics have been adopted:
 %\begin{itemize}
-%%\item {Average Path Lenght}:
+%%\item {Average Path Length}:
 %%\item {Average Link Weight}:
@@
 
-% TODO: long paper
-\subsection{Other Optimisations}
-Some optimisation parameters, which demostrated to improve the DiSR
-results have been fixed to some good values, but are not subject to
-further investigation; once again the focus here is not the
-optimal set of segments, but just demostrating a working approach. 
-These are optimisations are:
-\begin{itemize}
-\item{cycle\_links}: max number of retries across the set of links of
-each node. While searching for a free link due an incoming request,
-the same request is cancelled after a given number of tries. This
-gives to preceding node change to test a different paths. Default is set to 1.
-\item{bootstrap\_timeout}: number of time units that a bootstrap node
-should wait before assuming that a livelock in the starting segment
-process has occurred. In the worst case, we can imagine that longest
-path required is the one returning to the bootstrap node after having
-travelled across all the links. So, althought this is just an extreme
-situation, a good upper limit can be safely be set to NxN.
-\item{bootstrap\_immunity}: in order to avoid the failure of the whole DiSR
-setup process, a bootstrap node should not have defective links.
-Enabling this optimisation, a bootstrap node is immune to defects.
-We may think of a pre-bootstrap phase that properly selects (from upper
-layer via) a bootstrap node which is tested as properly connected. We
-enabled this optimisation, however empirical tests showed us that only
-simulations using bootstrap nodes placed on edges would be heavily
-affected, since these are nodes starting with a lower number of links,
-e.g. corner nodes could only have two connected direction, so even a
-defective link could prevent starting segment packet to return to
-bootstrap to close the loop a create the segment.
-\end{itemize}
-
 \subsection{Results}
@@
 \end{figure}
+
+% TODO: long paper
+\subsection{Other Optimizations}
+Some optimization parameters, which demonstrated to improve the \disr{}
+results have been fixed to some good values, but are not subject to
+further investigation; once again the focus here is not the
+optimal set of segments, but just demonstrating a working approach. 
+These are optimizations are:
+\begin{itemize}
+\item \emph{cycle\_links}: max number of retries across the set of links of
+each node. While searching for a free link due an incoming request,
+the same request is cancelled after a given number of tries. This
+gives to preceding node change to test a different paths. Default is set to 1.
+\item \emph{bootstrap\_timeout}: number of time units that a bootstrap node
+should wait before assuming that a livelock in the starting segment
+process has occurred. In the worst case, we can imagine that longest
+path required is the one returning to the bootstrap node after having
+traveled across all the links. So, although this is just an extreme
+situation, a good upper limit can be safely be set to NxN.
+\item \emph{bootstrap\_immunity}: in order to avoid the failure of the whole \disr{}
+setup process, a bootstrap node should not have defective links.
+Enabling this optimization, a bootstrap node is immune to defects.
+We may think of a pre-bootstrap phase that properly selects (from upper
+layer via) a bootstrap node which is tested as properly connected. We
+enabled this optimization, however empirical tests showed us that only
+simulations using bootstrap nodes placed on edges would be heavily
+affected, since these are nodes starting with a lower number of links,
+e.g. corner nodes could only have two connected direction, so even a
+defective link could prevent starting segment packet to return to
+bootstrap to close the loop a create the segment.
+\end{itemize}

### 2014-02-18 PAPER/disr.tex
Removed some typos

@@
 %------------------------------------------------------------------------------
-\section{\disr{} Sketch}
+\section{\disr{} Overview}
 %------------------------------------------------------------------------------
@@
 The main concept behind the kind of turn prohibition we want to
-achieve is the \emph{Segment}. A segment is basically a path of consecutive
-nodes and links, starts with a link attached to a node of a different
-segment and ending with a link attached to a
-node belonging another. In other words, a segment
+achieve is the \emph{segment}. A segment $S_y$ is basically a path of consecutive
+nodes and links, starting with a link attached to a node belonging to
+a different segment $S_x$ and ending with a link attached to a
+node of another segment $S_z$. In other words, a segment
 a path between connecting two other different segments. The example
 in Figure~\ref{fig:segments} shows the segment with id $1.4$, starting
-with a link connected to the node $9$, the going trought nodes
+with a link connected to the node $9$, the going through nodes
 $4$,$3$,$2$ and ending with the link connected to the node $1$. Other
@@
 segments. 
-\item Turn proibition in each confirmed segment.
+\item Turn prohibition in each confirmed segment.
 \item Draining of remaining packet due timeouts
@@
 
-\section{Detailed Description of \disr{}}
+\subsection{\disr{} Data Structures}
+\label{ssec:disr_data}
+
+We distinct between two different kind of data stored at each node:
+\emph{Dynamic Behavior Status} (\emph{DBS}) and \emph{Local
+Environment Data} (\emph{LED}).
+
+The \emph{DBS} stores information in order to capture the dynamic
+behavior of the node  in the context of the whole
+\disr{} execution phased. The \emph{DBS} can have the following values:
+
+\begin{itemize}
+\item{\emph{Free}}: a node that has  not been yet considered  by the \disr{} algorithm.
+\item{\emph{Bootstrap}}: a node which has been explicitly set as bootstrap node from
+an upper layer via. 
+\item{\emph{ActiveSearching}}: a node from which a find process of new segments has
+been started and not yet cancelled or confirmed. 
+\item{\emph{Candidate}}: a node currently candidate for belonging to some segment
+, but not being itself the node from which the find process was started. 
+\item{\emph{CandidateStarting}}: same as above, but the node is currently being considered as candidate
+for starting segment. 
+\item{\emph{Assigned}}: a node for which the segment has been determined.  
+\end{itemize}
+
+The \emph{LED} are like an instant snapshot of the \disr{} algorithm at each node,
+consisting in the following variables:
+\begin{itemize}
+\item{\emph{segID}}:a value used to specify the segment to which the
+node has been assigned or is candidate for being assigned.
+\item{\emph{visited}}: a boolean value. When \emph{true}
+then a \emph{segID} different from \texttt{NULL} specifies the segment 
+to which the node has been assigned. 
+\item{\emph{tvisited}}: a boolean value. If \emph{true}, the node is
+being considered as candidate for a segment, and the \emph{segID} value
+specifies the segment id for which the node is candidate. 
+\item{\emph{link\_visited[]}}: an array
+of values representing information about attached links, that is, the
+segID of the segment owning each link. When \texttt{NULL}, the corresponding link has not yet been
+assigned.
+\item{\emph{link\_tvisited[]}}: an array of
+values representing information about attached links, that is, the \emph{segID} of
+the segment for which the link is candidate. When \texttt{NULL}, the link is
+not candidate for any segment, i.e. maybe already assigned
+or free.
+\end{itemize}
+
 \subsection{Message Types Required}
@@
 \end{figure}
-\begin{itemize}
 
@@
 \end{tabular}
-\caption{\disr{} (a) and RPF (b) node coverage}
+\caption{Example of \disr{} segment setup: Nodes status are labeled as CandidateStarting($Cs$), Candidate ($C$), Free ($F$), Assigned ($A$) and Bootstrap ($B$)}
 \label{fig:disr_events}
@@
 
+\begin{itemize}
 \item{\textbf{Injecting bootstrap request}}: all nodes have an initial
@@
 %Note also that each of these packets has a max\_segment\_hops
-%field to prevent packets from travelling undefinitively.
+%field to prevent packets from traveling undefinitively.
 
@@
 %state as free. But they could also remain \emph{tvisited} for the
-%starting segment, since this doesn’t affect their behaviour for future
+%starting segment, since this does not affect their behavior for future
 %segment requests.
@@
 
-\item{\textbf{Injecting Segment Requests}: Each node in the
+\item{\textbf{Injecting Segment Requests}}: Each node in the
 \emph{Assigned} status can initiate a search for a segment, by sending
@@
 process in completed (Figure~\ref{disr_events}-f).
-Note also that nodes previosly set as \emph{CandidateStarting}, when receiving 
+Note also that nodes previously set as \emph{CandidateStarting}, when receiving 
 a \texttt{SEGMENT\_REQUEST} can simply cancel their
@@
 the bottom of Figure~\ref{fig:disr_events}).
-%Each of the subsequent nodes will forward this \texttt{SEGMENT\_CANCEL}
-%only if no more free links can be explored starting from them.
 \end{itemize}
 
-% TODO: FIX and RE-enable in long paper
-
-\section{Detailed Node behaviour Model}
+\section{Detailed Node behavior Model}
 \label{sec:execution_model}
 
-The \emph{LED} variables at each node are are initially set so the node and
-each of its links is set as free. The only node that makes exception
-is the bootstrap node, initialized in the \emph{Bootstrap} status. All
-the subsequent events happening at each node are the consequence of
-its current dynamic status (DBS) and the packets received.
+In this Section we provide further details about \disr{}
+execution model, describing the internal behavior implemented at
+each node. Note that this also corresponds exactly to what should be
+implemented from the node-hardware perspective, as discussed in
+Section~\ref{sec:implementation}.
 
-%TODO: add state machines
-
-% TODO: fix, move elsewhere or delete
-%Assumption: when discussing of visited/\emph{tvisited} nodes, we are assuming
-%with an id corresponding to the same subnet. Nodes involved in other
-%subnet processes can simply ignore these packets. (TBD: formalize more
-%clearly in which cases inter-subnet packets must be ignored, probably
-%this happens most of the times, but in some cases, e.g. when a
-%terminal node is found, some kind of communication packets are needed
-%in order to crearte the bridge between two subnets.)
+The \emph{LED} variables at each node
+($segID$,$visited$,$tvisited$,\emph{link\_visited[]},\emph{link\_tvisited[]})
+are initially set as \texttt{NULL}, so the node and each of its links
+are considered as free.
+The only node that makes exception is the bootstrap node, initialized
+in the \emph{Bootstrap} status. All the subsequent events happening at
+each node are the consequence of its current dynamic status (DBS), the
+packets received and the internal status represented by the
+\emph{LED}. Note that in the following, when using expression like
+``has a free link'' or ``free node'' we will assume the relationship between 
+$LED$ and $DBS$ discussed in Section~\ref{sec:disr_data}. Further, for
+each packet type all the cases not explicitly listed can simply be
+ignored since are associated to invalid/inconsistent events of the
+\disr{} execution model. A complete list of these cases can be checked
+in the environment simulator source code at~\ref{nanoxim}.
 
@@
 \subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
-When received, if the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
-the packet, the node learns to belong to the segment associated to the
-id. Further, it should forward this packet to the link where the
+When the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
+the packet: the node set itself as $Assigned$ to the segment $SegID$. Further, it should forward this packet to the link where the
 original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
-can learn the segment id they belong to.  \emph{LED} shoud be
-updated from \emph{tvisited} to \emph{visited}.  the
-\emph{link\_tvisited} previously set with the \emph{segID} should be invalidated the
-\emph{link\_visited} variable associated to the incoming confirm should be set
-as segID. Note that if the request was flooded across different links,
-the \emph{link\_visited} variable associated to the other paths should not be
-set.  the \emph{link\_visited} variable associated to the link from which the
-request was originated should be set segID
+can learn the segment id they belong to. \emph{LED} should be
+updated from \emph{tvisited} to \emph{visited}.
 
 \subsection{Receiving a \texttt{SEGMENT\_CANCEL}}
-When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that searching
-for a segment along that path was unsuccessful. But if the node still
-has other free links to try, it should forward a \texttt{SEGMENT\_REQUEST} to
-the next link (next according to some internal ordering). So a node
-forwards back the \texttt{SEGMENT\_CANCEL} packet along the link that originated
-the \texttt{SEGMENT\_REQUEST} packet only when there are no more free links to
-try. If this is the case, the node modifies its status from
-\emph{Candidate} to \emph{Free} and forwards the \texttt{SEGMENT\_CANCEL} packet to the link from which
-the request was received. The process stops when the \texttt{SEGMENT\_CANCEL}
-packet reach the starting node that originated the request.
+When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that
+searching for a segment along that path was unsuccessful. But if the
+node still has some other free link to try, it should forward a
+\texttt{SEGMENT\_REQUEST} to the that link. So a node forwards back
+the \texttt{SEGMENT\_CANCEL} packet along the link that originated the
+\texttt{SEGMENT\_REQUEST} packet $only$ when there are no more free
+links to try. If this is the case, the node modifies its status from
+\emph{Candidate} to \emph{Free} and forwards the
+\texttt{SEGMENT\_CANCEL} packet to the link from which the request was
+received. The process stops when the \texttt{SEGMENT\_CANCEL} packet
+reach the starting node that originated the request.
 
-%TODO REPEAT!!
-%When a node discovers that the path that includes
-%the node itself is no more suitable, a \texttt{SEGMENT\_CANCEL} is sent back
-%across the link from which the \texttt{SEGMENT\_REQUEST} was received.  Possible
-%reasons for that: The node it’s already candidate for another segment
-%The node it’s free but can’t find a free link (according the
-%cyclelinks timeout) The node it’s \emph{tvisited} for the same request id,
-%previously forwarded that request along some free direction, but now
-%it’s receiving a a cancel request and has no more free links
 \subsection{Intra-node vs Inter-node parallelism}
@@
 should we allow in \disr{} ? The adopted approach is that, although
-the nature of \disr{} itself is intrinsicly parallel, the use of
+the nature of \disr{} itself is intrinsically parallel, the use of
 parallelism makes things work in a more complex way. In other words,

### 2014-02-18 PAPER/introduction.tex
Removed some typos

@@
 Exploring long term alternatives to the CMOS technology is gaining
-more and more revelance as the scaling trend of such devices keeps
+more and more relevance as the scaling trend of such devices keeps
 introducing new challenges: power density, defect tolerance, testing
@@
 While software parallelism and multicore
-approaches~\cite{horowitz2004, powell2009} are partially mitigating the impact of such
+approaches~\cite{horowitz2004} and \cite{powell2009} are partially mitigating the impact of such
 constraints on performances, it is likely that the growing computing demand will
@@
 
-In the last years, Self-assembled nanoscale architectures~\cite{yan2003}
+In the last years, self-assembled nanoscale architectures~\cite{yan2003}
 emerged as a promising technology due their tera/peta scale of
@@
 %, patwardhan2006
-The main idea behind this approach is to exploit the physical regularity and
+The main idea behind this approach is exploiting the physical regularity and
 stability of DNA structures in order to create a scaffold onto which
@@
 symbols forming the DNA sequence is limited (sequence of 4 nucleobases
-G,A,T,C) and so creating many different tags (of a given lenght) would
+G,A,T,C) and so creating many different tags (of a given length) would
 mean make them more similar to each other, increasing the probability
@@
 Finally, \emph{defect rates}: while they are very hardly tolerated in mask
-based top down design , the same nature of a bottom up self
-assembled process cannot assume such a deterministic device placement
+based top down design, the same nature of a bottom up self-assembly
+ process cannot assume such a deterministic device placement
 process, thus defect tolerance is something like a design requirement
@@
  \end{tabular}
-  \caption{(a) DNA tag matching and (b) resulting trregualr topology}
+  \caption{(a) DNA tag matching and (b) resulting irregular topology}
   \label{fig:nana}
 \end{figure*}
-These aspects of a DNA-self assembly process lead to some important
+These aspects of a DNA self-assembly process lead to some important
 implications to be addressed when approaching to the design of
@@
 operands are move around the network in order to be processed.
-Indepentedly from the particular policy chosen for routing packets,
+Independently from the particular policy chosen for routing packets,
 such networks must be able to guarantee deadlock freedom without any
@@
 It is important to
-underline that, altougth we can assume an architecture similar to the
+underline that, although we can assume an architecture similar to the
 one depicted in Figure~\ref{fig:nana} as background, the topology discovery
@@
 the execution model of the proposed approach.  In Section~\ref{sec:simulation}
-simulations are carried out with the opensource tool Nanoxim to
+simulations are carried out with the open-source tool Nanoxim to
 demonstrate how \disr{} preserves some of the main segment-based
@@
 \label{sec:related_works}
-Several worksaddressed the problem of topology agnostic deadlock
+Several works addressed the problem of topology agnostic deadlock
 freedom introducing virtual channels~\cite{sancho2002, skeie2002,

### 2014-02-18 PAPER/paper.tex
Removed some typos

@@
-\documentclass[final,journal]{IEEEtran}
+%\documentclass[final,journal]{IEEEtran}
 %\IEEEoverridecommandlockouts
 
+% Elsevier specific styles
 %------------------------------------------------------------------------------
+\documentclass[review]{elsarticle}
+%\documentclass[3p]{elsarticle}
+\usepackage{lineno,hyperref}
 
-\usepackage{cite}
+\modulolinenumbers[5]
+
+\journal{Journal of \LaTeX\ Templates}
+
+%%%%%%%%%%%%%%%%%%%%%%%
+%% Elsevier bibliography styles
+%%%%%%%%%%%%%%%%%%%%%%%
+%% To change the style, put a % in front of the second line of the current style and
+%% remove the % from the second line of the style you would like to use.
+%%%%%%%%%%%%%%%%%%%%%%%
+
+%% Numbered
+%\bibliographystyle{model1-num-names}
+
+%% Numbered without titles
+%\bibliographystyle{model1a-num-names}
+
+%% Harvard
+%\bibliographystyle{model2-names.bst}\biboptions{authoryear}
+
+%% Vancouver numbered
+%\usepackage{numcompress}\bibliographystyle{model3-num-names}
+
+%% Vancouver name/year
+%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}
+
+%% APA style
+%\bibliographystyle{model5-names}\biboptions{authoryear}
+
+%% AMA style
+%\usepackage{numcompress}\bibliographystyle{model6-num-names}
+
+%% `Elsevier LaTeX' style
+\bibliographystyle{elsarticle-num}
+%%%%%%%%%%%%%%%%%%%%%%%
+%------------------------------------------------------------------------------
+%\usepackage{cite}
 \usepackage{amsmath}
@@
 discovery and defect mapping in a self-assembled nano
-networks-on-chip. The main aim is achieving the already-proven
+network-on-chip. The main aim is achieving the already-proven
 properties of segment-based deadlock freedom without neither requiring
@@
 configure network paths.  After introducing the conceptual elements
-and the execution model of \disr{}, we show how the opensource Nanoxim
+and the execution model of \disr{}, we show how the open-source Nanoxim
 platform has been used to evaluate the proposed approach in the
 process of discovering irregular network topology while establishing
-network segments. Comparison against a tree-based approach show how
+network segments. Comparison against a tree-based approach shows how
 \disr{} still preserves some important properties (coverage, defect

### 2014-02-18 PAPER/simulation.tex
Fixes

@@
 aware routing and selection strategies) new features specifically
-taylored for the nanoscale scenario were introduced, e.g. the ability to simulate a random
+tailored for the nanoscale scenario were introduced, e.g. the ability to simulate a random
 network, the implementation of the \disr{} to obtain the segment topology
@@
 %\item {\% defective links}: the probability that each link is
-%disconnected or not present, from 0 the amount that yelds
+%disconnected or not present, from 0 the amount that yields
 %no more segments.
@@
 \begin{itemize}
-\item{Node coverage}: this is the fraction of nodes that
+\item{\emph{Node coverage}}: this is the fraction of nodes that
 are assigned to a segment. In the ideal case, all the non defective
@@
 %\begin{itemize}
-%%\item {Average Path Lenght}:
+%%\item {Average Path Length}:
 %%\item {Average Link Weight}:
@@
 % TODO: long paper
-\subsection{Other Optimisations}
-Some optimisation parameters, which demostrated to improve the \disr{}
+\subsection{Other Optimizations}
+Some optimization parameters, which demonstrated to improve the \disr{}
 results have been fixed to some good values, but are not subject to
 further investigation; once again the focus here is not the
-optimal set of segments, but just demostrating a working approach. 
-These are optimisations are:
+optimal set of segments, but just demonstrating a working approach. 
+These are optimizations are:
 \begin{itemize}
 \item \emph{cycle\_links}: max number of retries across the set of links of
-each node. While searching for a free link due an incoming request,
+each node. While searching for a free link due an incoming segment request,
 the same request is cancelled after a given number of tries. This
-gives to preceding node change to test a different paths. Default is set to 1.
+gives to the preceding node receives a segment cancel and has the
+chance of testing a different path instead of waiting indefinitely.
+Default is set to 1, i.e. each link is tried one time.
+\item \emph{time to live (TTL}: when a segment request is cancelled
+along a certain path (using a segment cancel), a TTL field is
+decreased in the request packet, so that requests that have been
+denied too much times can desist, even if free links for going on are
+available. This is not only a optimisation for shortening 
+requests processes, but also solves some critical situations in which
+request packets looped in a particular path without neither succeeding
+nor failing.
 \item \emph{bootstrap\_timeout}: number of time units that a bootstrap node
@@
 path required is the one returning to the bootstrap node after having
-travelled across all the links. So, althought this is just an extreme
-situation, a good upper limit can be safely be set to NxN.
+traveled across all the links. So, although this is just an extreme
+situation, a good upper limit can be safely be set to $N \times N$.
 \item \emph{bootstrap\_immunity}: in order to avoid the failure of the whole \disr{}
 setup process, a bootstrap node should not have defective links.
-Enabling this optimisation, a bootstrap node is immune to defects.
+Enabling this optimization, a bootstrap node is immune to defects.
 We may think of a pre-bootstrap phase that properly selects (from upper
 layer via) a bootstrap node which is tested as properly connected. We
-enabled this optimisation, however empirical tests showed us that only
+enabled this optimization, however empirical tests showed us that only
 simulations using bootstrap nodes placed on edges would be heavily

### 2014-02-18 trunk/PAPER/disr.tex
Fixes

@@
 in Figure~\ref{fig:segments} shows the segment with id $1.4$, starting
-with a link connected to the node $9$, the going trought nodes
+with a link connected to the node $9$, the going through nodes
 $4$,$3$,$2$ and ending with the link connected to the node $1$. Other
@@
 We distinct between two different kind of data stored at each node:
-\emph{Dynamic Behaviour Status} (\emph{DBS}) and \emph{Local
+\emph{Dynamic Behavior Status} (\emph{DBS}) and \emph{Local
 Environment Data} (\emph{LED}).
@@
 The \emph{DBS} stores information in order to capture the dynamic
-behaviour of the node  in the context of the whole
+behavior of the node  in the context of the whole
 \disr{} execution phased. The \emph{DBS} can have the following values:
@@
 
-The \emph{LED} are like a instanst snapshot of the \disr{} algorithm at each node,
+The \emph{LED} are like an instant snapshot of the \disr{} algorithm at each node,
 consisting in the following variables:
@@
 \end{tabular}
-\caption{Example of \disr{} segment setup: Nodes status are labeled as CandidateStarting($Cs$), Candidate ($C$), Free ($F$), Assigned ($A$) and Boostrap ($B$)}
+\caption{Example of \disr{} segment setup: Nodes status are labeled as CandidateStarting($Cs$), Candidate ($C$), Free ($F$), Assigned ($A$) and Bootstrap ($B$)}
 \label{fig:disr_events}
@@
 \item{\textbf{Injecting Segment Requests}}: Each node in the
-\emph{Assigned} status can initiate a search for a segment, by sending
-a \texttt{SEGMENT\_REQUEST} across one of its free links $(c)$ (see
+\emph{Assigned} status can potentially initiate a new segment request.
+So it check its links and if a free link is found it changes its
+status to $ActiveSearching$ $(c)$, then sending
+a \texttt{SEGMENT\_REQUEST} across the link $(c)$ (see
 Figure~\ref{fig:disr_events}-e). 
-Note that each \emph{Assigned} note can inject the request just after
+Note that each \emph{Assigned} node can inject the request just after
 becoming assigned, i.e. it is not needed that the whole confirmation
-process in completed (Figure~\ref{disr_events}-f).
-Note also that nodes previosly set as \emph{CandidateStarting}, when receiving 
+process in completed (Figure~\ref{fig:disr_events}-f).
+Note also that nodes previously set as \emph{CandidateStarting}, when receiving 
 a \texttt{SEGMENT\_REQUEST} can simply cancel their
@@
 
-\section{Detailed Node behaviour Model}
+\section{Detailed Node behavior Model}
 \label{sec:execution_model}
@@
 \emph{LED}. Note that in the following, when using expression like
-``has a free link'' or ``free node'' we will assume the relationship beetween 
+``has a free link'' or ``free node'' we will assume the relationship between 
 $LED$ and $DBS$ discussed in Section~\ref{sec:disr_data}. Further, for
@@
 original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
-can learn the segment id they belong to. \emph{LED} shoud be
+can learn the segment id they belong to. \emph{LED} should be
 updated from \emph{tvisited} to \emph{visited}.

### 2014-02-18 trunk/PAPER/paper.tex
Fixed style
Fixes

@@
 %------------------------------------------------------------------------------
-\documentclass[a4]{article}
-%\documentclass[review]{elsarticle}
+\documentclass[preprint]{elsarticle}
+%\documentclass[3p]{elsarticle}
 \usepackage{lineno,hyperref}

### 2014-02-18 PAPER/introduction.tex
Removed typos

@@
 example in~\cite{patwardhan2006_1}, where instruction and data
-operands are move around the network in order to be processed.
-Independently from the particular policy chosen for routing packets,
+operands are moved around the network in order to be processed.
+Independently of the particular policy chosen to route packets,
 such networks must be able to guarantee deadlock freedom without any
@@
 
-In this work we introduce \disr{}, a Distributed Segment-based approach
-to deadlock freedom in large scale DNA self assembled networks. Our
+In this work, we introduce \disr{}, a Distributed Segment-based approach
+to deadlock freedom in large scale DNA self-assembled networks. Our
 contribution aims to achieve the classical properties of a
@@
 problem faced in this work is more general and not strictly dependent on any of the
-underlying computing architecture.
+underlying computing architectures.
 
 The paper is organized as follows: in Section~\ref{sec:related_works}
-we summarize the main approaches to topology agnostic routing. Next in
+we summarize the main approaches for topology agnostic routing. Next, in
 Section~\ref{sec:disr_concepts} are described the main elements and
-the execution model of the proposed approach.  In Section~\ref{sec:simulation}
+the execution model of the proposed approach. In Section~\ref{sec:simulation},
 simulations are carried out with the open-source tool Nanoxim to
@@
 properties and how compares to the tree-based approaches. Finally a
-draft of a architectural implementation is shown in
+draft of an architectural implementation is shown in
 Section~\ref{sec:implementation} to evaluate the feasibility of the

### 2014-02-18 trunk/PAPER/disr.tex
fixes

@@
 in Figure~\ref{fig:segments} shows the segment with id $1.4$, starting
-with a link connected to the node $9$, the going through nodes
-$4$,$3$,$2$ and ending with the link connected to the node $1$. Other
+with a link connected to the node $9$, traversing nodes
+$4$, $3$, $2$ and ending with the link connected to the node $1$. Other
 segments depicted are $9.2$ (link,node $10$,link) and $9.3$
-(link from $9$ ,$8$,link,$7$,link,$6$,link,$5$,link to the $1$). Note
+(link from $9$, node $8$, link, node $7$, link, node $6$, link, node $5$, link to the $1$). Note
 also that start/ending link can coincide and a segment can also be
@@
 
-\section{Detailed Node behavior Model}
+\section{Detailed Node Behavior Model}
 \label{sec:execution_model}
@@
 ``has a free link'' or ``free node'' we will assume the relationship between 
-$LED$ and $DBS$ discussed in Section~\ref{sec:disr_data}. Further, for
+$LED$ and $DBS$ discussed in Section~\ref{ssec:disr_data}. Further, for
 each packet type all the cases not explicitly listed can simply be
@@
 \disr{} execution model. A complete list of these cases can be checked
-in the environment simulator source code at~\ref{nanoxim}.
+in the environment simulator source code at~\cite{nanoxim}.
 
 \subsection{Receiving a \texttt{STARTING\_SEGMENT\_REQUEST}}
-
 The request for the first segment should be managed differently since
@@
 node must actually perform this action.  The point above is is
-strictly related to the general question: which level of “parallelism”
-should we allow in \disr{} ? The adopted approach is that, although
+strictly related to the general question: which level of
+parallelism should we allow in \disr{}? The adopted approach is that, although
 the nature of \disr{} itself is intrinsically parallel, the use of
@@
 \disr{} is parallel when needed, but it does not exploit parallelism
-as an “improving feature”. When not needed, things should be
+as an ``improving feature''. When not needed, things should be
 serialized. For example: when a node is “ready searching” could start

### 2014-02-18 PAPER/introduction.tex
Fixed typos, hilighted some doubts

@@
 skeie2004, koibuchi2003}, but while they show interesting
-performances, the low resources deadlock makes them not suitable for
-the specific DNA self assembled networks we are assuming as
-background.
+performances, the low resources available to prevent deadlocks makes them not suitable for
+the DNA self-assembled networks we are assuming as
+scenario.
 Other topology independent algorithms~\cite{schroeder1991,
-koibuchi2001, cherkasova1996} do not require any virtual channels but
+koibuchi2001, cherkasova1996} do not require any virtual channel but
 exploit the concept of ``turn prohibition''.
-In particular, authors of~\cite{Patwardhan05evaluatingthe} exploits the creation of a spanning tree of the
-topology, placing bidirectional restrictions by avoiding a packet
-to traverse the same link in both up and down directions.
+In particular, authors of~\cite{Patwardhan05evaluatingthe} exploit the creation of a spanning tree of the
+topology, placing bidirectional restrictions \hl{by avoiding a packet
+to traverse the same link in both up and down directions}.
 The hierarchical nature of this approach can lead to uneven traffic
@@
 FX~\cite{sancho2000} mitigate this
-issue, but the set of turn restrictions is still prefixed,
+issue, but the set of turn restrictions is still prefixed
 strictly depending on the particular tree root selected. 
@@
 
-In~\cite{mejia_ipdps06} authors present an approach the solves these
-limitations by allowing turn restrictions to be placed locally,
+In~\cite{mejia_ipdps06} authors present an approach that solves these
+limitations setting turn restrictions locally,
 independently from other restrictions. The whole network is
@@
 deadlock freedom while preserving network connectivity. This \emph{locality
-independence} property, avoiding the requirement of any particular tree/root
-choice, would make it the best choice for the given scenario;
+independence} property, removing the requirement of choosing a particular tree/root,
+would make this approach the best choice for the given scenario;
 however, it still requires the knowledge of the
@@
 
-The \disr{} approach presented in this work is a first attempt of
-achieving the same goals of a segment based turn prohibition  without
-requiring any topology graph or centralized execution. In particular
+The \disr{} approach presented in this work is a first attempt to
+achieve the same goals of a segment based turn prohibition without
+requiring neither the knowledge of a topology graph nor centralized execution. In particular
 \disr{} implements segment discovery and turn prohibition using a
@@
 \item At the end of the execution, no segment list is created or
-stored anywhere: each node is only aware of belonging to some segment,
-ignoring the presence of other nodes in the same segment and even the
+stored anywhere: each node is only aware of belonging to \hl{a segment | some segments},
+ignoring the presence of other nodes in the same segment and also the
 presence of other segments in the network

### 2014-02-18 trunk/PAPER/disr.tex
Fixed typos, rephrased some parts

@@
 a different segment $S_x$ and ending with a link attached to a
-node of another segment $S_z$. In other words, a segment
-a path between connecting two other different segments. The example
+node of another segment $S_z$. In other words, a segment is
+a path connecting two other different segments. The example
 in Figure~\ref{fig:segments} shows the segment with id $1.4$, starting
@@
 $4$, $3$, $2$ and ending with the link connected to the node $1$. Other
-segments depicted are $9.2$ (link,node $10$,link) and $9.3$
-(link from $9$, node $8$, link, node $7$, link, node $6$, link, node $5$, link to the $1$). Note
-also that start/ending link can coincide and a segment can also be
-formed by one single link (e.g. in $7.2$ or $5.4$).
+segments depicted are, for example, $9.2$ (link from $9$, node $10$, link to node $3$) and $9.3$
+(link from $9$, node $8$, link, node $7$, link, node $6$, link, node $5$, link to node $1$). Note
+also that start/ending links can coincide and a segment can also be
+formed by one single link (e.g. the case of $7.2$ and $5.4$).
 An exception to the rule that a segment must connect two other
@@
 A detailed description of the \disr{} execution model as depicted in
-the Figure~\ref{fig:disr_events} will be discussed in
-Subsection~\ref{sub:phases}. Roughly speaking, the execution of can be described as the execution
-of the following phases: 
+Figure~\ref{fig:disr_events} will be discussed in
+Subsection~\ref{sub:phases}. Roughly speaking, the execution phases consist of:
 \begin{enumerate}
 \item Injection of the \disr{} process from an upper layer to set a \emph{bootstrap
-node} 
-\item Broadcasting and confirmation to create the first segment of the subnet
+node}.
+\item Broadcasting and confirmation to create the first segment of the subnet.
 \item Parallel requests starting from assigned node to discover other
@@
 \item Turn prohibition in each confirmed segment.
-\item Draining of remaining packet due timeouts
+\item Draining of remaining packet due to timeouts.
 \end{enumerate}
@@
 
-We distinct between two different kind of data stored at each node:
+We distinct between two different kinds of data stored in each node:
 \emph{Dynamic Behavior Status} (\emph{DBS}) and \emph{Local
@@
 
-The \emph{DBS} stores information in order to capture the dynamic
+\hl{The \emph{DBS} stores information in order to capture the dynamic
 behavior of the node in the context of the whole
-\disr{} execution phased. The \emph{DBS} can have the following values:
+\disr{} execution phased.| \emph{DBS} information represent node's status and are related to the current execution phase}. 
+The \emph{DBS} can have the following values:
 
@@
 an upper layer via. 
-\item{\emph{ActiveSearching}}: a node from which a find process of new segments has
+\item{\emph{ActiveSearching}}: a node from which a new segments searching process has
 been started and not yet cancelled or confirmed. 
-\item{\emph{Candidate}}: a node currently candidate for belonging to some segment
-, but not being itself the node from which the find process was started. 
+\item{\emph{Candidate}}: a node currently candidate to be part of a segment, but not being itself the node from which the searching process was started. 
 \item{\emph{CandidateStarting}}: same as above, but the node is currently being considered as candidate
@@
 
-The \emph{LED} are like an instant snapshot of the \disr{} algorithm at each node,
+The \emph{LED} are a kind of instant snapshot of the execution of \disr{} algorithm, taken in each node,
 consisting in the following variables:
+
 \begin{itemize}
-\item{\emph{segID}}:a value used to specify the segment to which the
-node has been assigned or is candidate for being assigned.
+\item{\emph{segID}}: a value used to specify the segment to which the
+node has been assigned or is currently candidate to be part of.
 \item{\emph{visited}}: a boolean value. When \emph{true}
@@
 the segment for which the link is candidate. When \texttt{NULL}, the link is
-not candidate for any segment, i.e. maybe already assigned
-or free.
+not candidate for any segment, i.e. it has already been assigned or it is free.
 \end{itemize}
@@
 \begin{itemize}
-\item \emph{packet\_type}: encodes the meaning of the control message
-\item \emph{seg\_ID}: the id of the segment associated to the \disr{} control message
-\item \emph{src\_id}: the id of the node that originated the packet
+\item \emph{packet\_type}: encodes the meaning of the control packet.
+\item \emph{seg\_ID}: \hl{the id of the segment associated to the \disr{} control message}.
+\item \emph{src\_id}: the id of the node that originated the packet.
 \end{itemize}
 
-As regards \emph{packet\_type} field, we can have the following control packets:
+For what concerns\emph{packet\_type} field, we can have the following control packets types:
 \begin{itemize}
 \item{\texttt{STARTING\_SEGMENT\_REQUEST}}: Injected by the bootstrap
-node to when searching for the first segment. 
+node when searching the first segment. 
 \item{\texttt{STARTING\_SEGMENT\_CONFIRM}}: used when establishing
 the starting segment. 
-\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (not the
+\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (\hl{which is} not the
 first)
@@
 A quantitative analysis of the resources needed to implement and
-manage these structures is presented in Section~\ref{sec:implementation} when
-discussing the impact of the \disr{} control logic and storage on
-hardware implementation of the node.
+manage these structures is presented in Section~\ref{sec:implementation} where is discussed 
+the impact of \disr{} control logic and storage on the
+node's hardware implementation.
 
@@
 The \disr{} control packets described in the previous subsection trigger
-node events, which eventually change $DBS$ status according to the
-current value of $LED$ variables and the type of the packet received.
+node events, which \hl{eventually} change $DBS$ status according to the
+current value of $LED$ variables and the type of packet received.
 The main \disr{} phases, together with a reference to the particular
@@
 \end{tabular}
-\caption{Example of \disr{} segment setup: Nodes status are labeled as CandidateStarting($Cs$), Candidate ($C$), Free ($F$), Assigned ($A$) and Bootstrap ($B$)}
+\caption{Example of \disr{} segment setup: Nodes' status is labeled as CandidateStarting($Cs$), Candidate ($C$), Free ($F$), Assigned ($A$) or Bootstrap ($B$)}
 \label{fig:disr_events}
@@
 packet along the link from which it received the
-\texttt{STARTING\_SEGMENT\_REQUEST} and becomes $Assigned$ $(l)$. Each
-node receiving the confirm do same by changing its own status
+\texttt{STARTING\_SEGMENT\_REQUEST} and becomes \emph{Assigned} $(l)$. Each
+node receiving the confirmation does the same by changing its own status
 to \emph{Assigned}(Figure~\ref{fig:disr_events}-c). So the confirmation packet is sent back from
@@
 So it check its links and if a free link is found it changes its
-status to $ActiveSearching$ $(c)$, then sending
-a \texttt{SEGMENT\_REQUEST} across the link $(c)$ (see
+status to $ActiveSearching$ $(c)$ and then sends
+a \texttt{SEGMENT\_REQUEST} across the free link $(c)$ (see
 Figure~\ref{fig:disr_events}-e). 
 Note that each \emph{Assigned} node can inject the request just after
-becoming assigned, i.e. it is not needed that the whole confirmation
+becoming \emph{Assigned}, i.e. it is not needed that the whole confirmation
 process in completed (Figure~\ref{fig:disr_events}-f).
-Note also that nodes previously set as \emph{CandidateStarting}, when receiving 
+Note also that nodes previously set as \emph{CandidateStarting}, when receive
 a \texttt{SEGMENT\_REQUEST} can simply cancel their
-status and set as $Candidate$ for that request, since this new
+status and set themselves as $Candidate$ for that request, since this new
 request means that the first starting segment has already been found $(h)$. 
-\item{\textbf{Segment Confirmation}}: The find process is successful
+\item{\textbf{Segment Confirmation}}: The segment searching process is successful
 when an already \emph{Assigned} node receives the
@@
 (Figure~\ref{fig:disr_events}-g), while the
-node remain $Assigned$ (since it could confirm more segments). Each node
-previously set as $Candidate$ for that segment id, when receiving the
-a confirmation packet changes its status to $Assigned$ $(m)$ and forwards back
+node remains $Assigned$ \hl{(since it could confirm more segments)}. Each node
+previously set as $Candidate$ for that segment id, when receives a confirmation packet changes its status to \emph{Assigned} $(m)$ and send back
 the same confirmation until it reaches the initiator of the request,
@@
 
-\item{\textbf{Failing while searching a segment}}: this happen when a node received a \texttt{SEGMENT\_REQUEST} packet but
-matches one of two the following conditions: first, the node is $Free$ but has no
+\item{\textbf{Failing while searching a segment}}: this happen when a node receives a \texttt{SEGMENT\_REQUEST} packet but
+matches one of two the following conditions: the node is $Free$ but has no
 more suitable free links (thus can’t forward the
 \texttt{SEGMENT\_REQUEST})$(f)$; the node
-is already \emph{Candidate} with another segment id, i.e. another find
-process.  In all these cases the node
+is already \emph{Candidate} with another segment id, i.e. is part of another searching process. In all these cases the node
 sends back a \texttt{SEGMENT\_CANCEL} along the incoming link (see at
@@
 In this Section we provide further details about \disr{}
-execution model, describing the internal behavior implemented at
+execution model, describing the internal behavior implemented in
 each node. Note that this also corresponds exactly to what should be
-implemented from the node-hardware perspective, as discussed in
+implemented from the \hl{node-hardware} perspective, as discussed in
 Section~\ref{sec:implementation}.
 
-The \emph{LED} variables at each node
-($segID$,$visited$,$tvisited$,\emph{link\_visited[]},\emph{link\_tvisited[]})
-are initially set as \texttt{NULL}, so the node and each of its links
-are considered as free.
-The only node that makes exception is the bootstrap node, initialized
+The \emph{LED} variables in each node
+($segID$, $visited$, $tvisited$, \emph{link\_visited[]}, \emph{link\_tvisited[]})
+are initially set as \texttt{NULL}, so the node and all its links
+are considered as \emph{Free}.
+The only node that makes an exception is the bootstrap node, initialized
 in the \emph{Bootstrap} status. All the subsequent events happening at
@@
 \item The node is \emph{CandidateStarting} with the same
-\emph{segID} and \emph{src\_id} of the packet is equal to node id:
+\emph{segID} and \emph{src\_id} of the packet is equal to the node id:
 this means that the node was the initiator of the request, thus a starting segment has
@@
 \item The node is \emph{CandidateStarting}, with the same \emph{segID} of the
-packet but the \emph{src\_id} field is different from node id: since the node is candidate with the same id, it means
+packet but the \emph{src\_id} field is different from the node id: since the node is candidate with the same id, it means
 that it already accomplished the task of propagating that kind of
-packets, thus can simply ignore the event thrashing the packet.  
+packets, thus can simply ignore the event dropping the packet.  
 \item The node is \emph{Candidate}, with a different \emph{segID}: 
-this simply means that the starting segment request just received is deprecated,
-because the node has already accepted a non-starting segment request
-that originated from another \emph{Assigned} nodes.
+this simply means that the \texttt{STARTING\_SEGMENT\_REQUEST} just received is deprecated,
+because the node has already accepted a non-starting segment request originated from another \emph{Assigned} node.
 \item The node is \emph{Assigned}, with a different \emph{segID}:
@@
 \subsection{Receiving a \texttt{SEGMENT\_REQUEST}}
-When a node receives a \texttt{SEGMENT\_REQUEST}, the are the following cases:
+When a node receives a \texttt{SEGMENT\_REQUEST}, there are the following cases:
 
@@
 \item The node is \emph{Candidate}: it should discard the packet sending
-back a \texttt{SEGMENT\_CANCEL} 
+back a \texttt{SEGMENT\_CANCEL}.
 \item The node is \emph{Free} and has free
@@
 %begins with the starting node, which is marked as \emph{visited} by the SR
-%algorithm when searching for the first (starting) segment. Remember
+%algorithm when searching the first (starting) segment. Remember
 %that the first segment of a subnet is a loop beginning with the
@@
 When the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
-the packet: the node set itself as $Assigned$ to the segment $SegID$. Further, it should forward this packet to the link where the
+the packet: the node set itself as $Assigned$ to the segment $segID$. Further, it should forward this packet to the link where the
 original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
-can learn the segment id they belong to. \emph{LED} should be
+can learn the id of the segment they belong to. Then, \emph{LED} should be
 updated from \emph{tvisited} to \emph{visited}.
@@
 \subsection{Receiving a \texttt{SEGMENT\_CANCEL}}
-When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that
-searching for a segment along that path was unsuccessful. But if the
+When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that the research
+for a segment along that path was unsuccessful. But if the
 node still has some other free link to try, it should forward a
-\texttt{SEGMENT\_REQUEST} to the that link. So a node forwards back
+\texttt{SEGMENT\_REQUEST} to the those links. So a node forwards back
 the \texttt{SEGMENT\_CANCEL} packet along the link that originated the
@@
 In the processes described above, we assumed that each node in the
-\emph{Assigned} status can start a find segment process by injecting a
+\emph{Assigned} status can start a segment searching process by injecting a
 \texttt{SEGMENT\_REQUEST}. However, a more accurate decision when
 defining \disr{} should be made in order to decide whether or not the
-node must actually perform this action.  The point above is is
-strictly related to the general question: which level of
-parallelism should we allow in \disr{}? The adopted approach is that, although
-the nature of \disr{} itself is intrinsically parallel, the use of
-parallelism makes things work in a more complex way. In other words,
+node must actually perform this action. The point above is
+strictly related to a general question: which level of
+parallelism should we allow in \disr{}? The adopted approach, although
+the nature of \disr{} itself is intrinsically parallel, is that the use of
+parallelism makes things working in a more complex way. In other words,
 \disr{} is parallel when needed, but it does not exploit parallelism
 as an ``improving feature''. When not needed, things should be
-serialized. For example: when a node is “ready searching” could start
-several find segment process associated to the same segment, one for
-each free link. But serializing this by investigating the free links
-in order could be a simplest solution. We refer to this saying that we
+serialized. For example: when a node is ``ready to search'' it could start
+several segment searching processes associated to the same segment, one for
+each free link. But serializing this operation, by investigating the free links
+in order, could be a simpler solution. We refer to this saying that we
 avoid intra-node parallelism.  Note that while intra-node parallelism
@@
 complex than allowing the parallelism itself. Imagine for example the
-effort of trying to coordinate nodes so that an unique finding node
+effort generated trying to coordinate nodes so that an unique segment searching
 process is actually running in the whole subnet. Thus, in contrast to

### 2014-02-18 PAPER/introduction.tex
general fixing

@@
 what is going on, i.e. the status of the \disr{} execution is
-collectively distributed among the nodes
+collectively distributed among the nodes.
 \item  No defect map and/or topology graph is used as input,
 thus, the topology has to be discovered \emph{while} segments are
-created
+created.
 \item At the end of the execution, no segment list is created or
@@
 ignoring the presence of other nodes in the same segment and also the
-presence of other segments in the network
+presence of other segments in the network.
 \end{itemize}

### 2014-02-18 trunk/PAPER/implementation.tex
general fixing

--- 2014-02-12 trunk/PAPER/implementation.tex
@@
 
-A possible hardware implementation of the DiSR algorithm will be
-described in this section.  Before enter in to detail of  DiSR
-architecture,  an idea of node structure tailored for this particular
-scenario, can be found depicted in Fig.~\ref{fig:node_structure}. In
-particular, such node should have the following foundamental elements:
+A possible hardware implementation of \disr{} algorithm will be
+described in this section. Figure~\ref{fig:node_structure} depicts the general
+structure of a node in the particular scenario of DNA nano Network-On-Chip. In particular such a node
+is composed by the following fundamental elements:
 
@@
 
-\item I/O Buffers-Trasceivers: These elements, one for
-each port,  are responsible of data transmission between neighbours
-nodes. The packets received or sent are stored in specifieds buffers
-named input and output buffers respectivelly.
+	\item \textbf{I/O Buffers-Transceivers:} These elements, one for
+	each port,  are responsible for data transmission with neighbors
+	nodes. The packets received or sent are stored in specific buffers
+	named input and output buffers respectively.
 
-\item Switch Matrix: driven by a switch controller, enables the
-reciprocal connections beetween the devices inside the node. Before
-the creation of segments, such controller receives information from
-DiSR block.  After this phase, the switch controller will be driven by
-the block wich implements the routing algorithm. The Switch matrix is
-essentially a series of multiplexers and demultiplexers.
+	\item \textbf{Switch Matrix:} Driven by a switch controller, it enables the
+	reciprocal connections among devices inside the node. Before segments'
+	creation, this controller receives information from
+	\disr{} block. After this phase, the switch controller will be driven by
+	the block implementing the routing algorithm. The \emph{Switch Matrix} is
+	essentially composed of a series of multiplexers and demultiplexers.
 
-\item : Processing Element (PE):Is strictly related to the node
-functionality  and role inside a given network, e.g. being a
-computation or storage node.
+	\item  \textbf{Processing Element (PE):} Is strictly related to the
+	functionality and role that the node cover inside a given network (e.g. being a
+	computation or storage node).
 
-\item DiSR-Routing: The DiSR block contains all the hardware, control
-logic and configuration registers, related to the implementation of the
+	\item \textbf{\disr{}-Routing:} The \disr{} block contains all the hardware, control
+	logic and configuration registers, needed by the implementation of the
 	proposed approach. The routing algorithm receives information
-from DiSR  wich indicates the status of the segments that interests a
-particular node. The routing operation will take in account of these
-informations in order to perform a deadlock-free routing. Both Routing
-and DiSR are connected to the switch matrix in order to receive
+	from \disr{}  which indicates the status of segments related to a
+	particular node. Routing operations will take into account these
+	information to obtain deadlock freedom. Both Routing
+	and \disr{} are connected to the \emph{Switch Matrix} in order to receive
 	packets from the input buffer. Since the packets are processed one at
-a time, a specific arbiter should be present within the switch matrix
+	a time, a specific arbiter should be present within the \emph{Switch Matrix}
 	controller.
@@
   \includegraphics[width=0.45\textwidth]{pictures/node_structure.eps}
-  \caption{A possible node structure tailored for a DNA nanonetwork.}
+  \caption{A possible node structure tailored for a DNA nano Network-On-Chip.}
  \label{fig:node_structure}
@@
 
-To give a basic estimate of the overhead needed we will focus on DiSR-
-specific components, that is, the control logic and configuration
-registers needed to implement DiSR. In Figure~\ref{fig:implementation}
-is shown a sketch of the  architecture, which mainly consist in the
+To give a basic estimate of the overhead needed we focus on \disr{}-
+specific components namely the control logic and configuration
+registers needed to implement \disr{}. Figure~\ref{fig:implementation}
+shows an architecture sketch, which mainly consist in the
 following building elements:
@@
 	\item \textbf{DBS block:}
-	It takes trace of the DBS state machine, 
-	consisting of a 3-bit register (to cover six DBS values) and the 
-	required combinational logic. This block receives signals from 
-	stored packets  in order to decode the packet type, and from 
-	the control circuitry to change its status.
-	The bootstrap node is selected by setting the boot signal to high
-	during the initialization phase.
+
+	It takes trace of the DBS state machine, consisting of a 3-bit
+	register (to cover six DBS values) and the  required combinational
+	logic. This block receives signals from  stored packets  in order
+	to decode the packet type, and from  the control circuitry to
+	change its status. The bootstrap node is selected by setting the
+	boot signal to high during the initialization phase.
 
 	\item \textbf{LED registers:}
-	A set of registers store the \emph{LED} listed in the
-	section~\ref{sec:disr_concepts}.  In particular, in the
-	link\_visited[] table, can be pointed out the presence of two  
-	particular registernamed \emph{tflag} and \emph{busy}.  The Latter
-	is used to indicate if a specific port is alredy visited or tvisited and
-	the former indicates specifically if the node is visited or tvisited.
+	A set of registers store the \emph{LED} defined in
+	section~\ref{sec:disr_concepts}.  In the
+	link\_visited[] table, we defined two specific registers named
+	\emph{tflag} and \emph{busy}. While the first one indicates
+    if the specific port of a segment is already candidate or assigned,
+    the second one records if a specific port is already \emph{visited} or \emph{tvisited}.
 
     \item \textbf{Control circuitry:}
-    This circuitry decodes the the      incoming packet, the LED
-	registers and the DBS,     updating them when required. This block
-	drives the LED register   to store or, to read the LED data
-	according with     \emph{write enable (WE)} or \emph{read enable (RE)}
+    This circuitry decodes incoming packet, LED
+	registers and DBS, updating them when required. This block
+	drives LED register according with \emph{write enable (WE)} or \emph{read enable (RE)}
 	signals. Then, the resulting \emph{Ctrl-Out} drives the other
-	communication resources for actuating the DiSR routing operation.
+	communication resources to actuate \disr{} routing operations.
 
 	\item \textbf{Packager:}
-	Essentially is a set of registers and multiplexers. Starting from
-	an incoming packet stored in the input buffer, it updates the
-	content of the packet before the retransmission to   a destination
-	node.  In some cases, this circuitry build the packet from the
-	scratch.  For example this happens when a node is bootsrap and for
-	the first time it should inject a
-	\emph{strating\_segment\_request}. In Fig.~\ref{fig:packager} is
-	shown the architecture of such packager block. When a packet is
-	created for the first time, the multiplexers driven by the
-	controller select the information coming from the internal node
-	such as the \emph{soruce\_ID}. In this situation the TTL field
-	should be resetted to its initial value and the \emph{segment\_ID}
+	Essentially it is a set of registers and multiplexers. Starting from
+	an incoming packet stored in the input buffer, it updates packet's
+	content before retransmission to a destination
+	node.  In some cases, this circuitry builds the packet from
+	scratch e.g. when a node is bootstrap and for
+	the first time it should inject a \emph{starting\_segment\_request}. 
+	Figure~\ref{fig:packager} depicts the architecture of this
+	block. When a packet is created for the first time, the multiplexers 
+	driven by the controller, will select information incoming from an internal 
+    node such as the \emph{source\_ID}. In this situation the 
+	TTL field should be reset to its initial value and the \emph{segment\_ID}
 	is composed by the node ID and by the output port identification 
@@
 
-While the elements mentioned above are part of the DiSR circuitry, 
-the other devices depicted in Fig.~\ref{fig:implementation} like the 
-multiplexer and demultiplexer are implemented outside DiSR.
-In particular, such components will be within the switch matrix 
-(refers to the Fig~\ref{fig:node_structure}).
+While the elements mentioned above are part of the \disr{} circuitry,
+the other devices depicted in Figure~\ref{fig:implementation} like the
+multiplexer and demultiplexer are implemented outside \disr{}. In
+particular, such components will be inside the \emph{Switch Matrix} (see Figure~\ref{fig:node_structure}).
 
@@
   \includegraphics[width=0.40\textwidth]{pictures/pipeline.eps}
-  \caption{Pipeline description of DiSR operations}
+  \caption{Pipeline description of \disr{} operations.}
  \label{fig:pipeline}
@@
 
-Each just described building block, reacts with the rising edge  of
-the\emph{clock signal}. An asynchronous system \emph{reset} signal is
-also present for restoring all registers to their default values. When
-this last signal is set, the DBS state machines for each network's
+All the blocks described above, reacts with the rising edge of
+the \emph{clock signal}. An asynchronous system \emph{reset} signal is
+also present to restore all registers to their default values. When
+this signal is set, DBS state machines for each network
 node are set as \emph{Free}.  
-In Fig.~\ref{fig:pipeline} is described the pipeline structure of the
-DiSR architecture. The packet incoming from the neighbours node, or
-locally generated will be send to the DBS state machine in order to te
-ensure the status commutation. While the DBS update its state,  in the
-next clock cycle the control circuitry will update the Led status and
-will drive the sitch matrix in order to send eventually the packets to
+Figure~\ref{fig:pipeline} is shows the pipeline structure of the
+\disr{} architecture. Packets incoming from neighbor nodes (or
+generated locally) are sent to the DBS state machine in order to
+ensure the status commutation. While DBS updates its state, in the
+next clock cycle the control circuitry will update LED registers status and
+will drive the \emph{Switch Matrix} in order to send eventually the packets to
 the right output buffer.
@@
 
-As discussed above, one of the main design challenge of DNA Self-
-Assembled systems is the limited resource available to implement both
+As discussed above, one of the main design challenges of DNA Self-
+Assembled systems is the limited number of resources available to implement both
 computations and routing decisions for each node. Assuming a budget of
 $10^4$ CNFETs for each network's node~\cite{liu_jetcs}  we estimated
-the required resources for implementing the entire DiSR block. The RTL
+the required resources to implement the entire \disr{} block. The RTL
 description of the circuitry described in the last section (with an
-hardware description language)  of the DiSR circuitry has been written
-and synthesized at gate-level. Considering the specific layout of each
-single logic elements (NAND, full-adder, latch etc.), it has been
-possible to get a rough estimate of the number of transistors
-necessary to implement the DiSR logic. Figure~\ref{fig:imp_trend}
-shows the results of synthesis in terms of number of devices (CNFETs)
-versus the number of network nodes while the network scales up from
-$10\times10$ to $100\times100$ nodes.
+hardware description language)  of the \disr{} circuitry has been written
+and synthesized at gate-level using \emph{Synopsys Design Compiler} with 
+a generic technology library (GTECH).
+Considering the specific layout of each single logic elements  (NAND,
+full-adder, latch etc.), it has been possible to get a rough estimate
+of the number of transistors necessary to implement \disr{} logic.
+Figure~\ref{fig:synthesys} shows the results of synthesis in terms of
+number of devices (CNFETs) versus the number of network nodes while
+the network scales up from $10\times10$ to $100\times100$ nodes.
 
@@
   \includegraphics[width=0.50\textwidth]{pictures/synthesis.eps}
-  \caption{Number of network's node (N) vs number of CNFETs.}
+  \caption{Network size vs number of CNFETs necessary to implement
+  the \disr{} circuitry.}
  \label{fig:synthesys}
@@
 
-In particular, observing the Figure~\ref{fig:imp_trend} can 
-be pointed out that the proposed implementation occupies about 17,5\% of the node budget. In particular the main contribution is due to the controller circuitry followed by LED registers.
-Further, more than the absolute number of devices itself, it is interesting to
-observe that the circuitry
-complexity which implements the DiSR algorithm increases with a slowly
-growing trend.  
-An intuitive explanation of this is the relatively simple logic of
-DiSR, whose behaviour is almost code on scalable storage structures.
-For example, the number of registers
+In particular, Figure~\ref{fig:synthesys} shows that the proposed 
+implementation occupies about 17,5\% of our node budget. 
+The main contribution is due to the controller circuitry followed by LED registers. 
+Further, more than the
+absolute number of devices itself, it is interesting to observe that
+the circuitry complexity which implements \disr{} algorithm increases
+with a slowly growing trend. An intuitive explanation of this is the
+relatively simple logic of \disr{}, whose behavior is almost coded on
+scalable storage structures. For example, the number of registers
 implementing the \emph{link\_visited[]} and \emph{link\_tvisited[]}
 table follow the logarithmic function $N_{reg}=N_{port} \cdot
-log_2(N)$ where \emph{Nport} is the number of the router’s ports, N is
+log_2(N)$ where \emph{Nport} is the number of the router’s ports and N is
 the number of network’s nodes.
 
-In order ha have estimate the maximum working clock frequency for the implemented
-circuitry, the \cite{deng_isscc07}
+In order to have an idea of the maximum working clock frequency for
+the implemented circuitry, timing results can be obtained from a 
+gate-level netlist. Since a complete technology library useful for
+commercial synthesis tool (e.g. Design Compiler) is not available for
+this particular technology, we have
+synthesized the RTL description of \disr{}, with a standard 32~nm CMOS
+library, obtaining a delay of about $\mathrm{\tau_{\disr{}}=10} \ FO4$
+(fan-out of four). Considering the results obtained
+in~\cite{deng_isscc07}, which reports the ratio in terms of FO4
+between a standard 32~nm CMOS technology and a carbon nanotube ones, 
+rough delay estimation can be obtained. In particular in such work 
+has been reported a ratio of:  
+\begin{equation}
+\mathrm{\frac{FO4_{CMOS}}{FO4_{CNFET}}=2}  
+\end{equation}
+Considering that F04 CMOS is about 30~ps, and the results of last
+equation, a FO4 for the CNFET case is equal to about 15~ps, the working 
+frequency can be computed as:
+\begin{equation}
+\mathrm{f_{clk}=\frac{1}{T_{max}}=\frac{1}{\tau_{\disr{}} \cdot FO4_{CNFET}}}=
+\frac{1}{10\cdot 15 \cdot 10^{-12}}=6,6 GHz
+\end{equation}
+where $\mathrm{\tau_{\disr{}}}$ is expressed in terms of FO4.
+
+Regarding the power consumption of whole \disr{} devices, 
+we avoided an accurate power analysis with the switch activity
+annotation due to the fact that \disr{} circuitry will be active 
+only once during system startup. Indeed, after the setup phase, 
+when all segments are mapped, the \disr{} block will stop its activity 
+passing all the information related to segments to the routing
+algorithm. For this reason the dynamic power falls to zero and
+the only consumption could be due to the leakage
+consumption.

### 2014-02-18 trunk/PAPER/simulation.tex
general fixing

@@
 In this section we will test the proposed \disr{} approach to demonstrate
-its effectiveness and compare it against topology agnostic approach
+its effectiveness and compare it against a topology agnostic approach
 based on spanning trees and
@@
 specific simulation environment has been developed, resulting in
-the open source and freely available project called
+the open-source and freely available project called
 Nanoxim~\cite{nanoxim}.
-Nanoxim is a SystemC tool based on a almost rewritten
+Nanoxim is a SystemC tool based on an almost rewritten
 version of the Noxim Network-on-Chip simulator~\cite{noxim}. While some
@@
 tailored for the nanoscale scenario were introduced, e.g. the ability to simulate a random
-network, the implementation of the \disr{} to obtain the segment topology
+network, the implementation of \disr{} to obtain the segment topology
 and the support for defective links and nodes.
@@
 \item {\emph{\% defective nodes}}: the probability that a node is not
-working, thus having all its links cannot be utilized during \disr{} setup.  
+working, thus having all its links not able to be utilized during \disr{} setup.  
 %Same range as defective links parameter.
-\item {\emph{Bootstrap node}}: the node used from upper layer 
-to inject the \disr{} process. When not explicitly investigating the
+\item {\emph{Bootstrap node}}: the node from upper layer that
+injects the \disr{} process. When not explicitly investigating the
 impact of each single bootstrap choice, a set representative regions have been
@@
 \item{\emph{Latency}}: this measures how the cycles required to complete the
-segment assignment scales for increasing network sizes and defect rates
+segment assignment scale for increasing network sizes and defect rates.
 \item{\emph{Bootstrap node effect}}: this evaluates the impact of the chosen
@@
 In this section we analyze the results in terms of node
-coverage and latency at different network sizes, defect rates and
+coverage and latency with different network sizes, defect rates and
 bootstrap injection points. In particular
@@
 For example Figure~\ref{fig:net} show a 30x30 network with a 25\%
-defect in which the bottom-left part cannot be reached due
-disconnected regions. Note that remaining defective nodes belonging to
+defect in which the bottom-left part cannot be reached due to
+disconnected regions. Note that the remaining defective nodes belonging to
 connected regions are successfully surrounded by \disr{} coverage; in any
@@
 version of \disr{}. On the other hand, the network size seems to have a
-limited impact when defect rate do not introduce too much disconnected
+limited impact when defect rate does not introduce too many disconnected
 regions. 
@@
 \includegraphics[width=0.70\textwidth]{pictures/net.ps}
-\caption{Covered regions in a 30x30 network with 25\% defects}
+\caption{Covered regions in a 30x30 network with 25\% of defects}
 \label{fig:net}
@@
 The number of cycles required to complete segment mapping process
-is shown in Figure~\ref{fig:results_latency}. In this case comparison
-against tree-based shows better (lower) values at different defect
-rates.  Rather than the absolute numbers, what it's more interesting
+is shown in Figure~\ref{fig:results_latency}. In this case the comparison
+against the tree-based approach shows better (lower) values at different defect
+rates. Rather than the absolute numbers, what is more interesting
 to observe is how \disr{} latency scales with network size. For example,
@@
 also how the effect of defect rate is increasing until the threshold
-of $0.25$ is reached, meaning that until that limit \disr{} finds it more
-and more difficult to complete the process due increasing defective
-paths, but still discover new segments when let running for a more
+of $0.25$ is reached, meaning that until that limit \disr{} finds 
+the completion of the process more and more difficult due to the increasing defective
+paths, but it still discover new segments if it runs for an
 extended amount of cycles. This behavior is not reported in the RPF
-based approach, meaning that a tree based approach, although starting
+based approach, meaning that a tree-based approach, although starting
 from higher values, is less affected by defect rates (when low rates
 are considered).
-After the $0.25$ threshold, the impact of entire disconnected regions
+After the $0.25$ threshold, the impact of disconnected regions
 becomes predominant and both approaches become faster in completing
@@
 Finally, Figure~\ref{fig:results_bootstrap} visually represents the
-stability of the approach against choices of a different bootstrap
-node in a 10x10 network.  This is an important aspect to evaluate when
+stability of the approach against a different bootstrap node choice
+in a 10x10 network. This is an important aspect to evaluate 
 considering that one of the main advantages of \disr{} against all the
-tree based approaches should be the ability of choosing whatever
+tree-based approaches is the possibility of choosing whatever
 bootstrap node, without having to care about the role assumed in the
-future by the chosen root node.  In other words, after segments have
+future by the chosen root node. In other words, after the segments have
 been established, the bootstrap node is like every other node, i.e. it
@@
 and high defect profiles, demonstrate a relatively limited
-impact of the bootstrap choice in the low/medium scenarios, while a
+impact of the bootstrap node choice in the low/medium scenarios, while a
 $30\%$ instability is found for very high defect rates. This also
@@
 Some optimization parameters, which demonstrated to improve the \disr{}
-results have been fixed to some good values, but are not subject to
-further investigation; once again the focus here is not the
-optimal set of segments, but just demonstrating a working approach. 
-These are optimizations are:
+results, have been fixed to some good values and are not subject to
+further investigation in this paper; once again the focus here is not the
+optimal setup of segments, but just demonstrating a working approach. 
+These parameters are:
 \begin{itemize}
 \item \emph{cycle\_links}: max number of retries across the set of links of
-each node. While searching for a free link due an incoming request,
-the same request is cancelled after a given number of tries. This
-gives to preceding node change to test a different paths. Default is set to 1.
+each node. While searching for a free link due to an incoming \texttt{SEGMENT\_REQUEST},
+the request itself is cancelled after a given number of tries. \hl{This
+gives to the preceding node, that receives a \texttt{SEGMENT\_CANCEL}, the
+chance to test a different path instead of waiting indefinitely.}
+Default value is set to 1, i.e. each link is tried one time.
+\item \emph{time to live (TTL)}: when a segment request is cancelled
+along a certain path (using a \texttt{SEGMENT\_CANCEL}), a TTL field is
+decreased in the request packet, so that requests that have been
+denied too much times can desist, even if free links are
+available. This is not only an optimization to shorten
+requests' processes, but also solves some critical situations in which
+request packets are blocked in routing loops in a particular path.
 \item \emph{bootstrap\_timeout}: number of time units that a bootstrap node
@@
 traveled across all the links. So, although this is just an extreme
-situation, a good upper limit can be safely be set to NxN.
+situation, a good upper limit can be safely be set to $N \times N$.
 \item \emph{bootstrap\_immunity}: in order to avoid the failure of the whole \disr{}
@@
 Enabling this optimization, a bootstrap node is immune to defects.
-We may think of a pre-bootstrap phase that properly selects (from upper
+We may think about a pre-bootstrap phase that properly selects (from upper
 layer via) a bootstrap node which is tested as properly connected. We
-enabled this optimization, however empirical tests showed us that only
+enabled this optimization, however empirical tests have shown us that only
 simulations using bootstrap nodes placed on edges would be heavily
-affected, since these are nodes starting with a lower number of links,
-e.g. corner nodes could only have two connected direction, so even a
-defective link could prevent starting segment packet to return to
-bootstrap to close the loop a create the segment.
+affected by similar issues since these nodes start with a lower number of links,
+e.g. corner nodes could only have two connected direction, so even a \hl{single}
+defective link could prevent a starting segment packet from coming back to the
+bootstrap node to close the loop and create the \hl{first} segment.
 \end{itemize}

### 2014-02-18 PAPER/disr.tex
Changed $...$ to \emph{...} when needed

@@
 a different segment $S_x$ and ending with a link attached to a
-node of another segment $S_z$. In other words, a segment
-a path between connecting two other different segments. The example
+node of another segment $S_z$. In other words, a segment is
+a path connecting two other different segments. The example
 in Figure~\ref{fig:segments} shows the segment with id $1.4$, starting
-with a link connected to the node $9$, the going through nodes
-$4$,$3$,$2$ and ending with the link connected to the node $1$. Other
-segments depicted are $9.2$ (link,node $10$,link) and $9.3$
-(link from $9$ ,$8$,link,$7$,link,$6$,link,$5$,link to the $1$). Note
-also that start/ending link can coincide and a segment can also be
-formed by one single link (e.g. in $7.2$ or $5.4$).
+with a link connected to the node $9$, traversing nodes
+$4$, $3$, $2$ and ending with the link connected to the node $1$. Other
+segments depicted are, for example, $9.2$ (link from $9$, node $10$, link to node $3$) and $9.3$
+(link from $9$, node $8$, link, node $7$, link, node $6$, link, node $5$, link to node $1$). Note
+also that start/ending links can coincide and a segment can also be
+formed by one single link (e.g. the case of $7.2$ and $5.4$).
 An exception to the rule that a segment must connect two other
@@
 \begin{itemize}
-\item \emph{packet\_type}: encodes the meaning of the control message
-\item \emph{seg\_ID}: the id of the segment associated to the \disr{} control message
-\item \emph{src\_id}: the id of the node that originated the packet
+\item \emph{packet\_type}: encodes the meaning of the control packet.
+\item \emph{seg\_ID}: \hl{the id of the segment associated to the \disr{} control message}.
+\item \emph{src\_id}: the id of the node that originated the packet.
 \end{itemize}
 
-As regards \emph{packet\_type} field, we can have the following control packets:
+For what concerns\emph{packet\_type} field, we can have the following control packets types:
 \begin{itemize}
 \item{\texttt{STARTING\_SEGMENT\_REQUEST}}: Injected by the bootstrap
-node to when searching for the first segment. 
+node when searching the first segment. 
 \item{\texttt{STARTING\_SEGMENT\_CONFIRM}}: used when establishing
 the starting segment. 
-\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (not the
-first)
+\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (\hl{which is} not the
+first).
 \item{\texttt{SEGMENT\_CONFIRM}}: used to establish a segment. 
@@
 The \disr{} control packets described in the previous subsection trigger
-node events, which eventually change $DBS$ status according to the
-current value of $LED$ variables and the type of the packet received.
+node events, which \hl{eventually} change \emph{DBS} status according to the
+current value of \emph{LED} variables and the type of packet received.
 The main \disr{} phases, together with a reference to the particular
@@
 \end{tabular}
-\caption{Example of \disr{} segment setup: Nodes status are labeled as CandidateStarting($Cs$), Candidate ($C$), Free ($F$), Assigned ($A$) and Bootstrap ($B$)}
+\caption{Example of \disr{} segment setup: Nodes' status is labeled as \emph{CandidateStarting} (\emph{Cs}), \emph{Candidate} (\emph{C}), \emph{Free} (\emph{F}), \emph{Assigned} (\emph{A}) or \emph{Bootstrap} (\emph{B})}
 \label{fig:disr_events}
@@
  node with status \emph{Bootstrap}, set by some control signal from an
-upper layer via $(a)$. When starting, this bootstrap node 
-changes its status to \emph{CandidateStarting} $(b)$, injecting a
+upper layer via \emph{(a)}. When starting, this bootstrap node 
+changes its status to \emph{CandidateStarting} \emph{(b)}, injecting a
 \texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links
@@
 \item{\textbf{Bootnode Broadcasting}}: Each node receiving a \texttt{STARTING\_SEGMENT\_REQUEST},
-when $Free$, forwards it to its free links using a flooding mechanism and
-becoming $CandidateStarting$ $(g)$.
+when \emph{Free}, forwards it to its free links using a flooding mechanism and
+becoming \emph{CandidateStarting} \emph{(g)}.
 Each of its free links is then marked as \emph{tvisited} with the segment id
@@
 packet along the link from which it received the
-\texttt{STARTING\_SEGMENT\_REQUEST} and becomes $Assigned$ $(l)$. Each
-node receiving the confirm do same by changing its own status
+\texttt{STARTING\_SEGMENT\_REQUEST} and becomes \emph{Assigned} \emph{(l)}. Each
+node receiving the confirmation does the same by changing its own status
 to \emph{Assigned}(Figure~\ref{fig:disr_events}-c). So the confirmation packet is sent back from
@@
 \item{\textbf{Injecting Segment Requests}}: Each node in the
-\emph{Assigned} status can initiate a search for a segment, by sending
-a \texttt{SEGMENT\_REQUEST} across one of its free links $(c)$ (see
+\emph{Assigned} status can potentially initiate a new segment request.
+So it check its links and if a free link is found it changes its
+status to \emph{ActiveSearching} \emph{(c)} and then sends
+a \texttt{SEGMENT\_REQUEST} across the free link \emph{(c)} (see
 Figure~\ref{fig:disr_events}-e). 
-Note that each \emph{Assigned} note can inject the request just after
-becoming assigned, i.e. it is not needed that the whole confirmation
-process in completed (Figure~\ref{disr_events}-f).
-Note also that nodes previously set as \emph{CandidateStarting}, when receiving 
+Note that each \emph{Assigned} node can inject the request just after
+becoming \emph{Assigned}, i.e. it is not needed that the whole confirmation
+process in completed (Figure~\ref{fig:disr_events}-f).
+Note also that nodes previously set as \emph{CandidateStarting}, when receive
 a \texttt{SEGMENT\_REQUEST} can simply cancel their
-status and set as $Candidate$ for that request, since this new
-request means that the first starting segment has already been found $(h)$. 
-\item{\textbf{Segment Confirmation}}: The find process is successful
+status and set themselves as \emph{Candidate} for that request, since this new
+request means that the first starting segment has already been found \emph{(h)}. 
+\item{\textbf{Segment Confirmation}}: The segment searching process is successful
 when an already \emph{Assigned} node receives the
@@
 (Figure~\ref{fig:disr_events}-g), while the
-node remain $Assigned$ (since it could confirm more segments). Each node
-previously set as $Candidate$ for that segment id, when receiving the
-a confirmation packet changes its status to $Assigned$ $(m)$ and forwards back
+node remains \emph{Assigned} \hl{(since it could confirm more segments)}. Each node
+previously set as \emph{Candidate} for that segment id, when receives a confirmation packet changes its status to \emph{Assigned} \emph{(m)} and send back
 the same confirmation until it reaches the initiator of the request,
-which then changes from $ActiveSearching$ to $Assigned$ $(d)$.
+which then changes from \emph{ActiveSearching} to \emph{Assigned} \emph{(d)}.
 
-\item{\textbf{Failing while searching a segment}}: this happen when a node received a \texttt{SEGMENT\_REQUEST} packet but
-matches one of two the following conditions: first, the node is $Free$ but has no
+\item{\textbf{Failing while searching a segment}}: this happen when a node receives a \texttt{SEGMENT\_REQUEST} packet but
+matches one of two the following conditions: the node is \emph{Free} but has no
 more suitable free links (thus can’t forward the
-\texttt{SEGMENT\_REQUEST})$(f)$; the node
-is already \emph{Candidate} with another segment id, i.e. another find
-process.  In all these cases the node
+\texttt{SEGMENT\_REQUEST})\emph{(f)}; the node
+is already \emph{Candidate} with another segment id, i.e. is part of another searching process. In all these cases the node
 sends back a \texttt{SEGMENT\_CANCEL} along the incoming link (see at
@@
 In this Section we provide further details about \disr{}
-execution model, describing the internal behavior implemented at
+execution model, describing the internal behavior implemented in
 each node. Note that this also corresponds exactly to what should be
-implemented from the node-hardware perspective, as discussed in
+implemented from the \hl{node-hardware} perspective, as discussed in
 Section~\ref{sec:implementation}.
 
-The \emph{LED} variables at each node
-($segID$,$visited$,$tvisited$,\emph{link\_visited[]},\emph{link\_tvisited[]})
-are initially set as \texttt{NULL}, so the node and each of its links
-are considered as free.
-The only node that makes exception is the bootstrap node, initialized
+The \emph{LED} variables in each node
+(\emph{segID}, \emph{visited}, \emph{tvisited}, \emph{link\_visited[]}, \emph{link\_tvisited[]})
+are initially set as \texttt{NULL}, so the node and all its links
+are considered as \emph{Free}.
+The only node that makes an exception is the bootstrap node, initialized
 in the \emph{Bootstrap} status. All the subsequent events happening at
@@
 ``has a free link'' or ``free node'' we will assume the relationship between 
-$LED$ and $DBS$ discussed in Section~\ref{sec:disr_data}. Further, for
+\emph{LED} and \emph{DBS} discussed in Section~\ref{ssec:disr_data}. Further, for
 each packet type all the cases not explicitly listed can simply be
@@
 \begin{itemize}
-\item The node is $Free$: it should set itself as
+\item The node is \emph{Free}: it should set itself as
 \emph{CandidateStarting} and forward the packet along its free links, using
-broadcasting and marking these links as $tvisited$ with $segID$ found
+broadcasting and marking these links as \emph{tvisited} with \emph{segID} found
 in the packet.
 \item The node is \emph{CandidateStarting} with the same
-\emph{segID} and \emph{src\_id} of the packet is equal to node id:
+\emph{segID} and \emph{src\_id} of the packet is equal to the node id:
 this means that the node was the initiator of the request, thus a starting segment has
@@
 to one of its free links, according to some internal ordering.
-\item The node is \emph{CandidateStarting}: same as being $Free$,
+\item The node is \emph{CandidateStarting}: same as being \emph{Free},
 since a segment request circulating in the network indicates that the
@@
 When the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
-the packet: the node set itself as $Assigned$ to the segment $SegID$. Further, it should forward this packet to the link where the
+the packet: the node set itself as \emph{Assigned} to the segment \emph{segID}. Further, it should forward this packet to the link where the
 original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
-can learn the segment id they belong to. \emph{LED} should be
+can learn the id of the segment they belong to. Then, \emph{LED} should be
 updated from \emph{tvisited} to \emph{visited}.
@@
 \subsection{Receiving a \texttt{SEGMENT\_CANCEL}}
-When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that
-searching for a segment along that path was unsuccessful. But if the
+When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that the research
+for a segment along that path was unsuccessful. But if the
 node still has some other free link to try, it should forward a
-\texttt{SEGMENT\_REQUEST} to the that link. So a node forwards back
+\texttt{SEGMENT\_REQUEST} to the those links. So a node forwards back
 the \texttt{SEGMENT\_CANCEL} packet along the link that originated the
-\texttt{SEGMENT\_REQUEST} packet $only$ when there are no more free
+\texttt{SEGMENT\_REQUEST} packet \emph{only} when there are no more free
 links to try. If this is the case, the node modifies its status from
@@
 In the processes described above, we assumed that each node in the
-\emph{Assigned} status can start a find segment process by injecting a
+\emph{Assigned} status can start a segment searching process by injecting a
 \texttt{SEGMENT\_REQUEST}. However, a more accurate decision when
 defining \disr{} should be made in order to decide whether or not the
-node must actually perform this action.  The point above is is
-strictly related to the general question: which level of “parallelism”
-should we allow in \disr{} ? The adopted approach is that, although
-the nature of \disr{} itself is intrinsically parallel, the use of
-parallelism makes things work in a more complex way. In other words,
+node must actually perform this action. The point above is
+strictly related to a general question: which level of
+parallelism should we allow in \disr{}? The adopted approach, although
+the nature of \disr{} itself is intrinsically parallel, is that the use of
+parallelism makes things working in a more complex way. In other words,
 \disr{} is parallel when needed, but it does not exploit parallelism
-as an “improving feature”. When not needed, things should be
-serialized. For example: when a node is “ready searching” could start
-several find segment process associated to the same segment, one for
-each free link. But serializing this by investigating the free links
-in order could be a simplest solution. We refer to this saying that we
+as an ``improving feature''. When not needed, things should be
+serialized. For example: when a node is ``ready to search'' it could start
+several segment searching processes associated to the same segment, one for
+each free link. But serializing this operation, by investigating the free links
+in order, could be a simpler solution. We refer to this saying that we
 avoid intra-node parallelism.  Note that while intra-node parallelism

### 2014-02-19 trunk/PAPER/disr.tex
general fixing
English fixes

@@
 
-\hl{The \emph{DBS} stores information in order to capture the dynamic
-behavior of the node in the context of the whole
-\disr{} execution phased.| \emph{DBS} information represent node's status and are related to the current execution phase}. 
+\emph{DBS} information represent node status and is related to its
+current execution phase in the context of \disr{}.
 The \emph{DBS} can have the following values:
@@
 The \disr{} approach works with a distributed mechanism which is build
-upon an exchange of small packets containing the following fields:
+upon an exchange of small control packets containing the following fields:
 \begin{itemize}
 \item \emph{packet\_type}: encodes the meaning of the control packet.
-\item \emph{seg\_ID}: \hl{the id of the segment associated to the \disr{} control message}.
-\item \emph{src\_id}: the id of the node that originated the packet.
+\item \emph{seg\_ID}: the id of the segment targeted by the \disr{} control message.
+\item \emph{src\_ID}: the id of the node that originated the packet.
+\item \emph{TTL}: a counter which makes the packet expire after a
+given number of retries.
 \end{itemize}
 
-For what concerns\emph{packet\_type} field, we can have the following control packets types:
+As regards the \emph{packet\_type} field, we can have the following control packets types:
 \begin{itemize}
@@
 the starting segment. 
-\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (\hl{which is} not the
-first)
+\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (not the first).
 \item{\texttt{SEGMENT\_CONFIRM}}: used to establish a segment. 
@@
 The \disr{} control packets described in the previous subsection trigger
-node events, which \hl{eventually} change $DBS$ status according to the
-current value of $LED$ variables and the type of packet received.
+node events, which change \emph{DBS} according to the
+current value of \emph{LED} variables and the type of packet received.
 The main \disr{} phases, together with a reference to the particular
@@
 \end{tabular}
-\caption{Example of \disr{} segment setup: Nodes' status is labeled as CandidateStarting($Cs$), Candidate ($C$), Free ($F$), Assigned ($A$) or Bootstrap ($B$)}
+\caption{Example of \disr{} segment setup: Nodes' status is labeled as \emph{CandidateStarting} (\emph{Cs}), \emph{Candidate} (\emph{C}), \emph{Free} (\emph{F}), \emph{Assigned} (\emph{A}) or \emph{Bootstrap} (\emph{B})}
 \label{fig:disr_events}
@@
 packet along the link from which it received the
-\texttt{STARTING\_SEGMENT\_REQUEST} and becomes \emph{Assigned} $(l)$. Each
+\texttt{STARTING\_SEGMENT\_REQUEST} and becomes \emph{Assigned} \emph{(l)}. Each
 node receiving the confirmation does the same by changing its own status
@@
 So it check its links and if a free link is found it changes its
-status to $ActiveSearching$ $(c)$ and then sends
-a \texttt{SEGMENT\_REQUEST} across the free link $(c)$ (see
+status to \emph{ActiveSearching} \emph{(c)} and then sends
+a \texttt{SEGMENT\_REQUEST} across the free link \emph{(c)} (see
 Figure~\ref{fig:disr_events}-e). 
@@
 a \texttt{SEGMENT\_REQUEST} can simply cancel their
-status and set themselves as $Candidate$ for that request, since this new
-request means that the first starting segment has already been found $(h)$. 
+status and set themselves as \emph{Candidate} for that request, since this new
+request means that the first starting segment has already been found \emph{(h)}. 
 \item{\textbf{Segment Confirmation}}: The segment searching process is successful
@@
 (Figure~\ref{fig:disr_events}-g), while the
-node remains $Assigned$ \hl{(since it could confirm more segments)}. Each node
-previously set as $Candidate$ for that segment id, when receives a confirmation packet changes its status to \emph{Assigned} $(m)$ and send back
+node remains \emph{Assigned} (since it could confirm other segments). Each node
+previously set as \emph{Candidate} for that segment id, when receives a confirmation packet changes its status to \emph{Assigned} \emph{(m)} and send back
 the same confirmation until it reaches the initiator of the request,
-which then changes from $ActiveSearching$ to $Assigned$ $(d)$.
+which then changes from \emph{ActiveSearching} to \emph{Assigned} \emph{(d)}.
 
 \item{\textbf{Failing while searching a segment}}: this happen when a node receives a \texttt{SEGMENT\_REQUEST} packet but
-matches one of two the following conditions: the node is $Free$ but has no
+matches one of two the following conditions: the node is \emph{Free} but has no
 more suitable free links (thus can’t forward the
-\texttt{SEGMENT\_REQUEST})$(f)$; the node
+\texttt{SEGMENT\_REQUEST})\emph{(f)}; the node
 is already \emph{Candidate} with another segment id, i.e. is part of another searching process. In all these cases the node
@@
 each node. Note that this also corresponds exactly to what should be
-implemented from the \hl{node-hardware} perspective, as discussed in
+implemented from the hardware perspective, as discussed in
 Section~\ref{sec:implementation}.
@@
 The \emph{LED} variables in each node
-($segID$, $visited$, $tvisited$, \emph{link\_visited[]}, \emph{link\_tvisited[]})
+(\emph{segID}, \emph{visited}, \emph{tvisited}, \emph{link\_visited[]}, \emph{link\_tvisited[]})
 are initially set as \texttt{NULL}, so the node and all its links
@@
 ``has a free link'' or ``free node'' we will assume the relationship between 
-$LED$ and $DBS$ discussed in Section~\ref{ssec:disr_data}. Further, for
+\emph{LED} and \emph{DBS} discussed in Section~\ref{ssec:disr_data}. Further, for
 each packet type all the cases not explicitly listed can simply be
@@
 \begin{itemize}
-\item The node is $Free$: it should set itself as
+\item The node is \emph{Free}: it should set itself as
 \emph{CandidateStarting} and forward the packet along its free links, using
-broadcasting and marking these links as $tvisited$ with $segID$ found
+broadcasting and marking these links as \emph{tvisited} with \emph{segID} found
 in the packet.
@@
 When the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
-the packet: the node set itself as $Assigned$ to the segment $segID$. Further, it should forward this packet to the link where the
+the packet: the node set itself as \emph{Assigned} to the segment \emph{segID}. Further, it should forward this packet to the link where the
 original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
@@
 the \texttt{SEGMENT\_CANCEL} packet along the link that originated the
-\texttt{SEGMENT\_REQUEST} packet $only$ when there are no more free
+\texttt{SEGMENT\_REQUEST} packet \emph{only} when there are no more free
 links to try. If this is the case, the node modifies its status from

### 2014-02-19 trunk/PAPER/simulation.tex
English fixes

@@
 each node. While searching for a free link due to an incoming \texttt{SEGMENT\_REQUEST},
-the request itself is cancelled after a given number of tries. \hl{This
-gives to the preceding node, that receives a \texttt{SEGMENT\_CANCEL}, the
-chance to test a different path instead of waiting indefinitely.}
+the request itself is cancelled after a given number of tries. This
+gives to the preceding node on the path the
+chance to test a different route instead of waiting indefinitely.
 Default value is set to 1, i.e. each link is tried one time.
@@
 affected by similar issues since these nodes start with a lower number of links,
-e.g. corner nodes could only have two connected direction, so even a \hl{single}
+e.g. corner nodes could only have two connected direction, so even a single
 defective link could prevent a starting segment packet from coming back to the
-bootstrap node to close the loop and create the \hl{first} segment.
+bootstrap node to close the loop and create the first segment.
 \end{itemize}

### 2014-02-19 PAPER/introduction.tex
English fixes

@@
 In particular, authors of~\cite{Patwardhan05evaluatingthe} exploit the creation of a spanning tree of the
-topology, placing bidirectional restrictions \hl{by avoiding a packet
-to traverse the same link in both up and down directions}.
+topology, placing bidirectional restrictions to avoid that a packet
+can traverse a given link in both up and down directions.
 The hierarchical nature of this approach can lead to uneven traffic
@@
 \item At the end of the execution, no segment list is created or
-stored anywhere: each node is only aware of belonging to \hl{a segment | some segments},
+stored anywhere: each node is only aware of belonging to a segment,
 ignoring the presence of other nodes in the same segment and also the

### 2014-05-26 trunk/PAPER/implementation.tex
Reviewer comment fixed

@@
 %--------------------------------------------------------------------
-\subsection{Synthesis results}
+\subsection{Synthesis results: Timing, Area and Power consumption considerations}
 
@@
 the only consumption could be due to the leakage
-consumption.
+consumption. Finally with the reported results a coparison between 
+RPF configuration circuits and the proposed circuits could be performed.
+in particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{Patwardhan_nanoarch06}.
+In this work, as reported,  the implementation of the RPF requires an overhead of about 1692 CNFET for a $100\times\100$ network.
+Furthemore, regarding the power consumption, this last implementation require a setup phase beyond which, the consumptions tends to zero.
+Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.

### 2014-05-26 PAPER/implementation.tex
some error fixed

@@
 described in this section. Figure~\ref{fig:node_structure} depicts the general
-structure of a node in this particular scenario. In particular such a node
+structure of a node in the particular scenario of DNA nano Network-On-Chip. In particular such a node
 is composed by the following fundamental elements:
@@
     if the specific port of a segment is already candidate or assigned,
-    the second one records if a specific port is already visited or tvisited
+    the second one records if a specific port is already \emph{visited} or \emph{tvisited}.
 
@@
 the only consumption could be due to the leakage
-consumption.
+consumption. Finally with the reported results a coparison between 
+RPF configuration circuits and the proposed circuits could be performed.
+in particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{patwardhan_nanoarch06}.
+In this work, as reported,  the implementation of the RPF requires an overhead of about 1692 CNFET for a $100 \times 100$ network.
+Furthemore, regarding the power consumption, this last implementation require a setup phase beyond which, the consumptions tends to zero.
+Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.

### 2014-05-26 trunk/PAPER/implementation.tex
some error fixed

--- 2014-02-18 trunk/PAPER/implementation.tex
@@
 the only consumption could be due to the leakage
-consumption.
+consumption. Finally with the reported results a coparison between 
+RPF configuration circuits and the proposed circuits could be performed.
+In particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{patwardhan_nanoarch06}.
+As reported in this work,  the implemented hardware requires an overhead of about 1692 CNFET for a $100 \times 100$ network.
+Furthemore, regarding the power consumption, the RPF approach has a setup phase beyond which, the consumptions tends to zero.
+Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.

### 2014-05-26 PAPER/implementation.tex
some error fixed

@@
 the only consumption could be due to the leakage
-consumption. Finally with the reported results a coparison between 
+consumption. Finally, with the reported results, a coparison between 
 RPF configuration circuits and the proposed circuits could be performed.
-in particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{patwardhan_nanoarch06}.
-In this work, as reported,  the implementation of the RPF requires an overhead of about 1692 CNFET for a $100 \times 100$ network.
-Furthemore, regarding the power consumption, this last implementation require a setup phase beyond which, the consumptions tends to zero.
+In particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{patwardhan_nanoarch06}.
+As reported in this work,  the implemented hardware requires an overhead of about 1692 CNFET for a $100 \times 100$ network.
+Furthemore, regarding the power consumption, the RPF approach has a setup phase beyond which, the consumptions tends to zero.
 Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.

### 2014-06-26 trunk/PAPER/implementation.tex
Removed typo

@@
 the only consumption could be due to the leakage
-consumption. Finally with the reported results a coparison between 
+consumption. Finally, with the reported results, a comparison between 
 RPF configuration circuits and the proposed circuits could be performed.
@@
 As reported in this work,  the implemented hardware requires an overhead of about 1692 CNFET for a $100 \times 100$ network.
-Furthemore, regarding the power consumption, the RPF approach has a setup phase beyond which, the consumptions tends to zero.
+Furthermore, regarding the power consumption, the RPF approach has a setup phase beyond which, the consumptions tends to zero.
 Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.

### 2014-07-08 trunk/PAPER/disr.tex
fixes for review

@@
 The main concept behind the kind of turn prohibition we want to
-achieve is the \emph{segment}. A segment $S_y$ is basically a path of consecutive
+achieve is the \emph{segment}. A segment $S_b$ is basically a path of consecutive
 nodes and links, starting with a link attached to a node belonging to
-a different segment $S_x$ and ending with a link attached to a
-node of another segment $S_z$. In other words, a segment is
+a different segment $S_a$ and ending with a link attached to a
+node of another segment $S_c$. In other words, a segment is
 a path connecting two other different segments. The example
@@
 \centering
-    \includegraphics[width=0.25\textwidth]{pictures/network_slice.eps}
+    \includegraphics[width=0.45\textwidth]{pictures/network_slice.eps}
   \caption{Example of Segments}
@@
 \item Broadcasting and confirmation to create the first segment of the subnet.
-\item Parallel requests starting from assigned node to discover other
+\item Parallel segment requests starting from assigned nodes to discover other
 segments. 
+\item Resulting segment confirmation/cancel packets are processed.
 \item Turn prohibition in each confirmed segment.
-\item Draining of remaining packet due to timeouts.
 \end{enumerate}
+
+This first work is explicitly focused on demostrating
+the feasibility and scalability of \disr{} in the particular scenario
+assumed; for this reason we will not investigate the further degree of
+freedom that the last of the above steps introduces, i.e. choosing
+\emph{where} actually placing the restriction in the context of the
+segment. This choice would striclty depend on the particular routing
+strategy that will be used and could result in some interesting
+improvements. However, the scope of this work is understading how \disr{} can
+implement a distributed topology discovery, mapping defects and
+creating a segment partitioning that will be exploited in a second
+design phase which includes choosing and implementing a routing strategy. For this
+reason, the last two phases will be addressed as one, since we can
+safely assume that a random turn (e.g. the first) will be phohibited
+once each segment has been confirmed.
 
@@
   \centering
-    \includegraphics[width=0.25\textwidth]{pictures/dbs_updated.eps}
+    \includegraphics[width=0.45\textwidth]{pictures/dbs_updated.eps}
   \caption{\disr{} node execution model}
@@
 \end{tabular}
-\caption{Example of \disr{} segment setup: Nodes' status is labeled as \emph{CandidateStarting} (\emph{Cs}), \emph{Candidate} (\emph{C}), \emph{Free} (\emph{F}), \emph{Assigned} (\emph{A}) or \emph{Bootstrap} (\emph{B})}
+\caption{Example of \disr{} segment setup: Nodes status is labeled as \emph{CandidateStarting} (\emph{Cs}), \emph{Candidate} (\emph{C}), \emph{Free} (\emph{F}), \emph{Assigned} (\emph{A}) or \emph{Bootstrap} (\emph{B})}
 \label{fig:disr_events}
@@
 request means that the first starting segment has already been found \emph{(h)}.
-\item{\textbf{Segment Confirmation}}: The segment searching process is successful
-when an already \emph{Assigned} node receives the
+
+\item{\textbf{Segment Confirmation}}: The segment searching process is
+successful when an already \emph{Assigned} node receives the
 \texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
 sent back along the path that originated the request
-(Figure~\ref{fig:disr_events}-g), while the
-node remains \emph{Assigned} (since it could confirm other segments). Each node
-previously set as \emph{Candidate} for that segment id, when receives a confirmation packet changes its status to \emph{Assigned} \emph{(m)} and send back
-the same confirmation until it reaches the initiator of the request,
-which then changes from \emph{ActiveSearching} to \emph{Assigned} \emph{(d)}.
+(Figure~\ref{fig:disr_events}-g), while the node remains
+\emph{Assigned} (since it could confirm other segments). Each node
+previously set as \emph{Candidate} for that segment id, when receives
+a confirmation packet changes its status to \emph{Assigned} \emph{(m)}
+and send back the same confirmation until it reaches the initiator of
+the request, which then changes from \emph{ActiveSearching} to
+\emph{Assigned} \emph{(d)}.
 
@@
 In the processes described above, we assumed that each node in the
-\emph{Assigned} status can start a segment searching process by injecting a
-\texttt{SEGMENT\_REQUEST}. However, a more accurate decision when
-defining \disr{} should be made in order to decide whether or not the
-node must actually perform this action. The point above is
-strictly related to a general question: which level of
-parallelism should we allow in \disr{}? The adopted approach, although
-the nature of \disr{} itself is intrinsically parallel, is that the use of
-parallelism makes things working in a more complex way. In other words,
-\disr{} is parallel when needed, but it does not exploit parallelism
-as an ``improving feature''. When not needed, things should be
-serialized. For example: when a node is ``ready to search'' it could start
-several segment searching processes associated to the same segment, one for
-each free link. But serializing this operation, by investigating the free links
-in order, could be a simpler solution. We refer to this saying that we
-avoid intra-node parallelism.  Note that while intra-node parallelism
-can be avoided, trying to avoid inter-node parallelism could be more
-complex than allowing the parallelism itself. Imagine for example the
-effort generated trying to coordinate nodes so that an unique segment searching
-process is actually running in the whole subnet. Thus, in contrast to
-the intra-node parallelism, the inter-node parallelism is a structural
-property of the \disr{} algorithm and should not be avoided.
+\emph{Assigned} status can start a segment searching process by
+injecting a \texttt{SEGMENT\_REQUEST}. However, different choices
+could have been made when defining \disr{}, strictly related to which
+kind and level of parallelism should be supported. The approach adopted
+currently is that, although the nature of \disr{} is intrinsically
+parallel, the use of parallelism should not make things work in a too
+complex/uncontrollable way. In other words, \disr{} is parallel when
+needed, but it does not exploit parallelism as an ``improving
+feature''. Thus, when not needed, things should be serialized. For
+example: a node with free links could start several segment requests
+associated to the same \emph{segID}, one for each free link. But
+serializing this operation, by investigating the free links in order,
+could be a simpler solution. We refer to this \disr{} design choice
+saying that we avoid \emph{intra-node parallelism}.  Note that,
+conversely, avoiding \emph{inter-node parallelism} could be more
+complex than allowing it: for example, we can imagine the effort
+generated when trying to coordinate nodes so that a unique segment
+searching process is actually running in the whole subnet. Thus, in
+contrast to the \emph{intra-node parallelism}, the \emph{inter-node
+parallelism} is a structural property of the \disr{} algorithm and
+should not be avoided.
 %------------------------------------------------------------------------------

### 2014-07-08 trunk/PAPER/implementation.tex
fixes for review

@@
 structure of a node in the particular scenario of DNA nano Network-On-Chip. In particular such a node
-is composed by the following fundamental elements:
+is composed of the following fundamental elements:
 
@@
 registers needed to implement \disr{}. Figure~\ref{fig:implementation}
-shows an architecture sketch, which mainly consist in the
+shows an architecture sketch, which mainly consists in the
 following building elements:
@@
 	TTL field should be reset to its initial value and the \emph{segment\_ID}
-	is composed by the node ID and by the output port identification 
+	is composed of the node ID and by the output port identification 
 	number.
@@
 node are set as \emph{Free}.  
-Figure~\ref{fig:pipeline} is shows the pipeline structure of the
+Figure~\ref{fig:pipeline} shows the pipeline structure of the
 \disr{} architecture. Packets incoming from neighbor nodes (or

### 2014-07-08 trunk/PAPER/introduction.tex
fixes for review

@@
 \section{Introduction and Motivation}
+\label{sec:introduction}
 
 Exploring long term alternatives to the CMOS technology is gaining
-more and more revelance as the scaling trend of such devices keeps
+more and more relevance as the scaling trend of such devices keeps
 introducing new challenges: power density, defect tolerance, testing
@@
 While software parallelism and multicore
-approaches~\cite{horowitz2004} and \cite{powell2009} are partially mitigating the impact of such
-constraints on performances, it is likely that the growing computing demand will
-eventually need even more radical architectural modifications and new
-paradigms in order to address the Computer Design challenges of the next
+approaches~\cite{horowitz2004,powell2009} are partially mitigating the impact of such
+constraints on performances, it is likely that a growing computing demand will
+eventually need even more radical architectural modifications and 
+paradigms to address the Computer Design challenges of the next
 decades.
 
-In the last years, Self-assembled nanoscale architectures~\cite{yan2003}
-emerged as a promising technology due their tera/peta scale of
-integration, defect tolerance and huge potential computing
-capabilities. These technologies are certainly still at
-their early stage of development, however different laboratory demos and
-prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006_1, pistol2009}.
+In the last years, self-assembled nanoscale
+architectures~\cite{yan2003} emerged as a promising technology due
+their tera/peta scale of integration, defect tolerance and huge
+potential computing capabilities. These technologies are certainly
+still at their early stage of development, however different
+laboratory demos and proof-of-concepts have been
+presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1,
+pistol2009}. For a complete survey on self-assembled architectures and
+how they compare against classical many-core systems in terms of
+ technologies, fault tolerance, performance and software tools see
+ also~\cite{Future}.
 %, patwardhan2006
-The main idea behind this approach is to exploit the physical regularity and
-stability of DNA structures in order to create a scaffold onto which
-nano-devices (e.g. nanowires and CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be
-attached. This can be achieved by designing appropriate complementary DNA tags for
+The main idea behind this approach is exploiting the physical
+regularity and stability of DNA structures in order to create a
+scaffold onto which nano-devices (e.g. nanowires and
+CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be attached. This
+can be achieved by designing appropriate complementary DNA tags for
 each terminal to be placed, so that a nano device will be attached
 only where its own DNA tag matches a complementary tag on the DNA grid
-scaffold (see Figure~\ref{fig:nana}-a).
-A detailed description of the chemical properties involved is far
-beyond the scope of this paper (see also~\cite{braun1998, seeman1999}), so we will focus on
-the three main challenges that this new fabrication process introduces
-in Computer Design: \emph{(i) limited node complexity}, \emph{(ii) large scale
+scaffold (see Figure~\ref{fig:nana}-a).  Of course, a detailed
+description of the chemical properties involved is far beyond the
+scope of this paper (see also~\cite{braun1998, seeman1999}).
+
+In this work we present \disr{} (Distributed Segment Routing), a distributed
+approach focused on addressing the three main challenges that this new fabrication process introduces
+in nanoscale Network-on-Chip Design: \emph{(i) limited node complexity}, \emph{(ii) large scale
 randomness} and \emph{(iii) high defect rates}.  
-
 The \emph{limited node complexity} aspect is directly
 related to the use of complementary DNA tags in order to place circuit
-components. In a traditional CMOS process the complexity is introduced
-using a photolithography mask, so that larger (more complex) circuits
-only require larger masks; conversely, self-assembly achieves
+components. Traditional CMOS process introduces complexity 
+with larger photolithography mask: more complex (larger) circuits
+will only require larger masks. Conversely, self-assembly achieves
 complexity by increasing the number of unique DNA tags, since more
 different tags means having more control on component placement. Ideally, by specifying a single
-and unique tag for each nano transistor terminal, we could exactly
-choose where each component would be placed. But the number of DNA
+and unique tag for each nano device terminal, we could exactly
+choose where each component would be placed in the design. But the number of DNA
 symbols forming the DNA sequence is limited (sequence of 4 nucleobases
-G,A,T,C) and so creating many different tags (of a given lenght) would
+G,A,T,C) and so creating many different tags (of a prefixed length) would
 mean make them more similar to each other, increasing the probability
-of incorrect/partial matching. To avoid this problem we should limit
-the number of unique tags, thus limiting the complexity at each node.
-In particular, a budget of about $10,000$ CNFETs per node has been
-estimated in~\cite{liu_jetcs}.
-
+of incorrect/partial matching. To avoid this problem 
+the number of unique tags must be limited, thus limiting the
+complexity available at each node.
+In particular, in this work a budget of about $10,000$ CNFETs per node
+has been assumed , as estimated in~\cite{liu_jetcs}.
 \emph{Large scale randomness} is the other fundamental condition of
@@
 orientation and so on.
-
 Finally, \emph{defect rates}: while they are very hardly tolerated in mask
-based top down design , the same nature of a bottom up self
-assembled process cannot assume such a deterministic device placement
+based top down design, the same nature of a bottom up self-assembly
+ process cannot assume such a deterministic device placement
 process, thus defect tolerance is something like a design requirement
@@
 \begin{tabular}{cc}
-    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps} &
-    \includegraphics[width=0.40\textwidth]{pictures/dna1_complex2.eps} \\
+    \includegraphics[width=0.45\textwidth]{pictures/dna2b.eps} &
+    \includegraphics[width=0.45\textwidth]{pictures/dna1_complex2.eps} \\
  (a) & (b)
  \end{tabular}
-  \caption{(a) DNA tag matching and (b) resulting trregualr topology}
+  \caption{(a) Strands of complementary DNA tags self assemble to
+  generate larger structures (b) The resulting irregular topology of
+  processing(P) and storage(M) elements }
   \label{fig:nana}
 \end{figure*}
-These aspects of a DNA-self assembly process lead to some important
+These aspects of a DNA self-assembly process lead to some important
 implications to be addressed when approaching to the design of
-a computer architecture: computational model should be based on a
+a nanoscale Network-on-Chip architecture: computational model should be based on a
 distributed network of small processing and storage nodes, randomly
@@
 example in~\cite{patwardhan2006_1}, where instruction and data
-operands are move around the network in order to be processed.
-Indepentedly from the particular policy chosen for routing packets,
-such networks must be able to guarantee deadlock freedom without any
+operands are moved around the network in order to be processed.
+In addition, independently of the particular policy chosen to route instruction and
+data packets, such networks must be able to guarantee deadlock freedom without any
 prior assumption on topology.
 
-In this work we introduce \disr{}, a Distributed Segment-based approach
-to deadlock freedom in large scale DNA self assembled networks. Our
-contribution aims to achieve the classical properties of a
-segment-based approach~\cite{mejia_ipdps06} without requiring any
-topology graph, external defect map or centralized algorithm
-execution.  So the \disr{} approach is not intended to discover the
-``optimal'' segment choice (ideally reachable with the knowledge of
-the topology graph) but just to demonstrate a concrete model that can
-fit into such complex, irregular and large sized networks.
-It is important to
-underline that, altougth we can assume an architecture similar to the
-one depicted in Figure~\ref{fig:nana} as background, the topology discovery
-problem faced in this work is more general and not strictly dependent on any of the
-underlying computing architecture.
+In this work, we introduce \disr{}, a Distributed Segment-based
+approach to topology discovery and deadlock freedom in large scale DNA
+self-assembled on chip networks. Our contribution aims to achieve the
+classical properties of a segment-based approach~\cite{mejia_ipdps06}
+without requiring any topology graph, external defect map or
+centralized algorithm execution.  So the \disr{} approach is not
+intended to discover the ``optimal'' segment choice (ideally reachable
+with the knowledge of the topology graph) but just to demonstrate a
+concrete model that can fit into such complex, irregular and large
+sized networks.  It is important to underline that, although we can
+assume an architecture similar to the one depicted in
+Figure~\ref{fig:nana} as background, the \disr{} topology discovery
+approach presented this work is more general and not strictly
+dependent on any underlying computational model adopted.
 
 The paper is organized as follows: in Section~\ref{sec:related_works}
-we summarize the main approaches to topology agnostic routing. Next in
+we summarize the main approaches for topology agnostic deadlock
+freedom. Next, in
 Section~\ref{sec:disr_concepts} are described the main elements and
-the execution model of the proposed approach.  In Section~\ref{sec:simulation}
-simulations are carried out with the opensource tool Nanoxim to
+the execution model of the proposed approach. In Section~\ref{sec:simulation},
+simulations are carried out with the open-source tool Nanoxim to
 demonstrate how \disr{} preserves some of the main segment-based
 properties and how compares to the tree-based approaches. Finally a
-draft of a architectural implementation is shown in
+draft of an architectural implementation is shown in
 Section~\ref{sec:implementation} to evaluate the feasibility of the
@@
 \label{sec:related_works}
-Several worksaddressed the problem of topology agnostic deadlock
+Several works addressed the problem of topology agnostic deadlock
 freedom introducing virtual channels~\cite{sancho2002, skeie2002,
 skeie2004, koibuchi2003}, but while they show interesting
-performances, the low resources deadlock makes them not suitable for
-the specific DNA self assembled networks we are assuming as
-background.
+performances, the low resources available to prevent deadlocks makes them not suitable for
+the DNA self-assembled networks we are assuming as
+scenario.
 Other topology independent algorithms~\cite{schroeder1991,
-koibuchi2001, cherkasova1996} do not require any virtual channels but
+koibuchi2001, cherkasova1996} do not require any virtual channel but
 exploit the concept of ``turn prohibition''.
-In particular, authors of~\cite{Patwardhan05evaluatingthe} exploits the creation of a spanning tree of the
-topology, placing bidirectional restrictions by avoiding a packet
-to traverse the same link in both up and down directions.
+In particular, authors of~\cite{Patwardhan05evaluatingthe} exploit the creation of a spanning tree of the
+topology, placing bidirectional restrictions to avoid that a packet
+can traverse a given link in both up and down directions.
 The hierarchical nature of this approach can lead to uneven traffic
@@
 
-The \disr{} approach presented in this work is a first attempt of
-achieving the same goals of a segment based turn prohibition  without
-requiring any topology graph or centralized execution. In particular
+The \disr{} approach presented in this work is a first attempt to
+achieve the same goals of a segment based turn prohibition without
+requiring neither the knowledge of a topology graph nor centralized execution. In particular
 \disr{} implements segment discovery and turn prohibition using a
 completely different mechanism, based on a distributed exchange of
-small setup packets requiring on average $15\%$ of the available
+small setup packets requiring a limited and scalable portion of the available
 resource budget. The following main features distinguish \disr{}
@@
 what is going on, i.e. the status of the \disr{} execution is
-collectively distributed among the nodes
+collectively distributed among the nodes.
 \item  No defect map and/or topology graph is used as input,
 thus, the topology has to be discovered \emph{while} segments are
-created
+created.
 \item At the end of the execution, no segment list is created or
-stored anywhere: each node is only aware of belonging to some segment,
-ignoring the presence of other nodes in the same segment and even the
-presence of other segments in the network
+stored anywhere: each node is only aware of belonging to a segment,
+ignoring the presence of other nodes in the same segment and also the
+presence of other segments in the network.
 \end{itemize}

### 2014-07-08 PAPER/simulation.tex
fixes for review

@@
 
-In this section we will test the proposed \disr{} approach to demonstrate
-its effectiveness and compare it against topology agnostic approach
-based on spanning trees and
+In this section we will test the proposed \disr{} approach to
+demonstrate its effectiveness and compare it against a topology
+agnostic approach based on spanning trees and
 broadcasting~\cite{Patwardhan05evaluatingthe}, to measure how \disr{}
-performs in covering the network structure.
+performs in covering the network structure. Note that a direct
+comparison against the SR segment-based approach is not addressed
+here, since how described in Section~\ref{sec:introduction} our
+scenario assumes the non-feasibility of a centralized approach:
+however, all the properties of the centralized approach should be
+considered as preserved for all the nodes reached by the distributed
+segment coverage of \disr{}. Thus, the main points that remain to be
+addressed are:
+\begin{itemize}
+\item how \disr{} compares against state-of-art of tree based approach
+applied to equivalent scenario
+\item how \disr{} scales on large networks
+\item the real feasibility of the required hardware on the limited
+node size assumed
+\end{itemize}
 
@@
 In this section we analyze the results in terms of node
-coverage and latency at different network sizes, defect rates and
+coverage and latency with different network sizes, defect rates and
 bootstrap injection points. In particular
 Figure~\ref{fig:results_coverage} shows
-node coverage for \disr{} and RPF tree based approach respectively. While
+node coverage for \disr{} and Reverse Path Forwarding (RPF) tree based approach respectively. While
 the first aim of \disr{} is not to reach the optimal coverage, we still
@@
 regions of nodes that \disr{} currently cannot handle.
-For example Figure~\ref{fig:net} show a 30x30 network with a 25\%
-defect in which the bottom-left part cannot be reached due
-disconnected regions. Note that remaining defective nodes belonging to
+For example Figure~\ref{fig:net} shows a 30x30 network with a 25\%
+defect in which the bottom-left part cannot be reached due to
+disconnected regions. Note that the remaining defective nodes belonging to
 connected regions are successfully surrounded by \disr{} coverage; in any
@@
 Some optimization parameters, which demonstrated to improve the \disr{}
-results have been fixed to some good values, but are not subject to
-further investigation; once again the focus here is not the
-optimal set of segments, but just demonstrating a working approach. 
-These are optimizations are:
+results, have been fixed to some good values and are not subject to
+further investigation in this paper; once again the focus here is not the
+optimal setup of segments, but just demonstrating a working approach. 
+These parameters are:
 \begin{itemize}
 \item \emph{cycle\_links}: max number of retries across the set of links of
-each node. While searching for a free link due an incoming segment request,
-the same request is cancelled after a given number of tries. This
-gives to the preceding node receives a segment cancel and has the
-chance of testing a different path instead of waiting indefinitely.
-Default is set to 1, i.e. each link is tried one time.
-\item \emph{time to live (TTL}: when a segment request is cancelled
-along a certain path (using a segment cancel), a TTL field is
+each node. While searching for a free link due to an incoming \texttt{SEGMENT\_REQUEST},
+the request itself is cancelled after a given number of tries. This
+gives to the preceding node on the path the
+chance to test a different route instead of waiting indefinitely.
+Default value is set to 1, i.e. each link is tried one time.
+\item \emph{time to live (TTL)}: when a segment request is cancelled
+along a certain path (using a \texttt{SEGMENT\_CANCEL}), a TTL field is
 decreased in the request packet, so that requests that have been
-denied too much times can desist, even if free links for going on are
-available. This is not only a optimisation for shortening 
-requests processes, but also solves some critical situations in which
-request packets looped in a particular path without neither succeeding
-nor failing.
+denied too much times can desist, even if free links are
+available. This is not only an optimization to shorten
+requests' processes, but also solves some critical situations in which
+request packets are blocked in routing loops in a particular path.
 \item \emph{bootstrap\_timeout}: number of time units that a bootstrap node
@@
 Enabling this optimization, a bootstrap node is immune to defects.
-We may think of a pre-bootstrap phase that properly selects (from upper
+We may think about a pre-bootstrap phase that properly selects (from upper
 layer via) a bootstrap node which is tested as properly connected. We
-enabled this optimization, however empirical tests showed us that only
+enabled this optimization, however empirical tests have shown us that only
 simulations using bootstrap nodes placed on edges would be heavily
-affected, since these are nodes starting with a lower number of links,
-e.g. corner nodes could only have two connected direction, so even a
-defective link could prevent starting segment packet to return to
-bootstrap to close the loop a create the segment.
+affected by similar issues since these nodes start with a lower number of links,
+e.g. corner nodes could only have two connected direction, so even a single
+defective link could prevent a starting segment packet from coming back to the
+bootstrap node to close the loop and create the first segment.
 \end{itemize}

### 2014-07-08 trunk/PAPER/simulation.tex
fixed for review comments

@@
 
-In this section we will test the proposed \disr{} approach to demonstrate
-its effectiveness and compare it against a topology agnostic approach
-based on spanning trees and
+In this section we will test the proposed \disr{} approach to
+demonstrate its effectiveness and compare it against a topology
+agnostic approach based on spanning trees and
 broadcasting~\cite{Patwardhan05evaluatingthe}, to measure how \disr{}
-performs in covering the network structure.
+performs in covering the network structure. Note that a direct
+comparison against the SR segment-based approach is not addressed
+here, since how described in Section~\ref{sec:introduction} our
+scenario assumes the non-feasibility of a centralized approach:
+however, all the properties of the centralized approach should be
+considered as preserved for all the nodes reached by the distributed
+segment coverage of \disr{}. Thus, the main points that remain to be
+addressed are:
+\begin{itemize}
+\item how \disr{} compares against state-of-art of tree based approach
+applied to equivalent scenario
+\item how \disr{} scales on large networks
+\item the real feasibility of the required hardware on the limited
+node size assumed
+\end{itemize}
 
@@
 
-In this section we analyze the results in terms of node
-coverage and latency with different network sizes, defect rates and
-bootstrap injection points. In particular
-Figure~\ref{fig:results_coverage} shows
-node coverage for \disr{} and RPF tree based approach respectively. While
-the first aim of \disr{} is not to reach the optimal coverage, we still
-can observe a quite good performance as compared to the tree based
-approach. Note that defect rates beyond 25\% lead to many disconnected
-regions of nodes that \disr{} currently cannot handle.
-For example Figure~\ref{fig:net} show a 30x30 network with a 25\%
-defect in which the bottom-left part cannot be reached due to
+In this section we analyze the results in terms of node coverage and
+latency with different network sizes, defect rates and bootstrap
+injection points. In particular Figure~\ref{fig:results_coverage}
+shows node coverage for \disr{} and Reverse Path Forwarding (RPF) tree
+based approach respectively. While the first aim of \disr{} is not to
+reach the optimal coverage, we still can observe a quite good
+performance as compared to the tree based approach. For low defect
+rates, i.e. below 10\%, both approaches reach near ideal coverage for
+each of the tested network sizes. Higher defect rates seems to show
+more variance for \disr{}. For example at the high 20\% rate \disr{}
+ranges from 60\% to 75\% while RPF remains stable at 75\%. However we
+can consider this coverage sensibility at higher defect rates as still acceptable
+for this first, not yet optimized version of the proposed approach.
+Note that defect rates beyond 25\% lead to many disconnected
+regions of nodes that \disr{} currently cannot handle. This threshold can be
+intuitively related to the fact that in the topologies simulated a
+node has (on average) a cardinality of 4 connections to other nodes. This means
+that with a defect rate bigger than 25\% a node has at least one of its four
+paths as not-working, and this applies (on average) for each node,
+thus leading to increased probability of consecutive disconnected
+nodes, which eventually create disconnected regions. For example Figure~\ref{fig:net} shows a 30x30 network with a 25\%
+defect rate in which the bottom-left part cannot be reached due to
 disconnected regions. Note that the remaining defective nodes belonging to
@@
 
-The number of cycles required to complete segment mapping process
-is shown in Figure~\ref{fig:results_latency}. In this case the comparison
-against the tree-based approach shows better (lower) values at different defect
-rates. Rather than the absolute numbers, what is more interesting
-to observe is how \disr{} latency scales with network size. For example,
-going from 900 to 2500 nodes, at the medium defect rate of $0.15$,
-leads to an increase from 3000 to 4500 cycles. It should be noticed
-also how the effect of defect rate is increasing until the threshold
-of $0.25$ is reached, meaning that until that limit \disr{} finds 
-the completion of the process more and more difficult due to the increasing defective
-paths, but it still discover new segments if it runs for an
-extended amount of cycles. This behavior is not reported in the RPF
-based approach, meaning that a tree-based approach, although starting
-from higher values, is less affected by defect rates (when low rates
-are considered).
+The number of cycles required to complete segment mapping process is
+shown in Figure~\ref{fig:results_latency}. In this case the comparison
+against the tree-based approach shows better (lower) values at
+different defect rates. Rather than the absolute numbers, what is more
+interesting to observe is how \disr{} latency scales with network
+size. For example, going from 900 to 2500 nodes, at the medium defect
+rate of $0.15$, leads to an increase from 3000 to 4500 cycles. It
+should be noticed also how for \disr{} latency is increasing until the
+threshold of $0.25$ is reached, meaning that the completion of the
+process is more and more difficult due to the missing paths, but
+\disr{} is still able to finish the segment discovery using the retry/cancel mechanisms
+described in the previous section. This initial behavior is not reported in
+the RPF based approach, leading to higher latency values and not using
+the same retry/cancel approach as \disr{}.
+
 After the $0.25$ threshold, the impact of disconnected regions
@@
 Some optimization parameters, which demonstrated to improve the \disr{}
-results, have been fixed to some good values and are not subject to
+results, have been fixed to some reasonable default values (see below) and are not subject to
 further investigation in this paper; once again the focus here is not the

### 2014-07-08 trunk/PAPER/pictures/node_coverage/coverage_plot.m
Fixed pics for review

@@ -1,12 +1,13 @@
 %after that the workspace is loaded from file
 hold on;
-plot(def_node,ideal,'-');
+plot(def_node,ideal,'r--');
+plot(def_node, trenta,'-+');
 plot(def_node, trenta,'--o');
-plot(def_node,cinquanta,':.');
-plot(def_node,cento,'-.x');
+plot(def_node,cinquanta,':*');
+plot(def_node,cento,'-.');
 %plot(def_node,ottanta,':');
 
 
 xlabel('Node Defect Rate');
 ylabel('Node Coverage');
-legend('Ideal','30x30','50x50','100x100');
+legend('Ideal','10x10','30x30','50x50','100x100');

### 2014-07-12 trunk/PAPER/simulation.tex
Made changes to meet reviewers' comments

@@
 shows node coverage for \disr{} and Reverse Path Forwarding (RPF) tree
-based approach respectively. While the first aim of \disr{} is not to
+based approach (as adapted in \cite{patwardhan_nanoarch06}) respectively. While the first aim of \disr{} is not to
 reach the optimal coverage, we still can observe a quite good

### 2014-09-05 PAPER/disr.tex
Removed some typos

@@
 \item Broadcasting and confirmation to create the first segment of the subnet.
-\item Parallel requests starting from assigned node to discover other
+\item Parallel segment requests starting from assigned nodes to discover other
 segments. 
+\item Resulting segment confirmation/cancel packets are processed.
 \item Turn prohibition in each confirmed segment.
-\item Draining of remaining packet due to timeouts.
 \end{enumerate}
+
+This first work is explicitly focused on demonstrating
+the feasibility and scalability of \disr{} in the particular scenario
+assumed; for this reason we will not investigate the further degree of
+freedom that the last of the above steps introduces, i.e. choosing
+\emph{where} actually placing the restriction in the context of the
+segment. This choice would strictly depend on the particular routing
+strategy that will be used and could result in some interesting
+improvements. However, the scope of this work is understanding how \disr{} can
+implement a distributed topology discovery, mapping defects and
+creating a segment partitioning that will be exploited in a second
+design phase which includes choosing and implementing a routing strategy. For this
+reason, the last two phases will be addressed as one, since we can
+safely assume that a random turn (e.g. the first) will be prohibited
+once each segment has been confirmed.
 
@@
 the starting segment. 
-\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (\hl{which is} not the
-first).
+\item{\texttt{SEGMENT\_REQUEST}}: used to search candidates for a segment (not the first).
 \item{\texttt{SEGMENT\_CONFIRM}}: used to establish a segment. 
@@
 The \disr{} control packets described in the previous subsection trigger
-node events, which \hl{eventually} change \emph{DBS} status according to the
+node events, which change \emph{DBS} according to the
 current value of \emph{LED} variables and the type of packet received.
@@
 request means that the first starting segment has already been found \emph{(h)}.
-\item{\textbf{Segment Confirmation}}: The segment searching process is successful
-when an already \emph{Assigned} node receives the
+
+\item{\textbf{Segment Confirmation}}: The segment searching process is
+successful when an already \emph{Assigned} node receives the
 \texttt{SEGMENT\_REQUEST} packet. Then, a \texttt{SEGMENT\_CONFIRM} is
 sent back along the path that originated the request
-(Figure~\ref{fig:disr_events}-g), while the
-node remains \emph{Assigned} \hl{(since it could confirm more segments)}. Each node
-previously set as \emph{Candidate} for that segment id, when receives a confirmation packet changes its status to \emph{Assigned} \emph{(m)} and send back
-the same confirmation until it reaches the initiator of the request,
-which then changes from \emph{ActiveSearching} to \emph{Assigned} \emph{(d)}.
+(Figure~\ref{fig:disr_events}-g), while the node remains
+\emph{Assigned} (since it could confirm other segments). Each node
+previously set as \emph{Candidate} for that segment id, when receives
+a confirmation packet changes its status to \emph{Assigned} \emph{(m)}
+and send back the same confirmation until it reaches the initiator of
+the request, which then changes from \emph{ActiveSearching} to
+\emph{Assigned} \emph{(d)}.
 

### 2014-09-08 trunk/PAPER/paper.tex
fixes for review
quasi-final submission

@@
 \documentclass[preprint]{elsarticle}
-%\documentclass[3p]{elsarticle}
 \usepackage{lineno,hyperref}
@@
 
-\journal{Journal of \LaTeX\ Templates}
+\journal{Computers \& Electrical Engineering}
 
@@
 %------------------------------------------------------------------------------
+\usepackage{color,soul}
+%------------------------------------------------------------------------------
 
@@
 
-\title{Distributed Topology Discovery in Self-Assembled Nano Networks}
+\title{Distributed Topology Discovery in Self-Assembled Nano Network-On-Chip}
 
 %% Group authors per affiliation:
-\author{Elsevier\fnref{myfootnote}}
-\address{Radarweg 29, Amsterdam}
-\fntext[myfootnote]{Since 1880.}
+\author{Vincenzo Catania}
+\ead{vincenzo.catania@dieei.unict.it}
+\author{Andrea Mineo}
+\ead{andrea.mineo@dieei.unict.it}
+\author{Salvatore Monteleone}
+\ead{salvatore.monteleone@dieei.unict.it}
+\author{Davide Patti\corref{corr1}}
+\ead{davide.patti@dieei.unict.it}
+\address{DIEEI, University of Catania, v.le Andrea Doria 6, 95125 Catania, Italy}
+
+\cortext[corr1]{Corresponding author}
 
@@
 %------------------------------------------------------------------------------
+\vspace{10 mm}
+
+Vincenzo Catania received the Laurea degree in electrical engineering
+from the University of Catania, Italy, in 1982. Until 1984, he was
+responsible for testing microprocessor system at STMicroelectronics,
+Catania. He is a full professor of computer
+science. His research interests include performance and reliability
+assessment in parallel and distributed system, VLSI design, low power
+design, and fuzzy logic.
+
+Andrea Mineo received the B.Sc. and M.Sc. degrees in Electronic
+Engineering from the University of Catania, Italy, in 2010 and 2013,
+respectively, and is currently pursuing the Ph.D. degree in Systems,
+Energy, Computer and Telecommunications Engineering at the University
+of Catania.  His current research interests are VLSI systems,
+network-on-chip architectures  and emerging interconnect technologies
+for on-chip networks.
+
+Salvatore Monteleone is a post-doctoral research assistant at the
+Department of Electrical, Electronic and Computer Engineering -
+University of Catania, Italy. He obtained the BSc (2007) and MSc
+(2010) in Computer Engineering at University of Catania where he also
+completed the PhD course in Communications and Computer Engineering
+(2014).  His interests comprehend cooperative systems, user-centric
+systems and NoC.
+
+Davide Patti received the Laurea and PhD degrees in computer
+engineering from the University of Catania, Italy, in 2003 and 2007,
+respectively. His research focuses on Design Space exploration of VLIW
+systems, Network-on-Chip architectures, DNA self-assembled networks
+and Human-computer interface. He is currently research assistant
+at University of Catania.
 

### 2014-09-09 trunk/PAPER/implementation.tex
Made changes to meet reviewers' comments
Another commit to remove typos and errors

@@
 described in this section. Figure~\ref{fig:node_structure} depicts the general
-structure of a node in the particular scenario of DNA nano Network-On-Chip. In particular such a node
+structure of a node in the particular scenario of DNA nano Network-On-Chip. In particular, such a node
 is composed of the following fundamental elements:
@@
 
-	\item \textbf{Switch Matrix:} Driven by a switch controller, it enables the
+	\item \textbf{Switch Matrix:} Driven by a switch controller, it enables
 	reciprocal connections among devices inside the node. Before segments'
@@
 
-	\item  \textbf{Processing Element (PE):} Is strictly related to the
+	\item  \textbf{Processing Element (PE):} It is strictly related to the
 	functionality and role that the node cover inside a given network (e.g. being a
@@
 
-To give a basic estimate of the overhead needed we focus on \disr{}-
+To give a basic estimate of the overhead needed, we focus on \disr{}-
 specific components namely the control logic and configuration
@@
 	\item \textbf{LED registers:}
-	A set of registers store the \emph{LED} defined in
+	A set of registers stores the \emph{LED} defined in
 	section~\ref{sec:disr_concepts}.  In the
@@
 	scratch e.g. when a node is bootstrap and for
-	the first time it should inject a \emph{starting\_segment\_request}. 
+	the first time it should inject a \emph{STARTING\_SEGMENT\_REQUEST}. 
 	Figure~\ref{fig:packager} depicts the architecture of this
@@
 	driven by the controller, will select information incoming from an internal 
-    node such as the \emph{source\_ID}. In this situation the 
-	TTL field should be reset to its initial value and the \emph{segment\_ID}
+    node such as the \emph{src\_id}. In this situation the 
+	TTL field should be reset to its initial value and the \emph{segID}
 	is composed of the node ID and by the output port identification 
@@
 
-All the blocks described above, reacts with the rising edge of
+All the blocks described above, react with the rising edge of
 the \emph{clock signal}. An asynchronous system \emph{reset} signal is
@@
 next clock cycle the control circuitry will update LED registers status and
-will drive the \emph{Switch Matrix} in order to send eventually the packets to
+will drive the \emph{Switch Matrix} in order to send the packets to
 the right output buffer.
@@
 $10^4$ CNFETs for each network's node~\cite{liu_jetcs}  we estimated
-the required resources to implement the entire \disr{} block. The RTL
+the resources required to implement the entire \disr{} block. The RTL
 description of the circuitry described in the last section (with an
-hardware description language)  of the \disr{} circuitry has been written
+hardware description language) has been written
 and synthesized at gate-level using \emph{Synopsys Design Compiler} with 
 a generic technology library (GTECH).
-Considering the specific layout of each single logic elements  (NAND,
-full-adder, latch etc.), it has been possible to get a rough estimate
+Considering the specific layout of each single logic element (NAND,
+full-adder, latch etc.), it has been possible to get a rough estimation
 of the number of transistors necessary to implement \disr{} logic.
@@
 In particular, Figure~\ref{fig:synthesys} shows that the proposed 
-implementation occupies about 17,5\% of our node budget. 
+implementation occupies about 17,5\% of the node budget. 
 The main contribution is due to the controller circuitry followed by LED registers. 
@@
 absolute number of devices itself, it is interesting to observe that
-the circuitry complexity which implements \disr{} algorithm increases
-with a slowly growing trend. An intuitive explanation of this is the
-relatively simple logic of \disr{}, whose behavior is almost coded on
+the complexity of the circuitry necessary to implement \disr{} increases
+with a slowly growing trend. This is due to the
+relatively simple logic of \disr{} which is almost coded with
 scalable storage structures. For example, the number of registers
@@
 in~\cite{deng_isscc07}, which reports the ratio in terms of FO4
-between a standard 32~nm CMOS technology and a carbon nanotube ones, 
-rough delay estimation can be obtained. In particular in such work 
+between a standard 32~nm CMOS technology and a carbon nanotube one, 
+a rough delay estimation can be calculated. In particular in such work 
 has been reported a ratio of:  
@@
 
-Regarding the power consumption of whole \disr{} devices, 
-we avoided an accurate power analysis with the switch activity
-annotation due to the fact that \disr{} circuitry will be active 
-only once during system startup. Indeed, after the setup phase, 
+With regard to the power consumption of the whole set of \disr{} devices: 
+due to the fact that \disr{} circuitry will be active 
+only once during system startup, an accurate power analisys related to switching 
+activity is not provided in this work. After the setup phase, 
 when all segments are mapped, the \disr{} block will stop its activity 
@@
 algorithm. For this reason the dynamic power falls to zero and
-the only consumption could be due to the leakage
-consumption. Finally, with the reported results, a comparison between 
-RPF configuration circuits and the proposed circuits could be performed.
-In particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{patwardhan_nanoarch06}.
-As reported in this work,  the implemented hardware requires an overhead of about 1692 CNFET for a $100 \times 100$ network.
-Furthermore, regarding the power consumption, the RPF approach has a setup phase beyond which, the consumptions tends to zero.
-Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.
+the only consumption is due to leakage effects. A comparison between 
+the proposed circuitry and the state of the art implementation for the RPF 
+algorithm, presented in~\cite{patwardhan_nanoarch06}, can show that there 
+is not an appreciable discrepancy in terms of transistors cost and power 
+consumption. In facts, RPF requires an overhead of about 1692 CNFET for a 
+$100 \times 100$ network. Furthermore, regarding the power consumption, 
+also the RPF approach has a setup phase beyond which, the consumption tends 
+to zero.

### 2014-09-09 trunk/PAPER/introduction.tex
Made changes to meet reviewers' comments
Another commit to remove typos and errors

@@
 related to the use of complementary DNA tags in order to place circuit
-components. Traditional CMOS process introduces complexity 
-with larger photolithography mask: more complex (larger) circuits
-will only require larger masks. Conversely, self-assembly achieves
-complexity by increasing the number of unique DNA tags, since more
+components. The traditional CMOS process introduces complexity 
+with larger photolithography masks: more complex (larger) circuits
+will only require larger masks. Conversely, a self-assembly process achieves
+complexity by increasing the number of unique DNA tags, since having more
 different tags means having more control on component placement. Ideally, by specifying a single
 and unique tag for each nano device terminal, we could exactly
-choose where each component would be placed in the design. But the number of DNA
+choose where each component would be placed in the design, but the number of DNA
 symbols forming the DNA sequence is limited (sequence of 4 nucleobases
@@
 of incorrect/partial matching. To avoid this problem 
-the number of unique tags must be limited, thus limiting the
+the number of unique tags must be limited, this limits also the
 complexity available at each node.
-In particular, in this work a budget of about $10,000$ CNFETs per node
-has been assumed , as estimated in~\cite{liu_jetcs}.
+In this work a budget of about $10,000$ CNFETs per node
+has been assumed, as estimated in~\cite{liu_jetcs}.
 \emph{Large scale randomness} is the other fundamental condition of
-self-assembled technology: DNA tags allow a control placement inside
-node grid, but there is no control of where each of these  grids will
-be placed on the whole network. As a consequence, other typical
+self-assembled technology: DNA tags allow control placement inside the
+node grid, but there is no control over the placement of these grids
+in the whole network. As a consequence, other typical
 properties of regular networks cannot be guaranteed, e.g. being
@@
 Finally, \emph{defect rates}: while they are very hardly tolerated in mask
-based top down design, the same nature of a bottom up self-assembly
+based top-down design, the same nature of a bottom-up self-assembly
  process cannot assume such a deterministic device placement
-process, thus defect tolerance is something like a design requirement
-more than an exception to be avoided.
+process, thus defect tolerance is more a design requirement
+than an exception to be avoided.
 
@@
 data packets, such networks must be able to guarantee deadlock freedom without any
-prior assumption on topology.
+prior assumption about the topology.
 
@@
 without requiring any topology graph, external defect map or
-centralized algorithm execution.  So the \disr{} approach is not
+centralized algorithm execution.  The \disr{} approach is not
 intended to discover the ``optimal'' segment choice (ideally reachable
@@
 sized networks. It is important to underline that, although we can
-assume an architecture similar to the one depicted in
-Figure~\ref{fig:nana} as background, the \disr{} topology discovery
+assume as background an architecture similar to the one depicted in
+Figure~\ref{fig:nana}, the \disr{} topology discovery
 approach presented this work is more general and not strictly
@@
 Section~\ref{sec:disr_concepts} are described the main elements and
-the execution model of the proposed approach. In Section~\ref{sec:simulation},
+the execution model of the proposed approach. Further details about node behavior
+in relation to the execution model are provided in Section~\ref{sec:execution_model}. 
+In Section~\ref{sec:simulation},
 simulations are carried out with the open-source tool Nanoxim to
@@
 can traverse a given link in both up and down directions.
-The hierarchical nature of this approach can lead to uneven traffic
+The hierarchical nature of this approach can lead to an uneven traffic
 distribution, with many packets traversing upper links (near to the
@@
 The \disr{} approach presented in this work is a first attempt to
-achieve the same goals of a segment based turn prohibition without
-requiring neither the knowledge of a topology graph nor centralized execution. In particular
+achieve the same goals of a segment based turn prohibition
+requiring neither the knowledge of a topology graph nor centralized execution. In particular,
 \disr{} implements segment discovery and turn prohibition using a
@@
 \item At the end of the execution, no segment list is created or
-stored anywhere: each node is only aware of belonging to a segment,
+stored anywhere: each node is only aware of being part of a segment,
 ignoring the presence of other nodes in the same segment and also the

### 2014-09-09 trunk/PAPER/paper.tex
Another commit to remove typos and errors

@@
 network-on-chip. The main aim is achieving the already-proven
-properties of segment-based deadlock freedom without neither requiring
+properties of segment-based deadlock freedom with neither requiring
 a topology graph as input, nor needing a centralized algorithm to
@@
 coverage of the network without requiring any centralized approach
-that would request a graph topology as input. A draft hardware
+that would request the graph topology as input. A draft hardware
 implementation has been presented to evaluate the impact on the limited

### 2014-09-09 trunk/PAPER/simulation.tex
Another commit to remove typos and errors

@@
 comparison against the SR segment-based approach is not addressed
-here, since how described in Section~\ref{sec:introduction} our
-scenario assumes the non-feasibility of a centralized approach:
-however, all the properties of the centralized approach should be
+here since, how described in Section~\ref{sec:introduction}, our
+scenario assumes the non-feasibility of a centralized approach. 
+However, all the properties of the centralized approach should be
 considered as preserved for all the nodes reached by the distributed
-segment coverage of \disr{}. Thus, the main points that remain to be
-addressed are:
+segment coverage of \disr{}. 
+The main points that remain to be addressed are:
 \begin{itemize}
-\item how \disr{} compares against state-of-art of tree based approach
-applied to equivalent scenario
-\item how \disr{} scales on large networks
-\item the real feasibility of the required hardware on the limited
+\item how \disr{} compares against the state-of-art tree based approach
+applied to an equivalent scenario
+\item how \disr{} scales with large networks
+\item the feasibility of actual implementation of the required hardware on the limited
 node size assumed
@@
 \subsection{Experimental setup}
-The following parameters have been taken into account when
+The following parameters have been taken into account while
 performing the \disr{} simulation:
@@
 %Same range as defective links parameter.
-\item {\emph{Bootstrap node}}: the node from upper layer that
+\item {\emph{Bootstrap node}}: the node, from upper layer, that
 injects the \disr{} process. When not explicitly investigating the
 impact of each single bootstrap choice, a set representative regions have been
-considered, e.g. the central part of the network and the edge corners.
+considered, e.g. the central part of the network and the corners.
 \end{itemize}
@@
 shows node coverage for \disr{} and Reverse Path Forwarding (RPF) tree
-based approach (as adapted in \cite{patwardhan_nanoarch06}) respectively. While the first aim of \disr{} is not to
-reach the optimal coverage, we still can observe a quite good
-performance as compared to the tree based approach. For low defect
+based approach (as adapted in \cite{patwardhan_nanoarch06}) respectively. 
+While the first aim of \disr{} is not to
+reach the optimal coverage, we still can observe quite good
+performances as compared to the tree based approach. For low defect
 rates, i.e. below 10\%, both approaches reach near ideal coverage for
 each of the tested network sizes. Higher defect rates seems to show
-more variance for \disr{}. For example at the high 20\% rate \disr{}
-ranges from 60\% to 75\% while RPF remains stable at 75\%. However we
+more variance for \disr{}. For examplei, at the high 20\% rate \disr{}
+ranges from 60\% to 75\% while RPF remains stable at 75\%. However, we
 can consider this coverage sensibility at higher defect rates as still acceptable
@@
 regions of nodes that \disr{} currently cannot handle. This threshold can be
-intuitively related to the fact that in the topologies simulated a
+intuitively related to the fact that, in the topologies simulated, a
 node has (on average) a cardinality of 4 connections to other nodes. This means
@@
 paths as not-working, and this applies (on average) for each node,
-thus leading to increased probability of consecutive disconnected
+leading to higher probability of consecutive disconnected
 nodes, which eventually create disconnected regions. For example Figure~\ref{fig:net} shows a 30x30 network with a 25\%
@@
 interesting to observe is how \disr{} latency scales with network
-size. For example, going from 900 to 2500 nodes, at the medium defect
-rate of $0.15$, leads to an increase from 3000 to 4500 cycles. It
+size. For example, moving from 900 to 2500 nodes, at an average defect
+rate of $0.15$, leads to an increase of latency from 3000 to 4500 cycles. It
 should be noticed also how for \disr{} latency is increasing until the
@@
 described in the previous section. This initial behavior is not reported in
-the RPF based approach, leading to higher latency values and not using
-the same retry/cancel approach as \disr{}.
+the RPF based approach, which does not use
+the same retry/cancel approach as \disr{} and then suffers higher latency values.
 
@@
 bootstrap node, without having to care about the role assumed in the
-future by the chosen root node. In other words, after the segments have
+future by the chosen root node. In other words, after that the segments have
 been established, the bootstrap node is like every other node, i.e. it
@@
 results, have been fixed to some reasonable default values (see below) and are not subject to
-further investigation in this paper; once again the focus here is not the
+further investigations in this paper; once again the focus here is not the
 optimal setup of segments, but just demonstrating a working approach. 
@@
 decreased in the request packet, so that requests that have been
-denied too much times can desist, even if free links are
+denied too much times are canceled, even if free links are
 available. This is not only an optimization to shorten
@@
 should wait before assuming that a livelock in the starting segment
-process has occurred. In the worst case, we can imagine that longest
-path required is the one returning to the bootstrap node after having
+process has occurred. In the worst case, we can imagine that the longest
+path required is the one returning to bootstrap node after having
 traveled across all the links. So, although this is just an extreme
@@
 affected by similar issues since these nodes start with a lower number of links,
-e.g. corner nodes could only have two connected direction, so even a single
-defective link could prevent a starting segment packet from coming back to the
+e.g. corner nodes could only have two connected directions, so even a single
+defective link could prevent a \texttt{STARTING\_SEGMENT} packet from coming back to the
 bootstrap node to close the loop and create the first segment.

### 2014-09-09 PAPER/disr.tex
Another commit to remove typos and errors

@@
 \label{sec:disr_concepts}
-The main concept behind the kind of turn prohibition we want to
-achieve is the \emph{segment}. A segment $S_b$ is basically a path of consecutive
+The main concept behind the turn prohibition method we propose in this work
+is the \emph{segment}. A segment $S_b$ is basically a path of consecutive
 nodes and links, starting with a link attached to a node belonging to
@@
 with a link connected to the node $9$, traversing nodes
-$4$, $3$, $2$ and ending with the link connected to the node $1$. Other
+$4$, $3$, $2$ and ending with the link connected to node $1$. Other
 segments depicted are, for example, $9.2$ (link from $9$, node $10$, link to node $3$) and $9.3$
 (link from $9$, node $8$, link, node $7$, link, node $6$, link, node $5$, link to node $1$). Note
-also that start/ending links can coincide and a segment can also be
+also that starting/ending links can coincide and a segment can also be
 formed by one single link (e.g. the case of $7.2$ and $5.4$).
@@
 segments. 
-\item Resulting segment confirmation/cancel packets are processed.
+\item Processing of resulting segment confirmation/cancel packets.
 \item Turn prohibition in each confirmed segment.
@@
 the feasibility and scalability of \disr{} in the particular scenario
-assumed; for this reason we will not investigate the further degree of
+assumed; for this reason we will not investigate the degree of
 freedom that the last of the above steps introduces, i.e. choosing
-\emph{where} actually placing the restriction in the context of the
+\emph{where} to place the restriction in the context of a
 segment. This choice would strictly depend on the particular routing
 strategy that will be used and could result in some interesting
-improvements. However, the scope of this work is understanding how \disr{} can
+improvements. The scope of this work is understanding how \disr{} can
 implement a distributed topology discovery, mapping defects and
 creating a segment partitioning that will be exploited in a second
-design phase which includes choosing and implementing a routing strategy. For this
-reason, the last two phases will be addressed as one, since we can
-safely assume that a random turn (e.g. the first) will be prohibited
-once each segment has been confirmed.
+design phase which includes choosing and implementing a routing strategy. 
+For this reason, since we can safely assume that a random turn (e.g. 
+the first) can be prohibited once each segment has been confirmed, the 
+last two execution phases will be addressed as one.
 
@@
 been started and not yet cancelled or confirmed. 
-\item{\emph{Candidate}}: a node currently candidate to be part of a segment, but not being itself the node from which the searching process was started. 
-\item{\emph{CandidateStarting}}: same as above, but the node is currently being considered as candidate
-for starting segment. 
+\item{\emph{Candidate}}: a node currently candidate to be part of a segment, but not 
+being itself the node from which the searching process was started. 
+\item{\emph{CandidateStarting}}: same as above, but with the node considered as candidate
+for starting a segment. 
 \item{\emph{Assigned}}: a node for which the segment has been determined.
@@
 
-The \emph{LED} are a kind of instant snapshot of the execution of \disr{} algorithm, taken in each node,
+\emph{LED} variables are a kind of instant snapshot of the execution of \disr{} algorithm
 consisting in the following variables:
@@
 being considered as candidate for a segment, and the \emph{segID} value
-specifies the segment id for which the node is candidate. 
+specifies the segment ID for which the node is candidate. 
 \item{\emph{link\_visited[]}}: an array
-of values representing information about attached links, that is, the
-segID of the segment owning each link. When \texttt{NULL}, the corresponding link has not yet been
+of values containing information about attached links (\emph{segID} of the segment 
+owning each link). When \texttt{NULL}, the corresponding link has not yet been
 assigned.
 \item{\emph{link\_tvisited[]}}: an array of
-values representing information about attached links, that is, the \emph{segID} of
-the segment for which the link is candidate. When \texttt{NULL}, the link is
+values representing information about attached links (\emph{segID} of
+the segment for which the link is candidate). When \texttt{NULL}, the link is
 not candidate for any segment, i.e. it has already been assigned or it is free.
@@
 
-As regards the \emph{packet\_type} field, we can have the following control packets types:
+With regard to the \emph{packet\_type} field, we can have the following control packets types:
 \begin{itemize}
@@
 A quantitative analysis of the resources needed to implement and
-manage these structures is presented in Section~\ref{sec:implementation} where is discussed 
+manage these structures is presented in Section~\ref{sec:implementation} where it is discussed 
 the impact of \disr{} control logic and storage on the
@@
 
-The \disr{} control packets described in the previous subsection trigger
+\disr{} control packets described in the previous subsection trigger
 node events, which change \emph{DBS} according to the
@@
 upper layer via \emph{(a)}. When starting, this bootstrap node 
-changes its status to \emph{CandidateStarting} \emph{(b)}, injecting a
+changes its status to \emph{CandidateStarting} \emph{(b)}, and injects a
 \texttt{STARTING\_SEGMENT\_REQUEST} across one of its free links
@@
 process in completed (Figure~\ref{fig:disr_events}-f).
-Note also that nodes previously set as \emph{CandidateStarting}, when receive
+Note also that nodes previously set to \emph{CandidateStarting}, when receive
 a \texttt{SEGMENT\_REQUEST} can simply cancel their
-status and set themselves as \emph{Candidate} for that request, since this new
+status and set themselves to \emph{Candidate} for that request, since this new
 request means that the first starting segment has already been found \emph{(h)}.
@@
 \emph{Assigned} (since it could confirm other segments). Each node
-previously set as \emph{Candidate} for that segment id, when receives
+previously set to \emph{Candidate} for that segment id, when receives
 a confirmation packet changes its status to \emph{Assigned} \emph{(m)}
-and send back the same confirmation until it reaches the initiator of
-the request, which then changes from \emph{ActiveSearching} to
+and send back the same confirmation. When this confirmation reaches the initiator of
+the request it changes its status from \emph{ActiveSearching} to
 \emph{Assigned} \emph{(d)}.
@@
 matches one of two the following conditions: the node is \emph{Free} but has no
-more suitable free links (thus can’t forward the
+more suitable free links (thus cannot forward the
 \texttt{SEGMENT\_REQUEST})\emph{(f)}; the node
@@
 
-In this Section we provide further details about \disr{}
+In this Section, we provide further details about \disr{}
 execution model, describing the internal behavior implemented in
@@
 
-The \emph{LED} variables in each node
-(\emph{segID}, \emph{visited}, \emph{tvisited}, \emph{link\_visited[]}, \emph{link\_tvisited[]})
-are initially set as \texttt{NULL}, so the node and all its links
+The \emph{LED} variables 
+(\emph{segID}, \emph{visited}, \emph{tvisited}, \emph{link\_visited[]}, \emph{link\_tvisited[]}),
+stored in each node, are initially set to \texttt{NULL}, so the node and all its links
 are considered as \emph{Free}.
@@
 in the \emph{Bootstrap} status. All the subsequent events happening at
-each node are the consequence of its current dynamic status (DBS), the
-packets received and the internal status represented by the
-\emph{LED}. Note that in the following, when using expression like
+each node are consequence of its current dynamic status (DBS), 
+packets received and internal status (represented by the
+\emph{LED}). Note that in the following, when using expression like
 ``has a free link'' or ``free node'' we will assume the relationship between 
-\emph{LED} and \emph{DBS} discussed in Section~\ref{ssec:disr_data}. Further, for
+\emph{LED} and \emph{DBS} discussed in Section~\ref{ssec:disr_data}. Furthermore, for
 each packet type all the cases not explicitly listed can simply be
-ignored since are associated to invalid/inconsistent events of the
-\disr{} execution model. A complete list of these cases can be checked
-in the environment simulator source code at~\cite{nanoxim}.
+ignored since associated to invalid/inconsistent events of the
+\disr{} execution model. A complete list of these cases is 
+described in the simulator source code available at~\cite{nanoxim}.
 
@@
 \begin{itemize}
-\item The node is \emph{Free}: it should set itself as
+\item The node is \emph{Free}: it should set itself to
 \emph{CandidateStarting} and forward the packet along its free links, using
@@
 When the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
-the packet: the node set itself as \emph{Assigned} to the segment \emph{segID}. Further, it should forward this packet to the link where the
+the packet, the node set itself to \emph{Assigned} to the segment \emph{segID}. 
+Further, it should forward this packet to the link where the
 original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
@@
 When a node receives a \texttt{SEGMENT\_CANCEL} packet it means that the research
-for a segment along that path was unsuccessful. But if the
+for a segment along that path was unsuccessful. If the
 node still has some other free link to try, it should forward a
-\texttt{SEGMENT\_REQUEST} to the those links. So a node forwards back
+\texttt{SEGMENT\_REQUEST} to the those links. A node forwards back
 the \texttt{SEGMENT\_CANCEL} packet along the link that originated the
@@
 injecting a \texttt{SEGMENT\_REQUEST}. However, different choices
-could have been made when defining \disr{}, strictly related to which
+could have been made when defining \disr{}, these choices are strictly related to which
 kind and level of parallelism should be supported. The approach adopted
@@
 example: a node with free links could start several segment requests
-associated to the same \emph{segID}, one for each free link. But
+associated to the same \emph{segID}, one for each free link, but
 serializing this operation, by investigating the free links in order,

### 2014-09-09 PAPER/implementation.tex
Fixed bio for each author and some other typos

@@
 described in this section. Figure~\ref{fig:node_structure} depicts the general
-structure of a node in the particular scenario of DNA nano Network-On-Chip. In particular such a node
-is composed by the following fundamental elements:
+structure of a node in the particular scenario of DNA nano Network-On-Chip. In particular, such a node
+is composed of the following fundamental elements:
 
@@
 
-To give a basic estimate of the overhead needed we focus on \disr{}-
+To give a basic estimate of the overhead needed, we focus on \disr{}-
 specific components namely the control logic and configuration
 registers needed to implement \disr{}. Figure~\ref{fig:implementation}
-shows an architecture sketch, which mainly consist in the
+shows an architecture sketch, which mainly consists in the
 following building elements:
@@
 	driven by the controller, will select information incoming from an internal 
-    node such as the \emph{source\_ID}. In this situation the 
-	TTL field should be reset to its initial value and the \emph{segment\_ID}
-	is composed by the node ID and by the output port identification 
+    node such as the \emph{src\_id}. In this situation the 
+	TTL field should be reset to its initial value and the \emph{segID}
+	is composed of the node ID and by the output port identification 
 	number.
@@
 
-Regarding the power consumption of whole \disr{} devices, 
-we avoided an accurate power analysis with the switch activity
-annotation due to the fact that \disr{} circuitry will be active 
-only once during system startup. Indeed, after the setup phase, 
+With regard to the power consumption of the whole set of \disr{} devices: 
+due to the fact that \disr{} circuitry will be active 
+only once during system startup, an accurate power analysis related to switching 
+activity is not provided in this work. After the setup phase, 
 when all segments are mapped, the \disr{} block will stop its activity 
@@
 algorithm. For this reason the dynamic power falls to zero and
-the only consumption could be due to the leakage
-consumption. Finally, with the reported results, a coparison between 
-RPF configuration circuits and the proposed circuits could be performed.
-In particular, the state of the art implementation for the RPF algorithm has been shown in~\cite{patwardhan_nanoarch06}.
-As reported in this work,  the implemented hardware requires an overhead of about 1692 CNFET for a $100 \times 100$ network.
-Furthemore, regarding the power consumption, the RPF approach has a setup phase beyond which, the consumptions tends to zero.
-Starting from these results, an appreciable discrepancy in terms of transistors cost and power consumption can not be noted.
+the only consumption is due to leakage effects. A comparison between 
+the proposed circuitry and the state of the art implementation for the RPF 
+algorithm, presented in~\cite{patwardhan_nanoarch06}, can show that there 
+is not an appreciable discrepancy in terms of transistors cost and power 
+consumption. In facts, RPF requires an overhead of about 1692 CNFET for a 
+$100 \times 100$ network. Furthermore, regarding the power consumption, 
+also the RPF approach has a setup phase beyond which, the consumption tends 
+to zero.

### 2014-09-09 PAPER/introduction.tex
Fixed bio for each author and some other typos

@@
 \section{Introduction and Motivation}
+\label{sec:introduction}
 
@@
 While software parallelism and multicore
-approaches~\cite{horowitz2004} and \cite{powell2009} are partially mitigating the impact of such
-constraints on performances, it is likely that the growing computing demand will
-eventually need even more radical architectural modifications and new
-paradigms in order to address the Computer Design challenges of the next
+approaches~\cite{horowitz2004,powell2009} are partially mitigating the impact of such
+constraints on performances, it is likely that a growing computing demand will
+eventually need even more radical architectural modifications and 
+paradigms to address the Computer Design challenges of the next
 decades.
 
-In the last years, self-assembled nanoscale architectures~\cite{yan2003}
-emerged as a promising technology due their tera/peta scale of
-integration, defect tolerance and huge potential computing
-capabilities. These technologies are certainly still at
-their early stage of development, however different laboratory demos and
-prof-of-concepts architectures have been presented~\cite{patwardhan2004, patwardhan2006_1, pistol2009}.
+In the last years, self-assembled nanoscale
+architectures~\cite{yan2003} emerged as a promising technology due
+their tera/peta scale of integration, defect tolerance and huge
+potential computing capabilities. These technologies are certainly
+still at their early stage of development, however different
+laboratory demos and proof-of-concepts have been
+presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1,
+pistol2009}. For a complete survey on self-assembled architectures and
+how they compare against classical many-core systems in terms of
+ technologies, fault tolerance, performance and software tools see
+ also~\cite{Future}.
 %, patwardhan2006
-The main idea behind this approach is exploiting the physical regularity and
-stability of DNA structures in order to create a scaffold onto which
-nano-devices (e.g. nanowires and CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be
-attached. This can be achieved by designing appropriate complementary DNA tags for
+The main idea behind this approach is exploiting the physical
+regularity and stability of DNA structures in order to create a
+scaffold onto which nano-devices (e.g. nanowires and
+CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be attached. This
+can be achieved by designing appropriate complementary DNA tags for
 each terminal to be placed, so that a nano device will be attached
 only where its own DNA tag matches a complementary tag on the DNA grid
-scaffold (see Figure~\ref{fig:nana}-a).
-A detailed description of the chemical properties involved is far
-beyond the scope of this paper (see also~\cite{braun1998, seeman1999}), so we will focus on
-the three main challenges that this new fabrication process introduces
-in Computer Design: \emph{(i) limited node complexity}, \emph{(ii) large scale
+scaffold (see Figure~\ref{fig:nana}-a).  Of course, a detailed
+description of the chemical properties involved is far beyond the
+scope of this paper (see also~\cite{braun1998, seeman1999}).
+
+In this work, we present \disr{} (Distributed Segment Routing), a distributed
+approach focused on addressing the three main challenges that this new fabrication process introduces
+in nanoscale Network-on-Chip Design: \emph{(i) limited node complexity}, \emph{(ii) large scale
 randomness} and \emph{(iii) high defect rates}.  
-
 The \emph{limited node complexity} aspect is directly
 related to the use of complementary DNA tags in order to place circuit
-components. In a traditional CMOS process the complexity is introduced
-using a photolithography mask, so that larger (more complex) circuits
-only require larger masks; conversely, self-assembly achieves
-complexity by increasing the number of unique DNA tags, since more
+components. The traditional CMOS process introduces complexity 
+with larger photolithography masks: more complex (larger) circuits
+will only require larger masks. Conversely, a self-assembly process achieves
+complexity by increasing the number of unique DNA tags, since having more
 different tags means having more control on component placement. Ideally, by specifying a single
-and unique tag for each nano transistor terminal, we could exactly
-choose where each component would be placed. But the number of DNA
+and unique tag for each nano device terminal, we could exactly
+choose where each component would be placed in the design, but the number of DNA
 symbols forming the DNA sequence is limited (sequence of 4 nucleobases
-G,A,T,C) and so creating many different tags (of a given length) would
+G,A,T,C) and so creating many different tags (of a prefixed length) would
 mean make them more similar to each other, increasing the probability
-of incorrect/partial matching. To avoid this problem we should limit
-the number of unique tags, thus limiting the complexity at each node.
-In particular, a budget of about $10,000$ CNFETs per node has been
-estimated in~\cite{liu_jetcs}.
-
+of incorrect/partial matching. To avoid this problem 
+the number of unique tags must be limited, this limits also the
+complexity available at each node.
+In this work a budget of about $10,000$ CNFETs per node
+has been assumed, as estimated in~\cite{liu_jetcs}.
 \emph{Large scale randomness} is the other fundamental condition of
-self-assembled technology: DNA tags allow a control placement inside
-node grid, but there is no control of where each of these  grids will
-be placed on the whole network. As a consequence, other typical
+self-assembled technology: DNA tags allow control placement inside the
+node grid, but there is no control over the placement of these grids
+in the whole network. As a consequence, other typical
 properties of regular networks cannot be guaranteed, e.g. being
@@
 orientation and so on.
-
 Finally, \emph{defect rates}: while they are very hardly tolerated in mask
-based top down design, the same nature of a bottom up self-assembly
+based top-down design, the same nature of a bottom-up self-assembly
  process cannot assume such a deterministic device placement
-process, thus defect tolerance is something like a design requirement
-more than an exception to be avoided.
+process, thus defect tolerance is more a design requirement
+than an exception to be avoided.
 
@@
 \begin{tabular}{cc}
-    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps} &
-    \includegraphics[width=0.40\textwidth]{pictures/dna1_complex2.eps} \\
+    \includegraphics[width=0.45\textwidth]{pictures/dna2b.eps} &
+    \includegraphics[width=0.45\textwidth]{pictures/dna1_complex2.eps} \\
  (a) & (b)
  \end{tabular}
-  \caption{(a) DNA tag matching and (b) resulting irregular topology}
+  \caption{(a) Strands of complementary DNA tags self assemble to
+  generate larger structures (b) The resulting irregular topology of
+  processing(P) and storage(M) elements }
   \label{fig:nana}
@@
 implications to be addressed when approaching to the design of
-a computer architecture: computational model should be based on a
+a nanoscale Network-on-Chip architecture: computational model should be based on a
 distributed network of small processing and storage nodes, randomly
@@
 operands are moved around the network in order to be processed.
-Independently of the particular policy chosen to route packets,
-such networks must be able to guarantee deadlock freedom without any
-prior assumption on topology.
+In addition, independently of the particular policy chosen to route instruction and
+data packets, such networks must be able to guarantee deadlock freedom without any
+prior assumption about the topology.
 
-In this work, we introduce \disr{}, a Distributed Segment-based approach
-to deadlock freedom in large scale DNA self-assembled networks. Our
-contribution aims to achieve the classical properties of a
-segment-based approach~\cite{mejia_ipdps06} without requiring any
-topology graph, external defect map or centralized algorithm
-execution.  So the \disr{} approach is not intended to discover the
-``optimal'' segment choice (ideally reachable with the knowledge of
-the topology graph) but just to demonstrate a concrete model that can
-fit into such complex, irregular and large sized networks.
-It is important to
-underline that, although we can assume an architecture similar to the
-one depicted in Figure~\ref{fig:nana} as background, the topology discovery
-problem faced in this work is more general and not strictly dependent on any of the
-underlying computing architectures.
+In this work, we introduce \disr{}, a Distributed Segment-based
+approach to topology discovery and deadlock freedom in large scale DNA
+self-assembled on chip networks. Our contribution aims to achieve the
+classical properties of a segment-based approach~\cite{mejia_ipdps06}
+without requiring any topology graph, external defect map or
+centralized algorithm execution.  The \disr{} approach is not
+intended to discover the ``optimal'' segment choice (ideally reachable
+with the knowledge of the topology graph) but just to demonstrate a
+concrete model that can fit into such complex, irregular and large
+sized networks. It is important to underline that, although we can
+assume as background an architecture similar to the one depicted in
+Figure~\ref{fig:nana}, the \disr{} topology discovery
+approach presented this work is more general and not strictly
+dependent on any underlying computational model adopted.
 
 The paper is organized as follows: in Section~\ref{sec:related_works}
-we summarize the main approaches for topology agnostic routing. Next, in
+we summarize the main approaches for topology agnostic deadlock
+freedom. Next, in
 Section~\ref{sec:disr_concepts} are described the main elements and
-the execution model of the proposed approach. In Section~\ref{sec:simulation},
+the execution model of the proposed approach. Further details about node behavior
+in relation to the execution model are provided in Section~\ref{sec:execution_model}. 
+In Section~\ref{sec:simulation},
 simulations are carried out with the open-source tool Nanoxim to
@@
 The \disr{} approach presented in this work is a first attempt to
-achieve the same goals of a segment based turn prohibition without
-requiring neither the knowledge of a topology graph nor centralized execution. In particular
+achieve the same goals of a segment based turn prohibition
+requiring neither the knowledge of a topology graph nor centralized execution. In particular,
 \disr{} implements segment discovery and turn prohibition using a
 completely different mechanism, based on a distributed exchange of
-small setup packets requiring on average $15\%$ of the available
+small setup packets requiring a limited and scalable portion of the available
 resource budget. The following main features distinguish \disr{}

### 2014-09-09 PAPER/paper.tex
fixes
Added soul package to hilight text with \hl command
general fixing
English fixes
Removed some typos
Fixed bio for each author and some other typos

@@
 %------------------------------------------------------------------------------
-\documentclass[review]{elsarticle}
-%\documentclass[3p]{elsarticle}
+\documentclass[preprint]{elsarticle}
 \usepackage{lineno,hyperref}
@@
 %------------------------------------------------------------------------------
+\vspace{10 mm}
+
+Vincenzo Catania received the Laurea degree in Electrical Engineering
+from the University of Catania, Italy, in 1982. Until 1984, he was
+responsible for testing microprocessor system at STMicroelectronics,
+Catania. He is a full professor of computer
+science. His research interests include performance and reliability
+assessment in parallel and distributed system, VLSI design, low power
+design, and fuzzy logic.
+
+Andrea Mineo received the BSc and MSc degrees in Electronic
+Engineering from the University of Catania, Italy, in 2010 and 2013,
+respectively, and is currently pursuing the PhD degree in Systems,
+Energy, Computer and Telecommunications Engineering at the University
+of Catania. His current research interests are VLSI systems,
+Network-on-Chip architectures and emerging interconnect technologies
+for on-chip networks.
+
+Salvatore Monteleone is a post-doctoral research assistant at the
+Department of Electrical, Electronic and Computer Engineering -
+University of Catania, Italy. He obtained the BSc (2007) and MSc
+(2010) in Computer Engineering at University of Catania where he also
+completed the PhD course in Communications and Computer Engineering
+(2014). His interests comprehend cooperative systems, user-centric
+systems and Network-on-Chip architectures.
+
+Davide Patti received the Laurea and PhD degrees in computer
+engineering from the University of Catania, Italy, in 2003 and 2007,
+respectively. His research focuses on Design Space exploration of VLIW
+systems, Network-on-Chip architectures, DNA self-assembled networks
+and Human-computer interfaces. He is currently a research assistant
+at University of Catania.
 

### 2014-09-10 trunk/PAPER/introduction.tex
Fixed bib

@@
 While software parallelism and multicore
-approaches~\cite{horowitz2004,powell2009} are partially mitigating the impact of such
+approaches~\cite{Kavi2012243,Sibai2011958} are partially mitigating the impact of such
+%approaches~\cite{horowitz2004,powell2009} are partially mitigating the impact of such
 constraints on performances, it is likely that a growing computing demand will
@@
 laboratory demos and proof-of-concepts have been
-presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1,
-pistol2009}. For a complete survey on self-assembled architectures and
+presented~\cite{patwardhan2006_1, pistol2009}. For a complete survey on self-assembled architectures and
+%presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1, pistol2009}. For a complete survey on self-assembled architectures and
 how they compare against classical many-core systems in terms of
@@
 scaffold onto which nano-devices (e.g. nanowires and
-CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be attached. This
+CNFETs~\cite{bachtold2001, cui2001}) can be attached. This
+%CNFETs~\cite{bachtold2001, tans1998, cui2001}) can be attached. This
 can be achieved by designing appropriate complementary DNA tags for
@@
 description of the chemical properties involved is far beyond the
-scope of this paper (see also~\cite{braun1998, seeman1999}).
+scope of this paper (see also~\cite{seeman1999}).
 
-In this work we present \disr{} (Distributed Segment Routing), a distributed
+In this work, we present \disr{} (Distributed Segment Routing), a distributed
 approach focused on addressing the three main challenges that this new fabrication process introduces
@@
 Several works addressed the problem of topology agnostic deadlock
-freedom introducing virtual channels~\cite{sancho2002, skeie2002,
-skeie2004, koibuchi2003}, but while they show interesting
+freedom introducing virtual channels~\cite{Abbas2014, skeie2004, koibuchi2003}, but while they show interesting
+%freedom introducing virtual channels~\cite{sancho2002, skeie2002, skeie2004, koibuchi2003}, but while they show interesting
 performances, the low resources available to prevent deadlocks makes them not suitable for
@@
 scenario.
-Other topology independent algorithms~\cite{schroeder1991,
-koibuchi2001, cherkasova1996} do not require any virtual channel but
+Other topology independent algorithms do not require any virtual channel but
 exploit the concept of ``turn prohibition''.
@@
 Other solutions try to approach the issue of irregular
-topologies by limiting the number~\cite{duato1997, gomez2004, koibuchi2008} or the
-location~\cite{zhang2008, flich2008, liu2011} of missing links. This
+%topologies by limiting the number~\cite{duato1997, gomez2004, koibuchi2008} or the
+topologies by limiting the number~\cite{ gomez2004, koibuchi2008} or the
+location~\cite{flich2008, liu2011} of missing links. This
 restriction is clearly unacceptable given the hight-defect rates of
@@
 avoid considering solutions based on hardware-redundancy to
-dynamically recover defects as in~\cite{constantinides2006, kohler2010,  park2006, ebrahimi2013}.
+%dynamically recover defects as in~\cite{constantinides2006, kohler2010,  park2006, ebrahimi2013}. 
+dynamically recover defects as in~\cite{ebrahimi2013}.
 

### 2014-09-10 trunk/PAPER/disr.tex
cancelled to canceled

@@
 
-This first work is explicitly focused on demostrating
+This first work is explicitly focused on demonstrating
 the feasibility and scalability of \disr{} in the particular scenario
-assumed; for this reason we will not investigate the further degree of
+assumed; for this reason we will not investigate the degree of
 freedom that the last of the above steps introduces, i.e. choosing
-\emph{where} actually placing the restriction in the context of the
-segment. This choice would striclty depend on the particular routing
+\emph{where} to place the restriction in the context of a
+segment. This choice would strictly depend on the particular routing
 strategy that will be used and could result in some interesting
-improvements. However, the scope of this work is understading how \disr{} can
+improvements. The scope of this work is understanding how \disr{} can
 implement a distributed topology discovery, mapping defects and
 creating a segment partitioning that will be exploited in a second
-design phase which includes choosing and implementing a routing strategy. For this
-reason, the last two phases will be addressed as one, since we can
-safely assume that a random turn (e.g. the first) will be phohibited
-once each segment has been confirmed.
+design phase which includes choosing and implementing a routing strategy. 
+For this reason, since we can safely assume that a random turn (e.g. 
+the first) can be prohibited once each segment has been confirmed, the 
+last two execution phases will be addressed as one.
 
@@
 \item{\emph{ActiveSearching}}: a node from which a new segments searching process has
-been started and not yet cancelled or confirmed. 
-\item{\emph{Candidate}}: a node currently candidate to be part of a segment, but not being itself the node from which the searching process was started. 
-\item{\emph{CandidateStarting}}: same as above, but the node is currently being considered as candidate
-for starting segment. 
+been started and not yet canceled or confirmed. 
+\item{\emph{Candidate}}: a node currently candidate to be part of a segment, but not 
+being itself the node from which the searching process was started. 
+\item{\emph{CandidateStarting}}: same as above, but with the node considered as candidate
+for starting a segment. 
 \item{\emph{Assigned}}: a node for which the segment has been determined.

### 2014-09-10 trunk/PAPER/simulation.tex
Fixed bio for each author and some other typos
cancelled to canceled

@@
 each of the tested network sizes. Higher defect rates seems to show
-more variance for \disr{}. For examplei, at the high 20\% rate \disr{}
+more variance for \disr{}. For example, at the high 20\% rate \disr{}
 ranges from 60\% to 75\% while RPF remains stable at 75\%. However, we
@@
 each node. While searching for a free link due to an incoming \texttt{SEGMENT\_REQUEST},
-the request itself is cancelled after a given number of tries. This
+the request itself is canceled after a given number of tries. This
 gives to the preceding node on the path the
@@
 Default value is set to 1, i.e. each link is tried one time.
-\item \emph{time to live (TTL)}: when a segment request is cancelled
+\item \emph{time to live (TTL)}: when a segment request is canceled
 along a certain path (using a \texttt{SEGMENT\_CANCEL}), a TTL field is

### 2014-09-11 PAPER/introduction.tex
Changes suggested by Andrew

@@
 
-Exploring long term alternatives to the CMOS technology is gaining
+Exploring long-term alternatives to the CMOS technology is gaining
 more and more relevance as the scaling trend of such devices keeps
@@
 While software parallelism and multicore
-approaches~\cite{horowitz2004,powell2009} are partially mitigating the impact of such
+approaches~\cite{Kavi2012243,Sibai2011958} are partially mitigating the impact of such
+%approaches~\cite{horowitz2004,powell2009} are partially mitigating the impact of such
 constraints on performances, it is likely that a growing computing demand will
 eventually need even more radical architectural modifications and 
-paradigms to address the Computer Design challenges of the next
+paradigm shifts to address the Computer Design challenges of the upcoming
 decades.
 
-In the last years, self-assembled nanoscale
+In recent years, self-assembled nanoscale
 architectures~\cite{yan2003} emerged as a promising technology due
@@
 potential computing capabilities. These technologies are certainly
-still at their early stage of development, however different
-laboratory demos and proof-of-concepts have been
-presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1,
-pistol2009}. For a complete survey on self-assembled architectures and
+still at their early stage of development; however, different
+laboratory demos and proofs-of-concept have been
+presented~\cite{patwardhan2006_1, pistol2009}. For a complete survey on self-assembled architectures and
+%presented~\cite{patwardhan2004, patwardhan2006, patwardhan2006_1, pistol2009}. For a complete survey on self-assembled architectures and
 how they compare against classical many-core systems in terms of
@@
 description of the chemical properties involved is far beyond the
-scope of this paper (see also~\cite{braun1998, seeman1999}).
+scope of this paper (see also~\cite{seeman1999}).
 
@@
 symbols forming the DNA sequence is limited (sequence of 4 nucleobases
-G,A,T,C) and so creating many different tags (of a prefixed length) would
-mean make them more similar to each other, increasing the probability
+G,A,T,C) and so creating many different tags (of a predetermined length) would
+mean making them more similar to each other, increasing the probability
 of incorrect/partial matching. To avoid this problem 
-the number of unique tags must be limited, this limits also the
+the number of unique tags must be limited, which limits also the
 complexity available at each node.
-In this work a budget of about $10,000$ CNFETs per node
+In this work, a budget of about $10,000$ CNFETs per node
 has been assumed, as estimated in~\cite{liu_jetcs}.
 \emph{Large scale randomness} is the other fundamental condition of
-self-assembled technology: DNA tags allow control placement inside the
+self-assembled technology: DNA tags allow controlled placement inside the
 node grid, but there is no control over the placement of these grids
@@
 orientation and so on.
-Finally, \emph{defect rates}: while they are very hardly tolerated in mask
-based top-down design, the same nature of a bottom-up self-assembly
+Finally, \emph{defect rates}: while they are hardly tolerated in 
+mask-based top-down design, the same nature of a bottom-up self-assembly
  process cannot assume such a deterministic device placement

### 2014-09-11 PAPER/paper.tex
Changes suggested by Andrew

@@
 \begin{abstract}
-In this paper we present \disr{}, a distributed approach to topology
+In this paper, we present \disr{}, a distributed approach to topology
 discovery and defect mapping in a self-assembled nano
-network-on-chip. The main aim is achieving the already-proven
-properties of segment-based deadlock freedom with neither requiring
-a topology graph as input, nor needing a centralized algorithm to
+network-on-chip. The main aim is to achieve the already-proven
+properties of segment-based deadlock freedom requiring neither 
+a topology graph as input, nor a centralized algorithm to
 configure network paths.  After introducing the conceptual elements
@@
 \section{Conclusions}
-In this work we presented \disr{}, an initial attempt of achieving a segment based
-topology discovery into distributed self-assembled nanoscale scenario. We
+In this work, we presented \disr{}, an initial attempt of achieving a segment based
+topology discovery in a distributed self-assembled nanoscale scenario. We
 demonstrated how \disr{} can accomplish the aim of finding a segment
@@
 implementation has been presented to evaluate the impact on the limited
-node size typical of the assumed scenario. From an high-level
-perspective future works will focus on
-investigating \disr{} resulting network in order to support the
-execution of massively parallel applications, while keeping into
-developing a detailed low level hardware implementation on
-DNA grid using the appropriate nano devices models.
+node size typical of the assumed scenario. From a high-level
+perspective, future works will focus on
+investigating \disr{} resulting networks in order to support the
+execution of massively parallel applications, while continuing to
+develop a detailed low level hardware implementation on a
+DNA grid using the appropriate nano device models.
 
